### 2019-04-05 abstract.tex
initial commit

\documentclass[11pt,a4paper]{article}

\usepackage{url}
\usepackage{hyperref}

\title{Neural dialogue act tagging with transformer pre-training (or something like that...)}

\author{
  First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\and
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\
}

\date{}

\begin{document}
\maketitle

\begin{abstract}
  abstract
\end{abstract}

\section{Introduction}
\begin{itemize}
  \item \cite{austinHowThingsWords2009} -- Speech acts
  \item \cite{coreCodingDialogsDAMSL1997} -- DAMSL dialogue act scheme
  \item \cite{devlinBERTPretrainingDeep2018} -- BERT
\end{itemize}

\section{Related Work}
\begin{itemize}
  \item \cite{cerisaraEffectsUsingWord2vec2018}
  \item \cite{kalchbrennerRecurrentConvolutionalNeural2013}
  \item \cite{pragstVectorRepresentationUtterances2018}
  \item \cite{sordoniNeuralNetworkApproach2015}
  \item \cite{stolckeDialogueActModeling2000} - HMM dialogue act tagging
\end{itemize}

\section{Model}

\section{Experiments}

\bibliography{abstract}{}
\bibliographystyle{apalike}

\end{document}

### 2019-04-05 abstract.tex
use acl_natbib
add two related works

@@
 
+\usepackage[margin=1in]{geometry}
 \usepackage{url}
 \usepackage{hyperref}
+\usepackage{natbib}
 
@@
   \item \cite{devlinBERTPretrainingDeep2018} -- BERT
+    Main questions:
+    1. Are pre-trained transformer encoding (BERT) helpful for representation in a dialogue task (speficially, dialogue act tagging)?
+    2. Are additional dialogue specific features helpful (discourse markers, disfuency, laughter)?
 \end{itemize}
@@
 \begin{itemize}
-  \item \cite{cerisaraEffectsUsingWord2vec2018}
+  \item \cite{cerisaraEffectsUsingWord2vec2017}
   \item \cite{kalchbrennerRecurrentConvolutionalNeural2013}
@@
   \item \cite{stolckeDialogueActModeling2000} - HMM dialogue act tagging
+  \item \cite{khanpourDialogueActClassification}
+  \item \cite{tranPreservingDistributionalInformation2017}
 \end{itemize}
@@
 \section{Model}
+\begin{itemize}
+  \item We use a simple RNN to pass encode discourse context between utterances and predict dialogue act labels.
+  \item At each time step, the 
+\end{itemize}
 
@@
 \bibliography{abstract}{}
-\bibliographystyle{apalike}
+\bibliographystyle{acl_natbib}
 

### 2019-04-05 abstract.tex
experiments
some experimens

@@
 \section{Model}
-\begin{itemize}
-  \item We use a simple RNN to pass encode discourse context between utterances and predict dialogue act labels.
-  \item At each time step, the 
-\end{itemize}
+The proposed model has two components: an utterance encoder, and a sequence model that predicts the dialogue act tag.
+For the sequence model, we use a simple RNN.
+Conceptually the hidden state of this RNN represents the discourse context which, 
+together with the encoded utterance, is used to predict the discourse act tag.
 
 \section{Experiments}
+Our aim is to test the effectiveness of different utterance encoding schemas. 
+\begin{enumerate}
+  \item Average word embedding (word2vec)
+  \item CNN (with/without word2vec initalization)
+  \item BERT encoded sentences (with/without additional unsupervised pretraining)
+  \item Average BERT word embeddings
+\end{enumerate}
 

### 2019-04-05 abstract.tex
experiments, disfluences refs

@@
 \begin{enumerate}
-  \item Average word embedding (word2vec)
-  \item CNN (with/without word2vec initalization)
+  \item Average word embedding (word2vec, FastText)
+  \item CNN (with/without word2vec initalization, with/without `freezing' the embeddings )
   \item BERT encoded sentences (with/without additional unsupervised pretraining)
-  \item Average BERT word embeddings
+  \item Average BERT word embeddings (?)
   \end{enumerate}
+
+  Pre-trained models benefit from learning on large amounts of online data, however it might be the case that for dialogue act tagging additional information only present in natural dialogue data will be useful.
+Therefore, we evaluate the impact of disfluencies and non-verbal signals, such as laughters on the performance of our models.
+For the datasets where no annotation for disfluencies is available, this information can be predicted from recognised speech \citep{hough2017joint,shalyminov2018multi}.
+
+  PoS tags
 

### 2019-04-05 abstract.tex
upd

@@
 Therefore, we evaluate the impact of disfluencies and non-verbal signals, such as laughters on the performance of our models.
-For the datasets where no annotation for disfluencies is available, this information can be predicted from recognised speech \citep{hough2017joint,shalyminov2018multi}.
+\textbf{(How?)} For the datasets where no annotation for disfluencies is available, this information can be predicted from recognised speech \citep{hough2017joint,shalyminov2018multi}.
 
-  PoS tags
+  Furthermore PoS tags
 

### 2019-04-05 abstract.tex
notes for related work

--- 2019-04-05 abstract.tex
@@
   \item \cite{coreCodingDialogsDAMSL1997} -- DAMSL dialogue act scheme
-  \item \cite{devlinBERTPretrainingDeep2018} -- BERT
-    Main questions:
+  \item Recent transformer models, such as BERT, adopt the strategy of pre-training a neural network
+    on large corpora of unlabeled data with a language modeling task, 
+    and then fine-tuning an output layer on labeled data
+    They achive state-of-the-art results in various NLP token- and sentence-level tasks,
+    including (...) \cite{devlinBERTPretrainingDeep2018}.
+    In this work, we investigate whether these pre-trained models can be adapted for dialogue tasks.
+    In particular, we have two questions:
     1. Are pre-trained transformer encoding (BERT) helpful for representation in a dialogue task (speficially, dialogue act tagging)?
@@
 \begin{itemize}
-  \item \cite{cerisaraEffectsUsingWord2vec2017}
-  \item \cite{kalchbrennerRecurrentConvolutionalNeural2013}
-  \item \cite{pragstVectorRepresentationUtterances2018}
-  \item \cite{sordoniNeuralNetworkApproach2015}
-  \item \cite{stolckeDialogueActModeling2000} - HMM dialogue act tagging
-  \item \cite{khanpourDialogueActClassification}
-  \item \cite{tranPreservingDistributionalInformation2017}
+  \item \cite{cerisaraEffectsUsingWord2vec2017} -- 
+    Use LSTM with and without word2vec initialization to encode discourse utterances and predict dialogue act tags.
+    No notion of discourse context.
+    Word2vec does not improve dialogue act recoginition, possibly becasue it does not capture lexical-semantic information relevant to dialogue.
+
+  \item \cite{khanpourDialogueActClassification} -- 
+    Uses RNN and stacked LSTM with word2vec embeddings 
+    to encode utterances.
+    No notion of discourse context.
+
+  \item \cite{pragstVectorRepresentationUtterances2018} --
+    Uses a skip thought approach to learn utterance representations by predicting context utterances.
+
+  \item \cite{kalchbrennerRecurrentConvolutionalNeural2013} --
+    Encode utterances (sentences) convolution-based composition of the sequence of words (HCNN). 
+    Use an RNN with agent-specific weights to produce utterance label predictions.
+    Also talk about the hidden layer of the RNN as representing discourse context.
+
+  \item \cite{tranPreservingDistributionalInformation2017} --
+    Propogates a distribution over dialogue acts instead of greedily choosing a lable at each step, 
+    a kind of discourse context.
+
+  \item \cite{stolckeDialogueActModeling2000} - 
+    HMM dialogue act tagging
+
+  %\item \cite{sordoniNeuralNetworkApproach2015} - generate utterances taking into account previous countext
 \end{itemize}

### 2019-04-05 abstract.tex

@@
 \begin{enumerate}
-  \item Average word embedding (word2vec)
-  \item CNN (with/without word2vec initalization)
+  \item Average word embedding (word2vec, FastText)
+  \item CNN (with/without word2vec initalization, with/without `freezing' the embeddings )
   \item BERT encoded sentences (with/without additional unsupervised pretraining)
-  \item Average BERT word embeddings
+  \item Average BERT word embeddings (?)
   \end{enumerate}
+
+  Pre-trained models benefit from learning on large amounts of online data, however it might be the case that for dialogue act tagging additional information only present in natural dialogue data will be useful.
+Therefore, we evaluate the impact of disfluencies and non-verbal signals, such as laughters on the performance of our models.
+\textbf{(How?)} For the datasets where no annotation for disfluencies is available, this information can be predicted from recognised speech \citep{hough2017joint,shalyminov2018multi}.
+
+  Furthermore PoS tags
 

### 2019-04-05 abstract.tex
experiments

--- 2019-04-05 abstract.tex
@@
 Therefore, we evaluate the impact of disfluencies and non-verbal signals, such as laughters on the performance of our models.
-\textbf{(How?)} For the datasets where no annotation for disfluencies is available, this information can be predicted from recognised speech \citep{hough2017joint,shalyminov2018multi}.
+\textbf{(How?)} For the datasets where no annotation for disfluencies is available, it can be predicted from recognised speech \citep{hough2017joint,shalyminov2018multi}.
 

### 2019-04-06 abstract.tex
work on intro/related work

--- 2019-04-05 abstract.tex
@@
-\documentclass[11pt,a4paper]{article}
+\documentclass[11pt,a4paper,headings=standardclasses]{scrartcl}
 
@@
 
-\title{Neural dialogue act tagging with transformer pre-training (or something like that...)}
+\title{Neural dialogue act recognition with transformer pre-training} % or something like that...
 
@@
   First Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-Affiliation / Address line 3 \\
-  {\tt email@domain} \\\and
+  Affiliation / Address \\
+  %Affiliation / Address line 1 \\
+  %Affiliation / Address line 2 \\
+%Affiliation / Address line 3 \\
+  {\texttt email@domain} \\\and
   Second Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\
+  Affiliation / Address \\
+  %Affiliation / Address line 1 \\
+  %Affiliation / Address line 2 \\
+  %Affiliation / Address line 3 \\
+  {\texttt email@domain} \\
 }
@@
 
-\begin{abstract}
-  abstract
-\end{abstract}
+Dialogue acts represent the meaning of an utterance by the speech act it carries out \citep{austinHowThingsWords2009}.
+Dialogue act recognition (DAR) is the task of automatically labeling utterances with tags from a dialogue act schema such as DAMSL \citep{coreCodingDialogsDAMSL1997}.
 
-\section{Introduction}
-\begin{itemize}
-  \item \cite{austinHowThingsWords2009} -- Speech acts
-  \item \cite{coreCodingDialogsDAMSL1997} -- DAMSL dialogue act scheme
-  \item \cite{devlinBERTPretrainingDeep2018} -- BERT
-    Main questions:
-    1. Are pre-trained transformer encoding (BERT) helpful for representation in a dialogue task (speficially, dialogue act tagging)?
-    2. Are additional dialogue specific features helpful (discourse markers, disfuency, laughter)?
-\end{itemize}
+Dialogue acts depend on their conversational context.
+For example, a speaker may use \textit{okay} to agree with their interlocutor, answer a yes-no question in the affirmative, 
+or simply acknowledge the previous utterance, depending on what has transpired in the conversation so far.
+Naturally, many strategies attempt to model discourse context in addition to considering the content of the utterance in question.
+\cite{stolckeDialogueActModeling2000}, for example, use a Hidden Markov Model to tag dialogue acts.
+The hidden state of neural sequence models can also be used to represent discourse context 
+\citep[e.g.][]{kalchbrennerRecurrentConvolutionalNeural2013,tranPreservingDistributionalInformation2017}.
 
-\section{Related Work}
-\begin{itemize}
-  \item \cite{cerisaraEffectsUsingWord2vec2017}
-  \item \cite{kalchbrennerRecurrentConvolutionalNeural2013}
-  \item \cite{pragstVectorRepresentationUtterances2018}
-  \item \cite{sordoniNeuralNetworkApproach2015}
-  \item \cite{stolckeDialogueActModeling2000} - HMM dialogue act tagging
-  \item \cite{khanpourDialogueActClassification}
-  \item \cite{tranPreservingDistributionalInformation2017}
-\end{itemize}
+%Another approach learns representations of utterances by attempting to predict their conversational context directly,
+%in much the same way that word2vec attempts to predict context words \citep{pragstVectorRepresentationUtterances2018}.
+%The authors find that these utterance representations cluster in a way that corresponds closely to dialogue act tags
+%that were unavailable to the model at training time.
+%conversely, this result raises the possibility that a hidden state learned in service of DAR may be used to represent 
+%a more general notion of discourse context.
 
-\section{Model}
+It is now standard practice in NLP to initialize semantic word representations
+with pre-trained distributional word vectors such as word2vec \citep{mikolov2013distributed}.
+More recently, multi-layer neural language models pre-trained on massive amounts unlabeled data
+have been used to provide contextually sensitive word vectors and sentence-level distributional representations.
+One such model, BERT, uses an attention-based transformer architecture to achieve state of the art results
+on a variety of NLP tasks \citep{devlinBERTPretrainingDeep2018}.
+
+However, given that BERT is pre-trained on book and encyclopedia data, 
+there is no guarantee that the representations it learns will improve performance on dialogue-specific tasks.
+Adding that uncertainty, we note that word2vec is not consistently beneficial for DAR \citep{cerisaraEffectsUsingWord2vec2017}.
+To assess BERT's for dialogue applications, we propose a series of DAR experiments that BERT to encode utterances, 
+which are fed to simple RNN to predict sequences of dialogue acts.
+In particular, we are interested in whether BERT can be fine-tuned to adequately represent
+dialogue-specific features such as discourse markers, disfluency, and laughter.
+
+%%% RELATED WORK NOTES %%%
+%
+% cerisaraEffectsUsingWord2vec2017
+%     - Use LSTM with and without word2vec initialization to encode discourse utterances and predict dialogue act tags.
+%     - No notion of discourse context.
+%     - Word2vec does not improve dialogue act recoginition, possibly becasue it does not capture lexical-semantic information relevant to dialogue.
+% khanpourDialogueActClassification}
+%     - Uses RNN and stacked LSTM with word2vec embeddings to encode utterances.
+%     - No notion of discourse context.
+% pragstVectorRepresentationUtterances2018} --
+%     - Uses a skip thought approach to learn utterance representations by predicting context utterances.
+% kalchbrennerRecurrentConvolutionalNeural2013} --
+%     - Encode utterances (sentences) convolution-based composition of the sequence of words (HCNN). 
+%     - Use an RNN with agent-specific weights to produce utterance label predictions.
+%     - Also talk about the hidden layer of the RNN as representing discourse context. 
+% tranPreservingDistributionalInformation2017} --
+%     - Propogates a distribution over dialogue acts instead of greedily choosing a lable at each step, a kind of discourse context.
+% stolckeDialogueActModeling2000
+%     - classic HMM DAR 
+% chen2018dialogue
+%     - SOTA dialogue act recoginition, uses 
+% sordoniNeuralNetworkApproach2015} 
+%     - generate utterances taking into account previous countext
+
+\paragraph{Model.}
 The proposed model has two components: an utterance encoder, and a sequence model that predicts the dialogue act tag.
@@
 
-\section{Experiments}
-Our aim is to test the effectiveness of different utterance encoding schemas. 
+\paragraph{Experiments.}
+Our aim is to test the effectiveness of different utterance encoding strategies. 
 \begin{enumerate}
@@
 
-  Pre-trained models benefit from learning on large amounts of online data, however it might be the case that for dialogue act tagging additional information only present in natural dialogue data will be useful.
+  Pre-trained models benefit from learning on large amounts of online data, however it might be the case that for DAR, additional information only present in natural dialogue data will be useful.
 Therefore, we evaluate the impact of disfluencies and non-verbal signals, such as laughters on the performance of our models.
-\textbf{(How?)} For the datasets where no annotation for disfluencies is available, it can be predicted from recognised speech \citep{hough2017joint,shalyminov2018multi}.
+\textbf{(How?)} For the datasets where no annotation for disfluencies is available, this information can be predicted from recognised speech \citep{hough2017joint,shalyminov2018multi}.
 

### 2019-04-06 abstract.tex
add diagram

@@
-\documentclass[11pt,a4paper,headings=standardclasses]{scrartcl}
+\documentclass[11pt,a4paper,headings=standardclasses]{article}
 
@@
 \usepackage{natbib}
+\usepackage{tikz}
+\usepackage[bf]{caption}
 
@@
 However, given that BERT is pre-trained on book and encyclopedia data, 
-there is no guarantee that the representations it learns will improve performance on dialogue-specific tasks.
-Adding that uncertainty, we note that word2vec is not consistently beneficial for DAR \citep{cerisaraEffectsUsingWord2vec2017}.
-To assess BERT's for dialogue applications, we propose a series of DAR experiments that BERT to encode utterances, 
-which are fed to simple RNN to predict sequences of dialogue acts.
+there is no guarantee it will improve performance on dialogue-specific tasks.
+Adding to that uncertainty, we note that word2vec is not consistently beneficial for DAR \citep{cerisaraEffectsUsingWord2vec2017}.
+To assess BERT's potential for dialogue applications, we propose a series of DAR experiments 
+with various utterance encoders, including BERT.
+Utterance representations are then fed to a simple RNN to predict sequences of dialogue acts.
 In particular, we are interested in whether BERT can be fine-tuned to adequately represent
@@
 
+\input{architecture-diagram.tex}
+
 \paragraph{Experiments.}

### 2019-04-06 abstract.tex
experiments

@@
 \paragraph{Experiments.}
-Our aim is to test the effectiveness of different utterance encoding strategies. 
+Our aim is to test the effectiveness of different utterance encoding strategies. We investigate the following strategies:
 \begin{enumerate}
-  \item Average word embedding (word2vec, FastText)
-  \item CNN (with/without word2vec initalization, with/without `freezing' the embeddings )
-  \item BERT encoded sentences (with/without additional unsupervised pretraining)
-  \item Average BERT word embeddings (?)
+  \item Averaging of word2vec/BERT word embedding
+  \item Encoding utterances with CNN (with/without word2vec/BERT initalization, with/without `freezing' the embeddings)
+  \item BERT encoded sentences (with/without additional unsupervised pretraining on full Switchboard corpus)
   \end{enumerate}
@@
   Pre-trained models benefit from learning on large amounts of online data, however it might be the case that for DAR, additional information only present in natural dialogue data will be useful.
-Therefore, we evaluate the impact of disfluencies and non-verbal signals, such as laughters on the performance of our models.
-\textbf{(How?)} For the datasets where no annotation for disfluencies is available, it can be predicted from recognised speech \citep{hough2017joint,shalyminov2018multi}.
+In SWDA disfluencies are annotated and for the datasets where no annotation for disfluencies is available, they can be predicted from recognized speech \citep{hough2017joint,shalyminov2018multi}.
+We evaluate the impact of disfluencies and non-verbal signals, such as laughters on the performance of our models and suggests the ways to include information about disfluencies in pre-trained models.
 
-  Furthermore PoS tags
+  % PoS tags?
 

### 2019-04-06 abstract.tex
shorten the references, small comment
typo

@@
 In particular, we are interested in whether BERT can be fine-tuned to adequately represent
-dialogue-specific features such as discourse markers, disfluency, and laughter.
+dialogue-specific features such as discourse markers, disfluency, and laughter. \textbf{Vlad: disfluencies? maybe non-verbal vocalisations (such as laughter) instead of laughter?}
 
@@
 In SWDA disfluencies are annotated and for the datasets where no annotation for disfluencies is available, they can be predicted from recognized speech \citep{hough2017joint,shalyminov2018multi}.
-We evaluate the impact of disfluencies and non-verbal signals, such as laughters on the performance of our models and suggests the ways to include information about disfluencies in pre-trained models.
+We evaluate the impact of disfluencies and non-verbal signals, such as laughters on the performance of our models and suggest the ways to include information about disfluencies in pre-trained models.
 

### 2019-04-07 abstract.tex
small edits

--- 2019-04-06 abstract.tex
@@
 or simply acknowledge the previous utterance, depending on what has transpired in the conversation so far.
-Naturally, many strategies attempt to model discourse context in addition to considering the content of the utterance in question.
+Naturally, many DAR /strategies attempt to model discourse context in addition to considering the content of the utterance in question.
 \cite{stolckeDialogueActModeling2000}, for example, use a Hidden Markov Model to tag dialogue acts.
@@
 with various utterance encoders, including BERT.
-Utterance representations are then fed to a simple RNN to predict sequences of dialogue acts.
+Utterance representations are then fed to a simple RNN to predict sequences of dialogue acts (figure~\ref{fig:architecture}).
 In particular, we are interested in whether BERT can be fine-tuned to adequately represent
-dialogue-specific features such as discourse markers, disfluency, and laughter.
+dialogue-specific features such as discourse markers, disfluencies, and non-verbal vocalizations such as laughter.
 
@@
 
-\paragraph{Model.}
-The proposed model has two components: an utterance encoder, and a sequence model that predicts the dialogue act tag.
-For the sequence model, we use a simple RNN.
-Conceptually the hidden state of this RNN represents the discourse context which, 
-together with the encoded utterance, is used to predict the discourse act tag.
+%\paragraph{Model.}
+%The proposed model has two components: an utterance encoder, and a sequence model that predicts the dialogue act tag.
+%For the sequence model, we use a simple RNN.
+%Conceptually the hidden state of this RNN represents the discourse context which, 
+%together with the encoded utterance, is used to predict the discourse act tag.
 
@@
   \item Encoding utterances with CNN (with/without word2vec/BERT initalization, with/without `freezing' the embeddings)
-  \item BERT encoded sentences (with/without additional unsupervised pretraining on full Switchboard corpus)
+  \item BERT encoded sentences (with/without additional unsupervised pretraining on the full Switchboard corpus)
   \end{enumerate}

### 2019-04-07 abstract.tex
delete extranious '/'

@@
 or simply acknowledge the previous utterance, depending on what has transpired in the conversation so far.
-Naturally, many DAR /strategies attempt to model discourse context in addition to considering the content of the utterance in question.
+Naturally, many DAR strategies attempt to model discourse context in addition to considering the content of the utterance in question.
 \cite{stolckeDialogueActModeling2000}, for example, use a Hidden Markov Model to tag dialogue acts.

### 2019-04-07 abstract.tex
laughters -> laughter

@@
 In SWDA disfluencies are annotated and for the datasets where no annotation for disfluencies is available, they can be predicted from recognized speech \citep{hough2017joint,shalyminov2018multi}.
-We evaluate the impact of disfluencies and non-verbal signals, such as laughters on the performance of our models and suggest the ways to include information about disfluencies in pre-trained models.
+We evaluate the impact of disfluencies and non-verbal signals, such as laughter, on the performance of our models and suggest the ways to include information about disfluencies into pre-trained neural models.
 

### 2019-04-29 data.py
add swda submodule, preprocessing, and splits for reproducability

@@ -1,0 +1,62 @@
+import torch
+import torchtext as tt
+from swda.swda import CorpusReader
+import os
+import json
+import zipfile
+import random
+import argparse
+
+parser = argparse.ArgumentParser()
+parser.add_argument("step", choices=['prep-swda'], help="The preprocessing step")
+args = parser.parse_args()
+
+SWDA_CORPUS_DIR = "data/swda"
+SWDA_SPLITS = "data/swda_{}.json"
+
+def gen_splits(id_list, train=0.7, val=0.1, test=0.2):
+    assert(train+val+test == 1)
+    random.shuffle(id_list)
+    n_train, n_val, n_test = [int(x * len(id_list)) for x in (train, val, test)]
+    train, val, test = id_list[:n_train], id_list[n_train:n_train+n_val], id_list[n_train+n_val:]
+    return {'train': train, 'val': val, 'test': test} 
+
+def prep_swda():
+    """
+    Put the conversations into a json format that torchtext can read easily.
+    Each "example" is a conversation comprised of a list of utterances 
+    and a list of dialogue act tags (each the same length)
+    """
+
+    if not os.path.isfile(SWDA_CORPUS_DIR):
+        with zipfile.ZipFile("swda/swda.zip") as zip_ref:
+            zip_ref.extractall('data')
+
+    corpus = CorpusReader(SWDA_CORPUS_DIR)
+    corpus = {t.conversation_no: t for t in corpus.iter_transcripts()}
+
+    splits_file = SWDA_SPLITS.format('splits')
+    if os.path.isfile(splits_file): # use existing SWDA splits (for reproducibility purposes)
+        with open(splits_file) as f:
+            splits = json.load(f)
+    else: # save the splits file
+        splits = gen_splits(list(corpus.keys()))
+        with open(splits_file, 'w') as f:
+            json.dump(splits, f) 
+
+    def extract_example(transcript):
+        """ Gets the parts we need from the SWDA utterance object """ 
+        tags, utts = [], []
+        for utt in transcript.utterances:
+            utts.append(utt.text.lower())
+            tags.append(utt.act_tag)
+        return {'id': transcript.conversation_no, 'utts': utts, 'tags': tags}
+
+    splits = {split: [extract_example(corpus[ex_id]) for ex_id in splits[split]] for split in splits}
+    for split in splits:
+        with open(SWDA_SPLITS.format(split), 'w') as f:
+            json.dump(splits[split], f)
+
[…]

### 2019-04-29 model.py
add WIP model & training code

@@ -1,0 +1,42 @@
+import torch.nn as nn
+
+class DARRNN(nn.Module):
+    """Container module with an encoder, a recurrent module, and a decoder."""
+
+    def __init__(self, word_embedding, nembed, nlabels, nhid, nlayers, dropout=0.5):
+        """
+        ntokens - word vocabulary size # this should go in the encoder eventually
+        nlabels - number of dialogue act tags 
+        nembed  - size of the utterance embedding TODO: decouple from word embedding size
+        nhid    - size of the hidden layer
+        nlayers - number of hidden RNN layers
+        """
+        super(DARRNN, self).__init__()
+        self.drop = nn.Dropout(dropout)
+        self.word_embedding = word_embedding 
+
+        self.rnn = nn.RNN(nembed, nhid, nlayers, nonlinearity='relu', dropout=dropout) # TODO: try tanh too?
+        self.decoder = nn.Linear(nhid, nlabels)
+
+        self.init_weights()
+
+        self.nhid = nhid
+        self.nlayers = nlayers
+
+    def init_weights(self):
+        initrange = 0.1
+        # self.encoder.weight.data.uniform_(-initrange, initrange)
+        self.decoder.bias.data.zero_()
+        self.decoder.weight.data.uniform_(-initrange, initrange)
+
+    def forward(self, utt, hidden):
+        # emb = self.drop(self.encoder(input))
+        utt_embd = self.word_embedding(utt).mean(dim=0)
+        output, hidden = self.rnn(utt_embd, hidden)
+        output = self.drop(output)
+        decoded = self.decoder(output.view(output.size(0)*output.size(1), output.size(2)))
+        return decoded.view(output.size(0), output.size(1), decoded.size(1)), hidden
+
+    def init_hidden(self, batch_size):
+        weight = next(self.parameters())
+        return weight.new_zeros(self.nlayers, batch_size, self.nhid)

### 2019-04-29 train.py

@@ -1,0 +1,57 @@
+import torch
+import torch.nn as nn
+from model import DARRNN
+import json 
+import pprint 
+from collections import Counter
+
+pp = pprint.PrettyPrinter(indent=4)
+
+vocab_limit = 5000
+glove_dim = 50
+nlayers = 1
+nhidden = 200
+
+# Initialize word embedding from glove vectors
+# TODO: Use google news word2vec also/instead?
+# TODO: Add disfulency markers ('{f', '{c', etc) and '<laughter>' to the vocab. 
+#       Also: consider resetting embedding weights for tokens that are in the 
+#       vocab but have a specific annotation meaning ('[', /', --', '+', ...)
+word_vectors = [[0] * glove_dim ]
+idx2word = ['<UNK>'] 
+with open('data/glove.6B/glove.6B.{}d.txt'.format(glove_dim)) as f:
+    for i, line in enumerate(f.readlines()):
+        line = line.split()
+        idx2word.append(line[0])
+        word_vectors.append([float(w) for w in line[1:]])
+        if vocab_limit and i == vocab_limit:
+            break
+word2idx = {w: i for i,w in enumerate(idx2word)}
+word_vectors = torch.FloatTensor(word_vectors)
+embedding = nn.Embedding.from_pretrained(word_vectors)
+
+# initialize the DAR RNN 
+model = DARRNN(embedding, glove_dim, 100, nhidden, nlayers, dropout=0)
+
+# load the training data
+with open('data/swda_train.json') as f:
+    train_data = json.load(f)
+train_tags = [dialogue['tags'] for dialogue in train_data]
+train_utts = [dialogue['utts'] for dialogue in train_data]
+
+# TODO: Do we need additional pre-processing (clustering?) for tags?
+#       see https://web.stanford.edu/~jurafsky/ws97/manual.august1.html
+tag_counter = Counter([t for ts in train_tags for t in ts])
+idx2tag = [t for (t, count) in tag_counter.most_common()]
+tag2idx = {t: i for i,t in enumerate(idx2tag)}
+
+def utt2ids(utt):
+    return [word2idx[w] if w in word2idx else word2idx['<UNK>'] for w in utt ]
+
+model.train()
+for utts, tags in zip(train_utts, train_tags):
+    utts = [torch.LongTensor(utt2ids(utt)) for utt in utts]
+    print(utts)
+    break
+
+

### 2019-11-06 ami.py
add preprocesing for AMI; uniform corpus handling

@@ -1,7 +1,7 @@
 import xml.etree.ElementTree as ET
 import os
 from collections import defaultdict, namedtuple
-from tqdm import tqdm_notebook as tqdm
+from tqdm import tqdm
 import re
 import warnings
 
@@ -47,20 +47,14 @@ class AMIToken():
             return None
         token_type = element.tag
         start_time = element.get('starttime')
+        end_time   = element.get('endtime')
         if start_time:
             start_time = float(start_time)
-        else:
-            print('st null') 
-            print(meeting_id, speaker, index, token_type)
-            start_time = 0
-        end_time   = element.get('endtime')
         if end_time:
             end_time = float(end_time)
         else:
-            # print('et null')
-            # print(meeting_id, speaker, index, token_type)
             end_time = start_time
-        text = element.text
+        text = element.text if element.text else ''
         attrib = element.attrib
 
         return cls(meeting_id, speaker, index, token_type, start_time, end_time, text, attrib)
@@ -152,14 +146,12 @@ class AMIUtterance():
         self.meeting_id = meeting_id
         self.speaker = speaker
         self.start_time = min(t.start_time for t in tokens)
-        try: 
-            self.end_time = max(t.end_time for t in tokens)
-        except:
-            print([t.end_time for t in tokens])
-            print(meeting_id)
-            print(speaker)
+        self.end_time = max(t.end_time for t in tokens)
         self.dialogue_act = dialogue_act
         self.tokens = tokens
+
+    def text(self):
+        return ' '.join(t.text for t in self.tokens)
 
 
 class AMIMeeting():
@@ -243,42 +235,36 @@ class AMIMeeting():
         
         return utts
                 
-def get_corpus(ami_corpus_dir):
-    """
-    Returns a list of AMIMeetings.
-    """
+def get_corpus(ami_corpus_dir, da_only=True):
 
     words_dir = os.path.join(ami_corpus_dir, 'words')
     words_files = [f for f in os.listdir(words_dir) if f.endswith('.xml')]
-    ######### DEV SAMPLE ##########
-    # words_files = [f for f in words_files if f.startswith('ES2013')]
 
     da_dir = os.path.join(ami_corpus_dir, 'dialogueActs')
     da_files = [f for f in os.listdir(da_dir) if f.endswith('dialog-act.xml')] # ignore the adjacency-pairs files
-    ######### DEV SAMPLE ##########
[…]

### 2019-11-06 data.py

@@ -1,166 +1,35 @@
-import util
-from preproc import tokenize, damsl_tag_cluster, remove_laughters, remove_disfluencies
-
-from swda.swda import CorpusReader
-import ami
-
-from pytorch_pretrained_bert.tokenization import PRETRAINED_VOCAB_ARCHIVE_MAP, BertTokenizer
-from pytorch_pretrained_bert.tokenization import load_vocab as load_bert_vocab 
-
-import os
-import re
-import json
-import zipfile
-import random
 import argparse
 import logging
-from tqdm import tqdm
+import json
+import zipfile
+import tarfile
+import os
+
+import util
+import ami
+from swda import swda
+
+from preproc import tokenize, damsl_tag_cluster, remove_laughters, remove_disfluencies
 
 parser = argparse.ArgumentParser()
-parser.add_argument("command", choices=['prep-swda', 'prep-ami', 'download-glove', 'customize-bert-vocab'], help="What to process")
+parser.add_argument("command", choices=['prep-corpora', 'customize-bert-vocab'], 
+        help="What preprocessing to do.")
+parser.add_argument('-c','--corpora', nargs='+', default=[], 
+        help='A list of corpora to preprocess. (Default: preprocess all)'
+             'Options: swbd, swda, ami, ami-da')
 
-SWDA_CORPUS_DIR = "data/swda"
-SWDA_SPLITS = "data/swda_{}.json"
-
-BERT_MODEL = 'bert-base-uncased'
-BERT_VOCAB_FILE = "data/{}-vocab.SWDA.txt"
-BERT_RESERVED_TOKENS = ["[UNK]", "[SEP]", "[PAD]", "[CLS]", "[MASK]"] # used by the pre-trained BERT model
-BERT_CUSTOM_TOKENS = ['[SPKR_A]', '[SPKR_B]', '<laughter>'] # added by us TODO: add disfluencies
-
-vocab =  {"@@@@@":0, "[SPKR_A]":1, "[SPKR_B]":2}
-tag_vocab = {'@@@@@':0}
-
-def gen_splits(id_list, train=0.7, val=0.1, test=0.2):
-    assert(train+val+test == 1)
-    random.shuffle(id_list)
-    n_train, n_val, n_test = [int(x * len(id_list)) for x in (train, val, test)]
-    train, val, test = id_list[:n_train], id_list[n_train:n_train+n_val], id_list[n_train+n_val:]
-    return {'train': train, 'val': val, 'test': test} 
-
[…]

### 2019-11-07 ami.py
factor out interleave_streams so we can use it with the SWBD alinments too

@@ -4,6 +4,7 @@ from collections import defaultdict, namedtuple
 from tqdm import tqdm
 import re
 import warnings
+import util
 
 xml_ns = {"nite": "http://nite.sourceforge.net/"}
 
@@ -164,7 +165,7 @@ class AMIMeeting():
         self.speakers = set(speaker_streams.keys())
         self.transcript = None
         
-    def gen_transcript(self, split_utts_by_da=True, utt_pause_threshold=3):
+    def gen_transcript(self, split_utts_by_da=True, utt_pause_threshold=1):
         """
         Create a chronological transcript of the dialogue, split by utterances.
         
@@ -177,61 +178,34 @@ class AMIMeeting():
         if self.transcript:
             return transcript
         
-        if split_utts_by_da and not self.speaker_dialogue_acts:
-            warnings.warn("No dialogue acts in transcript {}. Proceeding with heuristic split.". format(
-                self.meeting_id))
-            split_utts_by_da = False
-        if split_utts_by_da:
-            utts = [utt for speaker in self.speakers for utt in self.__get_utts_da(speaker)]
+        if split_utts_by_da and self.speaker_dialogue_acts:
+            transcript = self.__get_transcript_da()
         else:
-            utts = [utt for speaker in self.speakers for utt in self.__get_utts_noda(speaker, utt_pause_threshold)]
-        
-        # interelave utts
-        transcript = sorted(utts, key=lambda x: x.start_time)
+            transcript = self.__get_transcript_noda(utt_pause_threshold) 
         
         self.transcript = transcript
         return transcript
     
-    def __get_utts_da(self, speaker):
-        dialogue_acts = self.speaker_dialogue_acts[speaker]
-        stream = {token.index: token for token in self.speaker_streams[speaker] 
-                if token.start_time is not None and token.end_time is not None}
+    def __get_transcript_da(self):
         utts = []
-        for da in dialogue_acts:
-            utts.append(AMIUtterance([stream[i] for i in range(da.start_token, da.end_token+1) if i in stream], da))
+        for speaker in self.speakers:
+            dialogue_acts = self.speaker_dialogue_acts[speaker]
+            stream = {token.index: token for token in self.speaker_streams[speaker] 
+                    if token.start_time is not None and token.end_time is not None}
+            for da in dialogue_acts:
+                utts.append(AMIUtterance([stream[i] for i in range(da.start_token, da.end_token+1) if i in stream], da))
+        utts = sorted(utts, key=lambda x: x.start_time)  # interleave utts
[…]

### 2019-11-07 data.py

@@ -77,10 +77,11 @@ class DialogueCorpus():
     Standardized corpus format for dialogue act recoginiton.
     """
 
-    def __init__(self, corpus_name, corpus_dir, corpus_file):
+    def __init__(self, corpus_name, corpus_dir, corpus_id):
         self.name = corpus_name
+        self.corpus_id = corpus_id
         self.corpus_dir = os.path.join(DATA_DIR, corpus_dir)
-        self.corpus_file = os.path.join(DATA_DIR, corpus_file)
+        self.corpus_file = os.path.join(DATA_DIR, f'{corpus_id}.json')
 
     def to_json(self):
         with open(self.corpus_file, 'w') as f:
@@ -103,11 +104,11 @@ class AMICorpus(DialogueCorpus):
         """
         corpus_name = "AMI Meeting Corpus"
         corpus_dir = "AMI"
-        corpus_file = "AMI-DA.json" if da_only else "AMI.json"
+        corpus_id = "AMI-DA" if da_only else "AMI"
         if da_only:
             corpus_name += " (dialogue act-tagged)"
         self.da_only = da_only
-        super().__init__(corpus_name, corpus_dir, corpus_file)
+        super().__init__(corpus_name, corpus_dir, corpus_id)
 
     def download_corpus(self):
         url = "http://groups.inf.ed.ac.uk/ami/AMICorpusAnnotations/ami_public_manual_1.6.2.zip"
@@ -121,8 +122,8 @@ class AMICorpus(DialogueCorpus):
         ami_meetings = ami.get_corpus(self.corpus_dir, self.da_only)
         dialogues = []
         for m in ami_meetings:
-            m.gen_transcript(split_utts_by_da=self.da_only)
-            utts = [Utterance(u.speaker, u.dialogue_act.da_tag, u.text()) 
+            m.gen_transcript()
+            utts = [Utterance(u.speaker, u.dialogue_act.da_tag if u.dialogue_act else None, u.text()) 
                     for u in m.transcript]
             dialogues.append(Dialogue(m.meeting_id, utts))
         self.dialogues = dialogues
@@ -133,8 +134,8 @@ class SWBDWordAlignedCorpus(DialogueCorpus):
     def __init__(self):
         corpus_name = "Switchboard Corpus"
         corpus_dir = "SWBD"
-        corpus_file = "SWBD.json"
-        super().__init__(corpus_name, corpus_dir, corpus_file)
+        corpus_id = "SWBD"
[…]

### 2019-11-07 util.py

@@ -2,6 +2,7 @@ import logging
 import urllib.request
 import shutil
 from tqdm import tqdm
+from collections import defaultdict
 
 class DownloadProgressBar(tqdm):
     def update_to(self, b=1, bsize=1, tsize=None):
@@ -49,3 +50,30 @@ def create_logger(console_log_level, log_file=None):
 
 def rm_dir(directory):
     shutil.rmtree(directory)
+
+def interleave_streams(stream, speaker, start, end, pause_threshold):
+    """
+    stream - the interable of objects (e.g., utterances) to be ordered.
+    speaker - a function that returtns the speaker for the object in the stream
+    start  - a function that returns the start time for objects in the stream
+    end    - a function returning the end time for objects in the stream
+    """
+
+    utts = defaultdict(list)
+    utt_tokens = []
+    prev_token = []
+
+    stream = sorted(stream, key=start) 
+    while stream:
+        token = stream.pop(0)
+        if not prev_token:
+            utt_tokens.append(token)
+        elif (speaker(token) != speaker(prev_token) or start(token) - end(prev_token) > pause_threshold):
+            utts[speaker(prev_token)].append(utt_tokens)
+            utt_tokens = [token]
+        else: 
+            utt_tokens.append(token)
+        prev_token = token
+    utts[speaker(prev_token)].append(utt_tokens)
+    return utts
+

### 2019-11-07 reports/ACL2020 Paper/acl2020-paper.tex
outline and draft intro

%
% File acl2020.tex
%
%% Based on the style files for ACL 2020, which were
%% Based on the style files for ACL 2018, NAACL 2018/19, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B\textsc{ib}\TeX}

\title{Instructions for ACL 2020 Proceedings}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
  Basically we want to see if language models pre-trained on text data are useful for dialogue.
  So we look at if BERT is useful for dialouge act recoginiton.
  But we want to know if it's really adapting to the domain, so we look at how it uses laughter, a phenomenon specific to dialogue.
\end{abstract}

% INTRODUCTION

Recently, large-scale language models, trained on massive corpora of text data, have achieved state-of-the-art results on a variety of traditonal NLP tasks.
We investigate whether such models might be useful for processing dialogue, and if so, whether they adapt to make use of dialogue-specific features.

Dialogue, especially spoken dialogue, is radically different from the kind of data that neural language models are prestrained on.
Not only is the internal structure of contributions different---with features such as disfluencies, repair, incomplete sentences, and various vocal sounds---but the sequential structure of the discourse is also very different.
In dialouge speakers take turns and switch perpsectives.
More generally, the way that utterances contribute and cohere to the discourse is different from the relationship between sentences in a piece of written text.

One important dialogical feature missing from text data is laughter.
In the Switchboard dialogue corpus, laughter appears in approximately \%X of utterances.
Laughter also relates to the discourse structure of dialogue. 
Laughables.
Also useful for predicting DAs (is that already a result?)

In this work, we investigate whether BERT, a well-know pre-trained language model, is useful for dialogue.
We use dialogue act recoginition as a proxy task, since both the interal content of conributions, and their sequential structure have bearing on the task.

\section{Background}
%  - dialogue acts
%  - laughter
%  - BERT

\section{Related work}
%  - BERT domain transfer
%  - BERT/LM for DAR

\section{Data}
%  - AMI, SWBD + comparison table
%  - Laughter with/without

\section{Model}
%  - DAR model -> utt encoder, RNN sequence tagger
%  - BERT encoder (12 heads, uncased,...)
%  - baseline encoder

\section{Experiments}
%  - BERT vs. baseline (L/NL)
%  - in-domain pre-training (L/NL)
%  - cross-domain pre-training

\section{Results and discussion}

\bibliography{anthology,acl2020}
\bibliographystyle{acl_natbib}

\end{document}

### 2019-11-09 ami.py
simplify corpus parsing

@@ -4,7 +4,6 @@ from collections import defaultdict, namedtuple
 from tqdm import tqdm
 import re
 import warnings
-import util
 
 xml_ns = {"nite": "http://nite.sourceforge.net/"}
 
@@ -69,6 +68,8 @@ class AMIToken():
             return '<disf>'
         elif self.token_type == 'gap':
             return ''
+        elif self.token_type == 'transformerror':  # is this right?
+            return '' 
         else:
             raise ValueError("undefined str for token {}".format(self.token_type))
 
@@ -202,13 +203,47 @@ class AMIMeeting():
         stream = [token for speaker in self.speakers 
                     for token in self.speaker_streams[speaker] 
                     if token.start_time is not None and token.end_time is not None]
-        utts = util.interleave_streams(stream, lambda x: x.speaker, 
+        utts = interleave_streams(stream, lambda x: x.speaker, 
                 lambda x: x.start_time, lambda x: x.end_time,
                 utt_pause_threshold)
         utts = [AMIUtterance(utt) for speaker in self.speakers for utt in utts[speaker]]
         
         return utts
+
+    def get_tokens(self):
+        tokens = [token for speaker in self.speaker_streams for token in self.speaker_streams[speaker]
+                    if token.start_time]
+
+        tokens = sorted(tokens, key=lambda x:x.start_time)
+        return tokens
+
                 
+def interleave_streams(stream, speaker, start, end, pause_threshold):
+    """
+    stream - the interable of objects (e.g., utterances) to be ordered.
+    speaker - a function that returtns the speaker for the object in the stream
+    start  - a function that returns the start time for objects in the stream
+    end    - a function returning the end time for objects in the stream
+    """
+
+    utts = defaultdict(list)
+    utt_tokens = []
+    prev_token = []
+
+    stream = sorted(stream, key=start) 
+    while stream:
+        token = stream.pop(0)
+        if not prev_token:
+            utt_tokens.append(token)
+        elif (speaker(token) != speaker(prev_token) or start(token) - end(prev_token) > pause_threshold):
+            utts[speaker(prev_token)].append(utt_tokens)
+            utt_tokens = [token]
+        else: 
+            utt_tokens.append(token)
+        prev_token = token
+    utts[speaker(prev_token)].append(utt_tokens)
+    return utts
+
 def get_corpus(ami_corpus_dir, da_only=True):
 
     words_dir = os.path.join(ami_corpus_dir, 'words')

### 2019-11-09 data.py

@@ -1,9 +1,12 @@
 import argparse
 import logging
+import os
 import json
+import csv
 import zipfile
 import tarfile
-import os
+from collections import namedtuple
+from tqdm import tqdm
 
 import util
 import ami
@@ -17,8 +20,10 @@ parser.add_argument("command", choices=['prep-corpora', 'customize-bert-vocab'],
 parser.add_argument('-c','--corpora', nargs='+', default=[], 
         help='A list of corpora to preprocess. (Default: preprocess all)'
              'Options: swbd, swda, ami, ami-da')
-
-DATA_DIR = 'data'
+parser.add_argument('-d','--data-dir', default='data',
+        help='Data storage directory.')
+parser.add_argument('-pt','--pause-threshold', default=1,
+        help='Threshold for heuristically segementing same-speaker utterances (seconds).')
 
 
 def customize_bert_vocab(bert_model='bert-base-uncased'):
@@ -45,148 +50,98 @@ def customize_bert_vocab(bert_model='bert-base-uncased'):
             f.write(token + '\n')
 
 
-class Utterance():
-
-    def __init__(self, speaker, da_tag, text):
-        self.speaker = speaker
-        self.da_tag = da_tag
-        self.text = text
-
-    def to_dict(self):
-        return {'speaker': self.speaker,
-                'da_tag': self.da_tag,
-                'text': f"[SPKR_{self.speaker}] {self.text}"}
+Dialogue = namedtuple('SegmentedDialogue', ['id', 'speakers', 'utts', 'da_tags'])
 
 
-class Dialogue():
+def extract_corpus(zip_file, corpus_dir):
+    if os.path.exists(corpus_dir):
+        log.info(f"The corpus directory, {corpus_dir} alrdeay exists.")
+        return
+    log.info(f"Extracting {zip_file} to {corpus_dir}.")
+    if zip_file.endswith('.zip'):
+        file_handler = lambda x: zipfile.ZipFile(x, 'r')
+    elif zip_file.endswith('tar.gz'):
+        file_handler = lambda x: tarfile.open(x, 'r:gz')
+    else:
+        raise ValueError(f"Can't handle extension {zip_ext} when unzipping {zip_file}.")
+    with file_handler(zip_file) as f:
+        f.extractall(corpus_dir)
 
-    def __init__(self, dialogue_id, utts):
-        self.id = dialogue_id
-        self.speakers = list({utt.speaker for utt in utts})
-        self.utts = utts
+def download_corpus(url, zip_file):
[…]

### 2019-11-09 util.py

@@ -3,22 +3,11 @@ import urllib.request
 import shutil
 from tqdm import tqdm
 from collections import defaultdict
-
-class DownloadProgressBar(tqdm):
-    def update_to(self, b=1, bsize=1, tsize=None):
-        if tsize is not None:
-            self.total = tsize
-        self.update(b * bsize - self.n)
-
-def download_url(url, output_path):
-    with DownloadProgressBar(unit='B', unit_scale=True,
-                             miniters=1, desc=url.split('/')[-1]) as t:
-        urllib.request.urlretrieve(url, filename=output_path, reporthook=t.update_to)
+import os
 
 class TqdmLoggingHandler(logging.Handler):
     def __init__(self, level=logging.NOTSET):
         super().__init__(level)
-
     def emit(self, record):
         try:
             msg = self.format(record)
@@ -32,12 +21,10 @@ class TqdmLoggingHandler(logging.Handler):
 def create_logger(console_log_level, log_file=None):
     log = logging.getLogger('DARLOGGER')
     log.setLevel(logging.DEBUG)
-
     # log to the console 
     ch = TqdmLoggingHandler()
     ch.setLevel(console_log_level)
     log.addHandler(ch)
-
     # log to a file 
     if log_file:
         fh = logging.FileHandler(log_file)
@@ -45,35 +32,19 @@ def create_logger(console_log_level, log_file=None):
         fh.setFormatter(fh_formatter)
         fh.setLevel(logging.DEBUG)
         log.addHandler(fh)
-
     return log
+
+class DownloadProgressBar(tqdm):
+    def update_to(self, b=1, bsize=1, tsize=None):
+        if tsize is not None:
+            self.total = tsize
+        self.update(b * bsize - self.n)
+
+def download_url(url, output_path):
+    with DownloadProgressBar(unit='B', unit_scale=True,
+                             miniters=1, desc=url.split('/')[-1]) as t:
+        urllib.request.urlretrieve(url, filename=output_path, reporthook=t.update_to)
 
 def rm_dir(directory):
     shutil.rmtree(directory)
-
-def interleave_streams(stream, speaker, start, end, pause_threshold):
-    """
-    stream - the interable of objects (e.g., utterances) to be ordered.
-    speaker - a function that returtns the speaker for the object in the stream
-    start  - a function that returns the start time for objects in the stream
-    end    - a function returning the end time for objects in the stream
-    """
-
-    utts = defaultdict(list)
-    utt_tokens = []
[…]

### 2019-11-15 eval_model.py
update BertEncoder call in eval

@@ -91,8 +91,9 @@ if __name__ == '__main__':
         encoder_model = model.KimCNN.random_init(vocab_size, args.utt_dims, 
                 args.embedding_size, window_sizes, feature_maps)
     elif args.encoder_model == 'bert':
-        encoder_model = model.BertUttEncoder(args.utt_dims,
-                from_pretrained/False, finetune_bert=False) 
+        encoder_model = model.BertEncoder(args.utt_dims,
+                from_pretrained=False, finetune_bert=False,
+                resize=len(tokenizer)) 
     else:
         raise ValueError("Unknown encoder model: {}".format(args.encoder_model))
 

### 2019-11-18 analysis/ACL/analyse.py
Add python script to combine all scores

@@ -1,0 +1,123 @@
+import sys
+sys.path.append('../..')
+
+from collections import defaultdict, namedtuple
+import os
+import data
+import transformers
+import argparse
+import json
+
+from swda import swda
+corpus = swda.CorpusReader('../../data/SWDA/swda')
+
+parser = argparse.ArgumentParser()
+parser.add_argument('corpus', choices=['SWDA', 'AMI-DA'],
+        help='Which dialouge act corpus to analyse.')
+parser.add_argument('-d','--data-dir', default='../../data',
+        help='Data storage directory.')
+args = parser.parse_args()
+
+flatten = lambda l: [item for sublist in l for item in sublist]
+
+def corpus_data():
+    # All DA tags
+    das = defaultdict(int)
+    # DAs with laughter
+    das_L = defaultdict(int)
+    # DAs with laughter in the preceding utterance 
+    das_preL = defaultdict(int)
+    # DAs with laughter in the following utterance 
+    das_postL = defaultdict(int)
+    
+    for trans in corpus.iter_transcripts():
+        for utt in trans.utterances:
+            das[utt.damsl_act_tag()] += 1
+            if '<laughter>' in utt.text.lower():
+                das_L[utt.damsl_act_tag()] += 1
+        for pre, utt in zip(trans.utterances, trans.utterances[1:]):
+            if '<laughter>' in pre.text.lower():
+                das_preL[utt.damsl_act_tag()] += 1
+        for utt, post in zip(trans.utterances, trans.utterances[1:]):        
+            if '<laughter>' in post.text.lower():
+                das_postL[utt.damsl_act_tag()] += 1
+    return das, das_L, das_preL, das_postL
+
+def test_data():
+    test_file = os.path.join(args.data_dir, f'{args.corpus}_test.json')
+    vocab_file = os.path.join(args.data_dir, f'bert-base-uncased_vocab.txt')
+    tag_vocab_file = os.path.join(args.data_dir, f'{args.corpus}_tags.txt')
+    tokenizer = data.load_tokenizer('bert-base-uncased')
+    tokenizer = transformers.BertTokenizer.from_pretrained(vocab_file, 
+                                                           never_split=data.BERT_RESERVED_TOKENS +\
+                                                           data.BERT_CUSTOM_TOKENS)
[…]

### 2019-11-20 analysis/ACL/analyse.py
add AMI dialogue acts description dict

@@ -93,7 +93,7 @@ class DialogueActStats(DialogueActStats):
         return f'|{self.nm}|{vals}|'
 
 if __name__ == '__main__':
-    names = json.load(open('dialogue-acts.json'))
+    names = json.load(open('SWDA_dialogue-acts.json'))
     totals = calculate_totals()
     total_c = sum([t[1] for t in totals])
     pre_c = sum([t[2] for t in totals])

### 2019-12-01 data.py
fix order of test split for comparison purproses

@@ -280,8 +280,9 @@ def write_splits(dialogues, data_dir, corpus_name):
         splits = gen_splits([d.id for d in dialogues])
         with open(splits_file, 'w') as f:
             json.dump(splits, f)
+    dialogues = {d.id: d for d in dialogues}
     for split in splits:
-        split_data = [d for d in dialogues if d.id in splits[split]]
+        split_data = [dialogues[dialogue_id] for dialogue_id in split[split]]
         write_corpus(split_data, data_dir, f"{corpus_name}_{split}.json")
 
 

### 2019-12-01 data.py
fix typo

@@ -282,7 +282,7 @@ def write_splits(dialogues, data_dir, corpus_name):
             json.dump(splits, f)
     dialogues = {d.id: d for d in dialogues}
     for split in splits:
-        split_data = [dialogues[dialogue_id] for dialogue_id in split[split]]
+        split_data = [dialogues[dialogue_id] for dialogue_id in splits[split]]
         write_corpus(split_data, data_dir, f"{corpus_name}_{split}.json")
 
 

### 2019-12-02 reports/ACL2020 Paper/acl2020-paper.tex
Update paper outline
add experiment 2 text

@@
 \renewcommand{\UrlFont}{\ttfamily\small}
+\usepackage{booktabs}
 
@@
 
-\section{Background}
+\paragraph{Fine-tuning and laughter}
+Since the laughter token doesn't appear in the original BERT vocabulary, only fine-tuned models can meaningfully make use of laughter in utterance representations. 
+This gives us another opportunity to assess whether laughter is useful in dialogue act recognition.
+We find that although \%4.6 of utterances in SWDA contain laughter, \%7.3 of utterances misclassified by \texttt{BERT} but correctly classified by \texttt{BERT-FT} contain laughter, suggesting that the fine-tuned model utterance encoder is making use of laughter.
+For AMI-DA, the effect is less pronounced, but still present§: \%8.5 of utterances contain laughter, and \%9.6 of utterances where fine-tuning makes a difference contain laughter.
+
+\section{Background} % Vlad
 %  - dialogue acts
@@
 
-\section{Related work}
+\section{Related work} % add references first
 %  - BERT domain transfer
@@
 \section{Data}
-%  - AMI, SWBD + comparison table
-%  - Laughter with/without
+% - DA distribution              % Vlad
+% - Laughter frequencies per DA  % Vlad
+% - AMI, SWBD + comparison table % Bill
+% - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, removing laughter % Bill
 
-\section{Model}
+\section{Model} % Bill
 %  - DAR model -> utt encoder, RNN sequence tagger
@@
 \section{Experiments}
-%  - BERT vs. baseline (L/NL)
-%  - in-domain pre-training (L/NL)
+\subsection{Experiment 1: Impact of laughter}   % Vlad
+% per dialogue act analysis
+% compare impacts of CNN vs BERT
+% for both AMI and SWDA
+
+\subsection{Experiment 2: Impact of pre-training} % Bill
+% - compare i) pre-trained BERT with freezing ii) pretrained with no freezing iii) randolmly initialized
+Next, we take a direct look at how pre-training affects BERT's performance as an utterance encoder for our DAR model.
+In particular, we consider the performance of DAR models with three different utterance encoders:
+\begin{itemize}
+  \item \texttt{BERT} -- pre-trained BERT without fine-tuning (frozen during DAR training)
+  \item \texttt{BERT-FT} -- pre-trained BERT with fine-tuninig 
+  \item \texttt{BERT-RI} -- randomly initialized BERT with fine-tuning 
+\end{itemize}
+
+\begin{table}[]
+\centering 
+\begin{tabular}{@{}lll@{}}
+\toprule
+                 & SWDA  & AMI-DA \\ \midrule
+\texttt{BERT}       & 55.61 & 46.59  \\
+\texttt{BERT-FT}    & 76.93 & 66.94  \\
+\texttt{BERT-RI}    & 73.80 & 61.53  
+\end{tabular}
+  \caption{Micro-average DAR accuracy}
+  \label{table:exp2-avg}
+\end{table}
+
+The pre-trained model performs better than the randomly initialized model by several percentage points on both DA corpora (table \ref{table:exp2-avg}). 
+These results suggest that BERT's extensive pre-training do provide some useful information for dialogue act recoginition.
+However, we note that pre-training is not enough: the poor performance of the frozen \texttt{BERT} model indicates that fine-tuning is important for BERT's performance as an utterance encoder.
+These observations raise two questions.
+First, how does BERT's pre-training help with DAR? 
+And second, in what way are the representations learned by pre-trained BERT lacking?
+In other words, what is the contribution of fine-tuning?
+
+To help answer these questions, we compare accuracy results of the above three models by dialogue act tag.
+
+% TODO: add per dialogue act accuracy figures
+
+\subsection{Experiment 3: Impact of dialogue pre-training} % Bill
+% - pre-train AMI+SWBD -> train SWDA/AMI-DA -> test SWDA/AMI-DA
+% - pre-traing tasks: 1) next utterance, 2) masked token, 3) both ?
+% - compare frozen with no dialogue pre-training vs pre-trained on dialogue w.r.t. L/NL (same as in Experiment 1)
+
+\subsection{Experiment 4: Cross-domain pre-training (if time permits)} % Bill
 %  - cross-domain pre-training
 
-\section{Results and discussion}
+\section{Discussion} % add items to discuss
 

### 2019-12-02 reports/ACL2020 Paper/acl2020-paper.tex
add some to the data section

@@
 \section{Data}
+We perform experiments on the Switchboard Dialogue Act Corpus (SWDA), which is a subset of the larger Switchboard corpus, and the dialogue act-tagged portion of the AMI Meeting Corpus (AMI-DA).
+
 % - DA distribution              % Vlad
 % - Laughter frequencies per DA  % Vlad
+
 % - AMI, SWBD + comparison table % Bill
+\begin{table}[]
+\centering
+\begin{tabular}{@{}ll@{}}
+\toprule
+\textbf{Switchboard}       & \textbf{AMI Corpus}                     \\ \midrule
+Dyadic                     & Multi-party                             \\
+Casual conversation        & Mock business meeting                   \\
+Telephone                  & In-person \& video                      \\ \midrule
+English                    & English                                 \\ 
+Native speakers            & Native \& non-native speakers           \\ 
+early '90s                 & 2000s                                   \\ \midrule
+2200 conversations         & 171 meetings                            \\
+  \hspace{1em} 1155 in SWDA               & \hspace{1em} 139 in AMI-DA                           \\
+400 utterances             & 118k utterances                         \\
+3M tokens                  & 1.2M tokens                             \\ \bottomrule
+\end{tabular}
+  \caption{Comparison between Switchboard and the AMI Meeting Corpus}
+  \label{table:corpora}
+\end{table}
+
 % - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, removing laughter % Bill

### 2019-12-03 data.py
add pre-training scripts

@@ -21,7 +21,8 @@ parser.add_argument("command", choices=[
     'prep-corpora', 
     'download-glove', 
     'get-bert-config',
-    'test-tokenization'
+    'test-tokenization',
+    'prep-pretraining-corpora'
     ],  help="What preprocessing to do.")
 parser.add_argument('-d','--data-dir', default='data',
         help='Data storage directory.')
@@ -102,11 +103,12 @@ def load_data_pretraining(corpus_file, tokenizer):
         dialogues = json.load(f)
     data = []
     for d in dialogues:
+        utts = []
         for speaker,utt in zip(d['speakers'], d['utts']):
-           utt = ['[CLS]', f'[SPKR_{speaker}]'] + tokenizer.tokenize(utt)
-           data.append(utt)
+           utt = [f'[SPKR_{speaker}]'] + tokenizer.tokenize(utt)
+           utts.append(utt)
+        data.append(utts)
     return data
-
 
 Dialogue = namedtuple('Dialogue', ['id', 'speakers', 'utts', 'da_tags'])
 
@@ -354,4 +356,24 @@ if __name__ == '__main__':
 
     if args.command == 'download-glove':
         download_glove(args.data_dir)
+
+    if args.command == 'prep-pretraining-corpora':
+
+        tokenizer = load_tokenizer('bert-base-uncased')
+
+        ami = (load_data_pretraining(os.path.join(args.data_dir, 'AMI-DA_train.json'), tokenizer) +
+               load_data_pretraining(os.path.join(args.data_dir, 'AMI-noDA.json'), tokenizer))
+        with open(os.path.join(args.data_dir, 'AMI_pretraining.txt'), 'w') as f:
+            for d in ami:
+                for utt in d:
+                    f.write(' '.join(utt) + '\n')
+                f.write('\n')
+
+        swbd = load_data_pretraining(os.path.join(args.data_dir, 'SWDA_train.json'), tokenizer)
+        with open(os.path.join(args.data_dir, 'SWBD_pretraining.txt'), 'w') as f:
+            for d in swbd:
+                for utt in d:
+                    f.write(' '.join(utt) + '\n')
+                f.write('\n')
+
 

### 2019-12-03 finetune_on_pregenerated.py

@@ -1,0 +1,344 @@
+"""
+Adapted from this script: https://github.com/huggingface/transformers/tree/1.1.0/examples/lm_finetuning
+"""
+
+from argparse import ArgumentParser
+from pathlib import Path
+import os
+import torch
+import logging
+import json
+import random
+import numpy as np
+from collections import namedtuple
+from tempfile import TemporaryDirectory
+
+from torch.utils.data import DataLoader, Dataset, RandomSampler
+from torch.utils.data.distributed import DistributedSampler
+from tqdm import tqdm
+
+from transformers import WEIGHTS_NAME, CONFIG_NAME, BertConfig
+from transformers.modeling_bert import BertForPreTraining, BertPreTrainingHeads
+from transformers.tokenization_bert import BertTokenizer
+from transformers.optimization import AdamW, WarmupLinearSchedule
+
+import data
+
+InputFeatures = namedtuple("InputFeatures", "input_ids input_mask segment_ids lm_label_ids is_next")
+
+log_format = '%(asctime)-10s: %(message)s'
+logging.basicConfig(level=logging.INFO, format=log_format)
+
+
+def convert_example_to_features(example, tokenizer, max_seq_length):
+    tokens = example["tokens"]
+    segment_ids = example["segment_ids"]
+    is_random_next = example["is_random_next"]
+    masked_lm_positions = example["masked_lm_positions"]
+    masked_lm_labels = example["masked_lm_labels"]
+
+    assert len(tokens) == len(segment_ids) <= max_seq_length  # The preprocessed data should be already truncated
+    input_ids = tokenizer.convert_tokens_to_ids(tokens)
+    masked_label_ids = tokenizer.convert_tokens_to_ids(masked_lm_labels)
+
+    input_array = np.zeros(max_seq_length, dtype=np.int)
+    input_array[:len(input_ids)] = input_ids
+
+    mask_array = np.zeros(max_seq_length, dtype=np.bool)
+    mask_array[:len(input_ids)] = 1
+
+    segment_array = np.zeros(max_seq_length, dtype=np.bool)
+    segment_array[:len(segment_ids)] = segment_ids
+
+    lm_label_array = np.full(max_seq_length, dtype=np.int, fill_value=-1)
+    lm_label_array[masked_lm_positions] = masked_label_ids
+
+    features = InputFeatures(input_ids=input_array,
+                             input_mask=mask_array,
+                             segment_ids=segment_array,
+                             lm_label_ids=lm_label_array,
[…]

### 2019-12-03 pregenerate_training_data.py

@@ -1,0 +1,361 @@
+"""
+Adapted from this script: https://github.com/huggingface/transformers/tree/1.1.0/examples/lm_finetuning
+"""
+
+from argparse import ArgumentParser
+from pathlib import Path
+from tqdm import tqdm, trange
+from tempfile import TemporaryDirectory
+import shelve
+from multiprocessing import Pool
+
+from random import random, randrange, randint, shuffle, choice
+from transformers.tokenization_bert import BertTokenizer
+import numpy as np
+import json
+import collections
+
+import data
+
+class DocumentDatabase:
+    def __init__(self, reduce_memory=False):
+        if reduce_memory:
+            self.temp_dir = TemporaryDirectory()
+            self.working_dir = Path(self.temp_dir.name)
+            self.document_shelf_filepath = self.working_dir / 'shelf.db'
+            self.document_shelf = shelve.open(str(self.document_shelf_filepath),
+                                              flag='n', protocol=-1)
+            self.documents = None
+        else:
+            self.documents = []
+            self.document_shelf = None
+            self.document_shelf_filepath = None
+            self.temp_dir = None
+        self.doc_lengths = []
+        self.doc_cumsum = None
+        self.cumsum_max = None
+        self.reduce_memory = reduce_memory
+
+    def add_document(self, document):
+        if not document:
+            return
+        if self.reduce_memory:
+            current_idx = len(self.doc_lengths)
+            self.document_shelf[str(current_idx)] = document
+        else:
+            self.documents.append(document)
+        self.doc_lengths.append(len(document))
+
+    def _precalculate_doc_weights(self):
+        self.doc_cumsum = np.cumsum(self.doc_lengths)
+        self.cumsum_max = self.doc_cumsum[-1]
+
+    def sample_doc(self, current_idx, sentence_weighted=True):
+        # Uses the current iteration counter to ensure we don't sample the same doc twice
+        if sentence_weighted:
+            # With sentence weighting, we sample docs proportionally to their sentence length
+            if self.doc_cumsum is None or len(self.doc_cumsum) != len(self.doc_lengths):
+                self._precalculate_doc_weights()
+            rand_start = self.doc_cumsum[current_idx]
+            rand_end = rand_start + self.cumsum_max - self.doc_lengths[current_idx]
+            sentence_index = randrange(rand_start, rand_end) % self.cumsum_max
+            sampled_doc_index = np.searchsorted(self.doc_cumsum, sentence_index, side='right')
+        else:
[…]

### 2019-12-03 finetune_on_pregenerated.py
fix some bugs with multigpu

@@ -201,13 +201,15 @@ def main():
 
     if args.local_rank == -1 or args.no_cuda:
         device = torch.device("cuda" if torch.cuda.is_available() and not args.no_cuda else "cpu")
-        n_gpu = torch.cuda.device_count()
+        # n_gpu = torch.cuda.device_count()
+        n_gpu = 1
     else:
         torch.cuda.set_device(args.local_rank)
         device = torch.device("cuda", args.local_rank)
-        n_gpu = 1
+        # n_gpu = 1
+        n_gpu = torch.cuda.device_count()
         # Initializes the distributed backend which will take care of sychronizing nodes/GPUs
-        torch.distributed.init_process_group(backend='nccl')
+        torch.distributed.init_process_group(backend='nccl', rank=args.local_rank, world_size=n_gpu)
     logging.info("device: {} n_gpu: {}, distributed training: {}, 16-bits training: {}".format(
         device, n_gpu, bool(args.local_rank != -1), args.fp16))
 

### 2019-12-03 model.py
add pretrained model loading

@@ -129,10 +129,11 @@ class KimCNN(nn.Module):
 
 class BertEncoder(nn.Module):
 
-    def __init__(self, utt_size, from_pretrained=True, finetune_bert=True, resize=False):
+    def __init__(self, utt_size, from_pretrained=True, pretrained_dir=None, finetune_bert=True, resize=False):
         super().__init__()
         if from_pretrained:
-            self.bert = transformers.BertModel.from_pretrained('bert-base-uncased')
+            pretrained_str = pretrained_dir or 'bert-base-uncased'  # default to library-suppled pre-trained model
+            self.bert = transformers.BertModel.from_pretrained(pretrained_str)
         else:
             config = transformers.BertConfig.from_json_file('data/bert-base-uncased_config.json')
             self.bert = transformers.BertModel(config)

### 2019-12-03 train.py

@@ -34,6 +34,8 @@ parser.add_argument('--dar-layers', default=1, type=int,
         help="Number of hidden layers in the DAR RNN.")
 parser.add_argument('--random-init', action='store_true', default=False,
         help='Start from an un-trained BERT model.')
+parser.add_argument('--pretrained-dir', type=str, default=None,
+        help='Custom path to a pre-trained encoder model')
 parser.add_argument('--glove', dest='use_glove', action='store_true', default=False,
         help="Use GloVe (with compatible utt encoders).")
 parser.add_argument('--embedding-size', type=int, default=100,
@@ -194,6 +196,7 @@ if __name__ == '__main__':
     elif args.encoder_model == 'bert':
         encoder_model = model.BertEncoder(args.utt_dims,
                 from_pretrained=not args.random_init, 
+                pretrained_dir=args.pretrained_dir,
                 finetune_bert=not args.freeze_embedding,
                 resize=len(tokenizer))
         

### 2019-12-03 reports/ACL2020 Paper/acl2020-paper.tex
Add accuracies for Experiment 1 (bert)

@@
 \usepackage{booktabs}
-
+\usepackage{graphicx}
 % This is not strictly necessary, and may be commented out,
@@
 \subsection{Experiment 1: Impact of laughter}   % Vlad
-% per dialogue act analysis
-% compare impacts of CNN vs BERT
-% for both AMI and SWDA
+In the first experiment we investigated whether laughter, as an example of a dialogue-specific signal, is a helpful feature for DAR.
+Therefore, we train another version of each model: one containing laughters (L) and with laughters left out (NL), and compare their performances in DAR task.
+
+\begin{table}
+  \centering
+  \begin{tabular}{@{}lll@{}}
+    \toprule
+                      & SWDA  & AMI-DA \\ \midrule
+    \texttt{BERT-NL}  & 77.07 & 67.06       \\ 
+    \texttt{BERT-L}   & 76.93 & 67.12       \\ \midrule
+    \texttt{CNN-NL}   & 75.08 & 63.46        \\
+    \texttt{CNN-L}    & 75.40 & 64.30        \\ \bottomrule
+
+  \end{tabular}
+  \caption{Comparison of models depending on using laughter in training phase.}
+\end{table}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{img/bertLvsNL.pdf}
+  \caption{Change in accuracy for each dialogue act. Positive changes when adding laughter are shown in blue. }
+\end{figure*}
+% TODO per dialogue act analysis
+% DONE compare impacts of CNN vs BERT
+% DONE for both AMI and SWDA
+% ?
 

### 2019-12-04 reports/ACL2020 Paper/acl2020-paper.tex
add to related work & background references

--- 2019-12-02 reports/ACL2020 Paper/acl2020-paper.tex
@@
 
+References
+\begin{itemize}
+  \item \citet{austinHowThingsWords2009} -- speeh acts
+  \item \citet{coreCodingDialogsDAMSL1997} -- DAMSL dialogue act tagging scheme. SWDA tags are based on this (I think AMI are too). Concept of multi-layer DA tags; forward/backward function
+  \item \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a} -- SWBD-DAMSL coders manual
+  \item \citet{devlinBERTPretrainingDeep2018} -- Original BERT paper
+  \item \citet{sunHowFineTuneBERT2019} -- recommendations for fine-tuninig BERT
+  \item \citet{mikolovDistributedRepresentationsWords2013} -- word2vec
+  \item \citet{petersTuneNotTune2019} -- when and how to fine-tune pre-trained representations
+  \item \citet{kimConvolutionalNeuralNetworks2014} -- CNN sentence representation
+\end{itemize}
+
 \section{Related work} % add references first
-%  - BERT domain transfer
-%  - BERT/LM for DAR
+Dialogue act recoginition
+\begin{itemize}
+  \item \citet{pragstVectorRepresentationUtterances2018} -- dialogue vector models.
+Uses vector-manual DA tag correspondance to argue for semantic relevance of their vector models (related to how we use DA tagging to verrify BERT usefulness)
+  \item \citet{cerisaraEffectsUsingWord2vec2017} -- standard pre-trained word embeddings do not help for DAR in any of three tested languages (English, French, Czech)
+  \item \citet{kalchbrennerRecurrentConvolutionalNeural2013} -- DAR model similar to our architecture. Uses an RNN ``discourse model'' and a CNN similar to our baseline encoder
+  \item \citet{stolckeDialogueActModeling2000} -- OG DAR model. Uses an HMM with various lexical and prosodic features
+  \item \citet{khanpourDialogueActClassification2016} -- Deep LSTM utt representation. No notion of context. Finds word vectors are useful.
+  \item \citet{tranPreservingDistributionalInformation2017} -- Sequential DA prediction with uncertainty propegation
+  \item \citet{chenDialogueActRecognition2017} -- SOTA? SWDA DAR using attention and CRF over utterances
+  \item \citet{ortegaNeuralbasedContextRepresentation2017} -- SWDA DAR with attention-based context representations and CNN utterance representations
+  \item \citet{shenNeuralAttentionModels2016} -- Uses attention for utt encoding in DAR. No notion of context, I think.
+  \item \citet{tranHierarchicalNeuralModel2017} -- RNNs at both the utteranec and dialogue level. Also attention. Very similar to our architecture.
+\end{itemize}
+
+Pre-training/transfer learning for dialogue
+\begin{itemize}
+  \item \citet{mehriStructuredFusionNetworks2019} -- ``Structured fusion networks''. Traditional dialogue system design with neural models.
+  \item \citet{chenSemanticallyConditionedDialog2019a} -- uses BERT for response generation
+  \item \citet{baoPLATOPretrainedDialogue2019} -- pre-traininig for dialogue generation
+  \item \citet{mehriPretrainingMethodsDialog2019} -- looks at various dialogue tasks using pre-training, including DAR and using BERT
+  \item \citet{vigComparisonTransferLearningApproaches} -- Transfer learning for response selection
+\end{itemize}
 
@@
 % - compare frozen with no dialogue pre-training vs pre-trained on dialogue w.r.t. L/NL (same as in Experiment 1)
+\begin{itemize}
+  \item Setup
+    \begin{itemize}
+      \item we do additional pre-training for the BERT encoder on in-domain data
+      \item note: this is sometimes referred to as fine-tuning, but we reserve that term for task-specific training of the encoder model
+
+      \item SWDA/AMI (excluding dialogues in the DAR test set)
+      \item 10 epoch AMI / 10 epochs SWBD / 5 epochs of each
+    \end{itemize}
+\end{itemize}
 
@@
 \section{Discussion} % add items to discuss
+\begin{itemize}
+  \item RoBERTa training scheme finds that next sentence prediction is of little importance.
+Is this true for us too?
+(suspect not due to discourse importance).
+see: https://github.com/huggingface/transformers/issues/1622
+\end{itemize}
 
-\bibliography{anthology,acl2020}
+\bibliography{acl2020}
 \bibliographystyle{acl_natbib}

### 2019-12-04 reports/ACL2020 Paper/acl2020-paper.tex
add model section

@@
 \usepackage{booktabs}
+\usepackage{tikz}
+\usepackage{amsmath}
 
@@
 \section{Model} % Bill
+
+Our DAR model has two components: an utterance encoder, and a sequence model that predicts the dialogue act tag (figure \ref{fig:model-architecture}).
+Since we are primarily interested in comparing different utterance encoders, we use a simple RNN as the sequence model in every configuration. 
+The RNN takes the encoded utterance as input at each time step
+Its hidden state is passed to a simple linear classification layer over dilague act tags.
+Conceptually, the encoded utterance represents the context-agnostic semantic content of the utterance, and the hidden state of the RNN represents the discourse context.
+
+\begin{figure*}
+  \include{model}
+  \caption{DAR model architecture}
+  \label{fig:model-architecture}
+\end{figure*}
 %  - DAR model -> utt encoder, RNN sequence tagger

### 2019-12-04 reports/ACL2020 Paper/acl2020-paper.tex

@@
 \usepackage{amsmath}
+\usepackage{graphicx}
 

### 2019-12-04 reports/ACL2020 Paper/acl2020-paper.tex
Add chart for AMI

@@
 Dialogue, especially spoken dialogue, is radically different from the kind of data that neural language models are prestrained on.
-Not only is the internal structure of contributions different---with features such as disfluencies, repair, incomplete sentences, and various vocal sounds---but the sequential structure of the discourse is also very different.
-In dialouge speakers take turns and switch perpsectives.
-More generally, the way that utterances contribute and cohere to the discourse is different from the relationship between sentences in a piece of written text.
-
-One important dialogical feature missing from text data is laughter.
-In the Switchboard dialogue corpus, laughter appears in approximately \%X of utterances.
-Laughter also relates to the discourse structure of dialogue. 
-Laughables.
-Also useful for predicting DAs (is that already a result?)
-
-In this work, we investigate whether BERT, a well-know pre-trained language model, is useful for dialogue.
-We use dialogue act recoginition as a proxy task, since both the interal content of conributions, and their sequential structure have bearing on the task.
-
-\paragraph{Fine-tuning and laughter}
-Since the laughter token doesn't appear in the original BERT vocabulary, only fine-tuned models can meaningfully make use of laughter in utterance representations. 
-This gives us another opportunity to assess whether laughter is useful in dialogue act recognition.
-We find that although \%4.6 of utterances in SWDA contain laughter, \%7.3 of utterances misclassified by \texttt{BERT} but correctly classified by \texttt{BERT-FT} contain laughter, suggesting that the fine-tuned model utterance encoder is making use of laughter.
-For AMI-DA, the effect is less pronounced, but still present§: \%8.5 of utterances contain laughter, and \%9.6 of utterances where fine-tuning makes a difference contain laughter.
-
-\section{Background} % Vlad
-%  - dialogue acts
-%  - laughter
-%  - BERT
-
-References
-\begin{itemize}
-  \item \citet{austinHowThingsWords2009} -- speeh acts
-  \item \citet{coreCodingDialogsDAMSL1997} -- DAMSL dialogue act tagging scheme. SWDA tags are based on this (I think AMI are too). Concept of multi-layer DA tags; forward/backward function
-  \item \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a} -- SWBD-DAMSL coders manual
-  \item \citet{devlinBERTPretrainingDeep2018} -- Original BERT paper
-  \item \citet{sunHowFineTuneBERT2019} -- recommendations for fine-tuninig BERT
-  \item \citet{mikolovDistributedRepresentationsWords2013} -- word2vec
-  \item \citet{petersTuneNotTune2019} -- when and how to fine-tune pre-trained representations
-  \item \citet{kimConvolutionalNeuralNetworks2014} -- CNN sentence representation
-\end{itemize}
-
-\section{Related work} % add references first
-Dialogue act recoginition
-\begin{itemize}
-  \item \citet{pragstVectorRepresentationUtterances2018} -- dialogue vector models.
-Uses vector-manual DA tag correspondance to argue for semantic relevance of their vector models (related to how we use DA tagging to verrify BERT usefulness)
-  \item \citet{cerisaraEffectsUsingWord2vec2017} -- standard pre-trained word embeddings do not help for DAR in any of three tested languages (English, French, Czech)
-  \item \citet{kalchbrennerRecurrentConvolutionalNeural2013} -- DAR model similar to our architecture. Uses an RNN ``discourse model'' and a CNN similar to our baseline encoder
-  \item \citet{stolckeDialogueActModeling2000} -- OG DAR model. Uses an HMM with various lexical and prosodic features
-  \item \citet{khanpourDialogueActClassification2016} -- Deep LSTM utt representation. No notion of context. Finds word vectors are useful.
-  \item \citet{tranPreservingDistributionalInformation2017} -- Sequential DA prediction with uncertainty propegation
-  \item \citet{chenDialogueActRecognition2017} -- SOTA? SWDA DAR using attention and CRF over utterances
-  \item \citet{ortegaNeuralbasedContextRepresentation2017} -- SWDA DAR with attention-based context representations and CNN utterance representations
-  \item \citet{shenNeuralAttentionModels2016} -- Uses attention for utt encoding in DAR. No notion of context, I think.
-  \item \citet{tranHierarchicalNeuralModel2017} -- RNNs at both the utteranec and dialogue level. Also attention. Very similar to our architecture.
-\end{itemize}
-
-Pre-training/transfer learning for dialogue
-\begin{itemize}
-  \item \citet{mehriStructuredFusionNetworks2019} -- ``Structured fusion networks''. Traditional dialogue system design with neural models.
-  \item \citet{chenSemanticallyConditionedDialog2019a} -- uses BERT for response generation
-  \item \citet{baoPLATOPretrainedDialogue2019} -- pre-traininig for dialogue generation
-  \item \citet{mehriPretrainingMethodsDialog2019} -- looks at various dialogue tasks using pre-training, including DAR and using BERT
-  \item \citet{vigComparisonTransferLearningApproaches} -- Transfer learning for response selection
-\end{itemize}
-
-\section{Data}
-We perform experiments on the Switchboard Dialogue Act Corpus (SWDA), which is a subset of the larger Switchboard corpus, and the dialogue act-tagged portion of the AMI Meeting Corpus (AMI-DA).
-
-% - DA distribution              % Vlad
+Not only is the internal structure of contributions differ% - DA distribution              % Vlad
 % - Laughter frequencies per DA  % Vlad
@@
 Therefore, we train another version of each model: one containing laughters (L) and with laughters left out (NL), and compare their performances in DAR task.
-
+From the results (see Table~\ref{tab:laughter}) we can conclude that .
 \begin{table}
+  \label{tab:laughter}
   \centering
@@
   \centering
-  \includegraphics[width=\textwidth]{img/bertLvsNL.pdf}
-  \caption{Change in accuracy for each dialogue act. Positive changes when adding laughter are shown in blue. }
+  \includegraphics[width=\textwidth]{img/SWDA-bertLvsNL.pdf}
+  \caption{Change in accuracy for each SWDA dialogue act. Positive changes when adding laughter are shown in blue. Vertical bars indicate how often dialogue act is associated with laughter.}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{img/AMI-DA-bertLvsNL.pdf}
+  \caption{Change in accuracy for each AMI dialogue act. Positive changes when adding laughter are shown in blue. Vertical bars indicate how often dialogue act is associated with laughter.}
 \end{figure*}

### 2019-12-04 analysis/ACL/analyse.py
Adapt analysis to AMI

@@ -10,11 +10,10 @@ import json
 
 from eval_model import get_max_val_loss
 from swda import swda
-corpus = swda.CorpusReader('../../data/SWDA/swda')
 
 parser = argparse.ArgumentParser()
 parser.add_argument('corpus', choices=['SWDA', 'AMI-DA'],
-        help='Which dialouge act corpus to analyse.')
+        help='Which dialogue act corpus to analyse.')
 parser.add_argument('-d','--data-dir', default='../../data',
         help='Data storage directory.')
 args = parser.parse_args()
@@ -32,15 +31,26 @@ def corpus_data():
     das_postL = defaultdict(int)
     # DAs associated with laughter
     das_assocL = defaultdict(int)
-    
-    for trans in corpus.iter_transcripts():
-        utts = [(u.damsl_act_tag(), u.text.lower()) for u in list(trans.utterances)]
-        for pre, utt, post in zip(['@@@@@']+utts, utts, (utts+['@@@@@'])[1:]):
-            das[utt[0]] += 1
-            if '<laughter>' in utt[1]:
-                das_L[utt[0]] += 1
-            if '<laughter>' in " ".join([pre[1], utt[1], post[1]]):
-                das_assocL[utt[0]] += 1
+    if args.corpus == 'SWDA':
+        corpus = swda.CorpusReader('../../data/SWDA/swda')
+        for trans in corpus.iter_transcripts():
+            utts = [(u.damsl_act_tag(), u.text.lower()) for u in list(trans.utterances)]
+            for pre, utt, post in zip(['@@@@@']+utts, utts, (utts+['@@@@@'])[1:]):
+                das[utt[0]] += 1
+                if '<laughter>' in utt[1]:
+                    das_L[utt[0]] += 1
+                if '<laughter>' in " ".join([pre[1], utt[1], post[1]]):
+                    das_assocL[utt[0]] += 1
+    elif args.corpus == 'AMI-DA':
+        transcripts = json.load(open(f'../../data/AMI-DA_train.json')) + json.load(open('../../data/AMI-DA_val.json')) + json.load(open('../../data/AMI-DA_test.json'))
+        for trans in transcripts:
+            utts = [(z[0], z[1]) for z in zip(trans['da_tags'], trans['utts'])]
+            for pre, utt, post in zip(['@@@@@']+utts, utts, (utts+['@@@@@'])[1:]):
[…]

### 2019-12-05 reports/ACL2020 Paper/acl2020-paper.tex
add experiment 3 analysis

--- 2019-12-04 reports/ACL2020 Paper/acl2020-paper.tex
@@
 
-\paragraph{Fine-tuning and laughter}
-Since the laughter token doesn't appear in the original BERT vocabulary, only fine-tuned models can meaningfully make use of laughter in utterance representations. 
-This gives us another opportunity to assess whether laughter is useful in dialogue act recognition.
-We find that although \%4.6 of utterances in SWDA contain laughter, \%7.3 of utterances misclassified by \texttt{BERT} but correctly classified by \texttt{BERT-FT} contain laughter, suggesting that the fine-tuned model utterance encoder is making use of laughter.
-For AMI-DA, the effect is less pronounced, but still present§: \%8.5 of utterances contain laughter, and \%9.6 of utterances where fine-tuning makes a difference contain laughter.
+\paragraph{Contributions}
+The main results of this paper have to do with to the usefulness of language model fine-tuning for DAR, 
+the impact of laughter on DAR, and the relationship between the two.
+\begin{itemize}
+  \item Laughter is useful for dialogue act recoginition (\S\ref{sec:experiment1}).
+  \item The impact of laughter is different for different dialogue acts. [Bigger for forward/backward?] (\S\ref{sec:experiment1})
+  \item Standard BERT pre-traininig is useful for DAR, but the impact of pre-training is smaller than than of fine-tuning (\S\ref{sec:experiment2})
+  \item 
+\end{itemize}
 
@@
   \item \citet{kimConvolutionalNeuralNetworks2014} -- CNN sentence representation
+  \item \citet{stolckeDialogueActModeling2000} -- OG DAR model. Uses an HMM with various lexical and prosodic features
 \end{itemize}
@@
   \item \citet{kalchbrennerRecurrentConvolutionalNeural2013} -- DAR model similar to our architecture. Uses an RNN ``discourse model'' and a CNN similar to our baseline encoder
-  \item \citet{stolckeDialogueActModeling2000} -- OG DAR model. Uses an HMM with various lexical and prosodic features
   \item \citet{khanpourDialogueActClassification2016} -- Deep LSTM utt representation. No notion of context. Finds word vectors are useful.
@@
   \hspace{1em} 1155 in SWDA               & \hspace{1em} 139 in AMI-DA                           \\
-400 utterances             & 118k utterances                         \\
+400k utterances             & 118k utterances                         \\
 3M tokens                  & 1.2M tokens                             \\ \bottomrule
@@
 
-Our DAR model has two components: an utterance encoder, and a sequence model that predicts the dialogue act tag (figure \ref{fig:model-architecture}).
+We employ a simple DAR model with two components: an encoder that vectorizes utterances, and a sequence model that predicts dialogue act tags from the vectorized utterances (figure \ref{fig:model-architecture}).
 Since we are primarily interested in comparing different utterance encoders, we use a simple RNN as the sequence model in every configuration. 
@@
 Conceptually, the encoded utterance represents the context-agnostic semantic content of the utterance, and the hidden state of the RNN represents the discourse context.
+
+As a baseline utterance encoder, we use a word-level CNN with window sizes of 3, 4, and 5, each with 100 feature maps \citep{kimConvolutionalNeuralNetworks2014}. 
+The model uses 100-dimensional word embeddings, which are initialized with pre-trained gloVe vectors in some configurations \citep{penningtonGloveGlobalVectors2014}.
+
+For the BERT utterance encoder, we use the BERT-BASE model with hidden size of 768 and 12 transformer layers and self-attention heads \citep[][see \S3.1]{devlinBERTPretrainingDeep2018}.
+We use the un-cased model implemenetd by \citet{wolfHuggingFaceTransformersStateoftheart2019}.
 
@@
 \section{Experiments}
-\subsection{Experiment 1: Impact of laughter}   % Vlad
+\subsection{Experiment 1: Impact of laughter} \label{sec:experiment1}   % Vlad
 In the first experiment we investigated whether laughter, as an example of a dialogue-specific signal, is a helpful feature for DAR.
@@
 
-\subsection{Experiment 2: Impact of pre-training} % Bill
+\subsection{Experiment 2: Impact of pre-training vs. fine-tuning} \label{sec:experiment2} % Bill
 % - compare i) pre-trained BERT with freezing ii) pretrained with no freezing iii) randolmly initialized
@@
 \begin{itemize}
-  \item \texttt{BERT} -- pre-trained BERT without fine-tuning (frozen during DAR training)
-  \item \texttt{BERT-FT} -- pre-trained BERT with fine-tuninig 
-  \item \texttt{BERT-RI} -- randomly initialized BERT with fine-tuning 
+  \item \texttt{BERT} -- pre-trained BERT without fine-tuning 
+  \item \texttt{BERT-FT} -- pre-trained BERT with DAR fine-tuninig 
+  \item \texttt{BERT-RI} -- randomly initialized BERT with dAR fine-tuning 
 \end{itemize}
@@
 \end{tabular}
-  \caption{Micro-average DAR accuracy}
+  \caption{Micro-average DAR recall}
   \label{table:exp2-avg}
@@
 
-To help answer these questions, we compare accuracy results of the above three models by dialogue act tag.
+To help answer these questions, we compare performance of the above three models by dialogue act tag.
 
@@
 
-\subsection{Experiment 3: Impact of dialogue pre-training} % Bill
+\paragraph{Fine-tuning and laughter}
+Since the laughter token doesn't appear in the original BERT vocabulary, only fine-tuned models can meaningfully make use of laughter in utterance representations. 
+This gives us another opportunity to assess whether laughter is useful in dialogue act recognition.
+We find that although \%4.6 of utterances in SWDA contain laughter, \%7.3 of utterances misclassified by \texttt{BERT} but correctly classified by \texttt{BERT-FT} contain laughter, suggesting that the fine-tuned encoder makes use of laughter.
+For AMI-DA, the effect is less pronounced, but still present§: \%8.5 of utterances contain laughter, and \%9.6 of utterances where fine-tuning makes a difference contain laughter.
+
+\subsection{Experiment 3: Impact of in-domain pre-training} \label{sec:experiment3} % Bill
 % - pre-train AMI+SWBD -> train SWDA/AMI-DA -> test SWDA/AMI-DA
@@
 % - compare frozen with no dialogue pre-training vs pre-trained on dialogue w.r.t. L/NL (same as in Experiment 1)
+
+Next, we assess the effect of in-domain pre-training of BERT's performance as an utterance encoder.\footnote{
+In-domain pre-training is sometimes referred to as fine-tuning, but we reserve that term for task-specific training on labeled data.}
+We construct pre-training corpora from the SWDA portion of the un-labelled Switchboard corpus and from the entire AMI corpus (including meetings with no human-annotated DA tags that are not included in the DAR training set).
+In both cases, we exclude dialogues that are reserved for DAR testing.
+
+We use the same pre-training task described by \citet{devlinBERTPretrainingDeep2018}, which combines masked token prediction and next sentence (utterance) detection. 
+Distractor utterances are drawn at random from another dialogue in the corpus
+and each epoch is generated separately so that different distractor sentences appear each time.
+We then performed DAR fine-tuning and inference with the in-domain pre-trained BERT models just as before.
+
+For AMI, in-domain pre-training offers a modest performance boost, but there is no discernable effect in the case of Switchboard.
+Indeed, when BERT is frozen during fine-tuning, the model that received no additional pre-training performs better by more than 3 percentage points (table \ref{tab:exp3-recall}).
+
+\begin{table}[]
+\begin{tabular}{@{}lll@{}}
+\toprule
+                       & SWDA  & AMI-DA \\ \midrule
+in-domain pre-training & 77.02 & 68.64  \\
+no fine-tuning         & 52.30 & 48.05  \\ \midrule
+standard pre-training  & 76.93 & 66.94  \\
+no fine-tuniing        & 55.61 & 46.59  \\ \bottomrule
+\end{tabular}
+  \caption{Micro-average DAR recall for different pre-training schemas.}
+  \label{tab:exp3-recall}
+\end{table}
+
+We found no discernable difference between pre-traininig on dialogues from the same corpus and pre-traininig on the combined corpus.
+These results could be explained by the relatively small size of the dialogue corpora.
+
 \begin{itemize}
@@
 
-\subsection{Experiment 4: Cross-domain pre-training (if time permits)} % Bill
+\subsection{Experiment 4: Cross-domain pre-training (if time permits)} \label{sec:experiment4} % Bill
 %  - cross-domain pre-training
@@
 see: https://github.com/huggingface/transformers/issues/1622
+  \item Issues related to working with transcribed speech: Different kinds of laughter are all represented by the same token.
+Does transcription orthography capture prosidy?
+We know prosidy is useful for DAR (Jurafsky).
 \end{itemize}

### 2019-12-05 analysis/ACL/util.py

@@ -1,0 +1,42 @@
+import sys
+sys.path.append("../..") # Adds package base dir to python modules path.
+from eval_model import get_max_val_loss
+import json
+import pandas as pd
+from collections import defaultdict
+import os
+
+
+def gen_model_preds_df(corpus, models, model_dirs):
+    """
+    corpus - one of: 'SWDA-L', 'SWDA-NL', 'AMI-L', 'AMI-NL'
+    """
+    with open(f'../../data/{corpus}_test.json') as f:
+        test_data = json.load(f)
+
+    test_data = [{
+        'dialogue_id': d['id'],
+        'utt_no': i,
+        'speaker':speaker,
+        'utt': utt,
+        'da_tag': da_tag} for d in test_data
+            for i, (speaker, utt, da_tag)
+            in enumerate(zip(d['speakers'], d['utts'], d['da_tags']))
+        ]
+
+    df = pd.DataFrame(test_data)
+    df = df.set_index(['dialogue_id', 'utt_no'])
+    
+    preds = defaultdict(lambda x: dict)
+    for model, model_dir in zip(models, model_dirs):
+        best_epoch, _ = get_max_val_loss(model_dir)
+        preds_file = os.path.join(model_dir, f'preds.E{best_epoch}.json')
+        with open(os.path.join(model_dir, preds_file), 'r') as f:
+            preds = json.load(f)
+            preds = [((u['dialogue_id'], u['utt_no']), pred_da)
+                        for pred_da, u in zip([da for d in preds for da in d], test_data)]
+            preds = list(zip(*preds))
+            preds = pd.Series(preds[1], index=preds[0])
+            df[model] = preds
+
+    return df

### 2019-12-05 reports/ACL2020 Paper/acl2020-paper.tex
remove section outline

@@
 
-\begin{itemize}
-  \item Setup
-    \begin{itemize}
-      \item we do additional pre-training for the BERT encoder on in-domain data
-      \item note: this is sometimes referred to as fine-tuning, but we reserve that term for task-specific training of the encoder model
-
-      \item SWDA/AMI (excluding dialogues in the DAR test set)
-      \item 10 epoch AMI / 10 epochs SWBD / 5 epochs of each
-    \end{itemize}
-\end{itemize}
-
 \subsection{Experiment 4: Cross-domain pre-training (if time permits)} \label{sec:experiment4} % Bill

### 2019-12-05 reports/ACL2020 Paper/acl2020-paper.tex
Update structure and Experiment 1

@@
 \usepackage{graphicx}
-
+\usepackage{natbib}
 % This is not strictly necessary, and may be commented out,
@@
 Laughter also relates to the discourse structure of dialogue. 
-Laughables.
+% Laughables.
 Also useful for predicting DAs (is that already a result?)
@@
   \item \citet{stolckeDialogueActModeling2000} -- OG DAR model. Uses an HMM with various lexical and prosodic features
-\end{itemize}
-
-\section{Related work} % add references first
-Dialogue act recoginition
-\begin{itemize}
-  \item \citet{pragstVectorRepresentationUtterances2018} -- dialogue vector models.
-Uses vector-manual DA tag correspondance to argue for semantic relevance of their vector models (related to how we use DA tagging to verrify BERT usefulness)
-  \item \citet{cerisaraEffectsUsingWord2vec2017} -- standard pre-trained word embeddings do not help for DAR in any of three tested languages (English, French, Czech)
-  \item \citet{kalchbrennerRecurrentConvolutionalNeural2013} -- DAR model similar to our architecture. Uses an RNN ``discourse model'' and a CNN similar to our baseline encoder
-  \item \citet{khanpourDialogueActClassification2016} -- Deep LSTM utt representation. No notion of context. Finds word vectors are useful.
-  \item \citet{tranPreservingDistributionalInformation2017} -- Sequential DA prediction with uncertainty propegation
-  \item \citet{chenDialogueActRecognition2017} -- SOTA? SWDA DAR using attention and CRF over utterances
-  \item \citet{ortegaNeuralbasedContextRepresentation2017} -- SWDA DAR with attention-based context representations and CNN utterance representations
-  \item \citet{shenNeuralAttentionModels2016} -- Uses attention for utt encoding in DAR. No notion of context, I think.
-  \item \citet{tranHierarchicalNeuralModel2017} -- RNNs at both the utteranec and dialogue level. Also attention. Very similar to our architecture.
-\end{itemize}
-
-Pre-training/transfer learning for dialogue
-\begin{itemize}
-  \item \citet{mehriStructuredFusionNetworks2019} -- ``Structured fusion networks''. Traditional dialogue system design with neural models.
-  \item \citet{chenSemanticallyConditionedDialog2019a} -- uses BERT for response generation
-  \item \citet{baoPLATOPretrainedDialogue2019} -- pre-traininig for dialogue generation
-  \item \citet{mehriPretrainingMethodsDialog2019} -- looks at various dialogue tasks using pre-training, including DAR and using BERT
-  \item \citet{vigComparisonTransferLearningApproaches} -- Transfer learning for response selection
 \end{itemize}
@@
 The RNN takes the encoded utterance as input at each time step
-Its hidden state is passed to a simple linear classification layer over dilague act tags.
+Its hidden state is passed to a simple linear classification layer over dialogue act tags.
 Conceptually, the encoded utterance represents the context-agnostic semantic content of the utterance, and the hidden state of the RNN represents the discourse context.
@@
 For the BERT utterance encoder, we use the BERT-BASE model with hidden size of 768 and 12 transformer layers and self-attention heads \citep[][see \S3.1]{devlinBERTPretrainingDeep2018}.
-We use the un-cased model implemenetd by \citet{wolfHuggingFaceTransformersStateoftheart2019}.
+We use the un-cased model implemented by \citet{wolfHuggingFaceTransformersStateoftheart2019}.
 
@@
 In the first experiment we investigated whether laughter, as an example of a dialogue-specific signal, is a helpful feature for DAR.
-Therefore, we train another version of each model: one containing laughters (L) and with laughters left out (NL), and compare their performances in DAR task.
-From the results (see Table~\ref{tab:laughter}) we can conclude that .
+Therefore, we train another version of each model: one containing laughs (\texttt{L}) and one with laughs left out (\texttt{NL}), and compare their performances in DAR task.
+Table~\ref{table:laughter-total-acc}) compares the results from applying the models with two different different utterance encoders (\texttt{BERT}, \texttt{CNN}).
+From observing the total accuracy scores, models appear to be almost unaffected by leaving out the laughters.
+On the other hand, we can observe differences in performance depending on the dialogue act, regardless how often laughter occurs in the current or adjacent utterances (see Figure~\ref{fig:swda-by-da} for Switchboard and Figure~\ref{fig:ami-by-da} for AMI corpus).
+
+In order to further investigate the differences we have grouped dialogue acts in Switchboard according to DAMSL coders manual \citep{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}.
+Different DA groups containing
 \begin{table}
-  \label{tab:laughter}
   \centering
@@
   \end{tabular}
-  \caption{Comparison of models depending on using laughter in training phase.}
+  \caption{Comparison of models depending on using laughter on the training phase. }
+  \label{table:laughter-total-acc}
+\end{table}
+
+\begin{table}
+  \label{tab:laughter}
+  \centering
+  \begin{tabular}{@{}lccc@{}}
+    \toprule
+    & \%lassoc & \%L  & $\Delta$ (mean acc.) \\ \midrule
+    Forward-CF & 11.86 & 4.59 & 11.40\\
+    Backward-CF & 11.57 & 3.03 & 4.30\\
+    Other & 12.71 & 4.40 & 2.39\\
+    CS & 20.63 & 14.17 & -1.50\\\bottomrule
+
+  \end{tabular}
+  \caption{Laughter impact by dialogue act group (SWDA, BERT), mean accuracy}
 \end{table}
@@
   \caption{Change in accuracy for each SWDA dialogue act. Positive changes when adding laughter are shown in blue. Vertical bars indicate how often dialogue act is associated with laughter.}
+    \label{fig:swda-by-da}
 \end{figure*}
@@
 \begin{figure*}
+  \label{fig:ami-by-da}
   \centering
@@
 
-\subsection{Experiment 4: Cross-domain pre-training (if time permits)} \label{sec:experiment4} % Bill
+%\subsection{Experiment 4: Cross-domain pre-training (if time permits)} \label{sec:experiment4} % Bill
 %  - cross-domain pre-training
+\section{Related work} % add references first
+Dialogue act recoginition
+\begin{itemize}
+  \item \citet{pragstVectorRepresentationUtterances2018} -- dialogue vector models.
+Uses vector-manual DA tag correspondance to argue for semantic relevance of their vector models (related to how we use DA tagging to verrify BERT usefulness)
+  \item \citet{cerisaraEffectsUsingWord2vec2017} -- standard pre-trained word embeddings do not help for DAR in any of three tested languages (English, French, Czech)
+  \item \citet{kalchbrennerRecurrentConvolutionalNeural2013} -- DAR model similar to our architecture. Uses an RNN ``discourse model'' and a CNN similar to our baseline encoder
+  \item \citet{khanpourDialogueActClassification2016} -- Deep LSTM utt representation. No notion of context. Finds word vectors are useful.
+  \item \citet{tranPreservingDistributionalInformation2017} -- Sequential DA prediction with uncertainty propegation
+  \item \citet{chenDialogueActRecognition2017} -- SOTA? SWDA DAR using attention and CRF over utterances
+  \item \citet{ortegaNeuralbasedContextRepresentation2017} -- SWDA DAR with attention-based context representations and CNN utterance representations
+  \item \citet{shenNeuralAttentionModels2016} -- Uses attention for utt encoding in DAR. No notion of context, I think.
+  \item \citet{tranHierarchicalNeuralModel2017} -- RNNs at both the utteranec and dialogue level. Also attention. Very similar to our architecture.
+\end{itemize}
+
+Pre-training/transfer learning for dialogue
+\begin{itemize}
+  \item \citet{mehriStructuredFusionNetworks2019} -- ``Structured fusion networks''. Traditional dialogue system design with neural models.
+  \item \citet{chenSemanticallyConditionedDialog2019a} -- uses BERT for response generation
+  \item \citet{baoPLATOPretrainedDialogue2019} -- pre-traininig for dialogue generation
+  \item \citet{mehriPretrainingMethodsDialog2019} -- looks at various dialogue tasks using pre-training, including DAR and using BERT
+  \item \citet{vigComparisonTransferLearningApproaches} -- Transfer learning for response selection
+\end{itemize}
 

### 2019-12-05 analysis/ACL/analyse.py
add group analysis

@@ -95,17 +95,18 @@ def compute_accuracy_for_da(da, test, pred):
     return accuracy(comp)
 
 DialogueActStats = namedtuple('DialogueActStats', 
-                              'nm name total total_ assoc_l assoc_l_ pre_l pre_l_ l l_ post_l post_l_ p1 p2')
+                              'nm name group total total_ assoc_l assoc_l_ pre_l pre_l_ l l_ post_l post_l_ p1 p2')
 class DialogueActStats(DialogueActStats):
     def __repr__(self):
-        stats = list(self._asdict().items())[2:]
+        stats = list(self._asdict().items())[3:]
         vals = "|".join([str(round(v, 7)) for k,v in stats])
-        return f'|{self.nm}|{self.name}|{vals}|'
+        return f'|{self.nm}|{self.name}|{self.group}|{vals}|'
 
 if __name__ == '__main__':
     models_dir = '/scratch/DistributionalDiscourse/models/'
     with open(args.corpus+'_dialogue-acts.json') as f:
         names = json.load(f)
+    groups = json.load(open(f'{args.corpus}_dialogue-acts-groups.json'))
     totals = calculate_totals()
     total_c = sum([t[1] for t in totals])
     assoc_c = sum([t[2] for t in totals])
@@ -133,7 +134,7 @@ if __name__ == '__main__':
         post_l_ = t[5] / t[1]
         p1acc = compute_accuracy_for_da(t[0], test, pred1)
         p2acc = compute_accuracy_for_da(t[0], test, pred2)
-        stats.append(DialogueActStats(t[0], names[key], t[1], total_, t[2], assoc_l_,
+        stats.append(DialogueActStats(t[0], names[key], groups[key], t[1], total_, t[2], assoc_l_,
                                       t[3], pre_l_, t[4], l_, t[5], post_l_, p1acc, p2acc))
     for s in stats:
         print(s)

### 2019-12-05 reports/ACL2020 Paper/acl2020-paper.tex
Add box plots

@@
 
-Recently, large-scale language models, trained on massive corpora of text data, have achieved state-of-the-art results on a variety of traditonal NLP tasks.
+Recently, large-scale language models, trained on massive corpora of text data, have achieved state-of-the-art results on a variety of traditional NLP tasks.
 We investigate whether such models might be useful for processing dialogue, and if so, whether they adapt to make use of dialogue-specific features.
@@
 Not only is the internal structure of contributions different---with features such as disfluencies, repair, incomplete sentences, and various vocal sounds---but the sequential structure of the discourse is also very different.
-In dialouge speakers take turns and switch perpsectives.
+In dialogue speakers take turns and switch perspectives.
 More generally, the way that utterances contribute and cohere to the discourse is different from the relationship between sentences in a piece of written text.
@@
 
-In this work, we investigate whether BERT, a well-know pre-trained language model, is useful for dialogue.
+In this work, we investigate whether BERT \citep{devlinBERTPretrainingDeep2018}, a well-know pre-trained language model, is useful for dialogue.
 We use dialogue act recoginition as a proxy task, since both the interal content of conributions, and their sequential structure have bearing on the task.
@@
   \item \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a} -- SWBD-DAMSL coders manual
-  \item \citet{devlinBERTPretrainingDeep2018} -- Original BERT paper
+  % \item \citet{devlinBERTPretrainingDeep2018} -- Original BERT paper 
   \item \citet{sunHowFineTuneBERT2019} -- recommendations for fine-tuninig BERT
@@
 % - DA distribution              % Vlad
-% - Laughter frequencies per DA  % Vlad
 
-% - AMI, SWBD + comparison table % Bill
 \begin{table}[]
@@
 \end{table}
+
+The distribution of laughs in different dialogue acts has a rather uniform shape with a few outliers (see box plots).
+Figures \ref{fig:swda-by-da} (for SWDA) and \ref{fig:ami-by-da} (for AMI-DA) provide a breakdown of dialogue act depending on whether current or adjacent utterances (the preceding utterance and the following one are counted as adjacent) contain a laughter.
+Note that SWDA has a ``Nonverbal'' dialogue act which is misguiding with respect to laughter, because utterances only containing a single laughter token fall into this category, however they can serve, for example, to acknowledge a statement or to deflect a question  \citep{mazzocconi2019phd}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\the\columnwidth]{img/box-swda.pdf}
+  \caption{Box plot for utterances associated with laughter for SWDA.
+On the left: proportion of DAs having laughter in one of the adjacent utterances, on the right: proportion of DAs containing laughter.
+}
+    \label{fig:box-swda}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\the\columnwidth]{img/box-ami.pdf}
+  \caption{Box plot for utterances associated with laughter for AMI-DA.
+On the left: proportion of DAs having laughter in one of the adjacent utterances, on the right: proportion of DAs containing laughter.
+}
+    \label{fig:box-ami}
+\end{figure}
+
+For SWDA corpus we also considered grouping the dialogue acts according to DAMSL coders manual \citep{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}: Forward-Communicative-Function (51.86\% of all DAs), Backwards-Communicative-Function (30.35\%), Other (9.04\%) and Communicative-Status (8.75\%).
+We observed even distribution of laughs in these groups, except the Communicative-Status group which contains ``Nonverbal'' dialogue acts.
 
@@
 Therefore, we train another version of each model: one containing laughs (\texttt{L}) and one with laughs left out (\texttt{NL}), and compare their performances in DAR task.
-Table~\ref{table:laughter-total-acc}) compares the results from applying the models with two different different utterance encoders (\texttt{BERT}, \texttt{CNN}).
+Table~\ref{table:laughter-total-acc}) compares the results from applying the models with two different utterance encoders (\texttt{BERT}, \texttt{CNN}).
 From observing the total accuracy scores, models appear to be almost unaffected by leaving out the laughters.
@@
 
-In order to further investigate the differences we have grouped dialogue acts in Switchboard according to DAMSL coders manual \citep{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}.
-Different DA groups containing
+In order to further investigate the differences, we looked at the dialogue act groups.
 \begin{table}

### 2019-12-05 reports/ACL2020 Paper/acl2020-paper.tex
Few typos

@@
   Basically we want to see if language models pre-trained on text data are useful for dialogue.
-  So we look at if BERT is useful for dialouge act recoginiton.
+  So we look at if BERT is useful for dialogue act recognition.
   But we want to know if it's really adapting to the domain, so we look at how it uses laughter, a phenomenon specific to dialogue.
@@
 
-\begin{table}
-  \label{tab:laughter}
-  \centering
-  \begin{tabular}{@{}lccc@{}}
-    \toprule
-    & \%lassoc & \%L  & $\Delta$ (mean acc.) \\ \midrule
-    Forward-CF & 11.86 & 4.59 & 11.40\\
-    Backward-CF & 11.57 & 3.03 & 4.30\\
-    Other & 12.71 & 4.40 & 2.39\\
-    CS & 20.63 & 14.17 & -1.50\\\bottomrule
+% \begin{table}
+%   \label{tab:laughter}
+%   \centering
+%   \begin{tabular}{@{}lccc@{}}
+%     \toprule
+%     & \%lassoc & \%L  & $\Delta$ (mean acc.) \\ \midrule
+%     Forward-CF & 11.86 & 4.59 & 11.40\\
+%     Backward-CF & 11.57 & 3.03 & 4.30\\
+%     Other & 12.71 & 4.40 & 2.39\\
+%     CS & 20.63 & 14.17 & -1.50\\\bottomrule
 
-  \end{tabular}
-  \caption{Laughter impact by dialogue act group (SWDA, BERT), mean accuracy}
-\end{table}
+%   \end{tabular}
+%   \caption{Laughter impact by dialogue act group (SWDA, BERT), mean accuracy}
+% \end{table}
 

### 2019-12-05 reports/ACL2020 Paper/acl2020-paper.tex
Tables for experiment 1

@@
   \includegraphics[width=\the\columnwidth]{img/box-swda.pdf}
-  \caption{Box plot for utterances associated with laughter for SWDA.
+  \caption{Box plot for utterances associated with laughter in SWDA.
 On the left: proportion of DAs having laughter in one of the adjacent utterances, on the right: proportion of DAs containing laughter.
@@
   \includegraphics[width=\the\columnwidth]{img/box-ami.pdf}
-  \caption{Box plot for utterances associated with laughter for AMI-DA.
+  \caption{Box plot for utterances associated with laughter in AMI-DA.
 On the left: proportion of DAs having laughter in one of the adjacent utterances, on the right: proportion of DAs containing laughter.
@@
 On the other hand, we can observe differences in performance depending on the dialogue act, regardless how often laughter occurs in the current or adjacent utterances (see Figure~\ref{fig:swda-by-da} for Switchboard and Figure~\ref{fig:ami-by-da} for AMI corpus).
-
-In order to further investigate the differences, we looked at the dialogue act groups.
 \begin{table}
   \centering
-  \begin{tabular}{@{}lll@{}}
+  \begin{tabular}{@{}lcccc@{}}
     \toprule
-                      & SWDA  & AMI-DA   \\ \midrule
-    \texttt{BERT-NL}  & 77.07 & 67.06       \\ 
-    \texttt{BERT-L}   & 76.93 & 67.12       \\ \midrule
-    \texttt{CNN-NL}   & 75.08 & 63.46        \\
-    \texttt{CNN-L}    & 75.40 & 64.30        \\ \bottomrule
+                      & \multicolumn{2}{c}{SWDA} & \multicolumn{2}{c}{AMI-DA} \\ \midrule
+                      & macro-F1 & acc. & macro-F1 & acc.       \\ 
+    \texttt{BERT-NL}  & 38.10 & 77.07 & 49.09 & 67.06       \\ 
+    \texttt{BERT-L}   & 45.99 & 76.93 & 50.17 & 67.12       \\ \midrule
+    \texttt{CNN-NL}   & 37.23 & 75.08 & 38.37 & 63.46        \\
+    \texttt{CNN-L}    & 27.59 & 75.40 & 37.94 & 64.30        \\ \bottomrule
 
@@
 
-% \begin{table}
-%   \label{tab:laughter}
-%   \centering
-%   \begin{tabular}{@{}lccc@{}}
-%     \toprule
-%     & \%lassoc & \%L  & $\Delta$ (mean acc.) \\ \midrule
-%     Forward-CF & 11.86 & 4.59 & 11.40\\
-%     Backward-CF & 11.57 & 3.03 & 4.30\\
-%     Other & 12.71 & 4.40 & 2.39\\
-%     CS & 20.63 & 14.17 & -1.50\\\bottomrule
+In order to further investigate the differences, we looked at the dialogue act groups.
 
-%   \end{tabular}
-%   \caption{Laughter impact by dialogue act group (SWDA, BERT), mean accuracy}
-% \end{table}
+\begin{table}
+  \centering
+  \begin{tabular}{@{}llcc@{}}
+    \toprule
+    &                  & Forward-CF  & Backward-CF   \\ \midrule
+    SWDA &\texttt{BERT-NL}  & 92.54 & 91.67       \\ 
+         &\texttt{BERT-L}   & 95.42 & 90.91       \\ 
+         &\texttt{CNN-NL}   & 93.30 & 90.85        \\
+         &\texttt{CNN-L}    & 94.64 & 90.13        \\ \midrule
+    AMI  &\texttt{BERT-NL}  & 87.77 & 80.83       \\ 
+         &\texttt{BERT-L}   & 87.36 & 79.87       \\
+         &\texttt{CNN-NL}   & 91.85 & 71.21        \\
+         &\texttt{CNN-L}    & 91.25 & 71.28        \\    \bottomrule
+  \end{tabular}
+  \caption{Comparison of models depending on using laughter on the training phase. }
+  \label{table:laughter-total-acc}
+\end{table}
 

### 2019-12-06 reports/ACL2020 Paper/acl2020-paper.tex
Add example, update Experiment 1

@@
 \usepackage{microtype}
+
+\usepackage{tabularx}
+\newcolumntype{L}{>{\raggedright\arraybackslash}X}
 
@@
 One important dialogical feature missing from text data is laughter.
-In the Switchboard dialogue corpus, laughter appears in approximately \%X of utterances.
+In the Switchboard dialogue corpus, laughter comes about every 200 tokens.
 Laughter also relates to the discourse structure of dialogue. 
@@
 Also useful for predicting DAs (is that already a result?)
+
+\begin{table}
+  \centering
+  \begin{tabularx}{\linewidth}{llL}
+    \toprule
+    Speaker & DA & Utterance \\ \midrule
+    A	&sd	& Well, I'm the kind of cook that I don't normally measure things,  \\
+    A	&sd	& I just kind of throw them in \\
+    A	&sd	& and, you know, I don't to the point of, you know, measuring down to the exact amount that they say.  \\
+    B	&sv	& That means you're a real cook. \\
+    A	&bd	& \texttt{<Laughter>} Oh, is that what it means.  \\
+    A	&b	& Uh-huh.  \\
+    A	&x	& \texttt{<Laughter>}.\\
+             \bottomrule
+  \end{tabularx}
+  \caption{Example from the SWDA corpus (sw2827).
+Dialogue acts: \emph{sd}---Statement-non-opinion, \emph{sv}---Statement-opinion, \emph{bd}---Downplayer, \emph{b}---Backchannel, \emph{x}---Non-verbal.
+}
+\end{table}
 
@@
 Table~\ref{table:laughter-total-acc}) compares the results from applying the models with two different utterance encoders (\texttt{BERT}, \texttt{CNN}).
-From observing the total accuracy scores, models appear to be almost unaffected by leaving out the laughters.
-On the other hand, we can observe differences in performance depending on the dialogue act, regardless how often laughter occurs in the current or adjacent utterances (see Figure~\ref{fig:swda-by-da} for Switchboard and Figure~\ref{fig:ami-by-da} for AMI corpus).
+First of all, we can see that \texttt{BERT} utterance encoder outperforms \texttt{CNN} in all the cases.
+From observing the effect of laughters, we can see differences in performance depending on the dialogue act, regardless how often laughter occurs in the current or adjacent utterances (see Figure~\ref{fig:swda-by-da} for Switchboard and Figure~\ref{fig:ami-by-da} for AMI corpus).
+The strongest evidence for laughter as a helpful feature was found in SWDA for the \texttt{BERT} utterance encoder, where macro-F1 score increases by 7.89 percentage points.
+
 \begin{table}
@@
 In order to further investigate the differences, we looked at the dialogue act groups.
+Mapping all dialogue acts into four groups allows direct comparison between model performances in SWDA and AMI-DA.
+Table~\ref{table:laughter-group-acc} compares accuracies between the two main groups: Forward-Communicative-Function and Backward-Communicative-Function (82.3\% of all DAs in SWDA and 76.7\% in AMI-DA).
+Our models tend to perform better for Forward-Communicative-Function group irrespective of presence the corpus and the presence of laughs.
+Also, our models perform better for AMI-DA corpus.
+Overall performance in these groups appears to be unaffected by presence of laughs.
 
@@
     \toprule
-    &                  & Forward-CF  & Backward-CF   \\ \midrule
+    &                  & Forward-CF  & Backwards-CF   \\ \midrule
     SWDA &\texttt{BERT-NL}  & 92.54 & 91.67       \\ 
@@
   \caption{Comparison of models depending on using laughter on the training phase. }
-  \label{table:laughter-total-acc}
+  \label{table:laughter-group-acc}
 \end{table}
 
+% to appendix?
 \begin{figure*}
@@
 \begin{figure*}
-  \label{fig:ami-by-da}
   \centering
@@
   \caption{Change in accuracy for each AMI dialogue act. Positive changes when adding laughter are shown in blue. Vertical bars indicate how often dialogue act is associated with laughter.}
+    \label{fig:ami-by-da}
   \end{figure*}
+
+%
 % TODO per dialogue act analysis

### 2019-12-06 analysis/ACL/util.py
Notebook for Experiment 1. Grouping option in util.

@@ -7,22 +7,34 @@ from collections import defaultdict
 import os
 
 
-def gen_model_preds_df(corpus, models, model_dirs):
+def gen_model_preds_df(corpus, models, model_dirs,group=False):
     """
     corpus - one of: 'SWDA-L', 'SWDA-NL', 'AMI-L', 'AMI-NL'
     """
     with open(f'../../data/{corpus}_test.json') as f:
         test_data = json.load(f)
-
-    test_data = [{
-        'dialogue_id': d['id'],
-        'utt_no': i,
-        'speaker':speaker,
-        'utt': utt,
-        'da_tag': da_tag} for d in test_data
-            for i, (speaker, utt, da_tag)
-            in enumerate(zip(d['speakers'], d['utts'], d['da_tags']))
-        ]
+    with open(f'{corpus}_dialogue-acts-groups.json') as f:
+        groups = json.load(f)
+        groups[None] = 'Other'
+    if not group:
+        test_data = [{
+            'dialogue_id': d['id'],
+            'utt_no': i,
+            'speaker':speaker,
+            'utt': utt,
+            'da_tag': da_tag} for d in test_data
+                     for i, (speaker, utt, da_tag)
+                     in enumerate(zip(d['speakers'], d['utts'], d['da_tags']))]
+    else:
+        test_data = [{
+            'dialogue_id': d['id'],
+            'utt_no': i,
+            'speaker':speaker,
+            'utt': utt,
+            'da_tag': groups[da_tag]} for d in test_data
+                     for i, (speaker, utt, da_tag)
+                     in enumerate(zip(d['speakers'], d['utts'], d['da_tags']))]
+        
 
     df = pd.DataFrame(test_data)
     df = df.set_index(['dialogue_id', 'utt_no'])
@@ -33,8 +45,12 @@ def gen_model_preds_df(corpus, models, model_dirs):
         preds_file = os.path.join(model_dir, f'preds.E{best_epoch}.json')
         with open(os.path.join(model_dir, preds_file), 'r') as f:
             preds = json.load(f)
-            preds = [((u['dialogue_id'], u['utt_no']), pred_da)
-                        for pred_da, u in zip([da for d in preds for da in d], test_data)]
+            if not group:
+                preds = [((u['dialogue_id'], u['utt_no']), pred_da)
+                         for pred_da, u in zip([da for d in preds for da in d], test_data)]
+            else:
+                preds = [((u['dialogue_id'], u['utt_no']), pred_da)
[…]

### 2019-12-06 reports/ACL2020 Paper/acl2020-paper.tex
Some structural rearrangements

@@
 Dialogue, especially spoken dialogue, is radically different from the kind of data that neural language models are prestrained on.
+On the example, from the Switchboard corpus shown in Table~\ref{table:example} it is evident that the syntactic structure of dialogue is very different from the written text, even if one imagines a script for a movie or a play.
 Not only is the internal structure of contributions different---with features such as disfluencies, repair, incomplete sentences, and various vocal sounds---but the sequential structure of the discourse is also very different.
@@
 }
+  \label{table:example}
 \end{table}
@@
 \paragraph{Contributions}
-The main results of this paper have to do with to the usefulness of language model fine-tuning for DAR, 
-the impact of laughter on DAR, and the relationship between the two.
+The main results of this paper have to do with to the usefulness of language model fine-tuning for DAR, the impact of laughter on DAR, and the relationship between the two.
 \begin{itemize}
-  \item Laughter is useful for dialogue act recoginition (\S\ref{sec:experiment1}).
-  \item The impact of laughter is different for different dialogue acts. [Bigger for forward/backward?] (\S\ref{sec:experiment1})
+  \item Laughter is useful for dialogue act recognition, and its impact varies across different dialogue acts (\S\ref{sec:experiment1}).
   \item Standard BERT pre-traininig is useful for DAR, but the impact of pre-training is smaller than than of fine-tuning (\S\ref{sec:experiment2})
   \item 
-\end{itemize}
-
-\section{Background} % Vlad
-%  - dialogue acts
-%  - laughter
-%  - BERT
-
-References
-\begin{itemize}
-  \item \citet{austinHowThingsWords2009} -- speeh acts
-  \item \citet{coreCodingDialogsDAMSL1997} -- DAMSL dialogue act tagging scheme. SWDA tags are based on this (I think AMI are too). Concept of multi-layer DA tags; forward/backward function
-  \item \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a} -- SWBD-DAMSL coders manual
-  % \item \citet{devlinBERTPretrainingDeep2018} -- Original BERT paper 
-  \item \citet{sunHowFineTuneBERT2019} -- recommendations for fine-tuninig BERT
-  \item \citet{mikolovDistributedRepresentationsWords2013} -- word2vec
-  \item \citet{petersTuneNotTune2019} -- when and how to fine-tune pre-trained representations
-  \item \citet{kimConvolutionalNeuralNetworks2014} -- CNN sentence representation
-  \item \citet{stolckeDialogueActModeling2000} -- OG DAR model. Uses an HMM with various lexical and prosodic features
 \end{itemize}
@@
   \centering
-  \includegraphics[width=\the\columnwidth]{img/box-swda.pdf}
+  \includegraphics[width=0.8\linewidth]{img/box-swda.pdf}
   \caption{Box plot for utterances associated with laughter in SWDA.
@@
   \centering
-  \includegraphics[width=\the\columnwidth]{img/box-ami.pdf}
+  \includegraphics[width=0.8\linewidth]{img/box-ami.pdf}
   \caption{Box plot for utterances associated with laughter in AMI-DA.
@@
 \section{Related work} % add references first
+For the background:
+
+References
+\begin{itemize}
+  \item \citet{austinHowThingsWords2009} -- speeh acts
+  \item \citet{coreCodingDialogsDAMSL1997} -- DAMSL dialogue act tagging scheme. SWDA tags are based on this (I think AMI are too). Concept of multi-layer DA tags; forward/backward function
+  \item \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a} -- SWBD-DAMSL coders manual
+  % \item \citet{devlinBERTPretrainingDeep2018} -- Original BERT paper 
+  \item \citet{sunHowFineTuneBERT2019} -- recommendations for fine-tuninig BERT
+  \item \citet{mikolovDistributedRepresentationsWords2013} -- word2vec
+  \item \citet{petersTuneNotTune2019} -- when and how to fine-tune pre-trained representations
+  \item \citet{kimConvolutionalNeuralNetworks2014} -- CNN sentence representation
+  \item \citet{stolckeDialogueActModeling2000} -- OG DAR model. Uses an HMM with various lexical and prosodic features
+\end{itemize}
+
 Dialogue act recoginition

### 2019-12-06 reports/ACL2020 Paper/acl2020-paper.tex
add macro stats to exp 2&3

--- 2019-12-05 reports/ACL2020 Paper/acl2020-paper.tex
@@
 \usepackage{booktabs}
+\usepackage{multirow}
 \usepackage{tikz}
@@
   \includegraphics[width=\the\columnwidth]{img/box-swda.pdf}
-  \caption{Box plot for utterances associated with laughter in SWDA.
+  \caption{Box plot for utterances associated with laughter for SWDA.
 On the left: proportion of DAs having laughter in one of the adjacent utterances, on the right: proportion of DAs containing laughter.
@@
   \includegraphics[width=\the\columnwidth]{img/box-ami.pdf}
-  \caption{Box plot for utterances associated with laughter in AMI-DA.
+  \caption{Box plot for utterances associated with laughter for AMI-DA.
 On the left: proportion of DAs having laughter in one of the adjacent utterances, on the right: proportion of DAs containing laughter.
@@
 
+\begin{figure*}
+  \include{model}
+  \caption{Simple neural dialogue act recognition sequence model}
+  \label{fig:model-architecture}
+\end{figure*}
+
 As a baseline utterance encoder, we use a word-level CNN with window sizes of 3, 4, and 5, each with 100 feature maps \citep{kimConvolutionalNeuralNetworks2014}. 
@@
 We use the un-cased model implemented by \citet{wolfHuggingFaceTransformersStateoftheart2019}.
-
-\begin{figure*}
-  \include{model}
-  \caption{DAR model architecture}
-  \label{fig:model-architecture}
-\end{figure*}
-%  - DAR model -> utt encoder, RNN sequence tagger
-%  - BERT encoder (12 heads, uncased,...)
-%  - baseline encoder
 
@@
 On the other hand, we can observe differences in performance depending on the dialogue act, regardless how often laughter occurs in the current or adjacent utterances (see Figure~\ref{fig:swda-by-da} for Switchboard and Figure~\ref{fig:ami-by-da} for AMI corpus).
+
+In order to further investigate the differences, we looked at the dialogue act groups.
 \begin{table}
   \centering
-  \begin{tabular}{@{}lcccc@{}}
+  \begin{tabular}{@{}lll@{}}
     \toprule
-                      & \multicolumn{2}{c}{SWDA} & \multicolumn{2}{c}{AMI-DA} \\ \midrule
-                      & macro-F1 & acc. & macro-F1 & acc.       \\ 
-    \texttt{BERT-NL}  & 38.10 & 77.07 & 49.09 & 67.06       \\ 
-    \texttt{BERT-L}   & 45.99 & 76.93 & 50.17 & 67.12       \\ \midrule
-    \texttt{CNN-NL}   & 37.23 & 75.08 & 38.37 & 63.46        \\
-    \texttt{CNN-L}    & 27.59 & 75.40 & 37.94 & 64.30        \\ \bottomrule
+                      & SWDA  & AMI-DA   \\ \midrule
+    \texttt{BERT-NL}  & 77.07 & 67.06       \\ 
+    \texttt{BERT-L}   & 76.93 & 67.12       \\ \midrule
+    \texttt{CNN-NL}   & 75.08 & 63.46        \\
+    \texttt{CNN-L}    & 75.40 & 64.30        \\ \bottomrule
 
@@
 
-In order to further investigate the differences, we looked at the dialogue act groups.
+% \begin{table}
+%   \label{tab:laughter}
+%   \centering
+%   \begin{tabular}{@{}lccc@{}}
+%     \toprule
+%     & \%lassoc & \%L  & $\Delta$ (mean acc.) \\ \midrule
+%     Forward-CF & 11.86 & 4.59 & 11.40\\
+%     Backward-CF & 11.57 & 3.03 & 4.30\\
+%     Other & 12.71 & 4.40 & 2.39\\
+%     CS & 20.63 & 14.17 & -1.50\\\bottomrule
 
-\begin{table}
-  \centering
-  \begin{tabular}{@{}llcc@{}}
-    \toprule
-    &                  & Forward-CF  & Backward-CF   \\ \midrule
-    SWDA &\texttt{BERT-NL}  & 92.54 & 91.67       \\ 
-         &\texttt{BERT-L}   & 95.42 & 90.91       \\ 
-         &\texttt{CNN-NL}   & 93.30 & 90.85        \\
-         &\texttt{CNN-L}    & 94.64 & 90.13        \\ \midrule
-    AMI  &\texttt{BERT-NL}  & 87.77 & 80.83       \\ 
-         &\texttt{BERT-L}   & 87.36 & 79.87       \\
-         &\texttt{CNN-NL}   & 91.85 & 71.21        \\
-         &\texttt{CNN-L}    & 91.25 & 71.28        \\    \bottomrule
-  \end{tabular}
-  \caption{Comparison of models depending on using laughter on the training phase. }
-  \label{table:laughter-total-acc}
-\end{table}
+%   \end{tabular}
+%   \caption{Laughter impact by dialogue act group (SWDA, BERT), mean accuracy}
+% \end{table}
 
@@
 \subsection{Experiment 2: Impact of pre-training vs. fine-tuning} \label{sec:experiment2} % Bill
-% - compare i) pre-trained BERT with freezing ii) pretrained with no freezing iii) randolmly initialized
-Next, we take a direct look at how pre-training affects BERT's performance as an utterance encoder for our DAR model.
-In particular, we consider the performance of DAR models with three different utterance encoders:
+Next, we analyze how pre-training affects BERT's performance as an utterance encoder.
+To do so, we consider the performance of DAR models with three different utterance encoders:
 \begin{itemize}
-  \item \texttt{BERT} -- pre-trained BERT without fine-tuning 
   \item \texttt{BERT-FT} -- pre-trained BERT with DAR fine-tuninig 
-  \item \texttt{BERT-RI} -- randomly initialized BERT with dAR fine-tuning 
+  \item \texttt{BERT-RI} -- randomly initialized BERT (with DAR fine-tuning)
+  \item \texttt{BERT-FZ} -- pre-trained BERT without fine-tuning (frozen during DAR training)
 \end{itemize}
@@
 \begin{table}[]
-\centering 
-\begin{tabular}{@{}lll@{}}
+\begin{tabular}{@{}clll@{}}
 \toprule
-                 & SWDA  & AMI-DA \\ \midrule
-\texttt{BERT}       & 55.61 & 46.59  \\
-\texttt{BERT-FT}    & 76.93 & 66.94  \\
-\texttt{BERT-RI}    & 73.80 & 61.53  
+                                                                                  &             & SWDA  & AMI-DA \\ \midrule
+\multirow{3}{*}{\begin{tabular}[c]{@{}c@{}}Micro-average\\ accuracy\end{tabular}} & \texttt{BERT-FT}     & 76.93 & 66.94  \\
+                                                                                  & \texttt{BERT-RI}     & 73.80 & 61.53  \\ 
+                                                                                  & \texttt{BERT-FZ}     & 55.61 & 46.59  \\ \midrule
+  \multirow{3}{*}{\begin{tabular}[c]{@{}c@{}}Macro-average\\ F1\end{tabular}}     & \texttt{BERT-FT}     & 45.99 & 50.03  \\
+                                                                                  & \texttt{BERT-RI}     & 32.18 & 33.45  \\ 
+                                                                                  & \texttt{BERT-FZ}     & 07.75 & 14.44  \\ \bottomrule
 \end{tabular}
-  \caption{Micro-average DAR recall}
-  \label{table:exp2-avg}
+  \caption{DAR performance comparison of BERT with standard pre-training and DAR fine-tuning (\texttt{BERT-FT}) vs.
+the same model without pre-training (\texttt{BERT-RI}) and without fine-tuning (\texttt{BERT-FZ}).}
+  \label{table:exp2}
 \end{table}
 
-The pre-trained model performs better than the randomly initialized model by several percentage points on both DA corpora (table \ref{table:exp2-avg}). 
-These results suggest that BERT's extensive pre-training do provide some useful information for dialogue act recoginition.
-However, we note that pre-training is not enough: the poor performance of the frozen \texttt{BERT} model indicates that fine-tuning is important for BERT's performance as an utterance encoder.
-These observations raise two questions.
-First, how does BERT's pre-training help with DAR? 
-And second, in what way are the representations learned by pre-trained BERT lacking?
-In other words, what is the contribution of fine-tuning?
+The pre-trained model is more accurate than the randomly initialized model by several percentage points on both DA corpora,
+suggesting that BERT's extensive pre-training does provide some useful information for recoginizing different dialogue acts (table \ref{table:exp2}).
+This performance boost is much more pronounced in the macro-averaged F1 score,
+which is explained by the fact that at the tag level, pre-training has a larger impact on less frequent tags.
 
-To help answer these questions, we compare performance of the above three models by dialogue act tag.
+A key asperation of transfer learning is to expose the model to phenomena that are too infrequent to learn from labeled training data alone.
+One explanation for pre-trained BERT's superrior performance on some infrequent dialogue acts is that it has learned to represent relevant features
+that the randomly initialized model was unable to learn due to their sparsity in the labeled training set.
+Indeed, a simple lexical probe supports this explanation: in utterances where the pre-trained model is correct and the randomly initalized model is not,
+the rarest word is 1.9 times rarer than is typcial of corpus as a whole.
+
+Comparing the performance of the fine-tuned encoder to that of the frozen model, we note that pre-training alone is not enough.
+The frozen model is heavily biased towards the most frequent tags, which explains its especially poor macro-average score (table \ref{table:exp2}).
+In SWDA, the model with the frozen encoder predicts one of the two most common tags (Statement-non-opinion or Acknowledge) \%86 of the time, whereas those two
+tags account for only \%51 of the ground truth tags.
+The fine-tuned model is much less biased; it predicts the two most common tags only \%59 of the time.
+
+%These observations raise two questions.
+%First, how does BERT's pre-training help with DAR? 
+%And second, in what way are the representations learned by pre-trained BERT lacking?
+%In other words, what is the contribution of fine-tuning?
+
+%To help answer these questions, we compare performance of the above three models by dialogue act tag.
 
@@
 This gives us another opportunity to assess whether laughter is useful in dialogue act recognition.
-We find that although \%4.6 of utterances in SWDA contain laughter, \%7.3 of utterances misclassified by \texttt{BERT} but correctly classified by \texttt{BERT-FT} contain laughter, suggesting that the fine-tuned encoder makes use of laughter.
-For AMI-DA, the effect is less pronounced, but still present§: \%8.5 of utterances contain laughter, and \%9.6 of utterances where fine-tuning makes a difference contain laughter.
+We find that although \%4.6 of utterances in SWDA contain laughter, 
+\%7.3 of utterances misclassified by the frozen model but correctly classified by the fine-tuned model contain laughter, 
+suggesting that the fine-tuned encoder makes use of laughter. 
+For AMI-DA, the effect is less pronounced, but still present: 
+overall, \%8.5 of utterances contain laughter, 
+compared to \%9.6 of utterances where fine-tuning makes a difference.
 
-\subsection{Experiment 3: Impact of in-domain pre-training} \label{sec:experiment3} % Bill
-% - pre-train AMI+SWBD -> train SWDA/AMI-DA -> test SWDA/AMI-DA
-% - pre-traing tasks: 1) next utterance, 2) masked token, 3) both ?
-% - compare frozen with no dialogue pre-training vs pre-trained on dialogue w.r.t. L/NL (same as in Experiment 1)
+\subsection{Experiment 3: Impact of dialogue pre-training} \label{sec:experiment3} % Bill
 
-Next, we assess the effect of in-domain pre-training of BERT's performance as an utterance encoder.\footnote{
-In-domain pre-training is sometimes referred to as fine-tuning, but we reserve that term for task-specific training on labeled data.}
-We construct pre-training corpora from the SWDA portion of the un-labelled Switchboard corpus and from the entire AMI corpus (including meetings with no human-annotated DA tags that are not included in the DAR training set).
+Next, we assess the effect of additional in-domain pre-training on BERT's performance as an utterance encoder.\footnote{
+In-domain pre-training is sometimes referred to as \textit{fine-tuning}, but we reserve that term for task-specific training on labeled data.}
+We construct pre-training corpora from the SWDA portion of the un-labelled Switchboard corpus and from the entire AMI corpus (including the 32 dialogues with no human-annotated DA tags that are not included in the DAR training set).
 In both cases, we exclude dialogues that are reserved for DAR testing.
@@
 and each epoch is generated separately so that different distractor sentences appear each time.
-We then performed DAR fine-tuning and inference with the in-domain pre-trained BERT models just as before.
+We pre-trained three BERT models: with Switchboard (10 epochs), AMI (10 epochs), and the combined corpus (5 epochs).
 
-For AMI, in-domain pre-training offers a modest performance boost, but there is no discernable effect in the case of Switchboard.
-Indeed, when BERT is frozen during fine-tuning, the model that received no additional pre-training performs better by more than 3 percentage points (table \ref{tab:exp3-recall}).
+For each dialogue act corpus, we trained DAR models with BERT encoders pre-trained on the in-domain corpus (\texttt{ID}) and the comined corpus (\texttt{CC}).
+As before, we experimented with both the fine-tuning and frozen conditions.
 
-\begin{table}[]
-\begin{tabular}{@{}lll@{}}
+The results are mixed.
+In-domain pre-training offers a modest boost in overall accuracy,
+but the macro-average scores are almost uniformly worse (table \ref{table:exp3}).
+%Indeed, when BERT is frozen during fine-tuning, the model that received no additional pre-training performs better by more than 3 percentage points (table \ref{tab:exp3-recall}).
+To fully assess the potential impact of in-domain pre-training, a larger dialogue corpus is required.
+
+\begin{table}
+\begin{tabular}{llrr}
 \toprule
-                       & SWDA  & AMI-DA \\ \midrule
-in-domain pre-training & 77.02 & 68.64  \\
-no fine-tuning         & 52.30 & 48.05  \\ \midrule
-standard pre-training  & 76.93 & 66.94  \\
-no fine-tuniing        & 55.61 & 46.59  \\ \bottomrule
+               &         &  SWBD &   AMI \\
+\midrule
+\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Micro-average\\ accuracy\end{tabular}} 
+               & \texttt{FT} & 76.93 & 66.95 \\
+               & \texttt{+ID-FT} & 77.02 & 68.66 \\
+               & \texttt{+CC-FT} & 77.35 & 68.58 \\ \cline{2-4}
+               & \texttt{FZ} & 55.61 & 46.60 \\
+               & \texttt{+ID-FZ} & 52.30 & 48.07 \\
+               & \texttt{+CC-FZ} & 51.14 & 42.42 \\ \hline
+\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Macro-average\\ F1 score\end{tabular}} 
+               & \texttt{FT} & 45.99 & 50.03 \\
+               & \texttt{+ID-FT} & 45.48 & 46.56 \\
+               & \texttt{+CC-FT} & 47.78 & 48.72 \\ \cline{2-4}
+               & \texttt{FZ} &  7.75 & 14.44 \\
+               & \texttt{+ID-FZ} &  6.46 & 14.43 \\
+               & \texttt{+CC-FZ} &  5.76 & 12.56 \\
+
+\bottomrule
 \end{tabular}
-  \caption{Micro-average DAR recall for different pre-training schemas.}
-  \label{tab:exp3-recall}
+  \caption{Comparing DAR performance of  with additional in-domain (\texttt{ID}) and cross-domain (\texttt{CC}) dialogue pre-training,
+    for both the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions.}
+  \label{table:exp3}
 \end{table}
-
-We found no discernable difference between pre-traininig on dialogues from the same corpus and pre-traininig on the combined corpus.
-These results could be explained by the relatively small size of the dialogue corpora.
 
@@
 \begin{itemize}
+  \item \citet{botheContextbasedApproachDialogue2018} -- uses an RNN for context (recently SOTA on SWDA)
   \item \citet{pragstVectorRepresentationUtterances2018} -- dialogue vector models.

### 2019-12-06 analysis/ACL/util.py

@@ -5,7 +5,27 @@ import json
 import pandas as pd
 from collections import defaultdict
 import os
+from sklearn import metrics
 
+
+def report_metrics(frames, conditions):
+    metric_funcs = [
+        lambda x,y: metrics.precision_score(x,y,average='macro'), 
+        lambda x,y: metrics.recall_score(x,y,average='macro'), 
+        lambda x,y: metrics.f1_score(x,y,average='macro'),
+        lambda x,y: metrics.precision_score(x,y,average='micro')]
+    metric_names = [
+        'macro precision',
+        'macro recall',
+        'macro f1',
+        'micro accuracy']
+    table = [[
+        metric(df['da_tag'], df[cond])
+            for df in frames]
+            for cond in conditions for metric in metric_funcs]
+    multiindex = [[c for c in conditions for m in metric_names],
+        [m for c in conditions for m in metric_names]]
+    return pd.DataFrame(table, columns=['SWBD', 'AMI'], index=multiindex)
 
 def gen_model_preds_df(corpus, models, model_dirs):
     """

### 2019-12-06 reports/ACL2020 Paper/acl2020-paper.tex

@@
 Also useful for predicting DAs (is that already a result?)
+
+\begin{table}
+  \centering
+  \begin{tabularx}{\linewidth}{llL}
+    \toprule
+    Speaker & DA & Utterance \\ \midrule
+    A	&sd	& Well, I'm the kind of cook that I don't normally measure things,  \\
+    A	&sd	& I just kind of throw them in \\
+    A	&sd	& and, you know, I don't to the point of, you know, measuring down to the exact amount that they say.  \\
+    B	&sv	& That means you're a real cook. \\
+    A	&bd	& \texttt{<Laughter>} Oh, is that what it means.  \\
+    A	&b	& Uh-huh.  \\
+    A	&x	& \texttt{<Laughter>}.\\
+             \bottomrule
+  \end{tabularx}
+  \caption{Example from the SWDA corpus (sw2827).
+Dialogue acts: \emph{sd}---Statement-non-opinion, \emph{sv}---Statement-opinion, \emph{bd}---Downplayer, \emph{b}---Backchannel, \emph{x}---Non-verbal.
+}
+  \label{table:example}
+\end{table}
 
@@
   \centering
-  \includegraphics[width=\the\columnwidth]{img/box-swda.pdf}
-  \caption{Box plot for utterances associated with laughter for SWDA.
+  \includegraphics[width=0.8\linewidth]{img/box-swda.pdf}
+  \caption{Box plot for utterances associated with laughter in SWDA.
 On the left: proportion of DAs having laughter in one of the adjacent utterances, on the right: proportion of DAs containing laughter.
@@
   \centering
-  \includegraphics[width=\the\columnwidth]{img/box-ami.pdf}
-  \caption{Box plot for utterances associated with laughter for AMI-DA.
+  \includegraphics[width=0.8\linewidth]{img/box-ami.pdf}
+  \caption{Box plot for utterances associated with laughter in AMI-DA.
 On the left: proportion of DAs having laughter in one of the adjacent utterances, on the right: proportion of DAs containing laughter.
@@
 Table~\ref{table:laughter-total-acc}) compares the results from applying the models with two different utterance encoders (\texttt{BERT}, \texttt{CNN}).
-From observing the total accuracy scores, models appear to be almost unaffected by leaving out the laughters.
-On the other hand, we can observe differences in performance depending on the dialogue act, regardless how often laughter occurs in the current or adjacent utterances (see Figure~\ref{fig:swda-by-da} for Switchboard and Figure~\ref{fig:ami-by-da} for AMI corpus).
+First of all, we can see that \texttt{BERT} utterance encoder outperforms \texttt{CNN} in all the cases.
+From observing the effect of laughters, we can see differences in performance depending on the dialogue act, regardless how often laughter occurs in the current or adjacent utterances (see Figure~\ref{fig:swda-by-da} for Switchboard and Figure~\ref{fig:ami-by-da} for AMI corpus).
+The strongest evidence for laughter as a helpful feature was found in SWDA for the \texttt{BERT} utterance encoder, where macro-F1 score increases by 7.89 percentage points.
 
-In order to further investigate the differences, we looked at the dialogue act groups.
 \begin{table}
   \centering
-  \begin{tabular}{@{}lll@{}}
+  \begin{tabular}{@{}lcccc@{}}
     \toprule
-                      & SWDA  & AMI-DA   \\ \midrule
-    \texttt{BERT-NL}  & 77.07 & 67.06       \\ 
-    \texttt{BERT-L}   & 76.93 & 67.12       \\ \midrule
-    \texttt{CNN-NL}   & 75.08 & 63.46        \\
-    \texttt{CNN-L}    & 75.40 & 64.30        \\ \bottomrule
+                      & \multicolumn{2}{c}{SWDA} & \multicolumn{2}{c}{AMI-DA} \\ \midrule
+                      & macro-F1 & acc. & macro-F1 & acc.       \\ 
+    \texttt{BERT-NL}  & 38.10 & 77.07 & 49.09 & 67.06       \\ 
+    \texttt{BERT-L}   & 45.99 & 76.93 & 50.17 & 67.12       \\ \midrule
+    \texttt{CNN-NL}   & 37.23 & 75.08 & 38.37 & 63.46        \\
+    \texttt{CNN-L}    & 27.59 & 75.40 & 37.94 & 64.30        \\ \bottomrule
 
@@
 
+In order to further investigate the differences, we looked at the dialogue act groups.
+Mapping all dialogue acts into four groups allows direct comparison between model performances in SWDA and AMI-DA.
+Table~\ref{table:laughter-group-acc} compares accuracies between the two main groups: Forward-Communicative-Function and Backward-Communicative-Function (82.3\% of all DAs in SWDA and 76.7\% in AMI-DA).
+Our models tend to perform better for Forward-Communicative-Function group irrespective of presence the corpus and the presence of laughs.
+Also, our models perform better for AMI-DA corpus.
+Overall performance in these groups appears to be unaffected by presence of laughs.
+
+\begin{table}
+  \centering
+  \begin{tabular}{@{}llcc@{}}
+    \toprule
+    &                  & Forward-CF  & Backwards-CF   \\ \midrule
+    SWDA &\texttt{BERT-NL}  & 92.54 & 91.67       \\ 
+         &\texttt{BERT-L}   & 95.42 & 90.91       \\ 
+         &\texttt{CNN-NL}   & 93.30 & 90.85        \\
+         &\texttt{CNN-L}    & 94.64 & 90.13        \\ \midrule
+    AMI  &\texttt{BERT-NL}  & 87.77 & 80.83       \\ 
+         &\texttt{BERT-L}   & 87.36 & 79.87       \\
+         &\texttt{CNN-NL}   & 91.85 & 71.21        \\
+         &\texttt{CNN-L}    & 91.25 & 71.28        \\    \bottomrule
+  \end{tabular}
+  \caption{Comparison of models depending on using laughter on the training phase. }
+  \label{table:laughter-group-acc}
+\end{table}
+
+% to appendix?
 \begin{figure*}

### 2019-12-06 reports/ACL2020 Paper/acl2020-paper.tex
add DAR background, abstract, title

@@
 
-\title{Instructions for ACL 2020 Proceedings}
+\title{Pre-trained encoders for dialogue: The case of laughter}
 
@@
 \begin{abstract}
-  Basically we want to see if language models pre-trained on text data are useful for dialogue.
-  So we look at if BERT is useful for dialogue act recognition.
-  But we want to know if it's really adapting to the domain, so we look at how it uses laughter, a phenomenon specific to dialogue.
+  The degree to which language models pre-trained on text data are useful for dialogue is an open question.
+  In this paper, we investigate the usefulness of BERT for dialogue act recognition.
+  We are interested in both how useful the pre-training proceedure is and 
+  how well the model adapts to the dialogue domain.
+  To confirm that the fine-tuned model learns to represent dialogical features, 
+  we look at how it uses laughter, a phenomenon specific to dialogue.
 \end{abstract}
@@
 Recently, large-scale language models, trained on massive corpora of text data, have achieved state-of-the-art results on a variety of traditional NLP tasks.
-We investigate whether such models might be useful for processing dialogue, and if so, whether they adapt to make use of dialogue-specific features.
+It is still uncertain whether these models might be useful for processing dialogue, and if so, whether they can adapt to make use of dialogue-specific features.
 
-Dialogue, especially spoken dialogue, is radically different from the kind of data that neural language models are prestrained on.
-On the example, from the Switchboard corpus shown in Table~\ref{table:example} it is evident that the syntactic structure of dialogue is very different from the written text, even if one imagines a script for a movie or a play.
+Dialogue, especially spoken dialogue, is radically different from the kind of data that neural language models are pre-trained on.
+In the example from the Switchboard corpus, shown in table~\ref{table:example}, it is evident that the syntactic structure of dialogue is very different from  written text, even if one imagines a script for a movie or a play.
 Not only is the internal structure of contributions different---with features such as disfluencies, repair, incomplete sentences, and various vocal sounds---but the sequential structure of the discourse is also very different.
-In dialogue speakers take turns and switch perspectives.
+In dialogue, speakers take turns and switch perspectives.
 More generally, the way that utterances contribute and cohere to the discourse is different from the relationship between sentences in a piece of written text.
@@
 % Laughables.
-Also useful for predicting DAs (is that already a result?)
+% Also (known to be?) useful for predicting DAs
 
@@
 In this work, we investigate whether BERT \citep{devlinBERTPretrainingDeep2018}, a well-know pre-trained language model, is useful for dialogue.
-We use dialogue act recoginition as a proxy task, since both the interal content of conributions, and their sequential structure have bearing on the task.
+We use dialogue act recognition  as a proxy task, since both the internal content of contributions, and their sequential structure have bearing on the task.
+
+\paragraph{Dialogue Act Recognition (DAR)}
+The concept of a dialogue act is based on that of speech acts \citep{austinHowThingsWords2009}.
+Breaking with classical semantic theory, speech act theory considers not only the propositional content of an utterance but also the actions, such as \emph{promising} or \emph{apologizing}, it carries out.
+Dialogue acts extend the concept of the speech act, with a focus on the interactional nature of most speech.
+DAMSL \citep{coreCodingDialogsDAMSL1997}, for example, is an influential dialogue act tagging scheme where dialogue acts are defined in part by whether they have a \emph{forward-looking} function (are expecting a response) or \emph{backward-looking} function (are in response to a previous utterance).
+
+DAR is the the task of labeling utterances with the dialogue act they perform 
+from a given set of dialogue act tags.
+As with other sequence labeling tasks in NLP, some notion of context is helpful in DAR.
+One of the first performant machine learning models for DAR was a Hidden Markov Model that used various lexical and prosodic features as input \citep{stolckeDialogueActModeling2000}.
+Most successful neural approaches also model some notion of context, 
+for example with a recurrent model \citep[e.g.,][]{botheContextbasedApproachDialogue2018} or conditional random field \citep[e.g.,][]{chenDialogueActRecognition2017}.
+
+\paragraph{Transfer learning for NLP}
+\begin{itemize}
+  \item \citet{mikolovDistributedRepresentationsWords2013} -- word2vec
+  % \item \citet{devlinBERTPretrainingDeep2018} -- Original BERT paper 
+  \item \citet{sunHowFineTuneBERT2019} -- recommendations for fine-tuning BERT
+  \item \citet{petersTuneNotTune2019} -- when and how to fine-tune pre-trained representations
+\end{itemize}
 
@@
   \item Laughter is useful for dialogue act recognition, and its impact varies across different dialogue acts (\S\ref{sec:experiment1}).
-  \item Standard BERT pre-traininig is useful for DAR, but the impact of pre-training is smaller than than of fine-tuning (\S\ref{sec:experiment2})
-  \item 
+  \item Standard BERT pre-training is useful for DAR, but the impact of pre-training is smaller than than of fine-tuning (\S\ref{sec:experiment2})
+  \item Performing additional in-domain pre-training shows promise for dialogue (\S\ref{sec:experiment3}), but further investigation with larger dialogue corpora is required.
 \end{itemize}
@@
 We perform experiments on the Switchboard Dialogue Act Corpus (SWDA), which is a subset of the larger Switchboard corpus, and the dialogue act-tagged portion of the AMI Meeting Corpus (AMI-DA). 
+SWDA is tagged with a set of 220 dialogue act tags which, following  \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a} we cluster into a smaller set of 42 tags.
+AMI uses a smaller tagset of 16 dialogue acts \citep{GuidelinesDialogueAct2005}.
 
@@
 
-We employ a simple DAR model with two components: an encoder that vectorizes utterances, and a sequence model that predicts dialogue act tags from the vectorized utterances (figure \ref{fig:model-architecture}).
-Since we are primarily interested in comparing different utterance encoders, we use a simple RNN as the sequence model in every configuration. 
-The RNN takes the encoded utterance as input at each time step
-Its hidden state is passed to a simple linear classification layer over dialogue act tags.
-Conceptually, the encoded utterance represents the context-agnostic semantic content of the utterance, and the hidden state of the RNN represents the discourse context.
+To test the effectiveness of BERT for DAR, we employ a simple neural architecture with two components: an encoder that vectorizes utterances, and a sequence model that predicts dialogue act tags from the vectorized utterances (figure \ref{fig:model-architecture}).
+Since we are primarily interested in comparing different utterance encoders, we use a basic RNN as the sequence model in every configuration. 
+The RNN takes the encoded utterance as input at each time step,
+and its hidden state is passed to a simple linear classification layer over dialogue act tags.
+Conceptually, the encoded utterance represents the context-agnostic semantic content of the utterance, and the hidden state of the RNN represents the full discourse context.
 
@@
 As a baseline utterance encoder, we use a word-level CNN with window sizes of 3, 4, and 5, each with 100 feature maps \citep{kimConvolutionalNeuralNetworks2014}. 
-The model uses 100-dimensional word embeddings, which are initialized with pre-trained gloVe vectors in some configurations \citep{penningtonGloveGlobalVectors2014}.
+The model uses 100-dimensional word embeddings, which are initialized with pre-trained gloVe vectors \citep{penningtonGloveGlobalVectors2014}.
 
-For the BERT utterance encoder, we use the BERT-BASE model with hidden size of 768 and 12 transformer layers and self-attention heads \citep[][see \S3.1]{devlinBERTPretrainingDeep2018}.
-We use the un-cased model implemented by \citet{wolfHuggingFaceTransformersStateoftheart2019}.
+For the BERT utterance encoder, we use the BERT\textsubscript{BASE} model with hidden size of 768 and 12 transformer layers and self-attention heads \citep[][\S3.1]{devlinBERTPretrainingDeep2018}.
+In our implementation, we use the un-cased model provided by \citet{wolfHuggingFaceTransformersStateoftheart2019}.
 
@@
 Therefore, we train another version of each model: one containing laughs (\texttt{L}) and one with laughs left out (\texttt{NL}), and compare their performances in DAR task.
-Table~\ref{table:laughter-total-acc}) compares the results from applying the models with two different utterance encoders (\texttt{BERT}, \texttt{CNN}).
+Table~\ref{table:laughter-total-acc} compares the results from applying the models with two different utterance encoders (\texttt{BERT}, \texttt{CNN}).
 First of all, we can see that \texttt{BERT} utterance encoder outperforms \texttt{CNN} in all the cases.
@@
 Our models tend to perform better for Forward-Communicative-Function group irrespective of presence the corpus and the presence of laughs.
-Also, our models perform better for AMI-DA corpus.
+Also, our models perform better on the AMI-DA corpus.
 Overall performance in these groups appears to be unaffected by presence of laughs.
@@
 
-A key asperation of transfer learning is to expose the model to phenomena that are too infrequent to learn from labeled training data alone.
-One explanation for pre-trained BERT's superrior performance on some infrequent dialogue acts is that it has learned to represent relevant features
+A key aspiration of transfer learning is to expose the model to phenomena that are too infrequent to learn from labeled training data alone.
+One explanation for pre-trained BERT's superior performance on some infrequent dialogue acts is that it has learned to represent relevant features
 that the randomly initialized model was unable to learn due to their sparsity in the labeled training set.
-Indeed, a simple lexical probe supports this explanation: in utterances where the pre-trained model is correct and the randomly initalized model is not,
-the rarest word is 1.9 times rarer than is typcial of corpus as a whole.
+Indeed, a simple lexical probe supports this explanation: in utterances where the pre-trained model is correct and the randomly initialized model is not,
+the rarest word is 1.9 times rarer than is typical of corpus as a whole.
 
@@
 The frozen model is heavily biased towards the most frequent tags, which explains its especially poor macro-average score (table \ref{table:exp2}).
-In SWDA, the model with the frozen encoder predicts one of the two most common tags (Statement-non-opinion or Acknowledge) \%86 of the time, whereas those two
+In SWDA, for example, the model with a frozen encoder predicts one of the two most common tags (Statement-non-opinion or Acknowledge) \%86 of the time, whereas those two
 tags account for only \%51 of the ground truth tags.
@@
 In-domain pre-training is sometimes referred to as \textit{fine-tuning}, but we reserve that term for task-specific training on labeled data.}
-We construct pre-training corpora from the SWDA portion of the un-labelled Switchboard corpus and from the entire AMI corpus (including the 32 dialogues with no human-annotated DA tags that are not included in the DAR training set).
+We construct pre-training corpora from the SWDA portion of the un-labeled Switchboard corpus and from the entire AMI corpus (including the 32 dialogues with no human-annotated DA tags that are not included in the DAR training set).
 In both cases, we exclude dialogues that are reserved for DAR testing.
@@
 
-For each dialogue act corpus, we trained DAR models with BERT encoders pre-trained on the in-domain corpus (\texttt{ID}) and the comined corpus (\texttt{CC}).
+For each dialogue act corpus, we trained DAR models with BERT encoders pre-trained on the in-domain corpus (\texttt{ID}) and the combined corpus (\texttt{CC}).
 As before, we experimented with both the fine-tuning and frozen conditions.
@@
 
-References
-\begin{itemize}
-  \item \citet{austinHowThingsWords2009} -- speeh acts
-  \item \citet{coreCodingDialogsDAMSL1997} -- DAMSL dialogue act tagging scheme. SWDA tags are based on this (I think AMI are too). Concept of multi-layer DA tags; forward/backward function
-  \item \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a} -- SWBD-DAMSL coders manual
-  % \item \citet{devlinBERTPretrainingDeep2018} -- Original BERT paper 
-  \item \citet{sunHowFineTuneBERT2019} -- recommendations for fine-tuninig BERT
-  \item \citet{mikolovDistributedRepresentationsWords2013} -- word2vec
-  \item \citet{petersTuneNotTune2019} -- when and how to fine-tune pre-trained representations
-  \item \citet{kimConvolutionalNeuralNetworks2014} -- CNN sentence representation
-  \item \citet{stolckeDialogueActModeling2000} -- OG DAR model. Uses an HMM with various lexical and prosodic features
-\end{itemize}
-
 Dialogue act recoginition
@@
   \item \citet{pragstVectorRepresentationUtterances2018} -- dialogue vector models.
-Uses vector-manual DA tag correspondance to argue for semantic relevance of their vector models (related to how we use DA tagging to verrify BERT usefulness)
+Uses vector-manual DA tag correspondance to argue for semantic relevance of their vector models (related to how we use DA tagging to verify BERT usefulness)
   \item \citet{cerisaraEffectsUsingWord2vec2017} -- standard pre-trained word embeddings do not help for DAR in any of three tested languages (English, French, Czech)
@@
   \item \citet{chenSemanticallyConditionedDialog2019a} -- uses BERT for response generation
-  \item \citet{baoPLATOPretrainedDialogue2019} -- pre-traininig for dialogue generation
+  \item \citet{baoPLATOPretrainedDialogue2019} -- pre-training for dialogue generation
   \item \citet{mehriPretrainingMethodsDialog2019} -- looks at various dialogue tasks using pre-training, including DAR and using BERT
@@
   \item Issues related to working with transcribed speech: Different kinds of laughter are all represented by the same token.
-Does transcription orthography capture prosidy?
+Does transcription orthography capture prosody?
 We know prosidy is useful for DAR (Jurafsky).
+  \item future work: pre-training on very large un-labeled dialogue corpora. How does text chat transfer to the spoken/transcribed setting?
 \end{itemize}

### 2019-12-06 reports/ACL2020 Paper/acl2020-paper.tex
Add confusion matrices. Update intro (about laughter). Update Exp 1.

@@
 In the Switchboard dialogue corpus, laughter comes about every 200 tokens.
-Laughter also relates to the discourse structure of dialogue. 
-% Laughables.
-% Also (known to be?) useful for predicting DAs
+Laughter also relates to the discourse structure of dialogue and can relate to a laughable, which can be any an event or an entity in the discourse (and external perceived event as well).
+Laughter can precede, follow or overlap the laughable, with the time alignment between the laughter and laughable dependent on who produces the laughable and the form of the laughter \citep{tian2016we}.
+In this work we found out that laughs can also be helpful to disambiguate a dialogue act.
 
 \begin{table}
+      \small
   \centering
@@
 The distribution of laughs in different dialogue acts has a rather uniform shape with a few outliers (see box plots).
-Figures \ref{fig:swda-by-da} (for SWDA) and \ref{fig:ami-by-da} (for AMI-DA) provide a breakdown of dialogue act depending on whether current or adjacent utterances (the preceding utterance and the following one are counted as adjacent) contain a laughter.
-Note that SWDA has a ``Nonverbal'' dialogue act which is misguiding with respect to laughter, because utterances only containing a single laughter token fall into this category, however they can serve, for example, to acknowledge a statement or to deflect a question  \citep{mazzocconi2019phd}.
+Figure \ref{fig:by-da} in Appendix~\ref{sec:suppl} provides a breakdown of dialogue act depending on whether current or adjacent utterances (the preceding utterance and the following one are counted as adjacent) contain laughter.\footnote{Note that SWDA has a ``Nonverbal'' dialogue act which is misguiding with respect to laughter, because utterances only containing a single laughter token fall into this category, however they can serve, for example, to acknowledge a statement or to deflect a question  \citep{mazzocconi2019phd}.}
 
@@
 First of all, we can see that \texttt{BERT} utterance encoder outperforms \texttt{CNN} in all the cases.
-From observing the effect of laughters, we can see differences in performance depending on the dialogue act, regardless how often laughter occurs in the current or adjacent utterances (see Figure~\ref{fig:swda-by-da} for Switchboard and Figure~\ref{fig:ami-by-da} for AMI corpus).
+From observing the effect of laughters, we can see differences in performance depending on the dialogue act, regardless how often laughter occurs in the current or adjacent utterances (see Figure~\ref{fig:by-da} in Appendix~\ref{sec:suppl}).
 The strongest evidence for laughter as a helpful feature was found in SWDA for the \texttt{BERT} utterance encoder, where macro-F1 score increases by 7.89 percentage points.
@@
 
-% \begin{table}
-%   \label{tab:laughter}
-%   \centering
-%   \begin{tabular}{@{}lccc@{}}
-%     \toprule
-%     & \%lassoc & \%L  & $\Delta$ (mean acc.) \\ \midrule
-%     Forward-CF & 11.86 & 4.59 & 11.40\\
-%     Backward-CF & 11.57 & 3.03 & 4.30\\
-%     Other & 12.71 & 4.40 & 2.39\\
-%     CS & 20.63 & 14.17 & -1.50\\\bottomrule
+Confusion matrices (Figure \ref{fig:swda-cm}) provide some food for thought.
+One of the most obvious things that can be observed is rhetorical questions: supposedly laughter, can be used as a device to cancel seriousness of the question.
+Therefore it can help to disambiguate such questions like the one we show in example in Table~\ref{table:example-qh}.
+\begin{table}
+      \small
+  \centering
+  \begin{tabularx}{\linewidth}{llL}
+    \toprule
+    Speaker & DA & Utterance \\ \midrule
+        \multicolumn{3}{c}{\emph{(Talking about hobbies)}}\\
+    B   & sd	&  Um, as far as spare time, they talked about, \\
+    B	& \% & I don't, + I think, \\
+    B	& qh & who has any spare time \texttt{<laughter>}? \\
+    A	& x & \texttt{<laughter>}.\\
+             \bottomrule
+  \end{tabularx}
+  \caption{Example from the SWDA corpus (sw3735). B's contribution \emph{qh}---Rhetorical question is misinterpreted as \emph{qw}---Wh-question by the BERT model without laughs in training data. }
+  \label{table:example-qh}
+\end{table}
 
-%   \end{tabular}
-%   \caption{Laughter impact by dialogue act group (SWDA, BERT), mean accuracy}
-% \end{table}
+  \begin{figure}
+  \centering
+  \includegraphics[width=0.9\linewidth]{img/swda-cm.pdf}
+  \caption{Confusion matrices for \texttt{BERT-NL} (top) vs \texttt{BERT-L} (bottom); SWDA corpus.}
+    \label{fig:swda-cm}
+  \end{figure}
 
-In order to further investigate the differences, we looked at the dialogue act groups.
+In order to further investigate the differences between the models and datasets, we looked at the dialogue act groups.
 Mapping all dialogue acts into four groups allows direct comparison between model performances in SWDA and AMI-DA.
@@
     \toprule
-    &                  & Forward-CF  & Backwards-CF   \\ \midrule
+    &                  & Forw.-CF  & Backw.-CF   \\ \midrule
     SWDA &\texttt{BERT-NL}  & 92.54 & 91.67       \\ 
@@
 \end{table}
-
-% to appendix?
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{img/SWDA-bertLvsNL.pdf}
-  \caption{Change in accuracy for each SWDA dialogue act. Positive changes when adding laughter are shown in blue. Vertical bars indicate how often dialogue act is associated with laughter.}
-    \label{fig:swda-by-da}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{img/AMI-DA-bertLvsNL.pdf}
-  \caption{Change in accuracy for each AMI dialogue act. Positive changes when adding laughter are shown in blue. Vertical bars indicate how often dialogue act is associated with laughter.}
-    \label{fig:ami-by-da}
-  \end{figure*}
 
@@
 \bibliographystyle{acl_natbib}
+\clearpage
+\appendix
+% to appendix?
+\begin{figure*}[h!]
+  \section{Supplementary materials}\label{sec:suppl}
+  \centering
+  \includegraphics[width=\linewidth]{img/SWDA-bertLvsNL.pdf}
+  \includegraphics[width=\linewidth]{img/AMI-DA-bertLvsNL.pdf}
+  \caption{Change in accuracy for each dialogue act.
+Positive changes when adding laughter are shown in blue.
+Vertical bars indicate how often dialogue act is associated with laughter.
+Top chart: SWDA, Bottom chart: AMI-DA.
+}
+    \label{fig:by-da}
+  \end{figure*}
 

### 2019-12-07 reports/ACL2020 Paper/acl2020-paper.tex
Fixes according to Staffan's comments

@@
   In this paper, we investigate the usefulness of BERT for dialogue act recognition.
-  We are interested in both how useful the pre-training proceedure is and 
+  We are interested in both how useful the pre-training procedure is and 
   how well the model adapts to the dialogue domain.
@@
 Dialogue, especially spoken dialogue, is radically different from the kind of data that neural language models are pre-trained on.
-In the example from the Switchboard corpus, shown in table~\ref{table:example}, it is evident that the syntactic structure of dialogue is very different from  written text, even if one imagines a script for a movie or a play.
+In the example from the Switchboard corpus, shown in Table~\ref{table:example}, it is evident that the syntactic structure of dialogue is very different from  written text, even if one imagines a script for a movie or a play.
 Not only is the internal structure of contributions different---with features such as disfluencies, repair, incomplete sentences, and various vocal sounds---but the sequential structure of the discourse is also very different.
 In dialogue, speakers take turns and switch perspectives.
-More generally, the way that utterances contribute and cohere to the discourse is different from the relationship between sentences in a piece of written text.
+More generally, the way that utterances contribute to and cohere with the discourse is different from the relationship between sentences in a piece of written text.
 
-One important dialogical feature missing from text data is laughter.
-In the Switchboard dialogue corpus, laughter comes about every 200 tokens.
+One important dialogical feature missing from text data is laughter, which is ubiquitous in our everyday interactions.
+We observe that in the Switchboard dialogue corpus laughter comes about every 200 tokens.
 Laughter also relates to the discourse structure of dialogue and can relate to a laughable, which can be any an event or an entity in the discourse (and external perceived event as well).
@@
 
+\paragraph{Laughs in the data}
 The distribution of laughs in different dialogue acts has a rather uniform shape with a few outliers (see box plots).
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{img/box-swda.pdf}
-  \caption{Box plot for utterances associated with laughter in SWDA.
+  \includegraphics[width=0.9\linewidth]{img/box-swda.pdf}
+  \caption{Box plot for dialogue acts associated with laughter in SWDA.
 On the left: proportion of DAs having laughter in one of the adjacent utterances, on the right: proportion of DAs containing laughter.
@@
   \centering
-  \includegraphics[width=0.8\linewidth]{img/box-ami.pdf}
-  \caption{Box plot for utterances associated with laughter in AMI-DA.
+  \includegraphics[width=0.9\linewidth]{img/box-ami.pdf}
+  \caption{Box plot for dialogue acts associated with laughter in AMI-DA.
 On the left: proportion of DAs having laughter in one of the adjacent utterances, on the right: proportion of DAs containing laughter.
@@
 
-For SWDA corpus we also considered grouping the dialogue acts according to DAMSL coders manual \citep{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}: Forward-Communicative-Function (51.86\% of all DAs), Backwards-Communicative-Function (30.35\%), Other (9.04\%) and Communicative-Status (8.75\%).
-We observed even distribution of laughs in these groups, except the Communicative-Status group which contains ``Nonverbal'' dialogue acts.
+\paragraph{Dialogue act grouping}
+For our corpora we also considered grouping the dialogue acts according to DAMSL coders manual \citep{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}: Forward-Communicative-Function (51.86\% of all DAs), Backwards-Communicative-Function (30.35\%), Other (9.04\%) and Communicative-Status (8.75\%).
+This allows the direct comparison between SWDA and AMI-DA.
+With respect to laughs, we observed even distribution of them in the groups, except the Communicative-Status group in the case of SWDA, because it contains ``Nonverbal'' dialogue acts.
 
@@
 Confusion matrices (Figure \ref{fig:swda-cm}) provide some food for thought.
-One of the most obvious things that can be observed is rhetorical questions: supposedly laughter, can be used as a device to cancel seriousness of the question.
+% TODO: explain why most of misclassifications are sd (majority class)
+One of the most obvious things that can be observed is rhetorical questions: supposedly, laughter can be used as a device to cancel seriousness \citep{ginzburg2015understanding} of the question.
 Therefore it can help to disambiguate such questions like the one we show in example in Table~\ref{table:example-qh}.
@@
   \end{tabularx}
-  \caption{Example from the SWDA corpus (sw3735). B's contribution \emph{qh}---Rhetorical question is misinterpreted as \emph{qw}---Wh-question by the BERT model without laughs in training data. }
+  \caption{Example from the SWDA corpus (sw3735). B's contribution \emph{qh} (Rhetorical question) is misinterpreted as \emph{qw} (Wh-question) by the BERT model without laughs in training data. }
   \label{table:example-qh}
@@
   \includegraphics[width=0.9\linewidth]{img/swda-cm.pdf}
-  \caption{Confusion matrices for \texttt{BERT-NL} (top) vs \texttt{BERT-L} (bottom); SWDA corpus.}
+  \caption{Confusion matrices for \texttt{BERT-NL} (top) vs \texttt{BERT-L} (bottom); SWDA corpus. Solid line shows the improvement in classification of rhetorical questions.}
     \label{fig:swda-cm}
@@
 Table~\ref{table:laughter-group-acc} compares accuracies between the two main groups: Forward-Communicative-Function and Backward-Communicative-Function (82.3\% of all DAs in SWDA and 76.7\% in AMI-DA).
-Our models tend to perform better for Forward-Communicative-Function group irrespective of presence the corpus and the presence of laughs.
-Also, our models perform better on the AMI-DA corpus.
+Our models tend to perform better for Forward-Communicative-Function group for both corpora irrespective of the presence of laughs.
+Also, our models perform better on the SWDA corpus.
 Overall performance in these groups appears to be unaffected by presence of laughs.
@@
   \item future work: pre-training on very large un-labeled dialogue corpora. How does text chat transfer to the spoken/transcribed setting?
+  \item Laughter is more helpful in SWDA than in AMI-DA.
+This observation may support the hypothesis that in SWDA due to the nature of interactions over the phone, dialogue participants can't rely on visual signals, such as gestures and facial expressions, therefore vocalisations, such as laughter, are more pronounced and therefore more helpful to disambiguate the utterances.
+  \item The point above can also explain why our models better on SWDA: just a larger proportion of stuff that interlocutors rely on is in the transcription.
 \end{itemize}
@@
 \appendix
-% to appendix?
 \begin{figure*}[h!]

### 2019-12-07 reports/ACL2020 Paper/acl2020-paper.tex
typo
lowercase figure and table

@@
 Dialogue, especially spoken dialogue, is radically different from the kind of data that neural language models are pre-trained on.
-In the example from the Switchboard corpus, shown in Table~\ref{table:example}, it is evident that the syntactic structure of dialogue is very different from  written text, even if one imagines a script for a movie or a play.
+In the example from the Switchboard corpus, shown in table~\ref{table:example}, it is evident that the syntactic structure of dialogue is very different from  written text, even if one imagines a script for a movie or a play.
 Not only is the internal structure of contributions different---with features such as disfluencies, repair, incomplete sentences, and various vocal sounds---but the sequential structure of the discourse is also very different.
@@
 First of all, we can see that \texttt{BERT} utterance encoder outperforms \texttt{CNN} in all the cases.
-From observing the effect of laughters, we can see differences in performance depending on the dialogue act, regardless how often laughter occurs in the current or adjacent utterances (see Figure~\ref{fig:by-da} in Appendix~\ref{sec:suppl}).
+From observing the effect of laughters, we can see differences in performance depending on the dialogue act, regardless how often laughter occurs in the current or adjacent utterances (see figure~\ref{fig:by-da} in Appendix~\ref{sec:suppl}).
 The strongest evidence for laughter as a helpful feature was found in SWDA for the \texttt{BERT} utterance encoder, where macro-F1 score increases by 7.89 percentage points.
@@
 
-Confusion matrices (Figure \ref{fig:swda-cm}) provide some food for thought.
+Confusion matrices (figure \ref{fig:swda-cm}) provide some food for thought.
 % TODO: explain why most of misclassifications are sd (majority class)
 One of the most obvious things that can be observed is rhetorical questions: supposedly, laughter can be used as a device to cancel seriousness \citep{ginzburg2015understanding} of the question.
-Therefore it can help to disambiguate such questions like the one we show in example in Table~\ref{table:example-qh}.
+Therefore it can help to disambiguate such questions like the one we show in example in table~\ref{table:example-qh}.
 \begin{table}
@@
 Table~\ref{table:laughter-group-acc} compares accuracies between the two main groups: Forward-Communicative-Function and Backward-Communicative-Function (82.3\% of all DAs in SWDA and 76.7\% in AMI-DA).
-Our models tend to perform better for Forward-Communicative-Function group for both corpora irrespective of the presence of laughs.
+Our models tend to perform better for the Forward-Communicative-Function group for both corpora irrespective of the presence of laughs.
 Also, our models perform better on the SWDA corpus.

### 2019-12-08 reports/ACL2020 Paper/acl2020-paper.tex
More comprehesive caption
Updates according to Chris’s comments

@@
 Laughter can precede, follow or overlap the laughable, with the time alignment between the laughter and laughable dependent on who produces the laughable and the form of the laughter \citep{tian2016we}.
-In this work we found out that laughs can also be helpful to disambiguate a dialogue act.
 
@@
 We use dialogue act recognition  as a proxy task, since both the internal content of contributions, and their sequential structure have bearing on the task.
+In this work we also show that laughs can be helpful to disambiguate a dialogue act.
 
@@
 The distribution of laughs in different dialogue acts has a rather uniform shape with a few outliers (see box plots).
-Figure \ref{fig:by-da} in Appendix~\ref{sec:suppl} provides a breakdown of dialogue act depending on whether current or adjacent utterances (the preceding utterance and the following one are counted as adjacent) contain laughter.\footnote{Note that SWDA has a ``Nonverbal'' dialogue act which is misguiding with respect to laughter, because utterances only containing a single laughter token fall into this category, however they can serve, for example, to acknowledge a statement or to deflect a question  \citep{mazzocconi2019phd}.}
+Figure \ref{fig:by-da} in Appendix~\ref{sec:suppl} provides a breakdown of dialogue act depending on whether current or adjacent utterances (the preceding utterance and the following one are counted as adjacent) contain laughter.\footnote{Note that SWDA has a ``Nonverbal'' dialogue act which is misleading with respect to laughter, because utterances only containing a single laughter token fall into this category, however they can serve, for example, to acknowledge a statement or to deflect a question  \citep{mazzocconi2019phd}.}
 
@@
 This allows the direct comparison between SWDA and AMI-DA.
-With respect to laughs, we observed even distribution of them in the groups, except the Communicative-Status group in the case of SWDA, because it contains ``Nonverbal'' dialogue acts.
-
+With respect to laughs, we observed an even distribution of them in the groups, except for the Communicative-Status group in the case of SWDA, because of the ``Nonverbal'' dialogue acts (see footnote~1).
 % - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, removing laughter % Bill
@@
 \begin{itemize}
-  \item \texttt{BERT-FT} -- pre-trained BERT with DAR fine-tuninig 
+  \item \texttt{BERT-FT} -- pre-trained BERT with DAR fine-tuning 
   \item \texttt{BERT-RI} -- randomly initialized BERT (with DAR fine-tuning)
@@
 The frozen model is heavily biased towards the most frequent tags, which explains its especially poor macro-average score (table \ref{table:exp2}).
-In SWDA, for example, the model with a frozen encoder predicts one of the two most common tags (Statement-non-opinion or Acknowledge) \%86 of the time, whereas those two
-tags account for only \%51 of the ground truth tags.
-The fine-tuned model is much less biased; it predicts the two most common tags only \%59 of the time.
+In SWDA, for example, the model with a frozen encoder predicts one of the two most common tags (Statement-non-opinion or Acknowledge) 86\% of the time, whereas those two
+tags account for only 51\% of the ground truth tags.
+The fine-tuned model is much less biased; it predicts the two most common tags only 59\% of the time.
 
@@
 This gives us another opportunity to assess whether laughter is useful in dialogue act recognition.
-We find that although \%4.6 of utterances in SWDA contain laughter, 
-\%7.3 of utterances misclassified by the frozen model but correctly classified by the fine-tuned model contain laughter, 
+We find that although 4.6\% of utterances in SWDA contain laughter, 
+7.3\% of utterances misclassified by the frozen model but correctly classified by the fine-tuned model contain laughter, 
 suggesting that the fine-tuned encoder makes use of laughter. 
 For AMI-DA, the effect is less pronounced, but still present: 
-overall, \%8.5 of utterances contain laughter, 
-compared to \%9.6 of utterances where fine-tuning makes a difference.
+overall, 8.5\% of utterances contain laughter, 
+compared to 9.6\% of utterances where fine-tuning makes a difference.
 
@@
   \includegraphics[width=\linewidth]{img/AMI-DA-bertLvsNL.pdf}
-  \caption{Change in accuracy for each dialogue act.
-Positive changes when adding laughter are shown in blue.
+  \caption{Change in accuracy for each dialogue act (\texttt{BERT-NL} vs \texttt{BERT-L}).
+Positive changes when adding laughter (\texttt{BERT-L}) are shown in blue.
 Vertical bars indicate how often dialogue act is associated with laughter.

### 2019-12-08 reports/ACL2020 Paper/acl2020-paper.tex
add transfer learning/BERT background

--- 2019-12-07 reports/ACL2020 Paper/acl2020-paper.tex
@@
 \paragraph{Transfer learning for NLP}
-\begin{itemize}
-  \item \citet{mikolovDistributedRepresentationsWords2013} -- word2vec
-  % \item \citet{devlinBERTPretrainingDeep2018} -- Original BERT paper 
-  \item \citet{sunHowFineTuneBERT2019} -- recommendations for fine-tuning BERT
-  \item \citet{petersTuneNotTune2019} -- when and how to fine-tune pre-trained representations
-\end{itemize}
+Transfer learning is are techniques that allow a model trained on one task---often unsupervised---to be applied to another. 
+Since annotating natural language data is expensive, there is a lot of interest in transfer learning for natural language processing. 
+The use of pre-trained word vectors \citep[e.g.,][]{mikolovDistributedRepresentationsWords2013;penningtonGloveGlobalVectors2014} is a ubiquitous example of transfer learning in NLP.
+Recently, large neural models trained on various unsupervised tasks have found success in producing sentence-level and contextual word representations.
+
+BERT \citep{devlinBERTPretrainingDeep2018} is one such model. 
+It is a large multi-layer transformer, pre-trained on two unsupervised tasks: \emph{masked token prediction} and \emph{next sentence prediction}.
+In masked token prediction, some percentage of words are randomly replaced with a \texttt{[MASK]} token, and the model is trained to predict the identity of these tokes based on the context sentence.
+In next sentence prediction, the model is give two sentences and trained to predict whether the second sentence follows the first in the original text, or if it was randomly chosen from elsewhere in the corpus.
+After pre-training, BERT can be applied to a supervised task by adding additional un-trained layers that take the hidden state of one or more of BERT's layers as input.
+
+Transfer learning schemes for pre-trained language models such as BERT draw on one or more of the following three adaptation strategies \citet{sunHowFineTuneBERT2019}:
+\emph{further pre-training}, in which the model is trained in an un-supervised way, similar to its initial training scheme, but on data that is in-domain for the target task; 
+\emph{single-task fine-tuning}, in which the model's encoder layers are optimized during training for the target task;
+and \emph{multi-task fine-tuning}, in which models with shared encoder layers are jointly trained on several related tasks.
+In this paper, we investigate the first two methods and their combination, as applied to DAR.
+
+Regardless of whether an encoder model has undergone further in-domain pre-training, the choice of whether to fine-tune during task training remains.
+Freezing the encoder model during task training is more efficient, since the gradient of the loss function need only be computed for the task-specific layers.
+However, fine-tuning can lead to better performance since the encoding itself is adapted to the target task and domain.
+
+\citet{petersTuneNotTune2019} investigate when and whether to fine-tune BERT for sentence classification tasks.
+They find that when the target task is very similar to the pre-training task, fine-tuning provides less of a performance boost.
+There is some conceptual relationship between DAR and next sentence prediction, since the a dialogue act constrains (or at least is predictive of) the dialogue act that follows it.
+
+\citet{petersTuneNotTune2019} also consider whether the similarity of the pre-training and target domains may have similar consequences, but don't find an effect of domain similarly for the natural language inference tasks they tested on.
+As discussed in \S\ref{sec:data}, however, there are dramatic differences between written text and transcribed dialogue which may mean that fine-tuning is necessary in this case.
 
@@
 \begin{itemize}
-  \item Laughter is useful for dialogue act recognition, and its impact varies across different dialogue acts (\S\ref{sec:experiment1}).
-  \item Standard BERT pre-training is useful for DAR, but the impact of pre-training is smaller than than of fine-tuning (\S\ref{sec:experiment2})
-  \item Performing additional in-domain pre-training shows promise for dialogue (\S\ref{sec:experiment3}), but further investigation with larger dialogue corpora is required.
+  \item Laughter is useful for dialogue act recognition, and its impact varies across different dialogue acts (\S\ref{sec:experiment2}).
+  \item During fine-tuning, BERT learns to represent laughter, a dialogical feature not seen in pre-training (\S\ref{sec:experiment2} and \S\ref{sec:experiment3}).
+  \item Standard BERT pre-training is useful for DAR, but the model performs poorly without fine-tuning (\S\ref{sec:experiment2})
+  \item Further pre-training with in-domain data shows promise for dialogue (\S\ref{sec:experiment3}), but further investigation with larger dialogue corpora is required.
 \end{itemize}
@@
 
-Next, we assess the effect of additional in-domain pre-training on BERT's performance as an utterance encoder.\footnote{
+Next, we assess the effect of further in-domain pre-training on BERT's performance as an utterance encoder.\footnote{
 In-domain pre-training is sometimes referred to as \textit{fine-tuning}, but we reserve that term for task-specific training on labeled data.}
@@
 but the macro-average scores are almost uniformly worse (table \ref{table:exp3}).
-%Indeed, when BERT is frozen during fine-tuning, the model that received no additional pre-training performs better by more than 3 percentage points (table \ref{tab:exp3-recall}).
-To fully assess the potential impact of in-domain pre-training, a larger dialogue corpus is required.
+%Indeed, when BERT is frozen during fine-tuning, the model that received no further pre-training performs better by more than 3 percentage points (table \ref{tab:exp3-recall}).
+To fully assess the potential impact of further in-domain pre-training, a larger dialogue corpus is required.
 
@@
 \end{tabular}
-  \caption{Comparing DAR performance of  with additional in-domain (\texttt{ID}) and cross-domain (\texttt{CC}) dialogue pre-training,
+  \caption{Comparing DAR performance of  with further in-domain (\texttt{ID}) and cross-domain (\texttt{CC}) dialogue pre-training,
     for both the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions.}

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
create background section
Some more minor fixes

@@
 \begin{abstract}
-  The degree to which language models pre-trained on text data are useful for dialogue is an open question.
   In this paper, we investigate the usefulness of BERT for dialogue act recognition.
@@
 
-In this work, we investigate whether BERT \citep{devlinBERTPretrainingDeep2018}, a well-know pre-trained language model, is useful for dialogue.
+We investigate whether BERT \citep{devlinBERTPretrainingDeep2018}, a well-know pre-trained language model, is useful for dialogue.
 We use dialogue act recognition  as a proxy task, since both the internal content of contributions, and their sequential structure have bearing on the task.
-In this work we also show that laughs can be helpful to disambiguate a dialogue act.
+We also show that laughs can be helpful to disambiguate a dialogue act.
+
+\paragraph{Contributions}
+The main results of this paper have to do with to the usefulness of language model fine-tuning for DAR, the impact of laughter on DAR, and the relationship between the two.
+\begin{itemize}
+  \item Laughter is useful for dialogue act recognition, and its impact varies across different dialogue acts (\S\ref{sec:experiment2}).
+  \item During fine-tuning, BERT learns to represent laughter, a dialogical feature not seen in pre-training (\S\ref{sec:experiment2} and \S\ref{sec:experiment3}).
+  \item Standard BERT pre-training is useful for DAR, but the model performs poorly without fine-tuning (\S\ref{sec:experiment2})
+  \item Further pre-training with in-domain data shows promise for dialogue (\S\ref{sec:experiment3}), but further investigation with larger dialogue corpora is required.
+\end{itemize}
+
+\section{Background}
 
@@
 for example with a recurrent model \citep[e.g.,][]{botheContextbasedApproachDialogue2018} or conditional random field \citep[e.g.,][]{chenDialogueActRecognition2017}.
+
+\begin{itemize}
+  % related because of the DAR sequence model
+  \item \citet{kalchbrennerRecurrentConvolutionalNeural2013} -- DAR model similar to our architecture. Uses an RNN ``discourse model'' and a CNN similar to our baseline encoder
+  \item \citet{botheContextbasedApproachDialogue2018} -- uses an RNN for context (recently SOTA on SWDA)
+  \item \citet{tranHierarchicalNeuralModel2017} -- RNNs at both the utteranec and dialogue level. Also attention. Very similar to our architecture.
+  \item \citet{tranPreservingDistributionalInformation2017} -- Sequential DA prediction with uncertainty propegation
+  % cf.
+  \item \citet{ortegaNeuralbasedContextRepresentation2017} -- SWDA DAR with attention-based context representations and CNN utterance representations
+  % related because of the utt encoder model
+  \item \citet{khanpourDialogueActClassification2016} -- Deep LSTM utt representation. No notion of context. Finds word vectors are useful.
+  \item \citet{shenNeuralAttentionModels2016} -- Uses attention for utt encoding in DAR. No notion of context, I think.
+  % related because of methodology
+  \item \citet{pragstVectorRepresentationUtterances2018} -- dialogue vector models.
+Uses vector-manual DA tag correspondance to argue for semantic relevance of their vector models (related to how we use DA tagging to verify BERT usefulness)
+  % ???
+  \item \citet{chenDialogueActRecognition2017} -- SOTA? SWDA DAR using attention and CRF over utterances
+\end{itemize}
 
@@
 
+\begin{itemize}
+  \item \citet{cerisaraEffectsUsingWord2vec2017} -- standard pre-trained word embeddings do not help for DAR in any of three tested languages (English, French, Czech)
+    % BERT for dialogue (not nesc. DAR)
+  \item \citet{chenSemanticallyConditionedDialog2019a} -- uses BERT for response generation
+  \item \citet{mehriPretrainingMethodsDialog2019} -- looks at various dialogue tasks using pre-training, including DAR and using BERT
+  \item \citet{baoPLATOPretrainedDialogue2019} -- pre-training for dialogue generation
+  \item \citet{vigComparisonTransferLearningApproaches} -- Transfer learning for response selection
+\end{itemize}
+
 \paragraph{Contributions}
@@
 \begin{itemize}
-  \item Laughter is useful for dialogue act recognition, and its impact varies across different dialogue acts (\S\ref{sec:experiment2}).
+  \item Laughter is useful for dialogue act recognition, and its impact varies across different dialogue acts (\S\ref{sec:experiment1}).
   \item During fine-tuning, BERT learns to represent laughter, a dialogical feature not seen in pre-training (\S\ref{sec:experiment2} and \S\ref{sec:experiment3}).
@@
 Confusion matrices (figure \ref{fig:swda-cm}) provide some food for thought.
-% TODO: explain why most of misclassifications are sd (majority class)
-One of the most obvious things that can be observed is rhetorical questions: supposedly, laughter can be used as a device to cancel seriousness \citep{ginzburg2015understanding} of the question.
-Therefore it can help to disambiguate such questions like the one we show in example in table~\ref{table:example-qh}.
+Most of the misclassifications fall into the majority classes, such as \emph{sd} (Statement-non-opinion), in the left edge of the matrix.
+However there are some important exceptions, such as \emph{rhetorical questions}, that are misclassified as other forms of questions due to their surface question-like form.
+Importantly, laughter helpes to classify rhetorical questions correctly, this is because in a conversation it can be used as a device to cancel seriousness \citep{ginzburg2015understanding}, in this case, of a question.
+Therefore questions, like the one we show in the example in table~\ref{table:example-qh}, are easier to disambiguate with the help of laughter.
 \begin{table}
@@
   \centering
-  \includegraphics[width=0.9\linewidth]{img/swda-cm.pdf}
+  \includegraphics[width=1.0\linewidth]{img/swda-cm.pdf}
   \caption{Confusion matrices for \texttt{BERT-NL} (top) vs \texttt{BERT-L} (bottom); SWDA corpus. Solid line shows the improvement in classification of rhetorical questions.}
@@
 %  - cross-domain pre-training
-\section{Related work} % add references first
-For the background:
-
-Dialogue act recoginition
-\begin{itemize}
-  \item \citet{botheContextbasedApproachDialogue2018} -- uses an RNN for context (recently SOTA on SWDA)
-  \item \citet{pragstVectorRepresentationUtterances2018} -- dialogue vector models.
-Uses vector-manual DA tag correspondance to argue for semantic relevance of their vector models (related to how we use DA tagging to verify BERT usefulness)
-  \item \citet{cerisaraEffectsUsingWord2vec2017} -- standard pre-trained word embeddings do not help for DAR in any of three tested languages (English, French, Czech)
-  \item \citet{kalchbrennerRecurrentConvolutionalNeural2013} -- DAR model similar to our architecture. Uses an RNN ``discourse model'' and a CNN similar to our baseline encoder
-  \item \citet{khanpourDialogueActClassification2016} -- Deep LSTM utt representation. No notion of context. Finds word vectors are useful.
-  \item \citet{tranPreservingDistributionalInformation2017} -- Sequential DA prediction with uncertainty propegation
-  \item \citet{chenDialogueActRecognition2017} -- SOTA? SWDA DAR using attention and CRF over utterances
-  \item \citet{ortegaNeuralbasedContextRepresentation2017} -- SWDA DAR with attention-based context representations and CNN utterance representations
-  \item \citet{shenNeuralAttentionModels2016} -- Uses attention for utt encoding in DAR. No notion of context, I think.
-  \item \citet{tranHierarchicalNeuralModel2017} -- RNNs at both the utteranec and dialogue level. Also attention. Very similar to our architecture.
-\end{itemize}
-
-Pre-training/transfer learning for dialogue
-\begin{itemize}
-  \item \citet{mehriStructuredFusionNetworks2019} -- ``Structured fusion networks''. Traditional dialogue system design with neural models.
-  \item \citet{chenSemanticallyConditionedDialog2019a} -- uses BERT for response generation
-  \item \citet{baoPLATOPretrainedDialogue2019} -- pre-training for dialogue generation
-  \item \citet{mehriPretrainingMethodsDialog2019} -- looks at various dialogue tasks using pre-training, including DAR and using BERT
-  \item \citet{vigComparisonTransferLearningApproaches} -- Transfer learning for response selection
-\end{itemize}
 

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
move contributions
Introduction, remove duplicate contributions

@@
 
-We investigate whether BERT \citep{devlinBERTPretrainingDeep2018}, a well-know pre-trained language model, is useful for dialogue.
-We use dialogue act recognition  as a proxy task, since both the internal content of contributions, and their sequential structure have bearing on the task.
-We also show that laughs can be helpful to disambiguate a dialogue act.
+We use dialogue act recognition (DAR) as a proxy task, since both the internal content of contributions, and their sequential structure have bearing on this task.
+DAR is the task of assigning a dialogue act to every utterance in the dialogue, according to dialogue act that they perform.
+This is the way to investigate whether transfer learning techniques based on pre-trained language models, such as BERT \citep{devlinBERTPretrainingDeep2018}, are useful for dialogue.
+We looked at laughter that is certainly missing in pre-trained model, and discovered that it can be useful to disambiguate a dialogue act.
 
@@
 \begin{itemize}
-  \item Laughter is useful for dialogue act recognition, and its impact varies across different dialogue acts (\S\ref{sec:experiment2}).
-  \item During fine-tuning, BERT learns to represent laughter, a dialogical feature not seen in pre-training (\S\ref{sec:experiment2} and \S\ref{sec:experiment3}).
+  \item Laughter is useful for dialogue act recognition, and its impact varies across different dialogue acts (\S\ref{sec:experiment1}).
+  \item During fine-tuning, BERT learns to represent laughter, a dialogical feature not seen in pre-training (\S\ref{sec:experiment1} and \S\ref{sec:experiment2}).
   \item Standard BERT pre-training is useful for DAR, but the model performs poorly without fine-tuning (\S\ref{sec:experiment2})
@@
   \end{itemize}
+
+In the following section we provide more details about the dialogue act recognition task and transfer learning techniques.
 
@@
 
-DAR is the the task of labeling utterances with the dialogue act they perform 
-from a given set of dialogue act tags.
+DAR is the task of labeling utterances with the dialogue act they perform from a given set of dialogue act tags.
 As with other sequence labeling tasks in NLP, some notion of context is helpful in DAR.
@@
   \item \citet{vigComparisonTransferLearningApproaches} -- Transfer learning for response selection
-\end{itemize}
-
-\paragraph{Contributions}
-The main results of this paper have to do with to the usefulness of language model fine-tuning for DAR, the impact of laughter on DAR, and the relationship between the two.
-\begin{itemize}
-  \item Laughter is useful for dialogue act recognition, and its impact varies across different dialogue acts (\S\ref{sec:experiment1}).
-  \item During fine-tuning, BERT learns to represent laughter, a dialogical feature not seen in pre-training (\S\ref{sec:experiment2} and \S\ref{sec:experiment3}).
-  \item Standard BERT pre-training is useful for DAR, but the model performs poorly without fine-tuning (\S\ref{sec:experiment2})
-  \item Further pre-training with in-domain data shows promise for dialogue (\S\ref{sec:experiment3}), but further investigation with larger dialogue corpora is required.
 \end{itemize}

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
Laughter and AMI vs SWDA discussion. Fixed ref to AMI docs.

@@
 
-%
-% TODO per dialogue act analysis
-% DONE compare impacts of CNN vs BERT
-% DONE for both AMI and SWDA
-% ?
-
 \subsection{Experiment 2: Impact of pre-training vs. fine-tuning} \label{sec:experiment2} % Bill
@@
 \section{Discussion} % add items to discuss
+On the question of laughter impact, this study found out that laughter is more helpful in SWDA corpus than in AMI-DA.
+This observation may support the hypothesis that in SWDA due to the nature of interactions over the phone, dialogue participants can not rely on visual signals, such as gestures and facial expressions, therefore vocalisations, such as laughter, are more pronounced and therefore more helpful to disambiguate the utterances.
+
+This also can explain why all our best models perform better on SWDA: much more information that interlocutors and dialogue act annotators can rely on is present in the transcription of SWDA, whereas AMI-DA annotators receive clear instructions to pay attention to the videos \citep{GuidelinesDialogueAct2005}.
+This finding is consistent with that of \citet{bavelas2008gesturing} who demonstrated that in face-to-face dialogue visual components, such as gestures, can convey information that is independent from one conveyed with speech.
+
 \begin{itemize}
@@
   \item Laughter is more helpful in SWDA than in AMI-DA. 
-This observation may support the hypothesis that in SWDA due to the nature of interactions over the phone, dialogue participants can't rely on visual signals, such as gestures and facial expressions, therefore vocalisations, such as laughter, are more pronounced and therefore more helpful to disambiguate the utterances.
   \item The point above can also explain why our models better on SWDA: just a larger proportion of stuff that interlocutors rely on is in the transcription.

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
integrate references in background

--- 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
@@
 \begin{abstract}
+  The degree to which language models pre-trained on text data are useful for dialogue is an open question.
   In this paper, we investigate the usefulness of BERT for dialogue act recognition.
@@
 
-We investigate whether BERT \citep{devlinBERTPretrainingDeep2018}, a well-know pre-trained language model, is useful for dialogue.
+In this work, we investigate whether BERT \citep{devlinBERTPretrainingDeep2018}, a well-know pre-trained language model, is useful for dialogue.
 We use dialogue act recognition  as a proxy task, since both the internal content of contributions, and their sequential structure have bearing on the task.
-We also show that laughs can be helpful to disambiguate a dialogue act.
+In this work we also show that laughs can be helpful to disambiguate a dialogue act.
 
@@
 
-\paragraph{Dialogue Act Recognition (DAR)}
+\subsection{Dialogue Act Recognition}
 The concept of a dialogue act is based on that of speech acts \citep{austinHowThingsWords2009}.
@@
 One of the first performant machine learning models for DAR was a Hidden Markov Model that used various lexical and prosodic features as input \citep{stolckeDialogueActModeling2000}.
-Most successful neural approaches also model some notion of context, 
-for example with a recurrent model \citep[e.g.,][]{botheContextbasedApproachDialogue2018} or conditional random field \citep[e.g.,][]{chenDialogueActRecognition2017}.
 
-\begin{itemize}
-  % related because of the DAR sequence model
-  \item \citet{kalchbrennerRecurrentConvolutionalNeural2013} -- DAR model similar to our architecture. Uses an RNN ``discourse model'' and a CNN similar to our baseline encoder
-  \item \citet{botheContextbasedApproachDialogue2018} -- uses an RNN for context (recently SOTA on SWDA)
-  \item \citet{tranHierarchicalNeuralModel2017} -- RNNs at both the utteranec and dialogue level. Also attention. Very similar to our architecture.
-  \item \citet{tranPreservingDistributionalInformation2017} -- Sequential DA prediction with uncertainty propegation
-  % cf.
-  \item \citet{ortegaNeuralbasedContextRepresentation2017} -- SWDA DAR with attention-based context representations and CNN utterance representations
-  % related because of the utt encoder model
-  \item \citet{khanpourDialogueActClassification2016} -- Deep LSTM utt representation. No notion of context. Finds word vectors are useful.
-  \item \citet{shenNeuralAttentionModels2016} -- Uses attention for utt encoding in DAR. No notion of context, I think.
+Most successful neural approaches also model some notion of context.
+We follow previous work that models dialogue act sequences with an RNN over utterances \citep{kalchbrennerRecurrentConvolutionalNeural2013,tranHierarchicalNeuralModel2017,botheContextbasedApproachDialogue2018}.
+Our model predicts the most likely tag given the hidden state of the RNN at each position, though other work has shown that DAR benefits from more sophistacted approaches, such as conditional random field \citep{chenDialogueActRecognition2017} or uncertainty propegation \citep{tranPreservingDistributionalInformation2017}.
+
+%\begin{itemize}
+  %\item \citet{kalchbrennerRecurrentConvolutionalNeural2013} -- DAR model similar to our architecture. Uses an RNN ``discourse model'' and a CNN similar to our baseline encoder
+  %\item \citet{botheContextbasedApproachDialogue2018} -- uses an RNN for context (recently SOTA on SWDA)
+  %\item \citet{tranHierarchicalNeuralModel2017} -- RNNs at both the utteranec and dialogue level. Also attention. Very similar to our architecture.
+  %\item \citet{tranPreservingDistributionalInformation2017} -- Sequential DA prediction with uncertainty propegation
+  %\item \citet{ortegaNeuralbasedContextRepresentation2017} -- SWDA DAR with attention-based context representations and CNN utterance representations
+  %\item \citet{shenNeuralAttentionModels2016} -- Uses attention for utt encoding in DAR. No notion of context, I think.
   % related because of methodology
-  \item \citet{pragstVectorRepresentationUtterances2018} -- dialogue vector models.
+  %\item \citet{pragstVectorRepresentationUtterances2018} -- dialogue vector models.
 Uses vector-manual DA tag correspondance to argue for semantic relevance of their vector models (related to how we use DA tagging to verify BERT usefulness)
-  % ???
-  \item \citet{chenDialogueActRecognition2017} -- SOTA? SWDA DAR using attention and CRF over utterances
-\end{itemize}
+  %\item \citet{chenDialogueActRecognition2017} -- SOTA? SWDA DAR using attention and CRF over utterances
+%\end{itemize}
 
 \paragraph{Transfer learning for NLP}
-Transfer learning is are techniques that allow a model trained on one task---often unsupervised---to be applied to another. 
+Transfer learning techniques allow a model trained on one task---often unsupervised---to be applied to another. 
 Since annotating natural language data is expensive, there is a lot of interest in transfer learning for natural language processing. 
-The use of pre-trained word vectors \citep[e.g.,][]{mikolovDistributedRepresentationsWords2013;penningtonGloveGlobalVectors2014} is a ubiquitous example of transfer learning in NLP.
-Recently, large neural models trained on various unsupervised tasks have found success in producing sentence-level and contextual word representations.
+Word vectors \citep[e.g.,][]{mikolovDistributedRepresentationsWords2013,penningtonGloveGlobalVectors2014} are a ubiquitous example of transfer learning in NLP.
+We note, however, that pre-trained word vectors are not always useful when applied to dialogue domains \citet{cerisaraEffectsUsingWord2vec2017}.
 
-BERT \citep{devlinBERTPretrainingDeep2018} is one such model. 
-It is a large multi-layer transformer, pre-trained on two unsupervised tasks: \emph{masked token prediction} and \emph{next sentence prediction}.
+Recently, neural models trained on large datasets with various unsupervised tasks have found success creating sentence-level and contextual word representations. 
+BERT, a multi-layer tranformer, is one such model \citep{devlinBERTPretrainingDeep2018} . 
+BERT is pre-trained on two unsupervised tasks: \emph{masked token prediction} and \emph{next sentence prediction}.
 In masked token prediction, some percentage of words are randomly replaced with a \texttt{[MASK]} token, and the model is trained to predict the identity of these tokes based on the context sentence.
@@
 
+There is some preivous work applying BERT to dialogue.
+\citet{baoPLATOPretrainedDialogue2019,chenSemanticallyConditionedDialog2019a} and both use BERT for dialogue generation tasks.
+Similarly \citet{vigComparisonTransferLearningApproaches2019} finds BERT useful for selecting a response from a list of candidate responses in a dialogue.
+Finally, \citet{mehriPretrainingMethodsDialog2019} evaluates BERT in various dialogue tasks including DAR, and find that a model incorporating BERT outperforms a baseline model.
+
+\paragraph{Fine-tuning vs.~further in-domain pre-training}
 Transfer learning schemes for pre-trained language models such as BERT draw on one or more of the following three adaptation strategies \citet{sunHowFineTuneBERT2019}:
@@
 
-\begin{itemize}
-  \item \citet{cerisaraEffectsUsingWord2vec2017} -- standard pre-trained word embeddings do not help for DAR in any of three tested languages (English, French, Czech)
-    % BERT for dialogue (not nesc. DAR)
-  \item \citet{chenSemanticallyConditionedDialog2019a} -- uses BERT for response generation
-  \item \citet{mehriPretrainingMethodsDialog2019} -- looks at various dialogue tasks using pre-training, including DAR and using BERT
-  \item \citet{baoPLATOPretrainedDialogue2019} -- pre-training for dialogue generation
-  \item \citet{vigComparisonTransferLearningApproaches} -- Transfer learning for response selection
-\end{itemize}
+%\begin{itemize}
+  %\item \citet{cerisaraEffectsUsingWord2vec2017} -- standard pre-trained word embeddings do not help for DAR in any of three tested languages (English, French, Czech)
+  %\item \citet{khanpourDialogueActClassification2016} -- Deep LSTM utt representation. No notion of context. Finds word vectors are useful.
+     %BERT for dialogue (not nesc. DAR)
+  %\item \citet{chenSemanticallyConditionedDialog2019a} -- uses BERT for response generation
+  %\item \citet{mehriPretrainingMethodsDialog2019} -- looks at various dialogue tasks using pre-training, including DAR and using BERT
+  %\item \citet{baoPLATOPretrainedDialogue2019} -- pre-training for dialogue generation
+  %\item \citet{vigComparisonTransferLearningApproaches} -- Transfer learning for response selection
+%\end{itemize}
 
-\paragraph{Contributions}
-The main results of this paper have to do with to the usefulness of language model fine-tuning for DAR, the impact of laughter on DAR, and the relationship between the two.
-\begin{itemize}
-  \item Laughter is useful for dialogue act recognition, and its impact varies across different dialogue acts (\S\ref{sec:experiment1}).
-  \item During fine-tuning, BERT learns to represent laughter, a dialogical feature not seen in pre-training (\S\ref{sec:experiment2} and \S\ref{sec:experiment3}).
-  \item Standard BERT pre-training is useful for DAR, but the model performs poorly without fine-tuning (\S\ref{sec:experiment2})
-  \item Further pre-training with in-domain data shows promise for dialogue (\S\ref{sec:experiment3}), but further investigation with larger dialogue corpora is required.
-\end{itemize}
-
-\section{Data}
+\section{Data}\label{sec:data}
 We perform experiments on the Switchboard Dialogue Act Corpus (SWDA), which is a subset of the larger Switchboard corpus, and the dialogue act-tagged portion of the AMI Meeting Corpus (AMI-DA). 
@@
 Confusion matrices (figure \ref{fig:swda-cm}) provide some food for thought.
-Most of the misclassifications fall into the majority classes, such as \emph{sd} (Statement-non-opinion), in the left edge of the matrix.
-However there are some important exceptions, such as \emph{rhetorical questions}, that are misclassified as other forms of questions due to their surface question-like form.
-Importantly, laughter helpes to classify rhetorical questions correctly, this is because in a conversation it can be used as a device to cancel seriousness \citep{ginzburg2015understanding}, in this case, of a question.
-Therefore questions, like the one we show in the example in table~\ref{table:example-qh}, are easier to disambiguate with the help of laughter.
+% TODO: explain why most of misclassifications are sd (majority class)
+One of the most obvious things that can be observed is rhetorical questions: supposedly, laughter can be used as a device to cancel seriousness \citep{ginzburg2015understanding} of the question.
+Therefore it can help to disambiguate such questions like the one we show in example in table~\ref{table:example-qh}.
 \begin{table}
@@
   \centering
-  \includegraphics[width=1.0\linewidth]{img/swda-cm.pdf}
+  \includegraphics[width=0.9\linewidth]{img/swda-cm.pdf}
   \caption{Confusion matrices for \texttt{BERT-NL} (top) vs \texttt{BERT-L} (bottom); SWDA corpus. Solid line shows the improvement in classification of rhetorical questions.}

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex

--- 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
@@
 One of the first performant machine learning models for DAR was a Hidden Markov Model that used various lexical and prosodic features as input \citep{stolckeDialogueActModeling2000}.
-Most successful neural approaches also model some notion of context, 
-for example with a recurrent model \citep[e.g.,][]{botheContextbasedApproachDialogue2018} or conditional random field \citep[e.g.,][]{chenDialogueActRecognition2017}.
 
-\begin{itemize}
-  % related because of the DAR sequence model
-  \item \citet{kalchbrennerRecurrentConvolutionalNeural2013} -- DAR model similar to our architecture. Uses an RNN ``discourse model'' and a CNN similar to our baseline encoder
-  \item \citet{botheContextbasedApproachDialogue2018} -- uses an RNN for context (recently SOTA on SWDA)
-  \item \citet{tranHierarchicalNeuralModel2017} -- RNNs at both the utteranec and dialogue level. Also attention. Very similar to our architecture.
-  \item \citet{tranPreservingDistributionalInformation2017} -- Sequential DA prediction with uncertainty propegation
-  % cf.
-  \item \citet{ortegaNeuralbasedContextRepresentation2017} -- SWDA DAR with attention-based context representations and CNN utterance representations
-  % related because of the utt encoder model
-  \item \citet{khanpourDialogueActClassification2016} -- Deep LSTM utt representation. No notion of context. Finds word vectors are useful.
-  \item \citet{shenNeuralAttentionModels2016} -- Uses attention for utt encoding in DAR. No notion of context, I think.
-  % related because of methodology
-  \item \citet{pragstVectorRepresentationUtterances2018} -- dialogue vector models.
-Uses vector-manual DA tag correspondance to argue for semantic relevance of their vector models (related to how we use DA tagging to verify BERT usefulness)
-  % ???
-  \item \citet{chenDialogueActRecognition2017} -- SOTA? SWDA DAR using attention and CRF over utterances
-\end{itemize}
+Most successful neural approaches also model some notion of context.
+We follow previous work that models dialogue act sequences with an RNN over utterances \citep{kalchbrennerRecurrentConvolutionalNeural2013,tranHierarchicalNeuralModel2017,botheContextbasedApproachDialogue2018}.
+Our model predicts the most likely tag given the hidden state of the RNN at each position, though other work has shown that DAR benefits from more sophistacted approaches, such as conditional random field \citep{chenDialogueActRecognition2017} or uncertainty propegation \citep{tranPreservingDistributionalInformation2017}.
 
 \paragraph{Transfer learning for NLP}
-Transfer learning is are techniques that allow a model trained on one task---often unsupervised---to be applied to another. 
+Transfer learning techniques allow a model trained on one task---often unsupervised---to be applied to another. 
 Since annotating natural language data is expensive, there is a lot of interest in transfer learning for natural language processing. 
-The use of pre-trained word vectors \citep[e.g.,][]{mikolovDistributedRepresentationsWords2013;penningtonGloveGlobalVectors2014} is a ubiquitous example of transfer learning in NLP.
-Recently, large neural models trained on various unsupervised tasks have found success in producing sentence-level and contextual word representations.
+Word vectors \citep[e.g.,][]{mikolovDistributedRepresentationsWords2013,penningtonGloveGlobalVectors2014} are a ubiquitous example of transfer learning in NLP.
+We note, however, that pre-trained word vectors are not always useful when applied to dialogue domains \citet{cerisaraEffectsUsingWord2vec2017}.
 
-BERT \citep{devlinBERTPretrainingDeep2018} is one such model. 
-It is a large multi-layer transformer, pre-trained on two unsupervised tasks: \emph{masked token prediction} and \emph{next sentence prediction}.
+Recently, neural models trained on large datasets with various unsupervised tasks have found success creating sentence-level and contextual word representations. 
+BERT, a multi-layer tranformer, is one such model \citep{devlinBERTPretrainingDeep2018} . 
+BERT is pre-trained on two unsupervised tasks: \emph{masked token prediction} and \emph{next sentence prediction}.
 In masked token prediction, some percentage of words are randomly replaced with a \texttt{[MASK]} token, and the model is trained to predict the identity of these tokes based on the context sentence.
@@
 
-\begin{itemize}
-  \item \citet{cerisaraEffectsUsingWord2vec2017} -- standard pre-trained word embeddings do not help for DAR in any of three tested languages (English, French, Czech)
-    % BERT for dialogue (not nesc. DAR)
-  \item \citet{chenSemanticallyConditionedDialog2019a} -- uses BERT for response generation
-  \item \citet{mehriPretrainingMethodsDialog2019} -- looks at various dialogue tasks using pre-training, including DAR and using BERT
-  \item \citet{baoPLATOPretrainedDialogue2019} -- pre-training for dialogue generation
-  \item \citet{vigComparisonTransferLearningApproaches} -- Transfer learning for response selection
-\end{itemize}
-
-\section{Data}
+\section{Data}\label{sec:data}
 We perform experiments on the Switchboard Dialogue Act Corpus (SWDA), which is a subset of the larger Switchboard corpus, and the dialogue act-tagged portion of the AMI Meeting Corpus (AMI-DA). 

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
table -> Table; figure -> Figure

@@
 Dialogue, especially spoken dialogue, is radically different from the kind of data that neural language models are pre-trained on.
-In the example from the Switchboard corpus, shown in table~\ref{table:example}, it is evident that the syntactic structure of dialogue is very different from  written text, even if one imagines a script for a movie or a play.
+In the example from the Switchboard corpus, shown in Table~\ref{table:example}, it is evident that the syntactic structure of dialogue is very different from  written text, even if one imagines a script for a movie or a play.
 Not only is the internal structure of contributions different---with features such as disfluencies, repair, incomplete sentences, and various vocal sounds---but the sequential structure of the discourse is also very different.
@@
 
-\paragraph{Transfer learning for NLP}
+\subsection{Transfer learning for NLP}
 Transfer learning techniques allow a model trained on one task---often unsupervised---to be applied to another. 
@@
 
-To test the effectiveness of BERT for DAR, we employ a simple neural architecture with two components: an encoder that vectorizes utterances, and a sequence model that predicts dialogue act tags from the vectorized utterances (figure \ref{fig:model-architecture}).
+To test the effectiveness of BERT for DAR, we employ a simple neural architecture with two components: an encoder that vectorizes utterances, and a sequence model that predicts dialogue act tags from the vectorized utterances (Figure~\ref{fig:model-architecture}).
 Since we are primarily interested in comparing different utterance encoders, we use a basic RNN as the sequence model in every configuration. 
@@
 First of all, we can see that \texttt{BERT} utterance encoder outperforms \texttt{CNN} in all the cases.
-From observing the effect of laughters, we can see differences in performance depending on the dialogue act, regardless how often laughter occurs in the current or adjacent utterances (see figure~\ref{fig:by-da} in Appendix~\ref{sec:suppl}).
+From observing the effect of laughters, we can see differences in performance depending on the dialogue act, regardless how often laughter occurs in the current or adjacent utterances (see Figure~\ref{fig:by-da} in Appendix~\ref{sec:suppl}).
 The strongest evidence for laughter as a helpful feature was found in SWDA for the \texttt{BERT} utterance encoder, where macro-F1 score increases by 7.89 percentage points.
@@
 
-Confusion matrices (figure \ref{fig:swda-cm}) provide some food for thought.
+Confusion matrices (Figure~\ref{fig:swda-cm}) provide some food for thought.
 Most of the misclassifications fall into the majority classes, such as \emph{sd} (Statement-non-opinion), in the left edge of the matrix.
@@
 Importantly, laughter helpes to classify rhetorical questions correctly, this is because in a conversation it can be used as a device to cancel seriousness \citep{ginzburg2015understanding}, in this case, of a question.
-Therefore questions, like the one we show in the example in table~\ref{table:example-qh}, are easier to disambiguate with the help of laughter.
+Therefore questions, like the one we show in the example in Table~\ref{table:example-qh}, are easier to disambiguate with the help of laughter.
 \begin{table}
@@
 The pre-trained model is more accurate than the randomly initialized model by several percentage points on both DA corpora,
-suggesting that BERT's extensive pre-training does provide some useful information for recoginizing different dialogue acts (table \ref{table:exp2}).
+suggesting that BERT's extensive pre-training does provide some useful information for recoginizing different dialogue acts (Table~\ref{table:exp2}).
 This performance boost is much more pronounced in the macro-averaged F1 score,
@@
 Comparing the performance of the fine-tuned encoder to that of the frozen model, we note that pre-training alone is not enough.
-The frozen model is heavily biased towards the most frequent tags, which explains its especially poor macro-average score (table \ref{table:exp2}).
+The frozen model is heavily biased towards the most frequent tags, which explains its especially poor macro-average score (Table~\ref{table:exp2}).
 In SWDA, for example, the model with a frozen encoder predicts one of the two most common tags (Statement-non-opinion or Acknowledge) 86\% of the time, whereas those two
@@
 In-domain pre-training offers a modest boost in overall accuracy,
-but the macro-average scores are almost uniformly worse (table \ref{table:exp3}).
-%Indeed, when BERT is frozen during fine-tuning, the model that received no further pre-training performs better by more than 3 percentage points (table \ref{tab:exp3-recall}).
+but the macro-average scores are almost uniformly worse (Table~\ref{table:exp3}).
+%Indeed, when BERT is frozen during fine-tuning, the model that received no further pre-training performs better by more than 3 percentage points (Table~\ref{tab:exp3-recall}).
 To fully assess the potential impact of further in-domain pre-training, a larger dialogue corpus is required.

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
Ref to laughter and sarcasm
make tables consistent

@@
                       & \multicolumn{2}{c}{SWDA} & \multicolumn{2}{c}{AMI-DA} \\ \midrule
-                      & macro-F1 & acc. & macro-F1 & acc.       \\ 
+                      & F1    & acc.  & F1    & acc.       \\ 
     \texttt{BERT-NL}  & 38.10 & 77.07 & 49.09 & 67.06       \\ 
@@
   \end{tabular}
-  \caption{Comparison of models depending on using laughter on the training phase. }
+  \caption{Comparison of macro-average F1 and micro-average accuracy depending on using laughter on the training phase. }
   \label{table:laughter-total-acc}
@@
     &                  & Forw.-CF  & Backw.-CF   \\ \midrule
-    SWDA &\texttt{BERT-NL}  & 92.54 & 91.67       \\ 
+    \multirow{4}{*}{SWDA}    &\texttt{BERT-NL}  & 92.54 & 91.67       \\ 
                              &\texttt{BERT-L}   & 95.42 & 90.91       \\ 
@@
                              &\texttt{CNN-L}    & 94.64 & 90.13        \\ \midrule
-    AMI  &\texttt{BERT-NL}  & 87.77 & 80.83       \\ 
+    \multirow{4}{*}{AMI-DA}  &\texttt{BERT-NL}  & 87.77 & 80.83       \\ 
                              &\texttt{BERT-L}   & 87.36 & 79.87       \\
@@
 \begin{table}[]
-\begin{tabular}{@{}clll@{}}
+\centering
+\begin{tabular}{@{}lrrrr@{}}
 \toprule
-                                                                                  &             & SWDA  & AMI-DA \\ \midrule
-\multirow{3}{*}{\begin{tabular}[c]{@{}c@{}}Micro-average\\ accuracy\end{tabular}} & \texttt{BERT-FT}     & 76.93 & 66.94  \\
-                                                                                  & \texttt{BERT-RI}     & 73.80 & 61.53  \\ 
-                                                                                  & \texttt{BERT-FZ}     & 55.61 & 46.59  \\ \midrule
-  \multirow{3}{*}{\begin{tabular}[c]{@{}c@{}}Macro-average\\ F1\end{tabular}}     & \texttt{BERT-FT}     & 45.99 & 50.03  \\
-                                                                                  & \texttt{BERT-RI}     & 32.18 & 33.45  \\ 
-                                                                                  & \texttt{BERT-FZ}     & 07.75 & 14.44  \\ \bottomrule
+                           & \multicolumn{2}{c}{SWDA}                          & \multicolumn{2}{c}{AMI-DA}                        \\ \midrule
+                           & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
+\texttt{BERT-FT} & 45.99           & 76.93                    & 50.03                  & 66.94                    \\
+\texttt{BERT-RI} & 32.18           & 73.80                    & 33.45                  & 61.53                    \\
+\texttt{BERT-FZ} & 7.75            & 55.61                    & 14.44                  & 46.59 \\
+  \bottomrule
 \end{tabular}
-  \caption{DAR performance comparison of BERT with standard pre-training and DAR fine-tuning (\texttt{BERT-FT}) vs.
-the same model without pre-training (\texttt{BERT-RI}) and without fine-tuning (\texttt{BERT-FZ}).}
+  \caption{Macro-average F1 and micro-average accuracy of BERT with standard pre-training and DAR fine-tuning (\texttt{BERT-FT}) vs.~the same model without pre-training (\texttt{BERT-RI}) and without fine-tuning (\texttt{BERT-FZ}).}
   \label{table:exp2}
@@
 
-For each dialogue act corpus, we trained DAR models with BERT encoders pre-trained on the in-domain corpus (\texttt{ID}) and the combined corpus (\texttt{CC}).
+For each dialogue act corpus, we trained DAR models with BERT encoders pre-trained on the in-domain corpus (\texttt{BERT+ID}) and the combined corpus (\texttt{BERT+CC}).
 As before, we experimented with both the fine-tuning and frozen conditions.
@@
 
-\begin{table}
-\begin{tabular}{llrr}
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+\begin{table}[]
+\begin{tabular}{@{}lrrrr@{}}
 \toprule
-               &         &  SWBD &   AMI \\
-\midrule
-\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Micro-average\\ accuracy\end{tabular}} 
-               & \texttt{FT} & 76.93 & 66.95 \\
-               & \texttt{+ID-FT} & 77.02 & 68.66 \\
-               & \texttt{+CC-FT} & 77.35 & 68.58 \\ \cline{2-4}
-               & \texttt{FZ} & 55.61 & 46.60 \\
-               & \texttt{+ID-FZ} & 52.30 & 48.07 \\
-               & \texttt{+CC-FZ} & 51.14 & 42.42 \\ \hline
-\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Macro-average\\ F1 score\end{tabular}} 
-               & \texttt{FT} & 45.99 & 50.03 \\
-               & \texttt{+ID-FT} & 45.48 & 46.56 \\
-               & \texttt{+CC-FT} & 47.78 & 48.72 \\ \cline{2-4}
-               & \texttt{FZ} &  7.75 & 14.44 \\
-               & \texttt{+ID-FZ} &  6.46 & 14.43 \\
-               & \texttt{+CC-FZ} &  5.76 & 12.56 \\
-
-\bottomrule
+           & \multicolumn{2}{c}{SWDA}                          & \multicolumn{2}{c}{AMI-DA}                        \\ \midrule
+           & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
+\texttt{BERT-FT}    & 45.99                  & 76.93                    & 50.03                  & 66.95                    \\
+\texttt{BERT+ID-FT} & 45.48                  & 77.02                    & 46.56                  & 68.66                    \\
+\texttt{BERT+CC-FT} & 47.78                  & 77.35                    & 48.72                  & 66.58                    \\ \midrule
+\texttt{BERT-FZ}    & 7.75                   & 55.61                    & 14.44                  & 46.60                    \\
+\texttt{BERT+ID-FZ} & 6.46                   & 52.30                    & 14.43                  & 48.07                    \\
+\texttt{BERT+CC-FZ} & 5.76                   & 51.14                    & 12.56                  & 42.42                    \\ \bottomrule
 \end{tabular}
-  \caption{Comparing DAR performance of  with further in-domain (\texttt{ID}) and cross-domain (\texttt{CC}) dialogue pre-training,
+  \caption{Comparison of macro-average F1 and micro-average accuracy  with further in-domain (\texttt{ID}) and cross-domain (\texttt{CC}) dialogue pre-training,
     for both the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions.}

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
Transitions.

@@
 Laughter can precede, follow or overlap the laughable, with the time alignment between the laughter and laughable dependent on who produces the laughable and the form of the laughter \citep{tian2016we}.
+Laughter can act as a contextual feature for determining the sincerity of an utterance, in order to understand sincerity of an utterance, e.g. to detect sarcasm \citep{tepperman2006yeah}.
 
@@
 
+\paragraph{} In the next section, we will present the datasets that we will use in our experiments along with their distinctive features.
+
 \section{Data}\label{sec:data}
@@
 With respect to laughs, we observed an even distribution of them in the groups, except for the Communicative-Status group in the case of SWDA, because of the ``Nonverbal'' dialogue acts (see footnote~1).
+
 % - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, removing laughter % Bill
+
+\paragraph{}
+Let us turn now to describing the neural network architectures that we used.
 
@@
 In our implementation, we use the un-cased model provided by \citet{wolfHuggingFaceTransformersStateoftheart2019}.
+
+The next section will introduce the experiments that we have carried out and will discuss the results that we obtained from them.
 
@@
 However there are some important exceptions, such as \emph{rhetorical questions}, that are misclassified as other forms of questions due to their surface question-like form.
-Importantly, laughter helpes to classify rhetorical questions correctly, this is because in a conversation it can be used as a device to cancel seriousness \citep{ginzburg2015understanding}, in this case, of a question.
+Importantly, laughter helpes to classify rhetorical questions correctly, this is because in a conversation it can be used as a device to cancel seriousness or sincerity \citep{ginzburg2015understanding,tepperman2006yeah}, in this case, of a question.
 Therefore questions, like the one we show in the example in Table~\ref{table:example-qh}, are easier to disambiguate with the help of laughter.
@@
 %  - cross-domain pre-training
+\paragraph{}
+Having discussed the experimental results, the final section of the paper provides broader explanations of our findings.
 

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
Caption for the results by DA groups

@@
 We perform experiments on the Switchboard Dialogue Act Corpus (SWDA), which is a subset of the larger Switchboard corpus, and the dialogue act-tagged portion of the AMI Meeting Corpus (AMI-DA). 
-SWDA is tagged with a set of 220 dialogue act tags which, following  \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a} we cluster into a smaller set of 42 tags.
+SWDA is tagged with a set of 220 dialogue act tags which, following  \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}, we cluster into a smaller set of 42 tags.
 AMI uses a smaller tagset of 16 dialogue acts \citep{GuidelinesDialogueAct2005}.
@@
 \end{table}
+
+\paragraph{Preprocesing}
+% - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, removing laughter % Bill
+
+We make an effort to normalize transcription conventions across SWDA and AMI.
+We remove disfluency annotations and slashes from the end of utterances in SWDA.
+In both corpora, acronyms are tokenized as individual letters. 
+All utterances are lower-cased.
+
+Utterances are tokenized using BERT's word piece tokenizer with a vocabulary of 30,000.
+We add a special laughter token to the vocabulary and map all transcribed laughter to that token.
+We also add five speaker tokens and prepend each utterance with a speaker token that uniquely identifies the corresponding speaker within that dialogue.
 
@@
 With respect to laughs, we observed an even distribution of them in the groups, except for the Communicative-Status group in the case of SWDA, because of the ``Nonverbal'' dialogue acts (see footnote~1).
-
-% - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, removing laughter % Bill
 
@@
   \end{tabular}
-  \caption{Comparison of macro-average F1 and micro-average accuracy depending on using laughter on the training phase. }
+  \caption{Comparison of macro-average F1 and accuracy depending on using laughter on the training phase. }
   \label{table:laughter-total-acc}
@@
   \end{tabular}
-  \caption{Comparison of models depending on using laughter on the training phase. }
+  \caption{Comparison of the accuracies among the two main dialogues act groups, depending on the utterance model and the presence of laughter.}
   \label{table:laughter-group-acc}
@@
 \end{tabular}
-  \caption{Macro-average F1 and micro-average accuracy of BERT with standard pre-training and DAR fine-tuning (\texttt{BERT-FT}) vs.~the same model without pre-training (\texttt{BERT-RI}) and without fine-tuning (\texttt{BERT-FZ}).}
+  \caption{Macro-average F1 and accuracy of BERT with standard pre-training and DAR fine-tuning (\texttt{BERT-FT}) vs.~the same model without pre-training (\texttt{BERT-RI}) and without fine-tuning (\texttt{BERT-FZ}).}
   \label{table:exp2}
@@
 \end{tabular}
-  \caption{Comparison of macro-average F1 and micro-average accuracy  with further in-domain (\texttt{ID}) and cross-domain (\texttt{CC}) dialogue pre-training,
+  \caption{Comparison of macro-average F1 and accuracy  with further in-domain (\texttt{ID}) and cross-domain (\texttt{CC}) dialogue pre-training,
     for both the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions.}

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
add preprocessing section

@@
 
-\paragraph{} In the next section, we will present the datasets that we will use in our experiments along with their distinctive features.
-
 \section{Data}\label{sec:data}
@@
 
-\paragraph{}
-Let us turn now to describing the neural network architectures that we used.
-
 \section{Model} % Bill
@@
 In our implementation, we use the un-cased model provided by \citet{wolfHuggingFaceTransformersStateoftheart2019}.
-
-The next section will introduce the experiments that we have carried out and will discuss the results that we obtained from them.
 
@@
 However there are some important exceptions, such as \emph{rhetorical questions}, that are misclassified as other forms of questions due to their surface question-like form.
-Importantly, laughter helpes to classify rhetorical questions correctly, this is because in a conversation it can be used as a device to cancel seriousness or sincerity \citep{ginzburg2015understanding,tepperman2006yeah}, in this case, of a question.
+Importantly, laughter helpes to classify rhetorical questions correctly, this is because in a conversation it can be used as a device to cancel seriousness \citep{ginzburg2015understanding}, in this case, of a question.
 Therefore questions, like the one we show in the example in Table~\ref{table:example-qh}, are easier to disambiguate with the help of laughter.
@@
   \end{tabular}
-  \caption{Comparison of the accuracies among the two main dialogues act groups, depending on the utterance model and the presence of laughter.}
+  \caption{Comparison of models depending on using laughter on the training phase. }
   \label{table:laughter-group-acc}
@@
 %  - cross-domain pre-training
-\paragraph{}
-Having discussed the experimental results, the final section of the paper provides broader explanations of our findings.
 

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
new title; add to discussion

--- 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
@@
 
-\title{Pre-trained encoders for dialogue: The case of laughter}
+\title{Tickle me BERT: Using laughter to probe pre-trained encoders for dialogue act recoginiton}
 
@@
 \end{tabular}
-  \caption{Comparison of macro-average F1 and accuracy  with further in-domain (\texttt{ID}) and cross-domain (\texttt{CC}) dialogue pre-training,
+  \caption{Comparison of macro-average F1 and accuracy  with further in-domain (\texttt{ID}) and combined corpus (\texttt{CC}) dialogue pre-training,
     for both the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions.}
@@
 
-\begin{itemize}
-  \item RoBERTa training scheme finds that next sentence prediction is of little importance.
+Although our experiments with further pre-training were inconclusive, \citet{baoPLATOPretrainedDialogue2019} finds that further pre-training BERT on a large-scale Reddit and Twitter corpus is helpful for response selection.
+Further pre-training may be helpful for DAR too, if the in-domain or cross-domain corpus is large enough.
+
+It remains an open question how well the text chat domain transfers to transcribed dialogue and what pre-training schemes are best for the dialogue domain.
+The training scheme for RoBERTa \citep{liuRoBERTaRobustlyOptimized2019}, for example, leaves out next sentence prediction as a pre-training task because they do not find that it improves performance on question answering and natural language inference tasks.
+The same may not be true of dialogue, however.
+
+%\begin{itemize}
+  %\item RoBERTa training scheme finds that next sentence prediction is of little importance.
 Is this true for us too?
@@
 see: https://github.com/huggingface/transformers/issues/1622
-  \item Issues related to working with transcribed speech: Different kinds of laughter are all represented by the same token.
+  %\item Issues related to working with transcribed speech: Different kinds of laughter are all represented by the same token.
 Does transcription orthography capture prosody?
 We know prosidy is useful for DAR (Jurafsky).
-  \item future work: pre-training on very large un-labeled dialogue corpora. How does text chat transfer to the spoken/transcribed setting?
-  \item Laughter is more helpful in SWDA than in AMI-DA. 
-  \item The point above can also explain why our models better on SWDA: just a larger proportion of stuff that interlocutors rely on is in the transcription.
-\end{itemize}
+  %\item future work: pre-training on very large un-labeled dialogue corpora. How does text chat transfer to the spoken/transcribed setting?
+  %\item Laughter is more helpful in SWDA than in AMI-DA. 
+  %\item The point above can also explain why our models better on SWDA: just a larger proportion of stuff that interlocutors rely on is in the transcription.
+%\end{itemize}
 

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
add appendix figure

@@
 which is explained by the fact that at the tag level, pre-training has a larger impact on less frequent tags.
+For a disaggregeated view, see Figure \ref{fig:f1-by-da} in Appendix~\ref{sec:suppl} p
 
@@
 \appendix
+
 \begin{figure*}[h!]
@@
 
+\begin{figure*}[h!]
+  \centering
+  \includegraphics[width=\linewidth]{img/swda-brf.pdf}
+  \includegraphics[width=\linewidth]{img/ami-brf.pdf}
+  \caption{F1 scores by dialogue act for BERT with standard pre-training and DAR fine-tuning (\texttt{BERT-FT}) vs.~the same model without pre-training (\texttt{BERT-RI}) and without fine-tuning (\texttt{BERT-FZ}).
+Dialogue acts are ordered with the most common on the left.
+    \label{fig:f1-by-da}
+  \end{figure*}
+
 \end{document}

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
fix typo
fix bracket
Few words about using speech-related information

@@
 which is explained by the fact that at the tag level, pre-training has a larger impact on less frequent tags.
-For a disaggregeated view, see Figure \ref{fig:f1-by-da} in Appendix~\ref{sec:suppl} p
+For a disaggregeated view, see Figure \ref{fig:f1-by-da} in Appendix~\ref{sec:suppl}.
 
@@
 
+There is abundant room for further progress in determining how other speech-related information, such as prosody and disfluencies, can be incorporated into the DAR model.
+\citet{stolckeDialogueActModeling2000} showed that dialogue acts can have specific prosodic manifestations that can be used to improve dialogue act classification.
+Furthermore, function of laughter and its position in relation to laughable can be reflected in the acoustic form of laughter \citep{tian2016we,mazzocconi2019phd}.
+
 Although our experiments with further pre-training were inconclusive, \citet{baoPLATOPretrainedDialogue2019} finds that further pre-training BERT on a large-scale Reddit and Twitter corpus is helpful for response selection.
@@
 \bibliographystyle{acl_natbib}
-\clearpage
 \appendix
+\onecolumn
+\section{Supplementary materials}\label{sec:suppl}
 
 \begin{figure*}[h!]
-\section{Supplementary materials}\label{sec:suppl}
   \centering
@@
   \caption{F1 scores by dialogue act for BERT with standard pre-training and DAR fine-tuning (\texttt{BERT-FT}) vs.~the same model without pre-training (\texttt{BERT-RI}) and without fine-tuning (\texttt{BERT-FZ}).
-Dialogue acts are ordered with the most common on the left.
+Dialogue acts are ordered with the most common on the left.}
     \label{fig:f1-by-da}

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
Some rewording

@@
 \citet{stolckeDialogueActModeling2000} showed that dialogue acts can have specific prosodic manifestations that can be used to improve dialogue act classification.
-Furthermore, function of laughter and its position in relation to laughable can be reflected in the acoustic form of laughter \citep{tian2016we,mazzocconi2019phd}.
+Furthermore, in relation to laughter, its form (duration, arousal level) can be informative about its function and position w.r.t. to laughable \citep{tian2016we,mazzocconi2019phd}.
 

### 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
Auch, typo in the title
Fix typos

@@
 
-\title{Tickle me BERT: Using laughter to probe pre-trained encoders for dialogue act recoginiton}
+\title{Tickle me BERT: Using laughter to probe pre-trained encoders for dialogue act recognition}
 
@@
 We follow previous work that models dialogue act sequences with an RNN over utterances \citep{kalchbrennerRecurrentConvolutionalNeural2013,tranHierarchicalNeuralModel2017,botheContextbasedApproachDialogue2018}.
-Our model predicts the most likely tag given the hidden state of the RNN at each position, though other work has shown that DAR benefits from more sophistacted approaches, such as conditional random field \citep{chenDialogueActRecognition2017} or uncertainty propegation \citep{tranPreservingDistributionalInformation2017}.
+Our model predicts the most likely tag given the hidden state of the RNN at each position, though other work has shown that DAR benefits from more sophisticated approaches, such as conditional random field \citep{chenDialogueActRecognition2017} or uncertainty propagation \citep{tranPreservingDistributionalInformation2017}.
 
@@
 Recently, neural models trained on large datasets with various unsupervised tasks have found success creating sentence-level and contextual word representations. 
-BERT, a multi-layer tranformer, is one such model \citep{devlinBERTPretrainingDeep2018} . 
+BERT, a multi-layer transformer, is one such model \citep{devlinBERTPretrainingDeep2018} . 
 BERT is pre-trained on two unsupervised tasks: \emph{masked token prediction} and \emph{next sentence prediction}.
@@
 
-There is some preivous work applying BERT to dialogue.
+There is some previous work applying BERT to dialogue.
 \citet{baoPLATOPretrainedDialogue2019,chenSemanticallyConditionedDialog2019a} and both use BERT for dialogue generation tasks.
@@
 
-\paragraph{Preprocesing}
+\paragraph{Preprocessing}
 % - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, removing laughter % Bill
@@
 which is explained by the fact that at the tag level, pre-training has a larger impact on less frequent tags.
-For a disaggregeated view, see Figure \ref{fig:f1-by-da} in Appendix~\ref{sec:suppl}.
+For a disaggregated view, see Figure \ref{fig:f1-by-da} in Appendix~\ref{sec:suppl}.
 

### 2019-12-11 data.py
pre-training dataprep tweaks from lark

@@ -110,6 +110,15 @@ def load_data_pretraining(corpus_file, tokenizer):
         data.append(utts)
     return data
 
+
+def write_pretraining_corpus(corpus_file, corpus):
+    with open(os.path.join(corpus_file), 'w') as f:
+        for d in corpus:
+            for utt in d:
+                f.write(' '.join(utt) + '\n')
+            f.write('\n')
+
+
 Dialogue = namedtuple('Dialogue', ['id', 'speakers', 'utts', 'da_tags'])
 
 
@@ -361,19 +370,11 @@ if __name__ == '__main__':
 
         tokenizer = load_tokenizer('bert-base-uncased')
 
-        ami = (load_data_pretraining(os.path.join(args.data_dir, 'AMI-DA_train.json'), tokenizer) +
-               load_data_pretraining(os.path.join(args.data_dir, 'AMI-noDA.json'), tokenizer))
-        with open(os.path.join(args.data_dir, 'AMI_pretraining.txt'), 'w') as f:
-            for d in ami:
-                for utt in d:
-                    f.write(' '.join(utt) + '\n')
-                f.write('\n')
+        ami = load_data_pretraining(os.path.join(args.data_dir, 'AMI-DA_train.json'), tokenizer)
+        ami_da = load_data_pretraining(os.path.join(args.data_dir, 'AMI-noDA.json'), tokenizer)
+        swda = load_data_pretraining(os.path.join(args.data_dir, 'SWDA_train.json'), tokenizer)
 
-        swbd = load_data_pretraining(os.path.join(args.data_dir, 'SWDA_train.json'), tokenizer)
-        with open(os.path.join(args.data_dir, 'SWBD_pretraining.txt'), 'w') as f:
-            for d in swbd:
-                for utt in d:
-                    f.write(' '.join(utt) + '\n')
-                f.write('\n')
-
+        write_pretraining_corpus(os.path.join(args.data_dir, 'AMI_pretraining.txt'), ami + ami_da)
+        write_pretraining_corpus(os.path.join(args.data_dir, 'SWBD_pretraining.txt'), swda)
+        write_pretraining_corpus(os.path.join(args.data_dir, 'AMI+SWBD_pretraining.txt'), ami + ami_da + swda)
 

### 2019-12-11 finetune_on_pregenerated.py

@@ -177,6 +177,10 @@ def main():
                         type=int,
                         default=42,
                         help="random seed for initialization")
+    parser.add_argument('--gpu_id', 
+                        type=int, default
+                        =0,
+                        help='Select with GPU to use')
     args = parser.parse_args()
 
     assert args.pregenerated_data.is_dir(), \
@@ -200,7 +204,7 @@ def main():
         num_data_epochs = args.epochs
 
     if args.local_rank == -1 or args.no_cuda:
-        device = torch.device("cuda" if torch.cuda.is_available() and not args.no_cuda else "cpu")
+        device = torch.device(f"cuda:{args.gpu_id}" if torch.cuda.is_available() and not args.no_cuda else "cpu")
         # n_gpu = torch.cuda.device_count()
         n_gpu = 1
     else:

### 2020-03-21 reports/ACL2020 Paper/acl2020-paper.tex

@@
 \usepackage{graphicx}
+\usepackage{subcaption}
 \usepackage{natbib}
@@
 Laughter can precede, follow or overlap the laughable, with the time alignment between the laughter and laughable dependent on who produces the laughable and the form of the laughter \citep{tian2016we}.
-Laughter can act as a contextual feature for determining the sincerity of an utterance, in order to understand sincerity of an utterance, e.g. to detect sarcasm \citep{tepperman2006yeah}.
+Laughter can act as a contextual feature for determining the sincerity of an utterance, e.g. to when detecting sarcasm \citep{tepperman2006yeah}.
 
@@
 We use dialogue act recognition (DAR) as a proxy task, since both the internal content of contributions, and their sequential structure have bearing on this task.
-DAR is the task of assigning a dialogue act to every utterance in the dialogue, according to dialogue act that they perform.
-This is the way to investigate whether transfer learning techniques based on pre-trained language models, such as BERT \citep{devlinBERTPretrainingDeep2018}, are useful for dialogue.
-We looked at laughter that is certainly missing in pre-trained model, and discovered that it can be useful to disambiguate a dialogue act.
+DAR is the task of assigning a dialogue act tag to each utterance in the dialogue, according to dialogue act it performs.
+Using this task we investigate whether transfer learning techniques based on pre-trained language models, such as BERT \citep{devlinBERTPretrainingDeep2018}, are useful for dialogue.
+By looking at laughter, which is certainly missing in pre-trained model, we can determine whether the domain-adapted model can make use of dialogue-specific features.
 
@@
 Word vectors \citep[e.g.,][]{mikolovDistributedRepresentationsWords2013,penningtonGloveGlobalVectors2014} are a ubiquitous example of transfer learning in NLP.
-We note, however, that pre-trained word vectors are not always useful when applied to dialogue domains \citet{cerisaraEffectsUsingWord2vec2017}.
+We note, however, that pre-trained word vectors are not always useful when applied to dialogue domains \cite{cerisaraEffectsUsingWord2vec2017}.
 
@@
 BERT is pre-trained on two unsupervised tasks: \emph{masked token prediction} and \emph{next sentence prediction}.
-In masked token prediction, some percentage of words are randomly replaced with a \texttt{[MASK]} token, and the model is trained to predict the identity of these tokes based on the context sentence.
-In next sentence prediction, the model is give two sentences and trained to predict whether the second sentence follows the first in the original text, or if it was randomly chosen from elsewhere in the corpus.
+In masked token prediction, some percentage of words are randomly replaced with a mask token, and the model is trained to predict the identity of the original token, based on the context sentence.
+In next sentence prediction, the model is given two sentences and trained to predict whether the second sentence follows the first in the original text, or if it was randomly chosen from elsewhere in the corpus.
 After pre-training, BERT can be applied to a supervised task by adding additional un-trained layers that take the hidden state of one or more of BERT's layers as input.
@@
 There is some previous work applying BERT to dialogue.
-\citet{baoPLATOPretrainedDialogue2019,chenSemanticallyConditionedDialog2019a} and both use BERT for dialogue generation tasks.
-Similarly \citet{vigComparisonTransferLearningApproaches2019} finds BERT useful for selecting a response from a list of candidate responses in a dialogue.
-Finally, \citet{mehriPretrainingMethodsDialog2019} evaluates BERT in various dialogue tasks including DAR, and find that a model incorporating BERT outperforms a baseline model.
+\citet{baoPLATOPretrainedDialogue2019} and \citet{chenSemanticallyConditionedDialog2019a} both use BERT for dialogue generation tasks.
+Similarly \citet{vigComparisonTransferLearningApproaches2019} find BERT useful for selecting a response from a list of candidate responses in a dialogue.
+Finally, \citet{mehriPretrainingMethodsDialog2019} evaluate BERT in various dialogue tasks including DAR, and find that a model incorporating BERT outperforms a baseline model.
 
 \paragraph{Fine-tuning vs.~further in-domain pre-training}
-Transfer learning schemes for pre-trained language models such as BERT draw on one or more of the following three adaptation strategies \citet{sunHowFineTuneBERT2019}:
+Transfer learning schemes for pre-trained language models such as BERT draw on one or more of the following three adaptation strategies \citep{sunHowFineTuneBERT2019}:
 \emph{further pre-training}, in which the model is trained in an un-supervised way, similar to its initial training scheme, but on data that is in-domain for the target task; 
@@
 
-\citet{petersTuneNotTune2019} investigate when and whether to fine-tune BERT for sentence classification tasks.
+\citet{petersTuneNotTune2019} investigate when it is best to fine-tune BERT for sentence classification tasks.
 They find that when the target task is very similar to the pre-training task, fine-tuning provides less of a performance boost.
-There is some conceptual relationship between DAR and next sentence prediction, since the a dialogue act constrains (or at least is predictive of) the dialogue act that follows it.
+We note that there is some conceptual relationship between DAR and next sentence prediction, since the a dialogue act constrains (or at least is predictive of) the dialogue act that follows it.
 
 \citet{petersTuneNotTune2019} also consider whether the similarity of the pre-training and target domains may have similar consequences, but don't find an effect of domain similarly for the natural language inference tasks they tested on.
-As discussed in \S\ref{sec:data}, however, there are dramatic differences between written text and transcribed dialogue which may mean that fine-tuning is necessary in this case.
+As discussed in \S\ref{sec:data}, however, there are dramatic differences between written text and transcribed dialogue which may make fine-tuning necessary for DAR.
 
@@
 \paragraph{Laughs in the data}
-The distribution of laughs in different dialogue acts has a rather uniform shape with a few outliers (see box plots).
-Figure \ref{fig:by-da} in Appendix~\ref{sec:suppl} provides a breakdown of dialogue act depending on whether current or adjacent utterances (the preceding utterance and the following one are counted as adjacent) contain laughter.\footnote{Note that SWDA has a ``Nonverbal'' dialogue act which is misleading with respect to laughter, because utterances only containing a single laughter token fall into this category, however they can serve, for example, to acknowledge a statement or to deflect a question  \citep{mazzocconi2019phd}.}
+The distribution of laughs in different dialogue acts has a rather uniform shape with a few outliers (Figure~\ref{fig:box}). 
+Figure~\ref{fig:by-da} in Appendix~\ref{sec:suppl} provides a breakdown of dialogue act depending on whether current or adjacent utterances (the preceding utterance and the following one are counted as adjacent) contain laughter.\footnote{Note that SWDA has a ``Nonverbal'' dialogue act which is misleading with respect to laughter, because utterances only containing a single laughter token fall into this category, however they can serve, for example, to acknowledge a statement or to deflect a question  \citep{mazzocconi2019phd}.}
 
@@
 \centering
+\begin{subfigure}[b]{0.55\textwidth}
   \includegraphics[width=0.9\linewidth]{img/box-swda.pdf}
-  \caption{Box plot for dialogue acts associated with laughter in SWDA.
-On the left: proportion of DAs having laughter in one of the adjacent utterances, on the right: proportion of DAs containing laughter.
-}
+  \caption{SWDA}
   \label{fig:box-swda}
-\end{figure}
+\end{subfigure}
 
-\begin{figure}
-  \centering
+\begin{subfigure}[b]{0.55\textwidth}
   \includegraphics[width=0.9\linewidth]{img/box-ami.pdf}
-  \caption{Box plot for dialogue acts associated with laughter in AMI-DA.
-On the left: proportion of DAs having laughter in one of the adjacent utterances, on the right: proportion of DAs containing laughter.
-}
+  \caption{AMI}
   \label{fig:box-ami}
+\end{subfigure}
+
+\caption{Box plots for dialogue acts associated with laughter. On the left: proportion of DAs having laughter in one of the adjacent utterances, on the right: proportion of DAs containing laughter. }
+\label{fig:box}
 \end{figure}
@@
 and its hidden state is passed to a simple linear classification layer over dialogue act tags.
-Conceptually, the encoded utterance represents the context-agnostic semantic content of the utterance, and the hidden state of the RNN represents the full discourse context.
+Conceptually, the encoded utterance represents the context-agnostic features of the utterance, and the hidden state of the RNN represents the full discourse context.
 
@@
 In the first experiment we investigated whether laughter, as an example of a dialogue-specific signal, is a helpful feature for DAR.
-Therefore, we train another version of each model: one containing laughs (\texttt{L}) and one with laughs left out (\texttt{NL}), and compare their performances in DAR task.
+Therefore, we train another version of each model: one that containing laughs (\texttt{L}) and one with laughs left out (\texttt{NL}), and compare their performances in DAR task.
 Table~\ref{table:laughter-total-acc} compares the results from applying the models with two different utterance encoders (\texttt{BERT}, \texttt{CNN}).
+
 First of all, we can see that \texttt{BERT} utterance encoder outperforms \texttt{CNN} in all the cases.
@@
 However there are some important exceptions, such as \emph{rhetorical questions}, that are misclassified as other forms of questions due to their surface question-like form.
-Importantly, laughter helpes to classify rhetorical questions correctly, this is because in a conversation it can be used as a device to cancel seriousness or sincerity \citep{ginzburg2015understanding,tepperman2006yeah}, in this case, of a question.
+Importantly, laughter helps to classify rhetorical questions correctly, this is because in a conversation it can be used as a device to cancel seriousness or sincerity \citep{ginzburg2015understanding,tepperman2006yeah}, in this case, of a question.
 Therefore questions, like the one we show in the example in Table~\ref{table:example-qh}, are easier to disambiguate with the help of laughter.
@@
 In order to further investigate the differences between the models and datasets, we looked at the dialogue act groups.
-Mapping all dialogue acts into four groups allows direct comparison between model performances in SWDA and AMI-DA.
+Mapping ground-truth labels and predictions into four groups allows direct comparison between model performances in SWDA and AMI-DA.
 Table~\ref{table:laughter-group-acc} compares accuracies between the two main groups: Forward-Communicative-Function and Backward-Communicative-Function (82.3\% of all DAs in SWDA and 76.7\% in AMI-DA).
@@
 The pre-trained model is more accurate than the randomly initialized model by several percentage points on both DA corpora,
-suggesting that BERT's extensive pre-training does provide some useful information for recoginizing different dialogue acts (Table~\ref{table:exp2}).
+suggesting that BERT's extensive pre-training does provide some useful information for recognizing different dialogue acts (Table~\ref{table:exp2}).
 This performance boost is much more pronounced in the macro-averaged F1 score,
@@
 \section{Discussion} % add items to discuss
-On the question of laughter impact, this study found out that laughter is more helpful in SWDA corpus than in AMI-DA.
-This observation may support the hypothesis that in SWDA due to the nature of interactions over the phone, dialogue participants can not rely on visual signals, such as gestures and facial expressions, therefore vocalisations, such as laughter, are more pronounced and therefore more helpful to disambiguate the utterances.
+On the question of laughter impact, this study found that laughter is more helpful in SWDA corpus than in AMI-DA.
+Due to the nature of interactions over the phone, SWDA dialogue participants can not rely on visual signals, such as gestures and facial expressions.
+Our results support the hypothesis that in SWDA, vocalizations such as laughter are more pronounced and therefore more helpful in disambiguating dialogue acts.
 
-This also can explain why all our best models perform better on SWDA: much more information that interlocutors and dialogue act annotators can rely on is present in the transcription of SWDA, whereas AMI-DA annotators receive clear instructions to pay attention to the videos \citep{GuidelinesDialogueAct2005}.
-This finding is consistent with that of \citet{bavelas2008gesturing} who demonstrated that in face-to-face dialogue visual components, such as gestures, can convey information that is independent from one conveyed with speech.
+This may also explain why all our best models perform better on SWDA: more of the information that interlocutors and dialogue act annotators rely on is present SWDA transcripts, whereas AMI-DA annotators receive clear instructions to pay attention to the videos \citep{GuidelinesDialogueAct2005}.
+This finding is consistent with that of \citet{bavelas2008gesturing} who demonstrate that in face-to-face dialogue, visual components, such as gestures, can convey information that is independent from what is conveyed by speech.
 
@@
 Furthermore, in relation to laughter, its form (duration, arousal level) can be informative about its function and position w.r.t. to laughable \citep{tian2016we,mazzocconi2019phd}.
+Incorporating such information is crucial if models pre-trained on large-scale text corpora are to be adapted for use in dialogue applications.
 
@@
 Further pre-training may be helpful for DAR too, if the in-domain or cross-domain corpus is large enough.
+It remains an open question, however, how well the text chat and social media domains transfer to transcribed dialogue
 
-It remains an open question how well the text chat domain transfers to transcribed dialogue and what pre-training schemes are best for the dialogue domain.
+Another avenue for future research is what pre-training schemes are best for the dialogue domain.
 The training scheme for RoBERTa \citep{liuRoBERTaRobustlyOptimized2019}, for example, leaves out next sentence prediction as a pre-training task because they do not find that it improves performance on question answering and natural language inference tasks.
-The same may not be true of dialogue, however.
+The same may not be true of dialogue, however, where sequentiality is essential.
 

### 2020-07-20 reports/Star-SEM Paper/starsem-paper.tex
add starsem dir

--- 2020-03-21 reports/ACL2020 Paper/acl2020-paper.tex
@@
 
+the in-domain corpus (\texttt{BERT+ID}) and the combined corpus (\texttt{BERT+CC}).
+
 We use the same pre-training task described by \citet{devlinBERTPretrainingDeep2018}, which combines masked token prediction and next sentence (utterance) detection. 
@@
 
-For each dialogue act corpus, we trained DAR models with BERT encoders pre-trained on the in-domain corpus (\texttt{BERT+ID}) and the combined corpus (\texttt{BERT+CC}).
+For each dialogue act corpus, we trained DAR models with BERT encoders that received additional pre-training on the three different pre-training corpora. 
 As before, we experimented with both the fine-tuning and frozen conditions.

### 2020-07-20 reports/Star-SEM Paper/starsem-paper.tex
typos, todos

@@
 \title{Tickle me BERT: Using laughter to probe pre-trained encoders for dialogue act recognition}
+% TODO rename
 
@@
 Our model predicts the most likely tag given the hidden state of the RNN at each position, though other work has shown that DAR benefits from more sophisticated approaches, such as conditional random field \citep{chenDialogueActRecognition2017} or uncertainty propagation \citep{tranPreservingDistributionalInformation2017}.
+% TODO: RNN with attention:
+% - Conversational Analysis using Utterance-level Attention-based Bidirectional Recurrent Neural Networks (Bothe et al., Interspeech 2018)
+% - A Unified Neural Architecture for Joint Dialog Act Segmentation and Recognition in Spoken Dialog System (Zhao and Kawahara, SIGdial 2018)
+
+% TODO DAR not for
 
@@
 
+% TODO: more refs
+% Chakravarty et al., "Dialog Acts Classification for Question-Answer Corpora," ASAIL 2019.
+% - Ribeiro et al., "Deep Dialog Act Recognition using Multiple Token, Segment, and Context Information Representations," Journal of Artificial Intelligence Research, 2019
+% - Yu et al., "MIDAS, A Dialog Act Annotation Scheme for Open-Domain Human-Machine Spoken Conversations," arxiv 2019.
+
 \paragraph{Fine-tuning vs.~further in-domain pre-training}
@@
 They find that when the target task is very similar to the pre-training task, fine-tuning provides less of a performance boost.
-We note that there is some conceptual relationship between DAR and next sentence prediction, since the a dialogue act constrains (or at least is predictive of) the dialogue act that follows it.
+We note that there is some conceptual relationship between DAR and next sentence prediction, since the dialogue act constrains (or at least is predictive of) the dialogue act that follows it.
 
@@
 Further pre-training may be helpful for DAR too, if the in-domain or cross-domain corpus is large enough.
-It remains an open question, however, how well the text chat and social media domains transfer to transcribed dialogue
+It remains an open question, however, how well the text chat and social media domains transfer to transcribed dialogue.
 

### 2020-07-20 reports/Star-SEM Paper/starsem-paper.tex
new abstract
more refs

--- 2020-07-20 reports/Star-SEM Paper/starsem-paper.tex
@@
   we look at how it uses laughter, a phenomenon specific to dialogue.
+
+  % New abstract?
+  % In this we investigate whether transformer models can learn to represent phenomena specific to dialogue.
+  % Laughter tokens which are not present in BERT pre-trained models can be learned during additional pre-training and fine-tuning on dialogue data. 
+  % We use dialogue act recognition as a proxy task and argue that laughter is a useful feature for it.
+  % We observe that pre-training and fine-tuning procedures are useful for learning laughter representation, and explore how well the model adapts to the dialogue domain.
+
 \end{abstract}
@@
 We observe that in the Switchboard dialogue corpus laughter comes about every 200 tokens.
-Laughter also relates to the discourse structure of dialogue and can relate to a laughable, which can be any an event or an entity in the discourse (and external perceived event as well).
+Laughter also relates to the discourse structure of dialogue and can relate to a laughable, which can be an event or an entity in the discourse (and external perceived event as well).
 Laughter can precede, follow or overlap the laughable, with the time alignment between the laughter and laughable dependent on who produces the laughable and the form of the laughter \citep{tian2016we}.
-Laughter can act as a contextual feature for determining the sincerity of an utterance, e.g. to when detecting sarcasm \citep{tepperman2006yeah}.
+Laughter can act as a contextual feature for determining the sincerity of an utterance, e.g. when detecting sarcasm \citep{tepperman2006yeah}.
 
@@
   \item Further pre-training with in-domain data shows promise for dialogue (\S\ref{sec:experiment3}), but further investigation with larger dialogue corpora is required.
+    % TODO: we did that but what can we conclude? Perhaps that the nature of the data is very different, so it is not very helpful..?
   \end{itemize}
@@
 Our model predicts the most likely tag given the hidden state of the RNN at each position, though other work has shown that DAR benefits from more sophisticated approaches, such as conditional random field \citep{chenDialogueActRecognition2017} or uncertainty propagation \citep{tranPreservingDistributionalInformation2017}.
+% TODO: RNN with attention: \citep{bothe2018conversational,zhao2018unified}
 
@@
 Recently, neural models trained on large datasets with various unsupervised tasks have found success creating sentence-level and contextual word representations. 
-BERT, a multi-layer transformer, is one such model \citep{devlinBERTPretrainingDeep2018} . 
+BERT, a multi-layer transformer, is one such model \citep{devlinBERTPretrainingDeep2018}. 
 BERT is pre-trained on two unsupervised tasks: \emph{masked token prediction} and \emph{next sentence prediction}.
@@
 Finally, \citet{mehriPretrainingMethodsDialog2019} evaluate BERT in various dialogue tasks including DAR, and find that a model incorporating BERT outperforms a baseline model.
+
+% TODO: \citep{chakravarty2019dialog,ribeiro2019deep,yu2019midas}
+% some motivation, maybe restate that we are not looking at the performance per say?
 

### 2020-07-20 reports/Star-SEM Paper/starsem-paper.tex
new title candidate
title and abstract (y)

@@
 
-\title{Tickle me BERT: Using laughter to probe pre-trained encoders for dialogue act recognition}
-% TODO rename
+\title{Can BERT learn dialogue specific phenomena? The case of laughter in dialogue act recognition. }
 
@@
 \begin{abstract}
-  In this paper, we investigate the usefulness of BERT for dialogue act recognition.
-  We are interested in both how useful the pre-training procedure is and 
-  how well the model adapts to the dialogue domain.
-  To confirm that the fine-tuned model learns to represent dialogical features, 
-  we look at how it uses laughter, a phenomenon specific to dialogue.
-
-  % New abstract?
-  % In this we investigate whether transformer models can learn to represent phenomena specific to dialogue.
-  % Laughter tokens which are not present in BERT pre-trained models can be learned during additional pre-training and fine-tuning on dialogue data. 
-  % We use dialogue act recognition as a proxy task and argue that laughter is a useful feature for it.
-  % We observe that pre-training and fine-tuning procedures are useful for learning laughter representation, and explore how well the model adapts to the dialogue domain.
-
+   In this work we investigate whether transformer models can learn to represent phenomena specific to dialogue.
+   Laughter tokens, which are not present in pre-trained BERT models, can be learned during additional pre-training and fine-tuning on dialogue data. 
+   We use dialogue act recognition as a proxy task and demonstrate that laughter is a useful feature for it.
+   We find that pre-training and fine-tuning procedures are useful for learning laughter representation, and explore how well the model adapts to the dialogue domain.
 \end{abstract}

### 2020-07-20 reports/Star-SEM Paper/starsem-paper.tex
more refs to RNN for DAR

@@
 Most successful neural approaches also model some notion of context.
-We follow previous work that models dialogue act sequences with an RNN over utterances \citep{kalchbrennerRecurrentConvolutionalNeural2013,tranHierarchicalNeuralModel2017,botheContextbasedApproachDialogue2018}.
+We follow previous work that models dialogue act sequences with an RNN over utterances \citep{kalchbrennerRecurrentConvolutionalNeural2013,tranHierarchicalNeuralModel2017,botheContextbasedApproachDialogue2018,bothe2018conversational,zhao2018unified}.
 Our model predicts the most likely tag given the hidden state of the RNN at each position, though other work has shown that DAR benefits from more sophisticated approaches, such as conditional random field \citep{chenDialogueActRecognition2017} or uncertainty propagation \citep{tranPreservingDistributionalInformation2017}.
-% TODO: RNN with attention: \citep{bothe2018conversational,zhao2018unified}
 

### 2020-07-20 reports/Star-SEM Paper/starsem-paper.tex
add opensubtitles results to table
BERT for DAR, note on LSTM

@@
 Similarly \citet{vigComparisonTransferLearningApproaches2019} find BERT useful for selecting a response from a list of candidate responses in a dialogue.
-Finally, \citet{mehriPretrainingMethodsDialog2019} evaluate BERT in various dialogue tasks including DAR, and find that a model incorporating BERT outperforms a baseline model.
+\citet{mehriPretrainingMethodsDialog2019} evaluate BERT in various dialogue tasks including DAR, and find that a model incorporating BERT outperforms a baseline model.
+Finally, \citet{chakravarty2019dialog} uses BERT for dialogue act classification for a proprietary domain and achieves promising results, and \citet{ribeiro2019deep} surpass the previous state-of-the-art on generic dialog act recognition for Switchboard and MRDA corpora.
+In our work we are not attempting to beat the current state-of-the-art due to the different aims of the study.
 
@@
 To test the effectiveness of BERT for DAR, we employ a simple neural architecture with two components: an encoder that vectorizes utterances, and a sequence model that predicts dialogue act tags from the vectorized utterances (Figure~\ref{fig:model-architecture}).
-Since we are primarily interested in comparing different utterance encoders, we use a basic RNN as the sequence model in every configuration. 
+Since we are primarily interested in comparing different utterance encoders, we use a basic RNN as the sequence model in every configuration.\footnote{We have experimented with LSTM as a the sequence model, but the accuracy was not significantly different compared to RNN.
+It can be explained by the absence of longer distance dependencies on this level of our model.}
 The RNN takes the encoded utterance as input at each time step,
@@
            & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
-\texttt{BERT-FT}    & 45.99                  & 76.93                    & 50.03                  & 66.95                    \\
-\texttt{BERT+ID-FT} & 45.48                  & 77.02                    & 46.56                  & 68.66                    \\
-\texttt{BERT+CC-FT} & 47.78                  & 77.35                    & 48.72                  & 66.58                    \\ \midrule
-\texttt{BERT-FZ}    & 7.75                   & 55.61                    & 14.44                  & 46.60                    \\
-\texttt{BERT+ID-FZ} & 6.46                   & 52.30                    & 14.43                  & 48.07                    \\
-\texttt{BERT+CC-FZ} & 5.76                   & 51.14                    & 12.56                  & 42.42                    \\ \bottomrule
+\texttt{BERT-FT}    & 36.75                  & 76.60                    & 43.42                  & 64.93                    \\
+\texttt{BERT+ID-FT} & 43.63                  & 77.01                    & 46.70                  & \textbf{68.88}           \\
+\texttt{BERT+CC-FT} & \textbf{47.78}         & \textbf{77.35}           & \textbf{48.86}         & 68.79                    \\ 
+\texttt{BERT+OS-FT} & 41.42                  & 76.95                    & 48.65                  & 68.07                    \\ \midrule
+\texttt{BERT-FZ}    &  7.75                  & 55.61           & 14.86                  & 48.34                    \\
+\texttt{BERT+ID-FZ} &  6.46                  & 52.30                    & 14.48                  & 48.18                    \\
+\texttt{BERT+CC-FZ} &  5.76                  & 51.14                    & 11.34                  & 40.48                    \\ 
+\texttt{BERT+OS-FZ} &  \textbf{9.60}         & \textbf{57.67}           & \textbf{17.03}         & \textbf{51.03}           \\ \bottomrule
 \end{tabular}

### 2020-07-20 reports/Star-SEM Paper/starsem-paper.tex
add results discussion

--- 2020-07-20 reports/Star-SEM Paper/starsem-paper.tex
@@
 
-\title{Can BERT learn dialogue specific phenomena? The case of laughter in dialogue act recognition. }
+\title{Can BERT learn dialogue-specific phenomena? The case of laughter in dialogue act recognition. }
 
@@
 
+\subsection{Pre-training corpora}
+
+We also experiment with three unlabeled dialogue corpora, which we use to provide further pre-training for the BERT encoder.
+
+The first two corpora are constructed from the same source as the dialogue act corpora.
+We use the SWDA portion of the un-labeled Switchboard corpus (SWBD) and the entire AMI corpus (including the 32 dialogues with no human-annotated DA tags that are not included in the DAR training set).
+In both cases, we exclude dialogues that are reserved for DAR testing.
+
+We also experiment with a much larger a corpus constructed from OpenSubtitles \citep{Lison2016}.
+We used a manually constructed list of words frequenty used to refer to laughter in subtitles and replaced every occurance of one of these words with the special laughter token. 
+Then, we collected every English-language subtitle file in which at least 1\% of the utterances contained laughter (about 11\% of the total).
+Because utterances are not labeled with speaker in the OpenSubtitles corpus, we randomly assigned a speaker token to each utterance to maintain the format of the other dialouge corpora.
+
+The pre-training corpora were prepared for the combined maksed language modeling and next sentence (utterance) prediction task, as described dy \citet{devlinBERTPretrainingDeep2018}.
+For the smaller SWBD and AMI corpora, we generate and train on multiple epochs of data.
+Since there is randomness in the data preparation (e.g., which distrcactor sentences are chosen and which tokens are masked), we generate each training epoch separately.\footnote{Also see the Hugging Face \href{https://github.com/huggingface/transformers/tree/1.1.0/examples/lm_finetuning}{finetuning example}.}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{@{}llll@{}}
+\toprule
+       & tokens & \% laughs & epochs\\ \midrule
+AMI           & 1M     & 1.3             & 10     \\
+SWBD          & 1.5M   & 0.5             & 10     \\
+OpenSubtitles & 350M   & 0.3             & 1      \\ \bottomrule
+\end{tabular}
+\caption{Pre-training corpora, showing laughter representation as a percentage of total tokens and number of pre-training epochs generated.}\label{tab:pretraining-corpora}
+\end{table}
+
 \paragraph{}
@@
 
-Next, we assess the effect of further in-domain pre-training on BERT's performance as an utterance encoder.\footnote{
+Next, we assess the effect of additional dialogue pre-training on BERT's performance as an utterance encoder.\footnote{
 In-domain pre-training is sometimes referred to as \textit{fine-tuning}, but we reserve that term for task-specific training on labeled data.}
-We construct pre-training corpora from the SWDA portion of the un-labeled Switchboard corpus and from the entire AMI corpus (including the 32 dialogues with no human-annotated DA tags that are not included in the DAR training set).
-In both cases, we exclude dialogues that are reserved for DAR testing.
+\citet{sunHowFineTuneBERT2019} has reported that performing additional pre-training on unlabeled in-domain data improves performance on classification tasks. 
+We want to see if BERT can bennefit from pre-training, on dialogue data, including from data outside the immediate target domain.
 
-the in-domain corpus (\texttt{BERT+ID}) and the combined corpus (\texttt{BERT+CC}).
+For each of the target corpora (SWDA and AMI-DA), we compare four different pre-training conditions: 
+The in-domain corpus (\texttt{ID}), consisting of the AMI pre-training corpus for the AMI-DA model and the SWBD pre-traning corpus for the SWDA model; 
+the cross-domain corpus (\texttt{CC}), consisting of both the AMI and SWBD pre-training corpora; 
+the OpenSubtitles corpus (\texttt{OS});
+and finally the standard BERT\textsubscript{BASE} model with no addational pre-training.
+As before, we experiment with both frozen and fine-tuned models at the task training stage.
 
-We use the same pre-training task described by \citet{devlinBERTPretrainingDeep2018}, which combines masked token prediction and next sentence (utterance) detection. 
-Distractor utterances are drawn at random from another dialogue in the corpus
-and each epoch is generated separately so that different distractor sentences appear each time.
-We pre-trained three BERT models: with Switchboard (10 epochs), AMI (10 epochs), and the combined corpus (5 epochs).
+We performed 10 epochs of pre-training on the in-domain models and 5 epochs of pre-training on the cross-domain models so that the total amount of training data was comparable.
+The OpenSubtitles models trained on much more data (see Table~\ref{tab:pretraining-corpora}) and were trained for only one epoch.
 
-For each dialogue act corpus, we trained DAR models with BERT encoders that received additional pre-training on the three different pre-training corpora. 
-As before, we experimented with both the fine-tuning and frozen conditions.
+In the fine-tuned condition, additional pre-training offers a modest boost in overall accuracy and a substantial boost to the macro-average scores.
+Any of the dialogue corpora appear helpful, but the cross-domain corpus generally provides the largest boost.
+In the frozen condition, only the very large OpenSubtitles corpus is helpful, suggesting that when adapting BERT to dialogue, the size of the corpus is more important than its quality or fidelity to the target domain.
+Still, pre-training provides nowhere near the performance improvement achieved by fine-tuning on the target task.
 
-The results are mixed.
-In-domain pre-training offers a modest boost in overall accuracy,
-but the macro-average scores are almost uniformly worse (Table~\ref{table:exp3}).
-%Indeed, when BERT is frozen during fine-tuning, the model that received no further pre-training performs better by more than 3 percentage points (Table~\ref{tab:exp3-recall}).
-To fully assess the potential impact of further in-domain pre-training, a larger dialogue corpus is required.
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
 \begin{table}[]

### 2020-07-21 reports/Star-SEM Paper/starsem-paper.tex
use lowest loss epoch, not highest accuracy
S-V agreement

@@
 \citet{mehriPretrainingMethodsDialog2019} evaluate BERT in various dialogue tasks including DAR, and find that a model incorporating BERT outperforms a baseline model.
-Finally, \citet{chakravarty2019dialog} uses BERT for dialogue act classification for a proprietary domain and achieves promising results, and \citet{ribeiro2019deep} surpass the previous state-of-the-art on generic dialog act recognition for Switchboard and MRDA corpora.
+Finally, \citet{chakravarty2019dialog} use BERT for dialogue act classification for a proprietary domain and achieves promising results, and \citet{ribeiro2019deep} surpass the previous state-of-the-art on generic dialog act recognition for Switchboard and MRDA corpora.
 In our work we are not attempting to beat the current state-of-the-art due to the different aims of the study.
@@
                            & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
-\texttt{BERT-FT} & 45.99           & 76.93                    & 50.03                  & 66.94                    \\
-\texttt{BERT-RI} & 32.18           & 73.80                    & 33.45                  & 61.53                    \\
-\texttt{BERT-FZ} & 7.75            & 55.61                    & 14.44                  & 46.59 \\
+\texttt{BERT-FT} & 36.75           & 76.60                    & 43.42                  & 64.93                    \\
+\texttt{BERT-RI} & 32.18           & 73.80                    & 34.88                  & 60.89                    \\
+\texttt{BERT-FZ} & 7.75            & 55.61                    & 14.86                  & 48.34 \\
   \bottomrule

### 2020-07-21 reports/Star-SEM Paper/starsem-paper.tex
typo

@@
 the OpenSubtitles corpus (\texttt{OS});
-and finally the standard BERT\textsubscript{BASE} model with no addational pre-training.
+and finally the standard BERT\textsubscript{BASE} model with no additional pre-training.
 As before, we experiment with both frozen and fine-tuned models at the task training stage.

### 2020-07-21 reports/Star-SEM Paper/starsem-paper.tex
add to OS discussion

--- 2020-07-20 reports/Star-SEM Paper/starsem-paper.tex
@@
    Laughter tokens, which are not present in pre-trained BERT models, can be learned during additional pre-training and fine-tuning on dialogue data. 
-   We use dialogue act recognition as a proxy task and demonstrate that laughter is a useful feature for it.
+   We use dialogue act recognition as a proxy task to demonstrate that laughter can help disambiguate between certain communicative intents.
    We find that pre-training and fine-tuning procedures are useful for learning laughter representation, and explore how well the model adapts to the dialogue domain.
@@
   \item Standard BERT pre-training is useful for DAR, but the model performs poorly without fine-tuning (\S\ref{sec:experiment2})
-  \item Further pre-training with in-domain data shows promise for dialogue (\S\ref{sec:experiment3}), but further investigation with larger dialogue corpora is required.
+  \item Further pre-training with data from the target domain shows promise for dialogue, but we find mixed results when pre-training with a larger corpus domain dialogical data from outside the target domain (\S\ref{sec:experiment3}).
     % TODO: we did that but what can we conclude? Perhaps that the nature of the data is very different, so it is not very helpful..?
@@
 Word vectors \citep[e.g.,][]{mikolovDistributedRepresentationsWords2013,penningtonGloveGlobalVectors2014} are a ubiquitous example of transfer learning in NLP.
-We note, however, that pre-trained word vectors are not always useful when applied to dialogue domains \cite{cerisaraEffectsUsingWord2vec2017}.
+We note, however, that pre-trained word vectors are not always useful when applied to dialogue \cite{cerisaraEffectsUsingWord2vec2017}.
 
@@
 
-First of all, we can see that \texttt{BERT} utterance encoder outperforms \texttt{CNN} in all the cases.
+First of all, we can see that the \texttt{BERT} utterance encoder outperforms \texttt{CNN} in all the cases.
 From observing the effect of laughters, we can see differences in performance depending on the dialogue act, regardless how often laughter occurs in the current or adjacent utterances (see Figure~\ref{fig:by-da} in Appendix~\ref{sec:suppl}).
@@
 \end{tabular}
-  \caption{Comparison of macro-average F1 and accuracy  with further in-domain (\texttt{ID}) and combined corpus (\texttt{CC}) dialogue pre-training,
-    for both the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions.}
+\caption{Comparison of macro-average F1 and accuracy with further in-domain (\texttt{ID}), combined corpus (\texttt{CC}), and OpenSubtitles (\texttt{OS}) dialogue pre-training,
+    for the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions.}
   \label{table:exp3}
@@
 
-Although our experiments with further pre-training were inconclusive, \citet{baoPLATOPretrainedDialogue2019} finds that further pre-training BERT on a large-scale Reddit and Twitter corpus is helpful for response selection.
-Further pre-training may be helpful for DAR too, if the in-domain or cross-domain corpus is large enough.
-It remains an open question, however, how well the text chat and social media domains transfer to transcribed dialogue.
+Our experiments with further pre-training were inconclusive. 
+Although pre-training on data from the target domain proved useful, training on a much larger corpus of dialogue-like data (OpenSubtitles) yielded less substantial improvements in the fine-tuned condition.
+\citet{baoPLATOPretrainedDialogue2019} finds that further pre-training BERT on a large-scale Reddit and Twitter corpus is helpful for response selection, but given unimpressive results with subtitles, it remains an open question how well the text chat and social media domains transfer to transcribed dialogue.
 

### 2020-07-21 reports/Star-SEM Paper/starsem-paper.tex
typos, commas

@@
 \citet{baoPLATOPretrainedDialogue2019} and \citet{chenSemanticallyConditionedDialog2019a} both use BERT for dialogue generation tasks.
-Similarly \citet{vigComparisonTransferLearningApproaches2019} find BERT useful for selecting a response from a list of candidate responses in a dialogue.
+Similarly, \citet{vigComparisonTransferLearningApproaches2019} find BERT useful for selecting a response from a list of candidate responses in a dialogue.
 \citet{mehriPretrainingMethodsDialog2019} evaluate BERT in various dialogue tasks including DAR, and find that a model incorporating BERT outperforms a baseline model.
@@
 To test the effectiveness of BERT for DAR, we employ a simple neural architecture with two components: an encoder that vectorizes utterances, and a sequence model that predicts dialogue act tags from the vectorized utterances (Figure~\ref{fig:model-architecture}).
-Since we are primarily interested in comparing different utterance encoders, we use a basic RNN as the sequence model in every configuration.\footnote{We have experimented with LSTM as a the sequence model, but the accuracy was not significantly different compared to RNN.
+Since we are primarily interested in comparing different utterance encoders, we use a basic RNN as the sequence model in every configuration.\footnote{We have experimented with LSTM as the sequence model, but the accuracy was not significantly different compared to RNN.
 It can be explained by the absence of longer distance dependencies on this level of our model.}
@@
 Most of the misclassifications fall into the majority classes, such as \emph{sd} (Statement-non-opinion), in the left edge of the matrix.
-However there are some important exceptions, such as \emph{rhetorical questions}, that are misclassified as other forms of questions due to their surface question-like form.
+However, there are some important exceptions, such as \emph{rhetorical questions}, that are misclassified as other forms of questions due to their surface question-like form.
 Importantly, laughter helps to classify rhetorical questions correctly, this is because in a conversation it can be used as a device to cancel seriousness or sincerity \citep{ginzburg2015understanding,tepperman2006yeah}, in this case, of a question.
-Therefore questions, like the one we show in the example in Table~\ref{table:example-qh}, are easier to disambiguate with the help of laughter.
+Therefore, questions, like the one we show in the example in Table~\ref{table:example-qh}, are easier to disambiguate with the help of laughter.
 \begin{table}
@@
 \citet{sunHowFineTuneBERT2019} has reported that performing additional pre-training on unlabeled in-domain data improves performance on classification tasks. 
-We want to see if BERT can bennefit from pre-training, on dialogue data, including from data outside the immediate target domain.
+We want to see if BERT can benefit from pre-training, on dialogue data, including from data outside the immediate target domain.
 

### 2020-07-21 reports/Star-SEM Paper/starsem-paper.tex
majority class baselines
samll fixes

@@
    In this work we investigate whether transformer models can learn to represent phenomena specific to dialogue.
-   Laughter tokens, which are not present in pre-trained BERT models, can be learned during additional pre-training and fine-tuning on dialogue data. 
-   We use dialogue act recognition as a proxy task to demonstrate that laughter can help disambiguate between certain communicative intents.
-   We find that pre-training and fine-tuning procedures are useful for learning laughter representation, and explore how well the model adapts to the dialogue domain.
+   Laughter tokens, which are not present in pre-trained BERT models, can be learned with additional pre-training and fine-tuning on dialogue data. 
+   We use dialogue act recognition as a proxy task to demonstrate that laughter can help to disambiguate between certain communicative intents.
+   We find that pre-training and fine-tuning procedures are useful for learning laughter representations, and explore how well the model adapts to the dialogue domain.
 \end{abstract}
@@
 We observe that in the Switchboard dialogue corpus laughter comes about every 200 tokens.
-Laughter also relates to the discourse structure of dialogue and can relate to a laughable, which can be an event or an entity in the discourse (and external perceived event as well).
+Laughter also relates to the discourse structure of dialogue and can relate to a \emph{laughable}, which can be an event or an entity in the discourse (or external perceived event as well).
 Laughter can precede, follow or overlap the laughable, with the time alignment between the laughter and laughable dependent on who produces the laughable and the form of the laughter \citep{tian2016we}.
@@
 Using this task we investigate whether transfer learning techniques based on pre-trained language models, such as BERT \citep{devlinBERTPretrainingDeep2018}, are useful for dialogue. 
-By looking at laughter, which is certainly missing in pre-trained model, we can determine whether the domain-adapted model can make use of dialogue-specific features.
+By looking at laughter, which is certainly missing in the stadnard pre-training corpus, we can determine whether the pre-training is used in the representation dialogue-specific features.
 
@@
   \item Standard BERT pre-training is useful for DAR, but the model performs poorly without fine-tuning (\S\ref{sec:experiment2})
-  \item Further pre-training with data from the target domain shows promise for dialogue, but we find mixed results when pre-training with a larger corpus domain dialogical data from outside the target domain (\S\ref{sec:experiment3}).
+  \item Further pre-training with data from the target domain shows promise for dialogue, but we find mixed results when pre-training with a larger corpus of dialogical data from outside the target domain (\S\ref{sec:experiment3}).
     % TODO: we did that but what can we conclude? Perhaps that the nature of the data is very different, so it is not very helpful..?
@@
 
-We also experiment with three unlabeled dialogue corpora, which we use to provide further pre-training for the BERT encoder.
+We also experiment with three unlabeled dialogue corpora (Table~\ref{tab:pretraining-corpora}), which we use to provide further pre-training for the BERT encoder.
 
@@
 For the smaller SWBD and AMI corpora, we generate and train on multiple epochs of data.
-Since there is randomness in the data preparation (e.g., which distrcactor sentences are chosen and which tokens are masked), we generate each training epoch separately.\footnote{Also see the Hugging Face \href{https://github.com/huggingface/transformers/tree/1.1.0/examples/lm_finetuning}{finetuning example}.}
+Since there is randomness in the data preparation (e.g., which distrcactor sentences are chosen and which tokens are masked), we generate each training epoch separately.\footnote{For details, see the \href{https://github.com/huggingface/transformers/tree/1.1.0/examples/lm_finetuning}{finetuning example} from Hugging Face.}
 
@@
     \texttt{CNN-NL}   & 37.23 & 75.08 & 38.37 & 63.46        \\
-    \texttt{CNN-L}    & 27.59 & 75.40 & 37.94 & 64.30        \\ \bottomrule
+    \texttt{CNN-L}    & 27.59 & 75.40 & 37.94 & 64.30        \\ \midrule
+    Majority class    & 0.78  & 33.56 &  1.88 & 28.27      \\ \bottomrule
 
@@
 \texttt{BERT-RI} & 32.18           & 73.80                    & 34.88                  & 60.89                    \\
-\texttt{BERT-FZ} & 7.75            & 55.61                    & 14.86                  & 48.34 \\
-  \bottomrule
+\texttt{BERT-FZ} & 7.75            & 55.61                    & 14.86                  & 48.34 \\ \midrule
+    Majority class    & 0.78  & 33.56 &  1.88 & 28.27      \\ \bottomrule
 \end{tabular}
@@
 \texttt{BERT+CC-FZ} &  5.76                  & 51.14                    & 11.34                  & 40.48                    \\ 
-\texttt{BERT+OS-FZ} &  \textbf{9.60}         & \textbf{57.67}           & \textbf{17.03}         & \textbf{51.03}           \\ \bottomrule
+\texttt{BERT+OS-FZ} &  \textbf{9.60}         & \textbf{57.67}           & \textbf{17.03}         & \textbf{51.03}           \\ \midrule
+    Majority class  & 0.78                   & 33.56                    &  1.88                  & 28.27      \\ \bottomrule
 \end{tabular}

### 2020-07-21 reports/Star-SEM Paper/starsem-paper.tex
typo

@@
 Using this task we investigate whether transfer learning techniques based on pre-trained language models, such as BERT \citep{devlinBERTPretrainingDeep2018}, are useful for dialogue. 
-By looking at laughter, which is certainly missing in the stadnard pre-training corpus, we can determine whether the pre-training is used in the representation dialogue-specific features.
+By looking at laughter, which is certainly missing in the stadnard pre-training corpus, we can determine whether the pre-training is used in the representation of dialogue-specific features.
 

### 2020-12-01 reports/CLASP seminar/abstract.tex
seminar absract

--- 2019-12-09 reports/ACL2020 Paper/acl2020-paper.tex
@@
-%
-% File acl2020.tex
-%
-%% Based on the style files for ACL 2020, which were
-%% Based on the style files for ACL 2018, NAACL 2018/19, which were
-%% Based on the style files for ACL-2015, with some improvements
-%%  taken from the NAACL-2016 style
-%% Based on the style files for ACL-2014, which were, in turn,
-%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
-%% EACL-2009, IJCNLP-2008...
-%% Based on the style files for EACL 2006 by 
-%%e.agirre@ehu.es or Sergi.Balari@uab.es
-%% and that of ACL 08 by Joakim Nivre and Noah Smith
-
 \documentclass[11pt,a4paper]{article}
-\usepackage[hyperref]{acl2020}
-\usepackage{times}
-\usepackage{latexsym}
-\renewcommand{\UrlFont}{\ttfamily\small}
-\usepackage{booktabs}
-\usepackage{multirow}
-\usepackage{tikz}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{natbib}
-% This is not strictly necessary, and may be commented out,
-% but it will improve the layout of the manuscript,
-% and will typically save some space.
-\usepackage{microtype}
-
-\usepackage{tabularx}
-\newcolumntype{L}{>{\raggedright\arraybackslash}X}
-
-%\aclfinalcopy % Uncomment this line for the final submission
-%\def\aclpaperid{***} %  Enter the acl Paper ID here
-
-%\setlength\titlebox{5cm}
-% You can expand the titlebox if you need extra space
-% to show all the authors. Please do not make the titlebox
-% smaller than 5cm (the original size); we will check this
-% in the camera-ready version and ask you to change it back.
-
-\newcommand\BibTeX{B\textsc{ib}\TeX}
 
@@
 
-\author{First Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  \texttt{email@domain} \\\And
-  Second Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  \texttt{email@domain} \\}
-
-\date{}
+\date{February 26, 2020}
+\author{Bill Noble \& Vladislav Maraev}
 
@@
 \maketitle
-\begin{abstract}
-  In this paper, we investigate the usefulness of BERT for dialogue act recognition.
+\pagenumbering{gobble}
+
+We investigate the usefulness of BERT for dialogue act recognition.
 We are interested in both how useful the pre-training procedure is and 
@@
 we look at how it uses laughter, a phenomenon specific to dialogue.
-\end{abstract}
-
-% INTRODUCTION
-
-Recently, large-scale language models, trained on massive corpora of text data, have achieved state-of-the-art results on a variety of traditional NLP tasks.
-It is still uncertain whether these models might be useful for processing dialogue, and if so, whether they can adapt to make use of dialogue-specific features.
-
-Dialogue, especially spoken dialogue, is radically different from the kind of data that neural language models are pre-trained on.
-In the example from the Switchboard corpus, shown in Table~\ref{table:example}, it is evident that the syntactic structure of dialogue is very different from  written text, even if one imagines a script for a movie or a play.
-Not only is the internal structure of contributions different---with features such as disfluencies, repair, incomplete sentences, and various vocal sounds---but the sequential structure of the discourse is also very different.
-In dialogue, speakers take turns and switch perspectives.
-More generally, the way that utterances contribute to and cohere with the discourse is different from the relationship between sentences in a piece of written text.
-
-One important dialogical feature missing from text data is laughter, which is ubiquitous in our everyday interactions.
-We observe that in the Switchboard dialogue corpus laughter comes about every 200 tokens.
-Laughter also relates to the discourse structure of dialogue and can relate to a laughable, which can be any an event or an entity in the discourse (and external perceived event as well).
-Laughter can precede, follow or overlap the laughable, with the time alignment between the laughter and laughable dependent on who produces the laughable and the form of the laughter \citep{tian2016we}.
-Laughter can act as a contextual feature for determining the sincerity of an utterance, in order to understand sincerity of an utterance, e.g. to detect sarcasm \citep{tepperman2006yeah}.
-
-\begin{table}
-      \small
-  \centering
-  \begin{tabularx}{\linewidth}{llL}
-    \toprule
-    Speaker & DA & Utterance \\ \midrule
-    A	&sd	& Well, I'm the kind of cook that I don't normally measure things,  \\
-    A	&sd	& I just kind of throw them in \\
-    A	&sd	& and, you know, I don't to the point of, you know, measuring down to the exact amount that they say.  \\
-    B	&sv	& That means you're a real cook. \\
-    A	&bd	& \texttt{<Laughter>} Oh, is that what it means.  \\
-    A	&b	& Uh-huh.  \\
-    A	&x	& \texttt{<Laughter>}.\\
-             \bottomrule
-  \end{tabularx}
-  \caption{Example from the SWDA corpus (sw2827).
-Dialogue acts: \emph{sd}---Statement-non-opinion, \emph{sv}---Statement-opinion, \emph{bd}---Downplayer, \emph{b}---Backchannel, \emph{x}---Non-verbal.
-}
-  \label{table:example}
-\end{table}
-
-We use dialogue act recognition (DAR) as a proxy task, since both the internal content of contributions, and their sequential structure have bearing on this task.
-DAR is the task of assigning a dialogue act to every utterance in the dialogue, according to dialogue act that they perform.
-This is the way to investigate whether transfer learning techniques based on pre-trained language models, such as BERT \citep{devlinBERTPretrainingDeep2018}, are useful for dialogue.
-We looked at laughter that is certainly missing in pre-trained model, and discovered that it can be useful to disambiguate a dialogue act.
-
-\paragraph{Contributions}
-The main results of this paper have to do with to the usefulness of language model fine-tuning for DAR, the impact of laughter on DAR, and the relationship between the two.
-\begin{itemize}
-  \item Laughter is useful for dialogue act recognition, and its impact varies across different dialogue acts (\S\ref{sec:experiment1}).
-  \item During fine-tuning, BERT learns to represent laughter, a dialogical feature not seen in pre-training (\S\ref{sec:experiment1} and \S\ref{sec:experiment2}).
-  \item Standard BERT pre-training is useful for DAR, but the model performs poorly without fine-tuning (\S\ref{sec:experiment2})
-  \item Further pre-training with in-domain data shows promise for dialogue (\S\ref{sec:experiment3}), but further investigation with larger dialogue corpora is required.
-  \end{itemize}
-
-In the following section we provide more details about the dialogue act recognition task and transfer learning techniques.
-
-\section{Background}
-
-\subsection{Dialogue Act Recognition}
-The concept of a dialogue act is based on that of speech acts \citep{austinHowThingsWords2009}.
-Breaking with classical semantic theory, speech act theory considers not only the propositional content of an utterance but also the actions, such as \emph{promising} or \emph{apologizing}, it carries out.
-Dialogue acts extend the concept of the speech act, with a focus on the interactional nature of most speech.
-DAMSL \citep{coreCodingDialogsDAMSL1997}, for example, is an influential dialogue act tagging scheme where dialogue acts are defined in part by whether they have a \emph{forward-looking} function (are expecting a response) or \emph{backward-looking} function (are in response to a previous utterance).
-
-DAR is the task of labeling utterances with the dialogue act they perform from a given set of dialogue act tags.
-As with other sequence labeling tasks in NLP, some notion of context is helpful in DAR.
-One of the first performant machine learning models for DAR was a Hidden Markov Model that used various lexical and prosodic features as input \citep{stolckeDialogueActModeling2000}.
-
-Most successful neural approaches also model some notion of context.
-We follow previous work that models dialogue act sequences with an RNN over utterances \citep{kalchbrennerRecurrentConvolutionalNeural2013,tranHierarchicalNeuralModel2017,botheContextbasedApproachDialogue2018}.
-Our model predicts the most likely tag given the hidden state of the RNN at each position, though other work has shown that DAR benefits from more sophisticated approaches, such as conditional random field \citep{chenDialogueActRecognition2017} or uncertainty propagation \citep{tranPreservingDistributionalInformation2017}.
-
-\subsection{Transfer learning for NLP}
-Transfer learning techniques allow a model trained on one task---often unsupervised---to be applied to another. 
-Since annotating natural language data is expensive, there is a lot of interest in transfer learning for natural language processing. 
-Word vectors \citep[e.g.,][]{mikolovDistributedRepresentationsWords2013,penningtonGloveGlobalVectors2014} are a ubiquitous example of transfer learning in NLP.
-We note, however, that pre-trained word vectors are not always useful when applied to dialogue domains \citet{cerisaraEffectsUsingWord2vec2017}.
-
-Recently, neural models trained on large datasets with various unsupervised tasks have found success creating sentence-level and contextual word representations. 
-BERT, a multi-layer transformer, is one such model \citep{devlinBERTPretrainingDeep2018} . 
-BERT is pre-trained on two unsupervised tasks: \emph{masked token prediction} and \emph{next sentence prediction}.
-In masked token prediction, some percentage of words are randomly replaced with a \texttt{[MASK]} token, and the model is trained to predict the identity of these tokes based on the context sentence.
-In next sentence prediction, the model is give two sentences and trained to predict whether the second sentence follows the first in the original text, or if it was randomly chosen from elsewhere in the corpus.
-After pre-training, BERT can be applied to a supervised task by adding additional un-trained layers that take the hidden state of one or more of BERT's layers as input.
-
-There is some previous work applying BERT to dialogue.
-\citet{baoPLATOPretrainedDialogue2019,chenSemanticallyConditionedDialog2019a} and both use BERT for dialogue generation tasks.
-Similarly \citet{vigComparisonTransferLearningApproaches2019} finds BERT useful for selecting a response from a list of candidate responses in a dialogue.
-Finally, \citet{mehriPretrainingMethodsDialog2019} evaluates BERT in various dialogue tasks including DAR, and find that a model incorporating BERT outperforms a baseline model.
-
-\paragraph{Fine-tuning vs.~further in-domain pre-training}
-Transfer learning schemes for pre-trained language models such as BERT draw on one or more of the following three adaptation strategies \citet{sunHowFineTuneBERT2019}:
-\emph{further pre-training}, in which the model is trained in an un-supervised way, similar to its initial training scheme, but on data that is in-domain for the target task; 
-\emph{single-task fine-tuning}, in which the model's encoder layers are optimized during training for the target task;
-and \emph{multi-task fine-tuning}, in which models with shared encoder layers are jointly trained on several related tasks.
-In this paper, we investigate the first two methods and their combination, as applied to DAR.
-
-Regardless of whether an encoder model has undergone further in-domain pre-training, the choice of whether to fine-tune during task training remains.
-Freezing the encoder model during task training is more efficient, since the gradient of the loss function need only be computed for the task-specific layers.
-However, fine-tuning can lead to better performance since the encoding itself is adapted to the target task and domain.
-
-\citet{petersTuneNotTune2019} investigate when and whether to fine-tune BERT for sentence classification tasks.
-They find that when the target task is very similar to the pre-training task, fine-tuning provides less of a performance boost.
-There is some conceptual relationship between DAR and next sentence prediction, since the a dialogue act constrains (or at least is predictive of) the dialogue act that follows it.
-
-\citet{petersTuneNotTune2019} also consider whether the similarity of the pre-training and target domains may have similar consequences, but don't find an effect of domain similarly for the natural language inference tasks they tested on.
-As discussed in \S\ref{sec:data}, however, there are dramatic differences between written text and transcribed dialogue which may mean that fine-tuning is necessary in this case.
-
-\paragraph{} In the next section, we will present the datasets that we will use in our experiments along with their distinctive features.
-
-\section{Data}\label{sec:data}
-We perform experiments on the Switchboard Dialogue Act Corpus (SWDA), which is a subset of the larger Switchboard corpus, and the dialogue act-tagged portion of the AMI Meeting Corpus (AMI-DA). 
-SWDA is tagged with a set of 220 dialogue act tags which, following  \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}, we cluster into a smaller set of 42 tags.
-AMI uses a smaller tagset of 16 dialogue acts \citep{GuidelinesDialogueAct2005}.
-
-% - DA distribution              % Vlad
-
-\begin{table}[]
-\centering
-\begin{tabular}{@{}ll@{}}
-\toprule
-\textbf{Switchboard}       & \textbf{AMI Corpus}                     \\ \midrule
-Dyadic                     & Multi-party                             \\
-Casual conversation        & Mock business meeting                   \\
-Telephone                  & In-person \& video                      \\ \midrule
-English                    & English                                 \\ 
-Native speakers            & Native \& non-native speakers           \\ 
-early '90s                 & 2000s                                   \\ \midrule
-2200 conversations         & 171 meetings                            \\
-  \hspace{1em} 1155 in SWDA               & \hspace{1em} 139 in AMI-DA                           \\
-400k utterances             & 118k utterances                         \\
-3M tokens                  & 1.2M tokens                             \\ \bottomrule
-\end{tabular}
-  \caption{Comparison between Switchboard and the AMI Meeting Corpus}
-  \label{table:corpora}
-\end{table}
-
-\paragraph{Preprocessing}
-% - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, removing laughter % Bill
-
-We make an effort to normalize transcription conventions across SWDA and AMI.
-We remove disfluency annotations and slashes from the end of utterances in SWDA.
-In both corpora, acronyms are tokenized as individual letters. 
-All utterances are lower-cased.
-
-Utterances are tokenized using BERT's word piece tokenizer with a vocabulary of 30,000.
-We add a special laughter token to the vocabulary and map all transcribed laughter to that token.
-We also add five speaker tokens and prepend each utterance with a speaker token that uniquely identifies the corresponding speaker within that dialogue.
-
-\paragraph{Laughs in the data}
-The distribution of laughs in different dialogue acts has a rather uniform shape with a few outliers (see box plots).
-Figure \ref{fig:by-da} in Appendix~\ref{sec:suppl} provides a breakdown of dialogue act depending on whether current or adjacent utterances (the preceding utterance and the following one are counted as adjacent) contain laughter.\footnote{Note that SWDA has a ``Nonverbal'' dialogue act which is misleading with respect to laughter, because utterances only containing a single laughter token fall into this category, however they can serve, for example, to acknowledge a statement or to deflect a question  \citep{mazzocconi2019phd}.}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.9\linewidth]{img/box-swda.pdf}
-  \caption{Box plot for dialogue acts associated with laughter in SWDA.
-On the left: proportion of DAs having laughter in one of the adjacent utterances, on the right: proportion of DAs containing laughter.
-}
-    \label{fig:box-swda}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.9\linewidth]{img/box-ami.pdf}
-  \caption{Box plot for dialogue acts associated with laughter in AMI-DA.
-On the left: proportion of DAs having laughter in one of the adjacent utterances, on the right: proportion of DAs containing laughter.
-}
-    \label{fig:box-ami}
-\end{figure}
-
-\paragraph{Dialogue act grouping}
-For our corpora we also considered grouping the dialogue acts according to DAMSL coders manual \citep{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}: Forward-Communicative-Function (51.86\% of all DAs), Backwards-Communicative-Function (30.35\%), Other (9.04\%) and Communicative-Status (8.75\%).
-This allows the direct comparison between SWDA and AMI-DA.
-With respect to laughs, we observed an even distribution of them in the groups, except for the Communicative-Status group in the case of SWDA, because of the ``Nonverbal'' dialogue acts (see footnote~1).
-
-\paragraph{}
-Let us turn now to describing the neural network architectures that we used.
-
-\section{Model} % Bill
-
-To test the effectiveness of BERT for DAR, we employ a simple neural architecture with two components: an encoder that vectorizes utterances, and a sequence model that predicts dialogue act tags from the vectorized utterances (Figure~\ref{fig:model-architecture}).
-Since we are primarily interested in comparing different utterance encoders, we use a basic RNN as the sequence model in every configuration. 
-The RNN takes the encoded utterance as input at each time step,
-and its hidden state is passed to a simple linear classification layer over dialogue act tags.
-Conceptually, the encoded utterance represents the context-agnostic semantic content of the utterance, and the hidden state of the RNN represents the full discourse context.
-
-\begin{figure*}
-  \include{model}
-  \caption{Simple neural dialogue act recognition sequence model}
-  \label{fig:model-architecture}
-\end{figure*}
-
-As a baseline utterance encoder, we use a word-level CNN with window sizes of 3, 4, and 5, each with 100 feature maps \citep{kimConvolutionalNeuralNetworks2014}. 
-The model uses 100-dimensional word embeddings, which are initialized with pre-trained gloVe vectors \citep{penningtonGloveGlobalVectors2014}.
-
-For the BERT utterance encoder, we use the BERT\textsubscript{BASE} model with hidden size of 768 and 12 transformer layers and self-attention heads \citep[][\S3.1]{devlinBERTPretrainingDeep2018}.
-In our implementation, we use the un-cased model provided by \citet{wolfHuggingFaceTransformersStateoftheart2019}.
-
-The next section will introduce the experiments that we have carried out and will discuss the results that we obtained from them.
-
-\section{Experiments}
-\subsection{Experiment 1: Impact of laughter} \label{sec:experiment1}   % Vlad
-In the first experiment we investigated whether laughter, as an example of a dialogue-specific signal, is a helpful feature for DAR.
-Therefore, we train another version of each model: one containing laughs (\texttt{L}) and one with laughs left out (\texttt{NL}), and compare their performances in DAR task.
-Table~\ref{table:laughter-total-acc} compares the results from applying the models with two different utterance encoders (\texttt{BERT}, \texttt{CNN}).
-First of all, we can see that \texttt{BERT} utterance encoder outperforms \texttt{CNN} in all the cases.
-From observing the effect of laughters, we can see differences in performance depending on the dialogue act, regardless how often laughter occurs in the current or adjacent utterances (see Figure~\ref{fig:by-da} in Appendix~\ref{sec:suppl}).
-The strongest evidence for laughter as a helpful feature was found in SWDA for the \texttt{BERT} utterance encoder, where macro-F1 score increases by 7.89 percentage points.
-
-\begin{table}
-  \centering
-  \begin{tabular}{@{}lcccc@{}}
-    \toprule
-                      & \multicolumn{2}{c}{SWDA} & \multicolumn{2}{c}{AMI-DA} \\ \midrule
-                      & F1    & acc.  & F1    & acc.       \\ 
-    \texttt{BERT-NL}  & 38.10 & 77.07 & 49.09 & 67.06       \\ 
-    \texttt{BERT-L}   & 45.99 & 76.93 & 50.17 & 67.12       \\ \midrule
-    \texttt{CNN-NL}   & 37.23 & 75.08 & 38.37 & 63.46        \\
-    \texttt{CNN-L}    & 27.59 & 75.40 & 37.94 & 64.30        \\ \bottomrule
-
-  \end{tabular}
-  \caption{Comparison of macro-average F1 and accuracy depending on using laughter on the training phase. }
-  \label{table:laughter-total-acc}
-\end{table}
-
-Confusion matrices (Figure~\ref{fig:swda-cm}) provide some food for thought.
-Most of the misclassifications fall into the majority classes, such as \emph{sd} (Statement-non-opinion), in the left edge of the matrix.
-However there are some important exceptions, such as \emph{rhetorical questions}, that are misclassified as other forms of questions due to their surface question-like form.
-Importantly, laughter helpes to classify rhetorical questions correctly, this is because in a conversation it can be used as a device to cancel seriousness or sincerity \citep{ginzburg2015understanding,tepperman2006yeah}, in this case, of a question.
-Therefore questions, like the one we show in the example in Table~\ref{table:example-qh}, are easier to disambiguate with the help of laughter.
-\begin{table}
-      \small
-  \centering
-  \begin{tabularx}{\linewidth}{llL}
-    \toprule
-    Speaker & DA & Utterance \\ \midrule
-        \multicolumn{3}{c}{\emph{(Talking about hobbies)}}\\
-    B   & sd	&  Um, as far as spare time, they talked about, \\
-    B	& \% & I don't, + I think, \\
-    B	& qh & who has any spare time \texttt{<laughter>}? \\
-    A	& x & \texttt{<laughter>}.\\
-             \bottomrule
-  \end{tabularx}
-  \caption{Example from the SWDA corpus (sw3735). B's contribution \emph{qh} (Rhetorical question) is misinterpreted as \emph{qw} (Wh-question) by the BERT model without laughs in training data. }
-  \label{table:example-qh}
-\end{table}
-
-  \begin{figure}
-  \centering
-  \includegraphics[width=1.0\linewidth]{img/swda-cm.pdf}
-  \caption{Confusion matrices for \texttt{BERT-NL} (top) vs \texttt{BERT-L} (bottom); SWDA corpus. Solid line shows the improvement in classification of rhetorical questions.}
-    \label{fig:swda-cm}
-  \end{figure}
-
-In order to further investigate the differences between the models and datasets, we looked at the dialogue act groups.
-Mapping all dialogue acts into four groups allows direct comparison between model performances in SWDA and AMI-DA.
-Table~\ref{table:laughter-group-acc} compares accuracies between the two main groups: Forward-Communicative-Function and Backward-Communicative-Function (82.3\% of all DAs in SWDA and 76.7\% in AMI-DA).
-Our models tend to perform better for the Forward-Communicative-Function group for both corpora irrespective of the presence of laughs.
-Also, our models perform better on the SWDA corpus.
-Overall performance in these groups appears to be unaffected by presence of laughs.
-
-\begin{table}
-  \centering
-  \begin{tabular}{@{}llcc@{}}
-    \toprule
-    &                  & Forw.-CF  & Backw.-CF   \\ \midrule
-    \multirow{4}{*}{SWDA}    &\texttt{BERT-NL}  & 92.54 & 91.67       \\ 
-                             &\texttt{BERT-L}   & 95.42 & 90.91       \\ 
-                             &\texttt{CNN-NL}   & 93.30 & 90.85        \\
-                             &\texttt{CNN-L}    & 94.64 & 90.13        \\ \midrule
-    \multirow{4}{*}{AMI-DA}  &\texttt{BERT-NL}  & 87.77 & 80.83       \\ 
-                             &\texttt{BERT-L}   & 87.36 & 79.87       \\
-                             &\texttt{CNN-NL}   & 91.85 & 71.21        \\
-                             &\texttt{CNN-L}    & 91.25 & 71.28        \\    \bottomrule
-  \end{tabular}
-  \caption{Comparison of the accuracies among the two main dialogues act groups, depending on the utterance model and the presence of laughter.}
-  \label{table:laughter-group-acc}
-\end{table}
-
-\subsection{Experiment 2: Impact of pre-training vs. fine-tuning} \label{sec:experiment2} % Bill
-Next, we analyze how pre-training affects BERT's performance as an utterance encoder.
-To do so, we consider the performance of DAR models with three different utterance encoders:
-\begin{itemize}
-  \item \texttt{BERT-FT} -- pre-trained BERT with DAR fine-tuning 
-  \item \texttt{BERT-RI} -- randomly initialized BERT (with DAR fine-tuning)
-  \item \texttt{BERT-FZ} -- pre-trained BERT without fine-tuning (frozen during DAR training)
-\end{itemize}
-
-\begin{table}[]
-\centering
-\begin{tabular}{@{}lrrrr@{}}
-\toprule
-                           & \multicolumn{2}{c}{SWDA}                          & \multicolumn{2}{c}{AMI-DA}                        \\ \midrule
-                           & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
-\texttt{BERT-FT} & 45.99           & 76.93                    & 50.03                  & 66.94                    \\
-\texttt{BERT-RI} & 32.18           & 73.80                    & 33.45                  & 61.53                    \\
-\texttt{BERT-FZ} & 7.75            & 55.61                    & 14.44                  & 46.59 \\
-  \bottomrule
-\end{tabular}
-  \caption{Macro-average F1 and accuracy of BERT with standard pre-training and DAR fine-tuning (\texttt{BERT-FT}) vs.~the same model without pre-training (\texttt{BERT-RI}) and without fine-tuning (\texttt{BERT-FZ}).}
-  \label{table:exp2}
-\end{table}
-
-The pre-trained model is more accurate than the randomly initialized model by several percentage points on both DA corpora,
-suggesting that BERT's extensive pre-training does provide some useful information for recoginizing different dialogue acts (Table~\ref{table:exp2}).
-This performance boost is much more pronounced in the macro-averaged F1 score,
-which is explained by the fact that at the tag level, pre-training has a larger impact on less frequent tags.
-For a disaggregated view, see Figure \ref{fig:f1-by-da} in Appendix~\ref{sec:suppl}.
-
-A key aspiration of transfer learning is to expose the model to phenomena that are too infrequent to learn from labeled training data alone.
-One explanation for pre-trained BERT's superior performance on some infrequent dialogue acts is that it has learned to represent relevant features
-that the randomly initialized model was unable to learn due to their sparsity in the labeled training set.
-Indeed, a simple lexical probe supports this explanation: in utterances where the pre-trained model is correct and the randomly initialized model is not,
-the rarest word is 1.9 times rarer than is typical of corpus as a whole.
-
-Comparing the performance of the fine-tuned encoder to that of the frozen model, we note that pre-training alone is not enough.
-The frozen model is heavily biased towards the most frequent tags, which explains its especially poor macro-average score (Table~\ref{table:exp2}).
-In SWDA, for example, the model with a frozen encoder predicts one of the two most common tags (Statement-non-opinion or Acknowledge) 86\% of the time, whereas those two
-tags account for only 51\% of the ground truth tags.
-The fine-tuned model is much less biased; it predicts the two most common tags only 59\% of the time.
-
-%These observations raise two questions.
-%First, how does BERT's pre-training help with DAR? 
-%And second, in what way are the representations learned by pre-trained BERT lacking?
-%In other words, what is the contribution of fine-tuning?
-
-%To help answer these questions, we compare performance of the above three models by dialogue act tag.
-
-% TODO: add per dialogue act accuracy figures
-
-\paragraph{Fine-tuning and laughter}
-Since the laughter token doesn't appear in the original BERT vocabulary, only fine-tuned models can meaningfully make use of laughter in utterance representations. 
-This gives us another opportunity to assess whether laughter is useful in dialogue act recognition.
-We find that although 4.6\% of utterances in SWDA contain laughter, 
-7.3\% of utterances misclassified by the frozen model but correctly classified by the fine-tuned model contain laughter, 
-suggesting that the fine-tuned encoder makes use of laughter. 
-For AMI-DA, the effect is less pronounced, but still present: 
-overall, 8.5\% of utterances contain laughter, 
-compared to 9.6\% of utterances where fine-tuning makes a difference.
-
-\subsection{Experiment 3: Impact of dialogue pre-training} \label{sec:experiment3} % Bill
-
-Next, we assess the effect of further in-domain pre-training on BERT's performance as an utterance encoder.\footnote{
-In-domain pre-training is sometimes referred to as \textit{fine-tuning}, but we reserve that term for task-specific training on labeled data.}
-We construct pre-training corpora from the SWDA portion of the un-labeled Switchboard corpus and from the entire AMI corpus (including the 32 dialogues with no human-annotated DA tags that are not included in the DAR training set).
-In both cases, we exclude dialogues that are reserved for DAR testing.
-
-We use the same pre-training task described by \citet{devlinBERTPretrainingDeep2018}, which combines masked token prediction and next sentence (utterance) detection. 
-Distractor utterances are drawn at random from another dialogue in the corpus
-and each epoch is generated separately so that different distractor sentences appear each time.
-We pre-trained three BERT models: with Switchboard (10 epochs), AMI (10 epochs), and the combined corpus (5 epochs).
-
-For each dialogue act corpus, we trained DAR models with BERT encoders pre-trained on the in-domain corpus (\texttt{BERT+ID}) and the combined corpus (\texttt{BERT+CC}).
-As before, we experimented with both the fine-tuning and frozen conditions.
-
-The results are mixed.
-In-domain pre-training offers a modest boost in overall accuracy,
-but the macro-average scores are almost uniformly worse (Table~\ref{table:exp3}).
-%Indeed, when BERT is frozen during fine-tuning, the model that received no further pre-training performs better by more than 3 percentage points (Table~\ref{tab:exp3-recall}).
-To fully assess the potential impact of further in-domain pre-training, a larger dialogue corpus is required.
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}[]
-\begin{tabular}{@{}lrrrr@{}}
-\toprule
-           & \multicolumn{2}{c}{SWDA}                          & \multicolumn{2}{c}{AMI-DA}                        \\ \midrule
-           & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
-\texttt{BERT-FT}    & 45.99                  & 76.93                    & 50.03                  & 66.95                    \\
-\texttt{BERT+ID-FT} & 45.48                  & 77.02                    & 46.56                  & 68.66                    \\
-\texttt{BERT+CC-FT} & 47.78                  & 77.35                    & 48.72                  & 66.58                    \\ \midrule
-\texttt{BERT-FZ}    & 7.75                   & 55.61                    & 14.44                  & 46.60                    \\
-\texttt{BERT+ID-FZ} & 6.46                   & 52.30                    & 14.43                  & 48.07                    \\
-\texttt{BERT+CC-FZ} & 5.76                   & 51.14                    & 12.56                  & 42.42                    \\ \bottomrule
-\end{tabular}
-  \caption{Comparison of macro-average F1 and accuracy  with further in-domain (\texttt{ID}) and combined corpus (\texttt{CC}) dialogue pre-training,
-    for both the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions.}
-  \label{table:exp3}
-\end{table}
-
-%\subsection{Experiment 4: Cross-domain pre-training (if time permits)} \label{sec:experiment4} % Bill
-%  - cross-domain pre-training
-\paragraph{}
-Having discussed the experimental results, the final section of the paper provides broader explanations of our findings.
-
-\section{Discussion} % add items to discuss
-On the question of laughter impact, this study found out that laughter is more helpful in SWDA corpus than in AMI-DA.
-This observation may support the hypothesis that in SWDA due to the nature of interactions over the phone, dialogue participants can not rely on visual signals, such as gestures and facial expressions, therefore vocalisations, such as laughter, are more pronounced and therefore more helpful to disambiguate the utterances.
-
-This also can explain why all our best models perform better on SWDA: much more information that interlocutors and dialogue act annotators can rely on is present in the transcription of SWDA, whereas AMI-DA annotators receive clear instructions to pay attention to the videos \citep{GuidelinesDialogueAct2005}.
-This finding is consistent with that of \citet{bavelas2008gesturing} who demonstrated that in face-to-face dialogue visual components, such as gestures, can convey information that is independent from one conveyed with speech.
-
-There is abundant room for further progress in determining how other speech-related information, such as prosody and disfluencies, can be incorporated into the DAR model.
-\citet{stolckeDialogueActModeling2000} showed that dialogue acts can have specific prosodic manifestations that can be used to improve dialogue act classification.
-Furthermore, in relation to laughter, its form (duration, arousal level) can be informative about its function and position w.r.t. to laughable \citep{tian2016we,mazzocconi2019phd}.
-
-Although our experiments with further pre-training were inconclusive, \citet{baoPLATOPretrainedDialogue2019} finds that further pre-training BERT on a large-scale Reddit and Twitter corpus is helpful for response selection.
-Further pre-training may be helpful for DAR too, if the in-domain or cross-domain corpus is large enough.
-
-It remains an open question how well the text chat domain transfers to transcribed dialogue and what pre-training schemes are best for the dialogue domain.
-The training scheme for RoBERTa \citep{liuRoBERTaRobustlyOptimized2019}, for example, leaves out next sentence prediction as a pre-training task because they do not find that it improves performance on question answering and natural language inference tasks.
-The same may not be true of dialogue, however.
-
-%\begin{itemize}
-  %\item RoBERTa training scheme finds that next sentence prediction is of little importance.
-Is this true for us too?
-(suspect not due to discourse importance).
-see: https://github.com/huggingface/transformers/issues/1622
-  %\item Issues related to working with transcribed speech: Different kinds of laughter are all represented by the same token.
-Does transcription orthography capture prosody?
-We know prosidy is useful for DAR (Jurafsky).
-  %\item future work: pre-training on very large un-labeled dialogue corpora. How does text chat transfer to the spoken/transcribed setting?
-  %\item Laughter is more helpful in SWDA than in AMI-DA. 
-  %\item The point above can also explain why our models better on SWDA: just a larger proportion of stuff that interlocutors rely on is in the transcription.
-%\end{itemize}
-
-\bibliography{acl2020}
-\bibliographystyle{acl_natbib}
-\appendix
-\onecolumn
-\section{Supplementary materials}\label{sec:suppl}
-
-\begin{figure*}[h!]
-  \centering
-  \includegraphics[width=\linewidth]{img/SWDA-bertLvsNL.pdf}
-  \includegraphics[width=\linewidth]{img/AMI-DA-bertLvsNL.pdf}
-  \caption{Change in accuracy for each dialogue act (\texttt{BERT-NL} vs \texttt{BERT-L}).
-Positive changes when adding laughter (\texttt{BERT-L}) are shown in blue.
-Vertical bars indicate how often dialogue act is associated with laughter.
-Top chart: SWDA, Bottom chart: AMI-DA.
-}
-    \label{fig:by-da}
-  \end{figure*}
-
-\begin{figure*}[h!]
-  \centering
-  \includegraphics[width=\linewidth]{img/swda-brf.pdf}
-  \includegraphics[width=\linewidth]{img/ami-brf.pdf}
-  \caption{F1 scores by dialogue act for BERT with standard pre-training and DAR fine-tuning (\texttt{BERT-FT}) vs.~the same model without pre-training (\texttt{BERT-RI}) and without fine-tuning (\texttt{BERT-FZ}).
-Dialogue acts are ordered with the most common on the left.}
-    \label{fig:f1-by-da}
-  \end{figure*}
 

### 2020-12-07 reports/ACL2020 Paper/starsem_reviews-response-notes.md

General comments

# Review 1.
- Although we are only concerned with text in this work, we agree that text is not enough to capture meaning of laughter. These experiments investigate how this model deals with dialogue, given that it was pre-trained on text data. Giving the model acoustic information would undermine that goal.
- We intentionally use a very simple model, which is partly why the description is so short. We will make our code available when the work is no longer under anonymity restrictions.
- DAR is not as appropriate as NLU for laughter?? 
- fix:
  - change to the 1st edition of Austin
  - I also wouldn't say that conditional random fields are more
    "sophisticated" than most flavors of RNNs. -- clarify
- reformulate the contributions
- laughter in non-dialogue?
- why single symbol, fix in Data (ref ginzburg/chiara) but we have
  just a single type.
- why laughter is helpful? restate that in the discussion

idea: can laughter help with repair? 
# Review 2.
- Yes -- $s^t$ is the speaker token and $w_n$ is the n'th word token. Thanks for noticing this omission. 
- This is indeed an interesting discrepancy between the effect of laughter on the CNN and BERT models. We don't have a hypothesis at the moment, but we plan to investigate further. Looking at the DA tag-specific performance may provide a clue.
- The opening two paragraphs get off on the wrong foot for me. The
  first sentence is too often repeated in papers like this, and the
  rest of these two paragraphs seems to under-state the extent to
  which there is prior work on using neural models for dialogue.
  - try to re-write first two para, more laughter and multi-modal dialogue
- label outliers on Fig 1
- say that non-verbal is not accounted for in the Task 1
- Fig 3. Plot: P(qw|qh) - P(qw) instead
- numbers for qh|qw improvement
- Fig 2: utterance encoder, context representation, softmax
- Table 6, add F1
- Experiment 2 -> add L/NL condition
- Experiment 3 -> as well add laughters

# Review 3.
- Thank you for your questions suggesting avenues for deeper analysis.
- Please see figure 4 in the appendix for the affect of laughter on performance for particular dialogue acts.
- We discuss linguistic work on the functional role of laughter and its relationship to our results in section 4.1.
- say something about the split. How is it different from the
  "canonical split" (optional)
- CNN: "a simple and popular baseline for text classification or
  encoding texts"

# Review 4.
- Thank you for these constructive comments.

### 2020-12-07 eval_model.py
save dialogue state

@@ -16,6 +16,8 @@ parser.add_argument('model_dir', type=str,
         help='The save directory for the model to evaluate')
 parser.add_argument('corpus', choices=['SWDA', 'AMI-DA'],
         help='Which dialouge act corpus to eval on.')
+parser.add_argument('-st', '--save-dialogue-state', type=bool, default=False,
+        help='Save the hidden state of the dialogue RNN at each utterance.')
 parser.add_argument('-e', '--epoch', type=int, default=None,
         help='The model checkpoint (training epoch) to load.')
 parser.add_argument('-d','--data-dir', default='data',
@@ -59,7 +61,7 @@ def eval_model(encoder_model, dar_model, data, n_tags, criterion, device, min_ut
         - no backpropegation, obviously
         - returns predictions as well as loss
     """
-    preds, loss = [], 0
+    preds, dar_states, loss, = [], [], 0
     with torch.no_grad():
         for i, (x, y) in enumerate(data, 1):
            log.debug("Evaluating on dialogue {:3d} of {} ({} utterances).".format(i, len(data), len(x)))
@@ -75,8 +77,9 @@ def eval_model(encoder_model, dar_model, data, n_tags, criterion, device, min_ut
            log.debug("Dialogue {:3d} loss: {:.6f}".format(i, diag_loss))
            loss += diag_loss
            preds.append(y_hat.max(dim=2)[1].squeeze(1).tolist())
+           dar_states.append(hidden.cpu().detach().numpy())
         loss = loss / len(data)
-    return loss, preds 
+    return loss, preds, dar_states
 
 
 if __name__ == '__main__':
@@ -95,6 +98,7 @@ if __name__ == '__main__':
     tag_vocab_file = os.path.join(args.data_dir, f'{args.corpus}_tags.txt')
     test_file = os.path.join(args.data_dir, f'{args.corpus}_test.json')
     preds_file = os.path.join(args.model_dir, f'preds.E{args.epoch}.json')
+    dialogue_state_file = os.path.join(args.model_dir, f'dialogue_state.E{args.epoch}.json')
     encoder_model_file = os.path.join(args.model_dir, f'encoder_model.E{args.epoch}.bin')
     dar_model_file = os.path.join(args.model_dir, f'dar_model.E{args.epoch}.bin')
 
@@ -135,7 +139,7 @@ if __name__ == '__main__':
[…]

### 2020-12-07 eval_model.py
eval epoch selection fix (from last year...)

@@ -39,18 +39,18 @@ def compute_accuracy(data, preds):
         total_correct += correct
     return total_correct / total
 
-def get_max_val_loss(model_dir):
+def get_min_val_loss(model_dir):
     """
     model_dir - the full path to the save directory for the model
     returns: a tuple containing the training epoch (stating with 1),
-             with the maxiumum validation accuracy, and its value 
+             with the minimum validation loss, and its value 
     """
-    val_loss_re = re.compile(r"\[INFO    \] Epoch (\d) validation loss: \d+\.\d+ \| accuracy: %(\d+\.\d+)")
+    val_loss_re = re.compile(r"\[INFO    \] Epoch (\d) validation loss: (\d+\.\d+) \| accuracy: %\d+\.\d+")
     with open(os.path.join(model_dir, 'train.log')) as f:
         train_log = f.read()
     epoch_val_loss = re.findall(val_loss_re, train_log)
-    max_epoch, max_loss = max(epoch_val_loss, key=lambda x:x[1])
-    return max_epoch, max_loss
+    min_epoch, min_loss = min(epoch_val_loss, key=lambda x:x[1])
+    return min_epoch, min_loss
 
 def eval_model(encoder_model, dar_model, data, n_tags, criterion, device, min_utt_len=None):
     """ Similar to train.train_epoch but:
@@ -83,7 +83,7 @@ if __name__ == '__main__':
 
     args = parser.parse_args()
     if not args.epoch:
-        args.epoch, _= get_max_val_loss(args.model_dir)
+        args.epoch, _= get_min_val_loss(args.model_dir)
     with open(os.path.join(args.model_dir, 'args.json'), 'r') as f:
         model_args = json.load(f)
     args.__dict__ = dict(list(model_args.items()) + list(args.__dict__.items()))

### 2020-12-15 reports/DnD2021-paper/dnd.tex

\documentclass[twoside,11pt]{article}

% Any additional packages needed should be included after dnd.
% Note that dnd.sty includes epsfig, amssymb, natbib and graphicx,
% and defines many common macros, such as 'proof' and 'example'.
%
% It also sets the bibliographystyle to plainnat; for more information on
% natbib citation styles, see the natbib documentation, a copy of which
% is archived at http://www.jmlr.org/format/natbib.pdf

\usepackage{dnd}
\usepackage{times}

% Heading arguments are {volume}{year}{pages}{submitted}{accepted}published online}{author-full-names}{doi-number}

\dndheading{issue(number)}{year}{firstpage--lastpage}{Name1 Surname1, Name2 Surname2, and Name3 Surname3}{10.5087/dad.DOINUMBER}

% Short headings should be running head and authors last names

\ShortHeadings{Dialogue Acts and Higher Order Structure}{{Di Eugenio}, Xie and Serafin}
\firstpageno{1}

%

% # Strand 1. Laughter and dialogue acts
% - (BN) Experiment 1, 2 (+L), 3 (+L)
% - ensure that "x" DAs are removed
% - PCA: DAs with and w/o L side-by-side
% - (?) AMI and SWBD mappings and comparison

% # Strand 2. Laughter prediction
% - (VM) re-do some experiments from Maraev et al. 2019
% - predict whether next utterance contains laughter, also predict suf/pre/infix or standalone
% - joint training with DAR (or pre-training?)
% - human evaluation
% - (VM) think of appropriate background, e.g. from Tian (?)

% # Strand 3. "Non-verbal" DAs
% - (BN) remove "x" from target classes for testing 
% - PCA?
% - (VM) background on non-verbals

\begin{document}

\title{Dialogue \& Discourse Article Template}

\author{\name Name1 Surname1 \email email@author1.com \\
       \addr Affiliation1\\
       Affiliation1 second line
       \AND
       \name Name2 Surname2 \email email@author2.com \\
       \addr Affiliation2\\
       Affiliation2 second line
       \AND 
       \name Name3 Surname3  \email email@author3.com\\
       \addr Affiliation3\\
       Affiliation3 second line}

\editor{Name Surname}
\submitted{MM/YYYY}{MM/YYYY}{MM/YYYY}

\maketitle

\begin{abstract}%
 Abstract from {\em Dialogue Act Classification, Higher Order Dialogue Structure, and
 Instance-Based Learning} by Barbara di Eugenio, Zhuli Xie, and Riccardo Serafin: 
  The main goal of this paper is to explore the predictive power of
  dialogue context on Dialogue Act classification, both as concerns 
  the linear context 
  provided by previous dialogue acts, and the hierarchical context 
  specified  by conversational
  games. As our learning approach, we  extend Latent Semantic
  Analysis (LSA) as Feature LSA (FLSA), and combine FLSA with
  the k-Nearest Neighbor algorithm. FLSA adds
  richer linguistic features to LSA, which only uses words.   
   The k-Nearest Neighbor algorithm obtains its best results when
  applied to the reduced semantic spaces generated by FLSA.
  Empirically, our results are better than previously published
  results on two different corpora, MapTask and CallHome
  Spanish. Linguistically, we confirm and extend previous observations
  that the hierarchical dialogue structure encoded via the notion of
  game is of primary importance for dialogue act recognition.
\end{abstract}

\begin{keywords}
keyword1, keyword2, keyword3, keyword4, keyword5
\end{keywords}

\section{Introduction}

%%bibliographystyle is included in dnd

\bibliography{...}

\end{document}

### 2021-01-20 analysis/ACL/util.py
laughter viz stuff i forogot to commit

@@ -1,6 +1,6 @@
 import sys
 sys.path.append("../..") # Adds package base dir to python modules path.
-from eval_model import get_max_val_loss
+from eval_model import get_min_val_loss
 import json
 import pandas as pd
 from collections import defaultdict
@@ -8,7 +8,6 @@ import os
 from sklearn import metrics
 
 
-<<<<<<< HEAD
 def report_metrics(frames, conditions):
     metric_funcs = [
         lambda x,y: metrics.precision_score(x,y,average='macro'), 
@@ -62,7 +61,7 @@ def gen_model_preds_df(corpus, models, model_dirs,group=False):
     
     preds = defaultdict(lambda x: dict)
     for model, model_dir in zip(models, model_dirs):
-        best_epoch, _ = get_max_val_loss(model_dir)
+        best_epoch, _ = get_min_val_loss(model_dir)
         preds_file = os.path.join(model_dir, f'preds.E{best_epoch}.json')
         with open(os.path.join(model_dir, preds_file), 'r') as f:
             preds = json.load(f)

### 2021-01-20 data.py

@@ -22,7 +22,8 @@ parser.add_argument("command", choices=[
     'download-glove', 
     'get-bert-config',
     'test-tokenization',
-    'prep-pretraining-corpora'
+    'prep-pretraining-corpora',
+    'prep-opensubtitles-pretraining-corpus'
     ],  help="What preprocessing to do.")
 parser.add_argument('-d','--data-dir', default='data',
         help='Data storage directory.')
@@ -81,9 +82,9 @@ def download_glove(data_dir):
 
 def load_data(corpus_file, tokenizer, tag2id, strip_laughter=False):
     with open(corpus_file) as f:
-        dialogues = json.load(f)
+        dialogs = json.load(f)
     data = []
-    for d in dialogues:
+    for d in dialogs:
         utts, tags = [], []
         for speaker,utt,tag in zip(d['speakers'], d['utts'], d['da_tags']):
             utt = [f'[SPKR_{speaker}]'] + tokenizer.tokenize(utt)
@@ -98,16 +99,20 @@ def load_data(corpus_file, tokenizer, tag2id, strip_laughter=False):
     return data 
 
 
-def load_data_pretraining(corpus_file, tokenizer):
+def prep_dialog_for_pretraining(dialog):
+    utts = []
+    for speaker,utt in zip(dialog['speakers'], dialog['utts']):
+       utt = f'[SPKR_{speaker}] ' + utt 
+       utts.append(utt)
+    return utts
+
+
+def load_data_pretraining(corpus_file):
     with open(corpus_file) as f:
-        dialogues = json.load(f)
+        dialogs = json.load(f)
     data = []
-    for d in dialogues:
-        utts = []
-        for speaker,utt in zip(d['speakers'], d['utts']):
-           utt = [f'[SPKR_{speaker}]'] + tokenizer.tokenize(utt)
-           utts.append(utt)
-        data.append(utts)
+    for d in dialogs:
+        data.append(prep_dialog_for_pretraining(d))
     return data
 
 
@@ -115,7 +120,7 @@ def write_pretraining_corpus(corpus_file, corpus):
     with open(os.path.join(corpus_file), 'w') as f:
         for d in corpus:
             for utt in d:
-                f.write(' '.join(utt) + '\n')
+                f.write(utt + '\n')
             f.write('\n')
 
 
@@ -160,23 +165,23 @@ def parse_ami(corpus_dir, pause_threshold):
     log.info("Parsing AMI...")
     ami_meetings = ami.get_corpus(corpus_dir, da_only=False)
 
[…]

### 2021-01-20 eval_model.py

@@ -16,7 +16,7 @@ parser.add_argument('model_dir', type=str,
         help='The save directory for the model to evaluate')
 parser.add_argument('corpus', choices=['SWDA', 'AMI-DA'],
         help='Which dialouge act corpus to eval on.')
-parser.add_argument('-st', '--save-dialogue-state', type=bool, default=False,
+parser.add_argument('-st', '--save-dialogue-state', default=False, action='store_true',
         help='Save the hidden state of the dialogue RNN at each utterance.')
 parser.add_argument('-e', '--epoch', type=int, default=None,
         help='The model checkpoint (training epoch) to load.')
@@ -77,7 +77,7 @@ def eval_model(encoder_model, dar_model, data, n_tags, criterion, device, min_ut
            log.debug("Dialogue {:3d} loss: {:.6f}".format(i, diag_loss))
            loss += diag_loss
            preds.append(y_hat.max(dim=2)[1].squeeze(1).tolist())
-           dar_states.append(hidden.cpu().detach().numpy())
+           dar_states.append(hidden.squeeze().tolist())
         loss = loss / len(data)
     return loss, preds, dar_states
 

### 2021-01-20 finetune_on_pregenerated.py

@@ -334,8 +334,8 @@ def main():
                 mean_loss = tr_loss * args.gradient_accumulation_steps / nb_tr_steps
                 pbar.set_postfix_str(f"Loss: {mean_loss:.5f}")
                 if (step + 1) % args.gradient_accumulation_steps == 0:
-                    scheduler.step()  # Update learning rate schedule
                     optimizer.step()
+                    scheduler.step()  # Update learning rate schedule
                     optimizer.zero_grad()
                     global_step += 1
 

### 2021-01-20 model.py

@@ -59,10 +59,10 @@ class DARRNN(nn.Module):
         self.decoder.weight.data.uniform_(-initrange, initrange)
 
     def forward(self, x, hidden):
-        x, hidden = self.rnn(x, hidden)
+        x, _ = self.rnn(x, hidden)
         x = self.drop(x)
         decoded = self.decoder(x.view(x.size(0)*x.size(1), x.size(2)))
-        return decoded.view(x.size(0), x.size(1), decoded.size(1)), hidden
+        return decoded.view(x.size(0), x.size(1), decoded.size(1)), x
 
     def init_hidden(self, batch_size):
         weight = next(self.parameters())

### 2021-01-20 opensubtitles.py

@@ -47,33 +47,40 @@ def normalize_laughs(sentence):
                             sentence, flags=re.IGNORECASE)
     global laughs
     laughs += lau
-    if lau:
-        print(new_sent)
-    return new_sent
+    # if lau:
+        # print(new_sent)
+    return new_sent, lau
 
 
 def xml_to_sentences(xml_corpus):
     with open(xml_corpus) as f:
         parse = ET.parse(f)
     sentences = []
+    total_laughs = 0
     for sentence in parse.getroot():
         joined_words = " ".join([t.text for t in sentence if t.tag == "w"])
-        sentences.append(normalize_laughs(joined_words))
-    return sentences
+        normalized_words, sentence_laughs = normalize_laughs(joined_words)
+        total_laughs += sentence_laughs
+        sentences.append(normalized_words)
+    return sentences, total_laughs
 
 
-def os_to_json(path, n_speakers=3):
+def os_to_json(path, n_speakers=3, shuffle=False):
     speakers = list(map(chr, range(65, 65+n_speakers)))
     dialogs = []
     # total = len(list(glob.iglob(path + '**/*.xml', recursive=True)))
     # print(f'{total} xml files in the corpus')
+    files = glob.iglob(path + '**/*.xml', recursive=True)
+    if shuffle:
+        files = list(files)
+        random.shuffle(files)
     i = 0
-    for filename in tqdm(glob.iglob(path + '**/*.xml', recursive=True), total=446612):
+    for filename in tqdm(files, total=446612):
         dialog = {}
         dialog['id'] = os.path.basename(filename)
-        dialog['utts'] = xml_to_sentences(filename)
+        dialog['utts'], n_laughs = xml_to_sentences(filename)
         dialog['speakers'] = random.choices(speakers, k=len(dialog['utts']))
-        yield dialog
+        yield dialog, n_laughs
 
 
 if __name__ == '__main__':

### 2021-01-20 laughter_position.py
vlad's laughter type function'

@@ -1,0 +1,20 @@
+def laughter_type(utt):
+    laugh = '<laughter>'
+    utt = re.sub(r'[#.\-,]','',utt).strip().lower()
+    if utt == laugh:
+        return 'stand alone'
+    elif laugh in utt:
+        if utt.startswith(laugh):
+            return 'prefix'
+        elif utt.endswith(laugh):
+            return 'suffix'
+        else:
+            return 'infix'
+    else:
+        return 'none'
+
+dar_models = {
+        'AMI-DA': "AMI-DA-L_bert_2019-11-20",
+	'SWDA': "SWDA-L_bert_2019-11-20"
+}
+

### 2021-01-20 eval_model.py
add load_models function

@@ -29,18 +29,6 @@ parser.add_argument('--gpu-id', type=int, default=0,
 parser.add_argument("-v", "--verbose", action="store_const", const=logging.DEBUG, default=logging.INFO, 
         help="Increase output verbosity")
 
-
-def compute_accuracy(data, preds):
-    tags = [diag[1] for diag in data]
-    total, total_correct = 0, 0
-    for y, y_hat in zip(tags, preds):
-        len_y = len(y)
-        assert(len_y == len(y_hat))
-        total += len_y
-        correct = sum([a == b for a,b in zip(y, y_hat)])
-        total_correct += correct
-    return total_correct / total
-
 def get_min_val_loss(model_dir):
     """
     model_dir - the full path to the save directory for the model
@@ -53,6 +41,65 @@ def get_min_val_loss(model_dir):
     epoch_val_loss = re.findall(val_loss_re, train_log)
     min_epoch, min_loss = min(epoch_val_loss, key=lambda x:x[1])
     return min_epoch, min_loss
+
+def load_models(model_dir, epoch=None, device='cpu'):
+
+    with open(os.path.join(model_dir, 'args.json'), 'r') as f:
+       args = json.load(f)
+    best_epoch, _ = get_min_val_loss(model_dir) 
+    epoch = best_epoch if epoch is None else epoch
+
+    dialogue_state_file = os.path.join(model_dir, f"dialogue_state.E{epoch}.json")
+    encoder_model_file = os.path.join(model_dir, f"encoder_model.E{epoch}.bin")
+    dar_model_file = os.path.join(model_dir, f"dar_model.E{epoch}.bin")
+
+    # tokenizer = data.load_tokenizer('bert-base-uncased')
+    # vocab_size = len(tokenizer)
+    # print(vocab_size)
+    vocab_size = 30528
+
+    tag_vocab_file = os.path.join(args['data_dir'], f'{args["corpus"]}_tags.txt')
+    tag_vocab, tag2id = data.load_tag_vocab(tag_vocab_file)
+    n_tags = len(tag_vocab)
+
+    if args['encoder_model'] == 'wordvec-avg': 
+        encoder_model = model.WordVecAvg.random_init(vocab_size, args['embedding_size'])
+    elif args['encoder_model'] == 'cnn':
+        window_sizes = [3, 4, 5]
+        feature_maps = 100
+        min_utt_len = max(window_sizes) 
+        encoder_model = model.KimCNN.random_init(vocab_size, args['utt_dims'], 
[…]

### 2021-01-20 laughter_position.py

@@ -1,3 +1,10 @@
+import torch
+import model
+import json
+from eval_model import load_models
+
+laughter_types = ['stand alone', 'prefix', 'suffix', 'infix', 'none']
+
 def laughter_type(utt):
     laugh = '<laughter>'
     utt = re.sub(r'[#.\-,]','',utt).strip().lower()
@@ -13,8 +20,40 @@ def laughter_type(utt):
     else:
         return 'none'
 
-dar_models = {
-        'AMI-DA': "AMI-DA-L_bert_2019-11-20",
-	'SWDA': "SWDA-L_bert_2019-11-20"
-}
+class LaughterTypePredictor(model.DARRNN):
+    """ 
+    Model for predicting laughter type of the next utterance. 
+    The architecture is exactly the same as the DARRNN, but we predict laughter types
+    instead of dialogue acts.
+    NOTE: The prediction scheme is slightly different since we are predicting the laughter
+    type of the *next* utterance (as opposed to the DA tag of *this* utterance*. But these
+    differences are in the definition of the training/evaluation loops, not them model itself.
+    """
 
+    def __init__(self, utt_size, hidden_size, n_layers, dropout=0.5, use_lstm=False):
+        super().__init__(utt_size, len(laughter_types), hidden_size, n_layers, 
+                dropout=dropout, use_lstm=use_lstm)
+    
+    @classmethod
+    def from_dar_model(self, dar_model):
+        """
+        We also allow the model to be initialized from a pre-trained DAR model, so that we can
+        test whether knowledege of the DAR task helps with laughter prediction.
+        """
+
+# 1. label the data with laughter position
+# 2. fine-tune the final layer of the DAR model to instead 
+#    predict laughter position of the next utternace
+#    - this means creating a new model type for laughter position
+#    - we should allow it to be initialized from a DAR model
+# 
+
+utt_dims = 100
+dar_hidden = 100
+dar_layers = 1
+use_lstm = False
+
+# model_dir = "models/AMI-DA-L_bert_2019-11-20"
+model_dir = "models/SWDA-L_bert_2019-11-20"
+
+encoder_model, dar_model = load_models(model_dir)

### 2021-01-20 model.py

@@ -148,3 +148,4 @@ class BertEncoder(nn.Module):
         _, x = self.bert(x)  # use the pooled [CLS] token output (_ is the 12 hidden states)
         x = self.linear(x)
         return x
+

### 2021-01-21 data.py
add next utterance laughter tags

@@ -80,13 +80,13 @@ def download_glove(data_dir):
         zip_ref.extractall('data/glove.6B')
 
 
-def load_data(corpus_file, tokenizer, tag2id, strip_laughter=False):
+def load_data(corpus_file, tokenizer, tag2id, strip_laughter=False, tag_field='da_tags'):
     with open(corpus_file) as f:
         dialogs = json.load(f)
     data = []
     for d in dialogs:
         utts, tags = [], []
-        for speaker,utt,tag in zip(d['speakers'], d['utts'], d['da_tags']):
+        for speaker,utt,tag in zip(d['speakers'], d['utts'], d[da_tags]):
             utt = [f'[SPKR_{speaker}]'] + tokenizer.tokenize(utt)
             if strip_laughter:
                 utt = [t for t in utt if t != LAUGHTER_TOKEN]
@@ -123,8 +123,7 @@ def write_pretraining_corpus(corpus_file, corpus):
                 f.write(utt + '\n')
             f.write('\n')
 
-
-Dialogue = namedtuple('Dialogue', ['id', 'speakers', 'utts', 'da_tags'])
+Dialogue = namedtuple('Dialogue', ['id', 'speakers', 'utts', 'da_tags', 'laughter_type_next'])
 
 
 def extract_corpus(zip_file, corpus_dir):
@@ -146,6 +145,21 @@ def download_corpus(url, zip_file):
         log.info(f"Skipping download of {zip_file} (already exists).")
         return
     util.download_url(url, zip_file)
+
+def laughter_type(utt):
+    laugh = '<laughter>'
+    utt = re.sub(r'[#.\-,]','',utt).strip().lower()
+    if utt == laugh:
+        return 'stand alone'
+    elif laugh in utt:
+        if utt.startswith(laugh):
+            return 'prefix'
+        elif utt.endswith(laugh):
+            return 'suffix'
+        else:
+            return 'infix'
+    else:
+        return 'none'
 
 def normalize_ami(utt):
     s = str(utt) # AMIUtterance to string defined in ami.py
@@ -169,43 +183,24 @@ def parse_ami(corpus_dir, pause_threshold):
     for m in tqdm(ami_meetings):
         m.gen_transcript(utt_pause_threshold=pause_threshold)
         if m.speaker_dialog_acts:  # DA-tagged meeting
-            speakers, utts, da_tags = [], [], []
+            speakers, utts, da_tags, laughter_types = [], [], [], []
             for utt in m.transcript:
[…]

### 2021-01-21 laughter_position.py

@@ -3,57 +3,5 @@ import model
 import json
 from eval_model import load_models
 
-laughter_types = ['stand alone', 'prefix', 'suffix', 'infix', 'none']
 
-def laughter_type(utt):
-    laugh = '<laughter>'
-    utt = re.sub(r'[#.\-,]','',utt).strip().lower()
-    if utt == laugh:
-        return 'stand alone'
-    elif laugh in utt:
-        if utt.startswith(laugh):
-            return 'prefix'
-        elif utt.endswith(laugh):
-            return 'suffix'
-        else:
-            return 'infix'
-    else:
-        return 'none'
 
-class LaughterTypePredictor(model.DARRNN):
-    """ 
-    Model for predicting laughter type of the next utterance. 
-    The architecture is exactly the same as the DARRNN, but we predict laughter types
-    instead of dialogue acts.
-    NOTE: The prediction scheme is slightly different since we are predicting the laughter
-    type of the *next* utterance (as opposed to the DA tag of *this* utterance*. But these
-    differences are in the definition of the training/evaluation loops, not them model itself.
-    """
-
-    def __init__(self, utt_size, hidden_size, n_layers, dropout=0.5, use_lstm=False):
-        super().__init__(utt_size, len(laughter_types), hidden_size, n_layers, 
-                dropout=dropout, use_lstm=use_lstm)
-    
-    @classmethod
-    def from_dar_model(self, dar_model):
-        """
-        We also allow the model to be initialized from a pre-trained DAR model, so that we can
-        test whether knowledege of the DAR task helps with laughter prediction.
-        """
-
-# 1. label the data with laughter position
-# 2. fine-tune the final layer of the DAR model to instead 
-#    predict laughter position of the next utternace
-#    - this means creating a new model type for laughter position
-#    - we should allow it to be initialized from a DAR model
-# 
-
-utt_dims = 100
-dar_hidden = 100
-dar_layers = 1
-use_lstm = False
-
-# model_dir = "models/AMI-DA-L_bert_2019-11-20"
-model_dir = "models/SWDA-L_bert_2019-11-20"
-
-encoder_model, dar_model = load_models(model_dir)

### 2021-01-22 model.py
bugs

@@ -59,10 +59,10 @@ class DARRNN(nn.Module):
         self.decoder.weight.data.uniform_(-initrange, initrange)
 
     def forward(self, x, hidden):
-        x, _ = self.rnn(x, hidden)
+        x, hidden = self.rnn(x, hidden)
         x = self.drop(x)
         decoded = self.decoder(x.view(x.size(0)*x.size(1), x.size(2)))
-        return decoded.view(x.size(0), x.size(1), decoded.size(1)), x
+        return decoded.view(x.size(0), x.size(1), decoded.size(1)), hidden
 
     def init_hidden(self, batch_size):
         weight = next(self.parameters())

### 2021-01-22 train.py

@@ -248,7 +248,7 @@ if __name__ == '__main__':
         torch.save(dar_model.state_dict(), os.path.join(save_dir, f'dar_model.E{epoch}.bin'))
         torch.save(encoder_model.state_dict(), os.path.join(save_dir, f'encoder_model.E{epoch}.bin'))
         log.info(f"Starting epoch {epoch} valdation")
-        val_loss, preds = eval_model.eval_model(encoder_model, dar_model, val_data, n_tags, 
+        val_loss, preds, _ = eval_model.eval_model(encoder_model, dar_model, val_data, n_tags, 
                 criterion, device, min_utt_len)
         accuracy = eval_model.compute_accuracy(val_data, preds)
         log.info(f"Epoch {epoch} validation loss: {val_loss:.6f} | accuracy: %{accuracy*100:.2f}")

### 2021-03-10 data.py
laughter->laugh for consistency

@@ -123,7 +123,7 @@ def write_pretraining_corpus(corpus_file, corpus):
                 f.write(utt + '\n')
             f.write('\n')
 
-Dialogue = namedtuple('Dialogue', ['id', 'speakers', 'utts', 'da_tags', 'laughter_type_next'])
+Dialogue = namedtuple('Dialogue', ['id', 'speakers', 'utts', 'da_tags', 'laugh_types'])
 
 
 def extract_corpus(zip_file, corpus_dir):
@@ -146,7 +146,7 @@ def download_corpus(url, zip_file):
         return
     util.download_url(url, zip_file)
 
-def laughter_type(utt):
+def laugh_type(utt):
     laugh = '<laughter>'
     utt = re.sub(r'[#.\-,]','',utt).strip().lower()
     if utt == laugh:
@@ -183,22 +183,20 @@ def parse_ami(corpus_dir, pause_threshold):
     for m in tqdm(ami_meetings):
         m.gen_transcript(utt_pause_threshold=pause_threshold)
         if m.speaker_dialog_acts:  # DA-tagged meeting
-            speakers, utts, da_tags, laughter_types = [], [], [], []
+            speakers, utts, da_tags, laugh_types = [], [], [], []
             for utt in m.transcript:
                 speakers.append(utt.speaker)
                 utts.append(normalize_ami(utt))
                 da_tags.append(utt.dialog_act.da_tag)
-                laughter_types.append(laughter_type(str(utt)))
-            laughter_type_next = laughter_types[1:] + ['none'] # predict the laughter type of the next utterance. for the last utterance, use 'none' 
-            dialogs_da.append(Dialogue(m.meeting_id, speakers, utts, da_tags, laughter_type_next))
+                laugh_types.append(laugh_type(str(utt)))
+            dialogs_da.append(Dialogue(m.meeting_id, speakers, utts, da_tags, laugh_types))
         else:  # not DA-tagged meeting
-            speakers, utts, laughter_types = [], [], []
+            speakers, utts, laugh_types = [], [], []
             for utt in m.transcript:
                 speakers.append(utt.speaker)
                 utts.append(normalize_ami(utt))
-                laughter_types.append(laughter_type(str(utt)))
-            laughter_type_next = laughter_types[1:] + ['none'] # predict the laughter type of the next utterance. for the last utterance, use 'none' 
-            dialogs_da.append(Dialogue(m.meeting_id, speakers, utts, None, laughter_type_next))
[…]

### 2021-03-10 reports/IWCS2021/iwcs-short-paper.tex
iwcs draft

--- 2020-07-21 reports/Star-SEM Paper/starsem-paper.tex
@@
 %
-% File acl2020.tex
+% File acl2021.tex
 %
+%% Based on the style files for EMNLP 2020, which were
 %% Based on the style files for ACL 2020, which were
@@
 \documentclass[11pt,a4paper]{article}
-\usepackage[hyperref]{acl2020}
+\usepackage[hyperref]{acl2021}
 \usepackage{times}
@@
 \renewcommand{\UrlFont}{\ttfamily\small}
-\usepackage{booktabs}
-\usepackage{multirow}
-\usepackage{tikz}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{subcaption}
-\usepackage{natbib}
+
 % This is not strictly necessary, and may be commented out,
@@
 
+\usepackage{booktabs}
 \usepackage{tabularx}
@@
 
-\title{Can BERT learn dialogue-specific phenomena? The case of laughter in dialogue act recognition. }
+\title{Pre-trained BERT helps with dialogue act recognition, but not very much}
 
@@
 \maketitle
+
 \begin{abstract}
-   In this work we investigate whether transformer models can learn to represent phenomena specific to dialogue.
-   Laughter tokens, which are not present in pre-trained BERT models, can be learned with additional pre-training and fine-tuning on dialogue data. 
-   We use dialogue act recognition as a proxy task to demonstrate that laughter can help to disambiguate between certain communicative intents.
-   We find that pre-training and fine-tuning procedures are useful for learning laughter representations, and explore how well the model adapts to the dialogue domain.
+This document contains the instructions for preparing a manuscript for the proceedings of ACL-IJCNLP 2021.
+The document itself conforms to its own specifications, and is therefore an example of what your manuscript should look like.
+These instructions should be used for both papers submitted for review and for final versions of accepted papers.
+Authors are asked to conform to all the directions reported in this document.
 \end{abstract}
 
-% INTRODUCTION
+%INTRODUCTION
 
@@
 More generally, the way that utterances contribute to and cohere with the discourse is different from the relationship between sentences in a piece of written text.
-
-One important dialogical feature missing from text data is laughter, which is ubiquitous in our everyday interactions.
-We observe that in the Switchboard dialogue corpus laughter comes about every 200 tokens.
-Laughter also relates to the discourse structure of dialogue and can relate to a \emph{laughable}, which can be an event or an entity in the discourse (or external perceived event as well).
-Laughter can precede, follow or overlap the laughable, with the time alignment between the laughter and laughable dependent on who produces the laughable and the form of the laughter \citep{tian2016we}.
-Laughter can act as a contextual feature for determining the sincerity of an utterance, e.g. when detecting sarcasm \citep{tepperman2006yeah}.
 
@@
 Using this task we investigate whether transfer learning techniques based on pre-trained language models, such as BERT \citep{devlinBERTPretrainingDeep2018}, are useful for dialogue.
-By looking at laughter, which is certainly missing in the stadnard pre-training corpus, we can determine whether the pre-training is used in the representation dialogue-specific features.
 
 \paragraph{Contributions}
-The main results of this paper have to do with to the usefulness of language model fine-tuning for DAR, the impact of laughter on DAR, and the relationship between the two.
+The main results of this paper have to do with to the usefulness of language model fine-tuning for DAR.
 \begin{itemize}
-  \item Laughter is useful for dialogue act recognition, and its impact varies across different dialogue acts (\S\ref{sec:experiment1}).
-  \item During fine-tuning, BERT learns to represent laughter, a dialogical feature not seen in pre-training (\S\ref{sec:experiment1} and \S\ref{sec:experiment2}).
   \item Standard BERT pre-training is useful for DAR, but the model performs poorly without fine-tuning (\S\ref{sec:experiment2})
   \item Further pre-training with data from the target domain shows promise for dialogue, but we find mixed results when pre-training with a larger corpus of dialogical data from outside the target domain (\S\ref{sec:experiment3}).
-    % TODO: we did that but what can we conclude? Perhaps that the nature of the data is very different, so it is not very helpful..?
   \end{itemize}
@@
 \paragraph{Preprocessing}
-% - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, removing laughter % Bill
+% - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, % Bill
 
@@
 
-Utterances are tokenized using BERT's word piece tokenizer with a vocabulary of 30,000.
-We add a special laughter token to the vocabulary and map all transcribed laughter to that token.
+Utterances are tokenized using with a word piece tokenizer \citep{Wu2016} with a vocabulary of 30,000.
 We also add five speaker tokens and prepend each utterance with a speaker token that uniquely identifies the corresponding speaker within that dialogue.
-
-\paragraph{Laughs in the data}
-The distribution of laughs in different dialogue acts has a rather uniform shape with a few outliers (Figure~\ref{fig:box}). 
-Figure~\ref{fig:by-da} in Appendix~\ref{sec:suppl} provides a breakdown of dialogue act depending on whether current or adjacent utterances (the preceding utterance and the following one are counted as adjacent) contain laughter.\footnote{Note that SWDA has a ``Nonverbal'' dialogue act which is misleading with respect to laughter, because utterances only containing a single laughter token fall into this category, however they can serve, for example, to acknowledge a statement or to deflect a question  \citep{mazzocconi2019phd}.}
-
-\begin{figure}
-\centering
-\begin{subfigure}[b]{0.55\textwidth}
-  \includegraphics[width=0.9\linewidth]{img/box-swda.pdf}
-  \caption{SWDA}
-  \label{fig:box-swda}
-\end{subfigure}
-
-\begin{subfigure}[b]{0.55\textwidth}
-  \includegraphics[width=0.9\linewidth]{img/box-ami.pdf}
-  \caption{AMI}
-  \label{fig:box-ami}
-\end{subfigure}
-
-\caption{Box plots for dialogue acts associated with laughter. On the left: proportion of DAs having laughter in one of the adjacent utterances, on the right: proportion of DAs containing laughter. }
-\label{fig:box}
-\end{figure}
 
@@
 We also experiment with a much larger a corpus constructed from OpenSubtitles \citep{Lison2016}.
-We used a manually constructed list of words frequenty used to refer to laughter in subtitles and replaced every occurance of one of these words with the special laughter token. 
-Then, we collected every English-language subtitle file in which at least 1\% of the utterances contained laughter (about 11\% of the total).
 Because utterances are not labeled with speaker in the OpenSubtitles corpus, we randomly assigned a speaker token to each utterance to maintain the format of the other dialouge corpora.
@@
 Since there is randomness in the data preparation (e.g., which distrcactor sentences are chosen and which tokens are masked), we generate each training epoch separately.\footnote{For details, see the \href{https://github.com/huggingface/transformers/tree/1.1.0/examples/lm_finetuning}{finetuning example} from Hugging Face.}
-
-\begin{table}[ht]
-\centering
-\begin{tabular}{@{}llll@{}}
-\toprule
-       & tokens & \% laughs & epochs\\ \midrule
-AMI           & 1M     & 1.3             & 10     \\
-SWBD          & 1.5M   & 0.5             & 10     \\
-OpenSubtitles & 350M   & 0.3             & 1      \\ \bottomrule
-\end{tabular}
-\caption{Pre-training corpora, showing laughter representation as a percentage of total tokens and number of pre-training epochs generated.}\label{tab:pretraining-corpora}
-\end{table}
 
@@
 The next section will introduce the experiments that we have carried out and will discuss the results that we obtained from them.
-
-\section{Experiments}
-\subsection{Experiment 1: Impact of laughter} \label{sec:experiment1}   % Vlad
-In the first experiment we investigated whether laughter, as an example of a dialogue-specific signal, is a helpful feature for DAR.
-Therefore, we train another version of each model: one that containing laughs (\texttt{L}) and one with laughs left out (\texttt{NL}), and compare their performances in DAR task.
-Table~\ref{table:laughter-total-acc} compares the results from applying the models with two different utterance encoders (\texttt{BERT}, \texttt{CNN}).
-
-First of all, we can see that the \texttt{BERT} utterance encoder outperforms \texttt{CNN} in all the cases.
-From observing the effect of laughters, we can see differences in performance depending on the dialogue act, regardless how often laughter occurs in the current or adjacent utterances (see Figure~\ref{fig:by-da} in Appendix~\ref{sec:suppl}).
-The strongest evidence for laughter as a helpful feature was found in SWDA for the \texttt{BERT} utterance encoder, where macro-F1 score increases by 7.89 percentage points.
-
-\begin{table}
-  \centering
-  \begin{tabular}{@{}lcccc@{}}
-    \toprule
-                      & \multicolumn{2}{c}{SWDA} & \multicolumn{2}{c}{AMI-DA} \\ \midrule
-                      & F1    & acc.  & F1    & acc.       \\ 
-    \texttt{BERT-NL}  & 38.10 & 77.07 & 49.09 & 67.06       \\ 
-    \texttt{BERT-L}   & 45.99 & 76.93 & 50.17 & 67.12       \\ \midrule
-    \texttt{CNN-NL}   & 37.23 & 75.08 & 38.37 & 63.46        \\
-    \texttt{CNN-L}    & 27.59 & 75.40 & 37.94 & 64.30        \\ \midrule
-    Majority class    & 0.78  & 33.56 &  1.88 & 28.27      \\ \bottomrule
-
-  \end{tabular}
-  \caption{Comparison of macro-average F1 and accuracy depending on using laughter on the training phase. }
-  \label{table:laughter-total-acc}
-\end{table}
-
-Confusion matrices (Figure~\ref{fig:swda-cm}) provide some food for thought.
-Most of the misclassifications fall into the majority classes, such as \emph{sd} (Statement-non-opinion), in the left edge of the matrix.
-However, there are some important exceptions, such as \emph{rhetorical questions}, that are misclassified as other forms of questions due to their surface question-like form.
-Importantly, laughter helps to classify rhetorical questions correctly, this is because in a conversation it can be used as a device to cancel seriousness or sincerity \citep{ginzburg2015understanding,tepperman2006yeah}, in this case, of a question.
-Therefore, questions, like the one we show in the example in Table~\ref{table:example-qh}, are easier to disambiguate with the help of laughter.
-\begin{table}
-      \small
-  \centering
-  \begin{tabularx}{\linewidth}{llL}
-    \toprule
-    Speaker & DA & Utterance \\ \midrule
-        \multicolumn{3}{c}{\emph{(Talking about hobbies)}}\\
-    B   & sd	&  Um, as far as spare time, they talked about, \\
-    B	& \% & I don't, + I think, \\
-    B	& qh & who has any spare time \texttt{<laughter>}? \\
-    A	& x & \texttt{<laughter>}.\\
-             \bottomrule
-  \end{tabularx}
-  \caption{Example from the SWDA corpus (sw3735). B's contribution \emph{qh} (Rhetorical question) is misinterpreted as \emph{qw} (Wh-question) by the BERT model without laughs in training data. }
-  \label{table:example-qh}
-\end{table}
-
-  \begin{figure}
-  \centering
-  \includegraphics[width=1.0\linewidth]{img/swda-cm.pdf}
-  \caption{Confusion matrices for \texttt{BERT-NL} (top) vs \texttt{BERT-L} (bottom); SWDA corpus. Solid line shows the improvement in classification of rhetorical questions.}
-    \label{fig:swda-cm}
-  \end{figure}
-
-In order to further investigate the differences between the models and datasets, we looked at the dialogue act groups.
-Mapping ground-truth labels and predictions into four groups allows direct comparison between model performances in SWDA and AMI-DA.
-Table~\ref{table:laughter-group-acc} compares accuracies between the two main groups: Forward-Communicative-Function and Backward-Communicative-Function (82.3\% of all DAs in SWDA and 76.7\% in AMI-DA).
-Our models tend to perform better for the Forward-Communicative-Function group for both corpora irrespective of the presence of laughs.
-Also, our models perform better on the SWDA corpus.
-Overall performance in these groups appears to be unaffected by presence of laughs.
-
-\begin{table}
-  \centering
-  \begin{tabular}{@{}llcc@{}}
-    \toprule
-    &                  & Forw.-CF  & Backw.-CF   \\ \midrule
-    \multirow{4}{*}{SWDA}    &\texttt{BERT-NL}  & 92.54 & 91.67       \\ 
-                             &\texttt{BERT-L}   & 95.42 & 90.91       \\ 
-                             &\texttt{CNN-NL}   & 93.30 & 90.85        \\
-                             &\texttt{CNN-L}    & 94.64 & 90.13        \\ \midrule
-    \multirow{4}{*}{AMI-DA}  &\texttt{BERT-NL}  & 87.77 & 80.83       \\ 
-                             &\texttt{BERT-L}   & 87.36 & 79.87       \\
-                             &\texttt{CNN-NL}   & 91.85 & 71.21        \\
-                             &\texttt{CNN-L}    & 91.25 & 71.28        \\    \bottomrule
-  \end{tabular}
-  \caption{Comparison of the accuracies among the two main dialogues act groups, depending on the utterance model and the presence of laughter.}
-  \label{table:laughter-group-acc}
-\end{table}
 
@@
 
-\paragraph{Fine-tuning and laughter}
-Since the laughter token doesn't appear in the original BERT vocabulary, only fine-tuned models can meaningfully make use of laughter in utterance representations. 
-This gives us another opportunity to assess whether laughter is useful in dialogue act recognition.
-We find that although 4.6\% of utterances in SWDA contain laughter, 
-7.3\% of utterances misclassified by the frozen model but correctly classified by the fine-tuned model contain laughter, 
-suggesting that the fine-tuned encoder makes use of laughter. 
-For AMI-DA, the effect is less pronounced, but still present: 
-overall, 8.5\% of utterances contain laughter, 
-compared to 9.6\% of utterances where fine-tuning makes a difference.
-
 \subsection{Experiment 3: Impact of dialogue pre-training} \label{sec:experiment3} % Bill
@@
 \section{Discussion} % add items to discuss
-On the question of laughter impact, this study found that laughter is more helpful in SWDA corpus than in AMI-DA.
-Due to the nature of interactions over the phone, SWDA dialogue participants can not rely on visual signals, such as gestures and facial expressions.
-Our results support the hypothesis that in SWDA, vocalizations such as laughter are more pronounced and therefore more helpful in disambiguating dialogue acts.
 
@@
 \citet{stolckeDialogueActModeling2000} showed that dialogue acts can have specific prosodic manifestations that can be used to improve dialogue act classification.
-Furthermore, in relation to laughter, its form (duration, arousal level) can be informative about its function and position w.r.t. to laughable \citep{tian2016we,mazzocconi2019phd}.
 Incorporating such information is crucial if models pre-trained on large-scale text corpora are to be adapted for use in dialogue applications.
@@
 
-%\begin{itemize}
-  %\item RoBERTa training scheme finds that next sentence prediction is of little importance.
-Is this true for us too?
-(suspect not due to discourse importance).
-see: https://github.com/huggingface/transformers/issues/1622
-  %\item Issues related to working with transcribed speech: Different kinds of laughter are all represented by the same token.
-Does transcription orthography capture prosody?
-We know prosidy is useful for DAR (Jurafsky).
-  %\item future work: pre-training on very large un-labeled dialogue corpora. How does text chat transfer to the spoken/transcribed setting?
-  %\item Laughter is more helpful in SWDA than in AMI-DA. 
-  %\item The point above can also explain why our models better on SWDA: just a larger proportion of stuff that interlocutors rely on is in the transcription.
-%\end{itemize}
-
 \bibliography{acl2020}
@@
 \onecolumn
-\section{Supplementary materials}\label{sec:suppl}
+\bibliographystyle{acl_natbib}
+\bibliography{iwcs-short-paper}
 
-\begin{figure*}[h!]
-  \centering
-  \includegraphics[width=\linewidth]{img/SWDA-bertLvsNL.pdf}
-  \includegraphics[width=\linewidth]{img/AMI-DA-bertLvsNL.pdf}
-  \caption{Change in accuracy for each dialogue act (\texttt{BERT-NL} vs \texttt{BERT-L}).
-Positive changes when adding laughter (\texttt{BERT-L}) are shown in blue.
-Vertical bars indicate how often dialogue act is associated with laughter.
-Top chart: SWDA, Bottom chart: AMI-DA.
-}
-    \label{fig:by-da}
-  \end{figure*}
-
-\begin{figure*}[h!]
-  \centering
-  \includegraphics[width=\linewidth]{img/swda-brf.pdf}
-  \includegraphics[width=\linewidth]{img/ami-brf.pdf}
-  \caption{F1 scores by dialogue act for BERT with standard pre-training and DAR fine-tuning (\texttt{BERT-FT}) vs.~the same model without pre-training (\texttt{BERT-RI}) and without fine-tuning (\texttt{BERT-FZ}).
-Dialogue acts are ordered with the most common on the left.}
-    \label{fig:f1-by-da}
-  \end{figure*}
+%\appendix
 

### 2021-03-12 reports/IWCS2021/iwcs-short-paper.tex
edits

@@
 
-\title{Pre-trained BERT helps with dialogue act recognition, but not very much}
+\title{Large-scale text pre-training helps with dialogue act recognition, but not without fine-tuning}
 
@@
 
+% We should make the comparison with other tasks where BERT representations work well AS IS (i.e., without finetuning) vs dialogue where 
+% the pretraining is helpful, but not without finetuning
+% Missing reference(s) from *SEM reviews
+% Usefulness of in-domain pre-training for spoken dialogue
+% Future work: dialogue act recognition is not enough to fully evaluate BERT for dialogue - other turn change prediction, intent classification, utterance segmentation and disfluency detection
+%
+
 \begin{document}
@@
 \begin{abstract}
-This document contains the instructions for preparing a manuscript for the proceedings of ACL-IJCNLP 2021.
-The document itself conforms to its own specifications, and is therefore an example of what your manuscript should look like.
-These instructions should be used for both papers submitted for review and for final versions of accepted papers.
-Authors are asked to conform to all the directions reported in this document.
+  We use dialogue act recognition (DAR)
+  to investigate how well BERT represents utterances in dialogue,
+  and how fine-tuning and large-scale pre-training contribute to its performance.
+  We find that while both the standard BERT pre-training and pretraining on
+  dialogue-like data are useful, task-specific fine-tuning is essential for good performance.
 \end{abstract}
@@
 
-Recently, large-scale language models, trained on massive corpora of text data, have achieved state-of-the-art results on a variety of traditional NLP tasks.
-It is still uncertain whether these models might be useful for processing dialogue, and if so, whether they can adapt to make use of dialogue-specific features.
+Recently, large-scale neural language models, trained on massive corpora of text data, 
+have achieved state-of-the-art results on a variety of traditional NLP tasks.
+Given that dialogue, especially spoken dialogue, 
+is radically different from the kind of data these language models are pre-trained on,
+it is uncertain whether these models would be useful for dialouge-oriented tasks.
+In the example from the Switchboard corpus, shown in Table~\ref{tab:example}, 
+it is evident that the structure of dialogue is quite different from that of written text.
+%even if one imagines a script for a movie or a play.
+Not only is the internal structure of the contributions different---%
+with features such as disfluencies, repair, incomplete sentences, and various vocal sounds---%
+but the sequential structure of the discourse is different as well.
+In dialogue, speakers take turns and switch perspectives.
+More generally, the way that utterances contribute to and cohere with the discourse
+is different from the relationship between sentences in a piece of written text.
 
-Dialogue, especially spoken dialogue, is radically different from the kind of data that neural language models are pre-trained on.
-In the example from the Switchboard corpus, shown in Table~\ref{table:example}, it is evident that the syntactic structure of dialogue is very different from  written text, even if one imagines a script for a movie or a play.
-Not only is the internal structure of contributions different---with features such as disfluencies, repair, incomplete sentences, and various vocal sounds---but the sequential structure of the discourse is also very different.
-In dialogue, speakers take turns and switch perspectives.
-More generally, the way that utterances contribute to and cohere with the discourse is different from the relationship between sentences in a piece of written text.
+In this paper, we investigate how well 
+one such large-scale language model,
+BERT \citep{devlinBERTPretrainingDeep2018}, 
+represents utterances in dialogue.
+We use dialogue act recognition (DAR) as a proxy task, 
+since both the internal content and the sequential structure of utterances 
+has bearing on this task
 
@@
 }
-  \label{table:example}
+  \label{tab:example}
 \end{table}
 
-We use dialogue act recognition (DAR) as a proxy task, since both the internal content of contributions, and their sequential structure have bearing on this task.
-DAR is the task of assigning a dialogue act tag to each utterance in the dialogue, according to dialogue act it performs.
-Using this task we investigate whether transfer learning techniques based on pre-trained language models, such as BERT \citep{devlinBERTPretrainingDeep2018}, are useful for dialogue.
-
-\paragraph{Contributions}
-The main results of this paper have to do with to the usefulness of language model fine-tuning for DAR.
-\begin{itemize}
-  \item Standard BERT pre-training is useful for DAR, but the model performs poorly without fine-tuning (\S\ref{sec:experiment2})
-  \item Further pre-training with data from the target domain shows promise for dialogue, but we find mixed results when pre-training with a larger corpus of dialogical data from outside the target domain (\S\ref{sec:experiment3}).
-  \end{itemize}
-
-In the following section we provide more details about the dialogue act recognition task and transfer learning techniques.
+We have two main contributions.
+First we find that while standard BERT pre-training is useful,
+but the model performs poorly without fine-tuning (\S\ref{sec:experiment2}).
+Second, we find that further pre-training with data from the target domain shows promise for dialogue, 
+but the results are mixed when pre-training with a larger corpus of dialogical data from outside the target domain (\S\ref{sec:experiment3}).
 
@@
 Breaking with classical semantic theory, speech act theory considers not only the propositional content of an utterance but also the actions, such as \emph{promising} or \emph{apologizing}, it carries out.
-Dialogue acts extend the concept of the speech act, with a focus on the interactional nature of most speech.
-DAMSL \citep{coreCodingDialogsDAMSL1997}, for example, is an influential dialogue act tagging scheme where dialogue acts are defined in part by whether they have a \emph{forward-looking} function (are expecting a response) or \emph{backward-looking} function (are in response to a previous utterance).
+Dialogue acts extend the concept of the speech act, 
+with a focus on the interactional nature of most speech.
+%DAMSL \citep{coreCodingDialogsDAMSL1997} is an influential dialogue act tagging scheme 
+%where dialogue acts are defined in part by whether they have a 
+%\emph{forward-looking} function (are expecting a response) or 
+%\emph{backward-looking} function (are in response to a previous utterance).
 
-DAR is the task of labeling utterances with the dialogue act they perform from a given set of dialogue act tags.
+DAR is the task of labeling utterances with the dialogue act they perform 
+from a given set of dialogue act tags.
 As with other sequence labeling tasks in NLP, some notion of context is helpful in DAR.
-One of the first performant machine learning models for DAR was a Hidden Markov Model that used various lexical and prosodic features as input \citep{stolckeDialogueActModeling2000}.
-
-Most successful neural approaches also model some notion of context.
-We follow previous work that models dialogue act sequences with an RNN over utterances \citep{kalchbrennerRecurrentConvolutionalNeural2013,tranHierarchicalNeuralModel2017,botheContextbasedApproachDialogue2018,bothe2018conversational,zhao2018unified}.
-Our model predicts the most likely tag given the hidden state of the RNN at each position, though other work has shown that DAR benefits from more sophisticated approaches, such as conditional random field \citep{chenDialogueActRecognition2017} or uncertainty propagation \citep{tranPreservingDistributionalInformation2017}.
+One of the first performant machine learning models for DAR was a Hidden Markov Model 
+that used various lexical and prosodic features as input \citep{stolckeDialogueActModeling2000}.
+Most successful neural approaches also model some notion of context \citep[e.g.,][]{kalchbrennerRecurrentConvolutionalNeural2013,tranHierarchicalNeuralModel2017,botheContextbasedApproachDialogue2018,bothe2018conversational,zhao2018unified}.
+Following previous work, we model dialogue act sequences with an RNN over utterance representations,
+which are constructed by BERT.
 
@@
 
-Recently, neural models trained on large datasets with various unsupervised tasks have found success creating sentence-level and contextual word representations. 
-BERT, a multi-layer transformer, is one such model \citep{devlinBERTPretrainingDeep2018}. 
-BERT is pre-trained on two unsupervised tasks: \emph{masked token prediction} and \emph{next sentence prediction}.
-In masked token prediction, some percentage of words are randomly replaced with a mask token, and the model is trained to predict the identity of the original token, based on the context sentence.
-In next sentence prediction, the model is given two sentences and trained to predict whether the second sentence follows the first in the original text, or if it was randomly chosen from elsewhere in the corpus.
+%Recently, neural models trained on large datasets with various unsupervised tasks have found success creating sentence-level and contextual word representations. 
+BERT, a multi-layer transformer model \citep{devlinBERTPretrainingDeep2018}, 
+is pre-trained on two unsupervised tasks: 
+\emph{masked token prediction} and \emph{next sentence prediction}.
+In masked token prediction, some percentage of words are randomly replaced with a mask token.
+The model is trained to predict the identity of the original token based on the context sentence.
+In next sentence prediction, the model is given two sentences and trained to predict whether the second sentence follows the first in the original text or if it was randomly chosen from elsewhere in the corpus.
 After pre-training, BERT can be applied to a supervised task by adding additional un-trained layers that take the hidden state of one or more of BERT's layers as input.
@@
 Finally, \citet{chakravarty2019dialog} use BERT for dialogue act classification for a proprietary domain and achieves promising results, and \citet{ribeiro2019deep} surpass the previous state-of-the-art on generic dialog act recognition for Switchboard and MRDA corpora.
-In our work we are not attempting to beat the current state-of-the-art due to the different aims of the study.
+This paper aims to supplement the findings of previous work by investigating how much of 
+BERT's sucess for dialogue tasks is due to its extensive pre-training and how much is due to 
+task-specific fine-tuning.
 
@@
 
-\citet{petersTuneNotTune2019} investigate when it is best to fine-tune BERT for sentence classification tasks.
-They find that when the target task is very similar to the pre-training task, fine-tuning provides less of a performance boost.
+\citet{petersTuneNotTune2019} investigate when it is best to fine-tune BERT for sentence classification tasks 
+and find that when the target task is very similar to the pre-training task, 
+fine-tuning provides less of a performance boost.
 We note that there is some conceptual relationship between DAR and next sentence prediction, since the dialogue act constrains (or at least is predictive of) the dialogue act that follows it.
-
-\citet{petersTuneNotTune2019} also consider whether the similarity of the pre-training and target domains may have similar consequences, but don't find an effect of domain similarly for the natural language inference tasks they tested on.
-As discussed in \S\ref{sec:data}, however, there are dramatic differences between written text and transcribed dialogue which may make fine-tuning necessary for DAR.
-
-\paragraph{} In the next section, we will present the datasets that we will use in our experiments along with their distinctive features.
+That said, the discourse strucutre of the encyclopedia and book data that makes up BERT's pre-training corpus
+is probably quite different from that of natural dialogue.
+%\citet{petersTuneNotTune2019} also consider whether the similarity of the pre-training and target domains may have similar consequences, but don't find an effect of domain similarly for the natural language inference tasks they tested on.
+%As discussed in \S\ref{sec:data}, however, there are dramatic differences between written text and transcribed dialogue which may make fine-tuning necessary for DAR.
 
 \section{Data}\label{sec:data}
-We perform experiments on the Switchboard Dialogue Act Corpus (SWDA), which is a subset of the larger Switchboard corpus, and the dialogue act-tagged portion of the AMI Meeting Corpus (AMI-DA). 
-SWDA is tagged with a set of 220 dialogue act tags which, following  \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}, we cluster into a smaller set of 42 tags.
-AMI uses a smaller tagset of 16 dialogue acts \citep{GuidelinesDialogueAct2005}.
-
-% - DA distribution              % Vlad
 
@@
   \caption{Comparison between Switchboard and the AMI Meeting Corpus}
-  \label{table:corpora}
+  \label{tab:corpora}
 \end{table}
+
+We perform experiments on the Switchboard Dialogue Act Corpus (SWDA), 
+which is a subset of the larger Switchboard corpus, 
+and the dialogue act-tagged portion of the AMI Meeting Corpus (AMI-DA). 
+SWDA is tagged with a set of 220 dialogue act tags which, following  \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}, we cluster into a smaller set of 42 tags.
+AMI uses a smaller tagset of 16 dialogue acts \citep{GuidelinesDialogueAct2005}.
+See Table~\ref{tab:corpora} for details.
+
+% - DA distribution              % Vlad
 
@@
 
-Utterances are tokenized using with a word piece tokenizer \citep{Wu2016} with a vocabulary of 30,000.
-We also add five speaker tokens and prepend each utterance with a speaker token that uniquely identifies the corresponding speaker within that dialogue.
+Utterances are tokenized with BERT's word piece tokenizer with a vocabulary of 30,000.
+To this vocabulary we added five speaker tokens and prepend each utterance with a speaker 
+token that uniquely identifies the corresponding speaker within that dialogue.
 
-\paragraph{Dialogue act grouping}
-For our corpora we also considered grouping the dialogue acts according to DAMSL coders manual \citep{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}: Forward-Communicative-Function (51.86\% of all DAs), Backwards-Communicative-Function (30.35\%), Other (9.04\%) and Communicative-Status (8.75\%).
-This allows the direct comparison between SWDA and AMI-DA.
-With respect to laughs, we observed an even distribution of them in the groups, except for the Communicative-Status group in the case of SWDA, because of the ``Nonverbal'' dialogue acts (see footnote~1).
+%\paragraph{Dialogue act grouping}
+%For our corpora we also considered grouping the dialogue acts according to DAMSL coders manual \citep{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}: Forward-Communicative-Function (51.86\% of all DAs), Backwards-Communicative-Function (30.35\%), Other (9.04\%) and Communicative-Status (8.75\%).
+%This allows the direct comparison between SWDA and AMI-DA.
+%With respect to laughs, we observed an even distribution of them in the groups, except for the Communicative-Status group in the case of SWDA, because of the ``Nonverbal'' dialogue acts (see footnote~1).
 
@@
 
-We also experiment with three unlabeled dialogue corpora (Table~\ref{tab:pretraining-corpora}), which we use to provide further pre-training for the BERT encoder.
+We also experiment with three unlabeled dialogue corpora, which we use to provide further pre-training for the BERT encoder.
 
@@
 
-We also experiment with a much larger a corpus constructed from OpenSubtitles \citep{Lison2016}.
-Because utterances are not labeled with speaker in the OpenSubtitles corpus, we randomly assigned a speaker token to each utterance to maintain the format of the other dialouge corpora.
+We also experiment with a much larger a corpus (350M tokens) constructed from OpenSubtitles \citep{Lison2016}.
+Because utterances are not labeled with speaker, we randomly assigned a speaker token to each utterance to maintain the format of the other dialouge corpora.
 
@@
 
-\paragraph{}
-Let us turn now to describing the neural network architectures that we used.
-
 \section{Model} % Bill
 
-To test the effectiveness of BERT for DAR, we employ a simple neural architecture with two components: an encoder that vectorizes utterances, and a sequence model that predicts dialogue act tags from the vectorized utterances (Figure~\ref{fig:model-architecture}).
-Since we are primarily interested in comparing different utterance encoders, we use a basic RNN as the sequence model in every configuration.\footnote{We have experimented with LSTM as the sequence model, but the accuracy was not significantly different compared to RNN.
+We use a simple neural architecture with two components: 
+an encoder that vectorizes utterances (BERT), 
+and a sequence model that takes the utterance representations as input.
+Since we are primarily interested in comparing different training and fine-tuning schemes for the utterance encoder, 
+we use a basic single-layer RNN as the sequence model in every configuration.\footnote{We have experimented with LSTM as the sequence model, but the accuracy was not significantly different compared to RNN.
 It can be explained by the absence of longer distance dependencies on this level of our model.}
-The RNN takes the encoded utterance as input at each time step,
-and its hidden state is passed to a simple linear classification layer over dialogue act tags.
-Conceptually, the encoded utterance represents the context-agnostic features of the utterance, and the hidden state of the RNN represents the full discourse context.
+At each time step, the RNN takes the encoded utterance as input 
+and its hidden state is passed to a simple linear classification layer over dialogue act tags.\footnote{
+Other work has shown that DAR benefits from more sophisticated decoding, such as conditional random field \citep{chenDialogueActRecognition2017} and uncertainty propagation \citep{tranPreservingDistributionalInformation2017}.}
 
-\begin{figure*}
-  \include{model}
-  \caption{Simple neural dialogue act recognition sequence model}
-  \label{fig:model-architecture}
-\end{figure*}
+Conceptually, the encoded utterance represents the context-agnostic features of the utterance 
+and the hidden state of the RNN represents the full discourse context.
 
-As a baseline utterance encoder, we use a word-level CNN with window sizes of 3, 4, and 5, each with 100 feature maps \citep{kimConvolutionalNeuralNetworks2014}. 
-The model uses 100-dimensional word embeddings, which are initialized with pre-trained gloVe vectors \citep{penningtonGloveGlobalVectors2014}.
+%As a baseline utterance encoder, we use a word-level CNN with window sizes of 3, 4, and 5, each with 100 feature maps \citep{kimConvolutionalNeuralNetworks2014}. 
+%The model uses 100-dimensional word embeddings, which are initialized with pre-trained gloVe vectors \citep{penningtonGloveGlobalVectors2014}.
 
@@
 In our implementation, we use the un-cased model provided by \citet{wolfHuggingFaceTransformersStateoftheart2019}.
+The RNN has a hidden layer size of 100.
 
-The next section will introduce the experiments that we have carried out and will discuss the results that we obtained from them.
-
-\subsection{Experiment 2: Impact of pre-training vs. fine-tuning} \label{sec:experiment2} % Bill
-Next, we analyze how pre-training affects BERT's performance as an utterance encoder.
+\subsection{Pre-training vs. fine-tuning} \label{sec:experiment2} % Bill
+First, we analyze how pre-training affects BERT's performance as an utterance encoder.
 To do so, we consider the performance of DAR models with three different utterance encoders:
@@
   \caption{Macro-average F1 and accuracy of BERT with standard pre-training and DAR fine-tuning (\texttt{BERT-FT}) vs.~the same model without pre-training (\texttt{BERT-RI}) and without fine-tuning (\texttt{BERT-FZ}).}
-  \label{table:exp2}
+  \label{tab:exp2}
 \end{table}
@@
 The pre-trained model is more accurate than the randomly initialized model by several percentage points on both DA corpora,
-suggesting that BERT's extensive pre-training does provide some useful information for recognizing different dialogue acts (Table~\ref{table:exp2}).
+suggesting that BERT's extensive pre-training does provide some useful information for recognizing different dialogue acts (Table~\ref{tab:exp2}).
 This performance boost is much more pronounced in the macro-averaged F1 score,
@@
 Comparing the performance of the fine-tuned encoder to that of the frozen model, we note that pre-training alone is not enough.
-The frozen model is heavily biased towards the most frequent tags, which explains its especially poor macro-average score (Table~\ref{table:exp2}).
+The frozen model is heavily biased towards the most frequent tags, which explains its especially poor macro-average score (Table~\ref{tab:exp2}).
 In SWDA, for example, the model with a frozen encoder predicts one of the two most common tags (Statement-non-opinion or Acknowledge) 86\% of the time, whereas those two
@@
     for the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions.}
-  \label{table:exp3}
+  \label{tab:exp3}
 \end{table}
@@
 
+\bibliographystyle{acl_natbib}
 \bibliography{acl2020}
-\bibliographystyle{acl_natbib}
-\appendix
-\onecolumn
-\bibliographystyle{acl_natbib}
-\bibliography{iwcs-short-paper}
 

### 2021-03-12 reports/IWCS2021/iwcs-short-paper.tex
typo

@@
 is radically different from the kind of data these language models are pre-trained on,
-it is uncertain whether these models would be useful for dialouge-oriented tasks.
+it is uncertain whether these models would be useful for dialogue-oriented tasks.
 In the example from the Switchboard corpus, shown in Table~\ref{tab:example}, 

### 2021-03-12 reports/IWCS2021/iwcs-short-paper.tex
drip

--- 2021-03-12 reports/IWCS2021/iwcs-short-paper.tex
@@
 which is explained by the fact that at the tag level, pre-training has a larger impact on less frequent tags.
-For a disaggregated view, see Figure \ref{fig:f1-by-da} in Appendix~\ref{sec:suppl}.
+For a disaggregated view, see Figure 1 in the supplementary materials.
 
@@
 Indeed, a simple lexical probe supports this explanation: in utterances where the pre-trained model is correct and the randomly initialized model is not,
-the rarest word is 1.9 times rarer than is typical of corpus as a whole.
+the rarest word is 1.9 times rarer on average than is typical of corpus as a whole.
 
-Comparing the performance of the fine-tuned encoder to that of the frozen model, we note that pre-training alone is not enough.
+Comparing the performance of the fine-tuned encoder to that of the frozen model, 
+we see that pre-training alone is not enough.
 The frozen model is heavily biased towards the most frequent tags, which explains its especially poor macro-average score (Table~\ref{tab:exp2}).

### 2021-03-12 reports/IWCS2021/iwcs-short-paper.tex
typo

@@
 \citet{mehriPretrainingMethodsDialog2019} evaluate BERT in various dialogue tasks including DAR, and find that a model incorporating BERT outperforms a baseline model.
-Finally, \citet{chakravarty2019dialog} use BERT for dialogue act classification for a proprietary domain and achieves promising results, and \citet{ribeiro2019deep} surpass the previous state-of-the-art on generic dialog act recognition for Switchboard and MRDA corpora.
+Finally, \citet{chakravarty2019dialog} use BERT for dialogue act classification for a proprietary domain and achieves promising results, and \citet{ribeiro2019deep} surpass the previous state-of-the-art on generic dialogue act recognition for Switchboard and MRDA corpora.
 This paper aims to supplement the findings of previous work by investigating how much of 

### 2021-03-12 reports/IWCS2021/iwcs-short-paper.tex
some cuts

--- 2021-03-12 reports/IWCS2021/iwcs-short-paper.tex
@@
 
-Recently, large-scale neural language models, trained on massive corpora of text data, 
+Large-scale neural language models trained on massive corpora of text data
 have achieved state-of-the-art results on a variety of traditional NLP tasks.
@@
 is radically different from the kind of data these language models are pre-trained on,
-it is uncertain whether these models would be useful for dialogue-oriented tasks.
+it is uncertain whether they would be useful for dialogue-oriented tasks.
 In the example from the Switchboard corpus, shown in Table~\ref{tab:example}, 
@@
 %even if one imagines a script for a movie or a play.
-Not only is the internal structure of the contributions different---%
+Not only is the internal structure of contributions different---%
 with features such as disfluencies, repair, incomplete sentences, and various vocal sounds---%
 but the sequential structure of the discourse is different as well.
-In dialogue, speakers take turns and switch perspectives.
-More generally, the way that utterances contribute to and cohere with the discourse
-is different from the relationship between sentences in a piece of written text.
+%In dialogue, speakers take turns and switch perspectives.
+%More generally, the way that utterances contribute to and cohere with the discourse
+%is different from the relationship between sentences in a piece of written text.
 
@@
 \paragraph{Fine-tuning vs.~further in-domain pre-training}
-Transfer learning schemes for pre-trained language models such as BERT draw on one or more of the following three adaptation strategies \citep{sunHowFineTuneBERT2019}:
-\emph{further pre-training}, in which the model is trained in an un-supervised way, similar to its initial training scheme, but on data that is in-domain for the target task; 
-\emph{single-task fine-tuning}, in which the model's encoder layers are optimized during training for the target task;
-and \emph{multi-task fine-tuning}, in which models with shared encoder layers are jointly trained on several related tasks.
-In this paper, we investigate the first two methods and their combination, as applied to DAR.
+We experiment with the following two transfer learning strategies \citep{sunHowFineTuneBERT2019}:
+\emph{further pre-training}, in which the model is trained in an un-supervised way, similar to its initial training scheme, but on data that is in-domain for the target task; and
+\emph{single-task fine-tuning}, in which the model's encoder layers are optimized during training for the target task.
 
-Regardless of whether an encoder model has undergone further in-domain pre-training, the choice of whether to fine-tune during task training remains.
-Freezing the encoder model during task training is more efficient, since the gradient of the loss function need only be computed for the task-specific layers.
+Whether or not encoder model has undergone further in-domain pre-training, 
+the choice of whether to fine-tune during task training remains.
+Freezing the encoder model during task training is more efficient, 
+since the gradient of the loss function need only be computed for the task-specific layers.
 However, fine-tuning can lead to better performance since the encoding itself is adapted to the target task and domain.
@@
 \begin{itemize}
-  \item \texttt{BERT-FT} -- pre-trained BERT with DAR fine-tuning 
-  \item \texttt{BERT-RI} -- randomly initialized BERT (with DAR fine-tuning)
-  \item \texttt{BERT-FZ} -- pre-trained BERT without fine-tuning (frozen during DAR training)
+  \item \texttt{BERT-FT} -- pre-trained + DAR fine-tuning 
+  \item \texttt{BERT-FZ} -- pre-trained, frozen during DAR
+  \item \texttt{BERT-RI} -- randomly initialized + DAR fine-tuning 
 \end{itemize}
 
-\begin{table}[]
-\centering
-\begin{tabular}{@{}lrrrr@{}}
-\toprule
-                           & \multicolumn{2}{c}{SWDA}                          & \multicolumn{2}{c}{AMI-DA}                        \\ \midrule
-                           & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
-\texttt{BERT-FT} & 36.75           & 76.60                    & 43.42                  & 64.93                    \\
-\texttt{BERT-RI} & 32.18           & 73.80                    & 34.88                  & 60.89                    \\
-\texttt{BERT-FZ} & 7.75            & 55.61                    & 14.86                  & 48.34 \\ \midrule
-    Majority class    & 0.78  & 33.56 &  1.88 & 28.27      \\ \bottomrule
-\end{tabular}
-  \caption{Macro-average F1 and accuracy of BERT with standard pre-training and DAR fine-tuning (\texttt{BERT-FT}) vs.~the same model without pre-training (\texttt{BERT-RI}) and without fine-tuning (\texttt{BERT-FZ}).}
-  \label{tab:exp2}
-\end{table}
+%\begin{table}[]
+%\centering
+%\begin{tabular}{@{}lrrrr@{}}
+%\toprule
+                           %& \multicolumn{2}{c}{SWDA}                          & \multicolumn{2}{c}{AMI-DA}                        \\ \midrule
+                           %& \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
+%\texttt{BERT-FT} & 36.75           & 76.60                    & 43.42                  & 64.93                    \\
+%\texttt{BERT-RI} & 32.18           & 73.80                    & 34.88                  & 60.89                    \\
+%\texttt{BERT-FZ} & 7.75            & 55.61                    & 14.86                  & 48.34 \\ \midrule
+    %Majority class    & 0.78  & 33.56 &  1.88 & 28.27      \\ \bottomrule
+%\end{tabular}
+  %\caption{Macro-average F1 and accuracy of BERT with standard pre-training and DAR fine-tuning (\texttt{BERT-FT}) vs.~the same model without pre-training (\texttt{BERT-RI}) and without fine-tuning (\texttt{BERT-FZ}).}
+  %\label{tab:exp2}
+%\end{table}
 
 The pre-trained model is more accurate than the randomly initialized model by several percentage points on both DA corpora,
-suggesting that BERT's extensive pre-training does provide some useful information for recognizing different dialogue acts (Table~\ref{tab:exp2}).
+suggesting that BERT's extensive pre-training does provide some useful information for recognizing different dialogue acts (Table~\ref{tab:results}).
 This performance boost is much more pronounced in the macro-averaged F1 score,
@@
 we see that pre-training alone is not enough.
-The frozen model is heavily biased towards the most frequent tags, which explains its especially poor macro-average score (Table~\ref{tab:exp2}).
+The frozen model is heavily biased towards the most frequent tags, which explains its especially poor macro-average score (Table~\ref{tab:results}).
 In SWDA, for example, the model with a frozen encoder predicts one of the two most common tags (Statement-non-opinion or Acknowledge) 86\% of the time, whereas those two
 tags account for only 51\% of the ground truth tags.
-The fine-tuned model is much less biased; it predicts the two most common tags only 59\% of the time.
+The model with a fine-tuned encoder is much less biased; it predicts the two most common tags only 59\% of the time.
 
@@
 
-\subsection{Experiment 3: Impact of dialogue pre-training} \label{sec:experiment3} % Bill
+\subsection{Impact of dialogue pre-training} \label{sec:experiment3} % Bill
 
@@
 \citet{sunHowFineTuneBERT2019} has reported that performing additional pre-training on unlabeled in-domain data improves performance on classification tasks. 
-We want to see if BERT can benefit from pre-training, on dialogue data, including from data outside the immediate target domain.
+We want to see if BERT can benefit from pre-training on dialogue data, including from data outside the immediate target domain.
 
@@
 \texttt{BERT+OS-FZ} &  \textbf{9.60}         & \textbf{57.67}           & \textbf{17.03}         & \textbf{51.03}           \\ \midrule
+\texttt{BERT-RI} & 32.18           & 73.80                    & 34.88                  & 60.89                    \\ \midrule
     Majority class  & 0.78                   & 33.56                    &  1.88                  & 28.27      \\ \bottomrule
@@
 \caption{Comparison of macro-average F1 and accuracy with further in-domain (\texttt{ID}), combined corpus (\texttt{CC}), and OpenSubtitles (\texttt{OS}) dialogue pre-training,
-    for the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions.}
-  \label{tab:exp3}
+for the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions. \texttt{BERT-RI} uses a randomly initialized utterance encoder with no pre-training but with fine-tuning.}
+  \label{tab:results}
 \end{table}

### 2021-03-12 reports/IWCS2021/iwcs-short-paper.tex
combined -> cross-domain

@@
 \end{tabular}
-\caption{Comparison of macro-average F1 and accuracy with further in-domain (\texttt{ID}), combined corpus (\texttt{CC}), and OpenSubtitles (\texttt{OS}) dialogue pre-training,
+\caption{Comparison of macro-average F1 and accuracy with further in-domain (\texttt{ID}), cross-domain corpus (\texttt{CC}), and OpenSubtitles (\texttt{OS}) dialogue pre-training,
 for the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions. \texttt{BERT-RI} uses a randomly initialized utterance encoder with no pre-training but with fine-tuning.}

### 2021-03-12 reports/IWCS2021/iwcs-short-paper.tex
edit discussion

--- 2021-03-12 reports/IWCS2021/iwcs-short-paper.tex
@@
 First we find that while standard BERT pre-training is useful,
-but the model performs poorly without fine-tuning (\S\ref{sec:experiment2}).
+the model performs poorly without fine-tuning (\S\ref{sec:experiment2}).
 Second, we find that further pre-training with data from the target domain shows promise for dialogue, 
@@
 Most successful neural approaches also model some notion of context \citep[e.g.,][]{kalchbrennerRecurrentConvolutionalNeural2013,tranHierarchicalNeuralModel2017,botheContextbasedApproachDialogue2018,bothe2018conversational,zhao2018unified}.
-Following previous work, we model dialogue act sequences with an RNN over utterance representations,
-which are constructed by BERT.
+%Following previous work, we model dialogue act sequences with an RNN over utterance representations,
+%which are constructed by BERT.
 
@@
 
-Whether or not encoder model has undergone further in-domain pre-training, 
+Whether or not the encoder model has undergone further in-domain pre-training, 
 the choice of whether to fine-tune during task training remains.
@@
 To do so, we consider the performance of DAR models with three different utterance encoders:
-\begin{itemize}
+\begin{itemize}\setlength\itemsep{-0.5em}
   \item \texttt{BERT-FT} -- pre-trained + DAR fine-tuning 
   \item \texttt{BERT-FZ} -- pre-trained, frozen during DAR
-  \item \texttt{BERT-RI} -- randomly initialized + DAR fine-tuning 
+  \item \texttt{BERT-RI} -- random init. + DAR fine-tuning 
 \end{itemize}
@@
 
-The pre-trained model is more accurate than the randomly initialized model by several percentage points on both DA corpora,
-suggesting that BERT's extensive pre-training does provide some useful information for recognizing different dialogue acts (Table~\ref{tab:results}).
+\texttt{BERT-FT} is more accurate than \texttt{BERT-RI} by several percentage points on both DA corpora,
+suggesting that BERT's extensive pre-training does provide some useful information for DAR (Table~\ref{tab:results}).
 This performance boost is much more pronounced in the macro-averaged F1 score,
-which is explained by the fact that at the tag level, pre-training has a larger impact on less frequent tags.
-For a disaggregated view, see Figure 1 in the supplementary materials.
+which is explained by the fact that at the tag level, pre-training has a larger impact on less frequent tags
+(see Figure 1 in the supplementary materials).
 
-A key aspiration of transfer learning is to expose the model to phenomena that are too infrequent to learn from labeled training data alone.
-One explanation for pre-trained BERT's superior performance on some infrequent dialogue acts is that it has learned to represent relevant features
-that the randomly initialized model was unable to learn due to their sparsity in the labeled training set.
-Indeed, a simple lexical probe supports this explanation: in utterances where the pre-trained model is correct and the randomly initialized model is not,
-the rarest word is 1.9 times rarer on average than is typical of corpus as a whole.
-
-Comparing the performance of the fine-tuned encoder to that of the frozen model, 
-we see that pre-training alone is not enough.
-The frozen model is heavily biased towards the most frequent tags, which explains its especially poor macro-average score (Table~\ref{tab:results}).
+%Comparing the performance of the fine-tuned encoder to that of the frozen model, 
+%we see that pre-training alone is not enough.
+The \texttt{BERT-FZ} performs very poorly compared to either \texttt{BERT-FT} or \texttt{BERT-RI}, however.
+It is heavily biased towards the most frequent tags, which explains its especially poor macro-average score (Table~\ref{tab:results}).
 In SWDA, for example, the model with a frozen encoder predicts one of the two most common tags (Statement-non-opinion or Acknowledge) 86\% of the time, whereas those two
 tags account for only 51\% of the ground truth tags.
-The model with a fine-tuned encoder is much less biased; it predicts the two most common tags only 59\% of the time.
+\texttt{BERT-FT} is much less biased; it predicts the two most common tags only 59\% of the time.
 
@@
 the cross-domain corpus (\texttt{CC}), consisting of both the AMI and SWBD pre-training corpora; 
-the OpenSubtitles corpus (\texttt{OS});
-and finally the standard BERT\textsubscript{BASE} model with no additional pre-training.
+and finally the OpenSubtitles corpus (\texttt{OS}).
 As before, we experiment with both frozen and fine-tuned models at the task training stage.
@@
 We performed 10 epochs of pre-training on the in-domain models and 5 epochs of pre-training on the cross-domain models so that the total amount of training data was comparable.
-The OpenSubtitles models trained on much more data (see Table~\ref{tab:pretraining-corpora}) and were trained for only one epoch.
+The OpenSubtitles models were trained for only one epoch but with much more total training time.
 
-In the fine-tuned condition, additional pre-training offers a modest boost in overall accuracy and a substantial boost to the macro-average scores.
-Any of the dialogue corpora appear helpful, but the cross-domain corpus generally provides the largest boost.
+In the fine-tuned condition, additional pre-training offers a modest boost in overall accuracy and a substantial boost to the macro-average scores, with the cross-domain corpus providing the largest boost.
 In the frozen condition, only the very large OpenSubtitles corpus is helpful, suggesting that when adapting BERT to dialogue, the size of the corpus is more important than its quality or fidelity to the target domain.
@@
 
-%\subsection{Experiment 4: Cross-domain pre-training (if time permits)} \label{sec:experiment4} % Bill
-%  - cross-domain pre-training
-\paragraph{}
-Having discussed the experimental results, the final section of the paper provides broader explanations of our findings.
+\section{Discussion}
 
-\section{Discussion} % add items to discuss
+A key aspiration of transfer learning is to expose the model to 
+phenomena that are too infrequent to learn from labeled training data alone.
+We show some evidence of that here.
+Pre-trained \texttt{BERT-FT} performs better on infrequent dialogue acts than \texttt{BERT-RI}, 
+suggesting it draws on the extensive pre-training to represent infrequent features of those utterances.
+Indeed, a simple lexical probe supports this explanation: in utterances where the pre-trained model is correct and the randomly initialized model is not,the rarest word is 1.9 times rarer on average than is typical of corpus as a whole.
 
-This may also explain why all our best models perform better on SWDA: more of the information that interlocutors and dialogue act annotators rely on is present SWDA transcripts, whereas AMI-DA annotators receive clear instructions to pay attention to the videos \citep{GuidelinesDialogueAct2005}.
-This finding is consistent with that of \citet{bavelas2008gesturing} who demonstrate that in face-to-face dialogue, visual components, such as gestures, can convey information that is independent from what is conveyed by speech.
+In spite of that, the representations learned through pre-training are simply not performant without
+task-specific fine-tuning, suggesting that they are fundamentally lacking in information that is 
+important for the dialogue context.
+We should note that this is in stark contrast to many other non-dialogical semantic tasks,
+where frozen BERT performs on par or \emph{better} than the fine-tuned model \citep{petersTuneNotTune2019}.
 
-There is abundant room for further progress in determining how other speech-related information, such as prosody and disfluencies, can be incorporated into the DAR model.
-\citet{stolckeDialogueActModeling2000} showed that dialogue acts can have specific prosodic manifestations that can be used to improve dialogue act classification.
+By performing additional pre-training on a large dialogue-like corpus (OpenSubtitles),
+we were able to raise the performance of the frozen encoder by a small amount.
+This deserves further investigation. 
+\citet{baoPLATOPretrainedDialogue2019} find that further pre-training BERT on a large-scale Reddit and Twitter corpus is helpful for response selection, but given the unimpressive results with subtitles, it remains an open question how well the text chat and social media domains transfer to natural dialogue.
+
+%This may also explain why all our best models perform better on SWDA: more of the information that interlocutors and dialogue act annotators rely on is present SWDA transcripts, whereas AMI-DA annotators receive clear instructions to pay attention to the videos \citep{GuidelinesDialogueAct2005}.
+%This finding is consistent with that of \citet{bavelas2008gesturing} who demonstrate that in face-to-face dialogue, visual components, such as gestures, can convey information that is independent from what is conveyed by speech.
+
+There is also abundant room to investigate how speech-related information, such as laughter, prosody, 
+and disfluencies can be incorporated into the DAR model.
+\citet{stolckeDialogueActModeling2000} showed, for example, that dialogue acts can have specific prosodic manifestations that can be used to improve dialogue act classification.
 Incorporating such information is crucial if models pre-trained on large-scale text corpora are to be adapted for use in dialogue applications.
 
-Our experiments with further pre-training were inconclusive. 
-Although pre-training on data from the target domain proved useful, training on a much larger corpus of dialogue-like data (OpenSubtitles) yielded less substantial improvements in the fine-tuned condition.
-\citet{baoPLATOPretrainedDialogue2019} finds that further pre-training BERT on a large-scale Reddit and Twitter corpus is helpful for response selection, but given unimpressive results with subtitles, it remains an open question how well the text chat and social media domains transfer to transcribed dialogue.
-
-Another avenue for future research is what pre-training schemes are best for the dialogue domain.
-The training scheme for RoBERTa \citep{liuRoBERTaRobustlyOptimized2019}, for example, leaves out next sentence prediction as a pre-training task because they do not find that it improves performance on question answering and natural language inference tasks.
-The same may not be true of dialogue, however, where sequentiality is essential.
+%Another avenue for future research is what pre-training schemes are best for the dialogue domain.
+%The training scheme for RoBERTa \citep{liuRoBERTaRobustlyOptimized2019}, for example, leaves out next sentence prediction as a pre-training task because they do not find that it improves performance on question answering and natural language inference tasks.
+%The same may not be true of dialogue, however, where sequentiality is essential.
 

### 2021-03-12 reports/IWCS2021/iwcs-short-paper.tex
small edits

@@
 an encoder that vectorizes utterances (BERT), 
-and a sequence model that takes the utterance representations as input.
-Since we are primarily interested in comparing different training and fine-tuning schemes for the utterance encoder, 
-we use a basic single-layer RNN as the sequence model in every configuration.\footnote{We have experimented with LSTM as the sequence model, but the accuracy was not significantly different compared to RNN.
+and single-layer RNN sequence model that takes the utterance representations as input.\footnote{
+We have experimented with LSTM as the sequence model, but the accuracy was not significantly different compared to RNN.
 It can be explained by the absence of longer distance dependencies on this level of our model.}
+%Since we are primarily interested in comparing different training and fine-tuning schemes for the utterance encoder, 
+%we use a basic single-layer RNN as the sequence model in every configuration.
 At each time step, the RNN takes the encoded utterance as input 
-and its hidden state is passed to a simple linear classification layer over dialogue act tags.\footnote{
+and its hidden state is passed to a linear layer with softmax over dialogue act tags.\footnote{
 Other work has shown that DAR benefits from more sophisticated decoding, such as conditional random field \citep{chenDialogueActRecognition2017} and uncertainty propagation \citep{tranPreservingDistributionalInformation2017}.}
 
-Conceptually, the encoded utterance represents the context-agnostic features of the utterance 
+Conceptually, the encoded utterance represents the context-agnostic features of the utterance,
 and the hidden state of the RNN represents the full discourse context.
@@
 suggesting it draws on the extensive pre-training to represent infrequent features of those utterances.
-Indeed, a simple lexical probe supports this explanation: in utterances where the pre-trained model is correct and the randomly initialized model is not,the rarest word is 1.9 times rarer on average than is typical of corpus as a whole.
+Indeed, a simple lexical probe supports this explanation: in utterances where the pre-trained model is correct and the randomly initialized model is not, the rarest word is 1.9 times rarer on average than is typical of corpus as a whole.
 
@@
 There is also abundant room to investigate how speech-related information, such as laughter, prosody, 
-and disfluencies can be incorporated into the DAR model.
+and disfluencies can be incorporated into a DAR model that uses pre-trained features.
 \citet{stolckeDialogueActModeling2000} showed, for example, that dialogue acts can have specific prosodic manifestations that can be used to improve dialogue act classification.

### 2021-05-06 reports/IWCS2021/iwcs-short-paper.tex
address a couple reviewer comments

@@
 This paper aims to supplement the findings of previous work by investigating how much of 
-BERT's sucess for dialogue tasks is due to its extensive pre-training and how much is due to 
+BERT's success for dialogue tasks is due to its extensive pre-training and how much is due to 
 task-specific fine-tuning.
@@
 Whether or not the encoder model has undergone further in-domain pre-training, 
-the choice of whether to fine-tune during task training remains.
-Freezing the encoder model during task training is more efficient, 
+there remains a choice of whether to fine-tune during task training,
+or simply extract features from the encoder model without training it (i.e., \emph{freezing}).
+Freezing the encoder model is more efficient, 
 since the gradient of the loss function need only be computed for the task-specific layers.
@@
 We also experiment with a much larger a corpus (350M tokens) constructed from OpenSubtitles \citep{Lison2016}.
-Because utterances are not labeled with speaker, we randomly assigned a speaker token to each utterance to maintain the format of the other dialouge corpora.
+Because utterances are not labeled with speaker, we randomly assigned a speaker token to each utterance to maintain the format of the other dialogue corpora.
 
-The pre-training corpora were prepared for the combined maksed language modeling and next sentence (utterance) prediction task, as described dy \citet{devlinBERTPretrainingDeep2018}.
+The pre-training corpora were prepared for the combined masked language modeling and next sentence (utterance) prediction task, as described by \citet{devlinBERTPretrainingDeep2018}.
 For the smaller SWBD and AMI corpora, we generate and train on multiple epochs of data.
-Since there is randomness in the data preparation (e.g., which distrcactor sentences are chosen and which tokens are masked), we generate each training epoch separately.\footnote{For details, see the \href{https://github.com/huggingface/transformers/tree/1.1.0/examples/lm_finetuning}{finetuning example} from Hugging Face.}
+Since there is randomness in the data preparation (e.g., which distractor sentences are chosen and which tokens are masked), we generate each training epoch separately.\footnote{For details, see the \href{https://github.com/huggingface/transformers/tree/1.1.0/examples/lm_finetuning}{finetuning example} from Hugging Face.}
 
@@
 suggesting that BERT's extensive pre-training does provide some useful information for DAR (Table~\ref{tab:results}).
-This performance boost is much more pronounced in the macro-averaged F1 score,
+This performance boost is much more pronounced in the macro-averaged F1 score,\footnote{We report both \emph{accuracy} (which is equal to micro-averaged or class-weighted F1) and \emph{macro-F1}, which is the unweighted average of the F1 scores of each class.}
 which is explained by the fact that at the tag level, pre-training has a larger impact on less frequent tags
@@
 The \texttt{BERT-FZ} performs very poorly compared to either \texttt{BERT-FT} or \texttt{BERT-RI}, however.
-It is heavily biased towards the most frequent tags, which explains its especially poor macro-average score (Table~\ref{tab:results}).
+It is heavily biased towards the most frequent tags, which explains its especially poor macro-F1 score (Table~\ref{tab:results}).
 In SWDA, for example, the model with a frozen encoder predicts one of the two most common tags (Statement-non-opinion or Acknowledge) 86\% of the time, whereas those two
@@
 
-In the fine-tuned condition, additional pre-training offers a modest boost in overall accuracy and a substantial boost to the macro-average scores, with the cross-domain corpus providing the largest boost.
+In the fine-tuned condition, additional pre-training offers a modest boost in overall accuracy and a substantial boost to the macro-F1 scores, with the cross-domain corpus providing the largest boost.
 In the frozen condition, only the very large OpenSubtitles corpus is helpful, suggesting that when adapting BERT to dialogue, the size of the corpus is more important than its quality or fidelity to the target domain.
@@
 \end{tabular}
-\caption{Comparison of macro-average F1 and accuracy with further in-domain (\texttt{ID}), cross-domain corpus (\texttt{CC}), and OpenSubtitles (\texttt{OS}) dialogue pre-training,
+\caption{Comparison of macro-F1 and accuracy with further in-domain (\texttt{ID}), cross-domain corpus (\texttt{CC}), and OpenSubtitles (\texttt{OS}) dialogue pre-training,
 for the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions. \texttt{BERT-RI} uses a randomly initialized utterance encoder with no pre-training but with fine-tuning.}

### 2021-05-07 reports/IWCS2021/iwcs-short-paper.tex
update refs and add SotA

@@
 SWDA is tagged with a set of 220 dialogue act tags which, following  \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}, we cluster into a smaller set of 42 tags.
-AMI uses a smaller tagset of 16 dialogue acts \citep{GuidelinesDialogueAct2005}.
+AMI uses a smaller tagset of 16 dialogue acts \citep{Carletta2007}.
 See Table~\ref{tab:corpora} for details.
@@
 \texttt{BERT-RI} & 32.18           & 73.80                    & 34.88                  & 60.89                    \\ \midrule
-    Majority class  & 0.78                   & 33.56                    &  1.88                  & 28.27      \\ \bottomrule
+    Majority class  & 0.78                   & 33.56                    &  1.88                  & 28.27      \\ 
+    SotA            &    -                   & 83.1\footnotemark                     &     -                  &     -      \\ \bottomrule
 \end{tabular}
@@
 \end{table}
+
+\footnotetext{\citet{Ravi2018}} % Not sure whether I really trust this SotA.
+I doesn't even use dialogue context as far as I can tell and this person https://github.com/glicerico/SGNN says they tried to replicate it and could only get %71.3 accuracy.
 

### 2021-05-07 reports/IWCS2021/iwcs-short-paper.tex
small reference changes

@@
 
-%\aclfinalcopy % Uncomment this line for the final submission
+\usepackage{graphicx}
+\usepackage{placeins}
+
+\aclfinalcopy % Uncomment this line for the final submission
 %\def\aclpaperid{***} %  Enter the acl Paper ID here
@@
 
-\author{First Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  \texttt{email@domain} \\\And
-  Second Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  \texttt{email@domain} \\}
+\author{
+  Bill Noble  \and  Vladislav Maraev\\ 
+  Centre for Linguistic Theory and Studies in Probability\\%
+  Department of Philosophy, Linguistics and Theory of Science\\%
+  University of Gothenburg\\
+  \texttt{\{bill.noble,vladislav.maraev\}@gu.se} \\
+  \\
+}
 
@@
 
-\footnotetext{\citet{Ravi2018}} % Not sure whether I really trust this SotA.
-I doesn't even use dialogue context as far as I can tell and this person https://github.com/glicerico/SGNN says they tried to replicate it and could only get %71.3 accuracy.
+\footnotetext{\citet{Kozareva2019}}
 
@@
 
-%\appendix
+\input{iwcs-short-paper-appendix}
 

### 2021-05-31 reports/SemDial2021/semdial.tex
semdial blob

--- 2020-07-21 reports/Star-SEM Paper/starsem-paper.tex
@@
 
+\usepackage{booktabs}
 \usepackage{tabularx}
 \newcolumntype{L}{>{\raggedright\arraybackslash}X}
+\usepackage{graphicx}
+\usepackage{multirow}
+\usepackage{tikz}
+\usepackage{amsmath}
+\usepackage{natbib}
 
@@
 
-\title{Can BERT learn dialogue-specific phenomena? The case of laughter in dialogue act recognition. }
+\title{Instructions for ACL-IJCNLP 2021 Proceedings}
 
@@
 \begin{abstract}
-   In this work we investigate whether transformer models can learn to represent phenomena specific to dialogue.
-   Laughter tokens, which are not present in pre-trained BERT models, can be learned with additional pre-training and fine-tuning on dialogue data. 
-   We use dialogue act recognition as a proxy task to demonstrate that laughter can help to disambiguate between certain communicative intents.
-   We find that pre-training and fine-tuning procedures are useful for learning laughter representations, and explore how well the model adapts to the dialogue domain.
+What we do: i) corpus study of laughter associated with dialogue acts and ii) testing the importance of laughter for DAR
 \end{abstract}
 
-% INTRODUCTION
+\section{Introduction}
+% studies of laughter: humour, puns, functional role of laughter (Chiara), laughter prediction (Vlad)
+% DAR and dialogue acts: why it is important
+% gap: laughter was studied, but not when concerned with its co-locations with dialogue acts
+% fill the gap:
+% 1. we take a closer look, in which contexts laughter can occur w.r.t. DAs, this leads us to a hypothesis that laughter can be important for DAR
+% 2. therefore, we look at laughter and its potential impact in DAR task
+% 3. (we looks at non-verbals --- are they DAs?)
 
-Recently, large-scale language models, trained on massive corpora of text data, have achieved state-of-the-art results on a variety of traditional NLP tasks.
-It is still uncertain whether these models might be useful for processing dialogue, and if so, whether they can adapt to make use of dialogue-specific features.
+\section{Corpus study}
+\label{sec:corpus}
 
-Dialogue, especially spoken dialogue, is radically different from the kind of data that neural language models are pre-trained on.
-In the example from the Switchboard corpus, shown in Table~\ref{table:example}, it is evident that the syntactic structure of dialogue is very different from  written text, even if one imagines a script for a movie or a play.
-Not only is the internal structure of contributions different---with features such as disfluencies, repair, incomplete sentences, and various vocal sounds---but the sequential structure of the discourse is also very different.
-In dialogue, speakers take turns and switch perspectives.
-More generally, the way that utterances contribute to and cohere with the discourse is different from the relationship between sentences in a piece of written text.
+\section{Laughter’s role in dialogue act recognition}
+\label{sec:dar}
 
-One important dialogical feature missing from text data is laughter, which is ubiquitous in our everyday interactions.
-We observe that in the Switchboard dialogue corpus laughter comes about every 200 tokens.
-Laughter also relates to the discourse structure of dialogue and can relate to a \emph{laughable}, which can be an event or an entity in the discourse (or external perceived event as well).
-Laughter can precede, follow or overlap the laughable, with the time alignment between the laughter and laughable dependent on who produces the laughable and the form of the laughter \citep{tian2016we}.
-Laughter can act as a contextual feature for determining the sincerity of an utterance, e.g. when detecting sarcasm \citep{tepperman2006yeah}.
+% TODO motivation
 
-\begin{table}
-      \small
-  \centering
-  \begin{tabularx}{\linewidth}{llL}
-    \toprule
-    Speaker & DA & Utterance \\ \midrule
-    A	&sd	& Well, I'm the kind of cook that I don't normally measure things,  \\
-    A	&sd	& I just kind of throw them in \\
-    A	&sd	& and, you know, I don't to the point of, you know, measuring down to the exact amount that they say.  \\
-    B	&sv	& That means you're a real cook. \\
-    A	&bd	& \texttt{<Laughter>} Oh, is that what it means.  \\
-    A	&b	& Uh-huh.  \\
-    A	&x	& \texttt{<Laughter>}.\\
-             \bottomrule
-  \end{tabularx}
-  \caption{Example from the SWDA corpus (sw2827).
-Dialogue acts: \emph{sd}---Statement-non-opinion, \emph{sv}---Statement-opinion, \emph{bd}---Downplayer, \emph{b}---Backchannel, \emph{x}---Non-verbal.
-}
-  \label{table:example}
-\end{table}
-
-We use dialogue act recognition (DAR) as a proxy task, since both the internal content of contributions, and their sequential structure have bearing on this task.
-DAR is the task of assigning a dialogue act tag to each utterance in the dialogue, according to dialogue act it performs.
-Using this task we investigate whether transfer learning techniques based on pre-trained language models, such as BERT \citep{devlinBERTPretrainingDeep2018}, are useful for dialogue. 
-By looking at laughter, which is certainly missing in the stadnard pre-training corpus, we can determine whether the pre-training is used in the representation dialogue-specific features.
-
-\paragraph{Contributions}
-The main results of this paper have to do with to the usefulness of language model fine-tuning for DAR, the impact of laughter on DAR, and the relationship between the two.
-\begin{itemize}
-  \item Laughter is useful for dialogue act recognition, and its impact varies across different dialogue acts (\S\ref{sec:experiment1}).
-  \item During fine-tuning, BERT learns to represent laughter, a dialogical feature not seen in pre-training (\S\ref{sec:experiment1} and \S\ref{sec:experiment2}).
-  \item Standard BERT pre-training is useful for DAR, but the model performs poorly without fine-tuning (\S\ref{sec:experiment2})
-  \item Further pre-training with data from the target domain shows promise for dialogue, but we find mixed results when pre-training with a larger corpus of dialogical data from outside the target domain (\S\ref{sec:experiment3}).
-    % TODO: we did that but what can we conclude? Perhaps that the nature of the data is very different, so it is not very helpful..?
-  \end{itemize}
-
-In the following section we provide more details about the dialogue act recognition task and transfer learning techniques.
-
-\section{Background}
-
-\subsection{Dialogue Act Recognition}
-The concept of a dialogue act is based on that of speech acts \citep{austinHowThingsWords2009}.
-Breaking with classical semantic theory, speech act theory considers not only the propositional content of an utterance but also the actions, such as \emph{promising} or \emph{apologizing}, it carries out.
-Dialogue acts extend the concept of the speech act, with a focus on the interactional nature of most speech.
-DAMSL \citep{coreCodingDialogsDAMSL1997}, for example, is an influential dialogue act tagging scheme where dialogue acts are defined in part by whether they have a \emph{forward-looking} function (are expecting a response) or \emph{backward-looking} function (are in response to a previous utterance).
-
-DAR is the task of labeling utterances with the dialogue act they perform from a given set of dialogue act tags.
-As with other sequence labeling tasks in NLP, some notion of context is helpful in DAR.
-One of the first performant machine learning models for DAR was a Hidden Markov Model that used various lexical and prosodic features as input \citep{stolckeDialogueActModeling2000}.
-
-Most successful neural approaches also model some notion of context.
-We follow previous work that models dialogue act sequences with an RNN over utterances \citep{kalchbrennerRecurrentConvolutionalNeural2013,tranHierarchicalNeuralModel2017,botheContextbasedApproachDialogue2018,bothe2018conversational,zhao2018unified}.
-Our model predicts the most likely tag given the hidden state of the RNN at each position, though other work has shown that DAR benefits from more sophisticated approaches, such as conditional random field \citep{chenDialogueActRecognition2017} or uncertainty propagation \citep{tranPreservingDistributionalInformation2017}.
-
-\subsection{Transfer learning for NLP}
-Transfer learning techniques allow a model trained on one task---often unsupervised---to be applied to another. 
-Since annotating natural language data is expensive, there is a lot of interest in transfer learning for natural language processing. 
-Word vectors \citep[e.g.,][]{mikolovDistributedRepresentationsWords2013,penningtonGloveGlobalVectors2014} are a ubiquitous example of transfer learning in NLP.
-We note, however, that pre-trained word vectors are not always useful when applied to dialogue \cite{cerisaraEffectsUsingWord2vec2017}.
-
-Recently, neural models trained on large datasets with various unsupervised tasks have found success creating sentence-level and contextual word representations. 
-BERT, a multi-layer transformer, is one such model \citep{devlinBERTPretrainingDeep2018}. 
-BERT is pre-trained on two unsupervised tasks: \emph{masked token prediction} and \emph{next sentence prediction}.
-In masked token prediction, some percentage of words are randomly replaced with a mask token, and the model is trained to predict the identity of the original token, based on the context sentence.
-In next sentence prediction, the model is given two sentences and trained to predict whether the second sentence follows the first in the original text, or if it was randomly chosen from elsewhere in the corpus.
-After pre-training, BERT can be applied to a supervised task by adding additional un-trained layers that take the hidden state of one or more of BERT's layers as input.
-
-There is some previous work applying BERT to dialogue.
-\citet{baoPLATOPretrainedDialogue2019} and \citet{chenSemanticallyConditionedDialog2019a} both use BERT for dialogue generation tasks.
-Similarly, \citet{vigComparisonTransferLearningApproaches2019} find BERT useful for selecting a response from a list of candidate responses in a dialogue.
-\citet{mehriPretrainingMethodsDialog2019} evaluate BERT in various dialogue tasks including DAR, and find that a model incorporating BERT outperforms a baseline model.
-Finally, \citet{chakravarty2019dialog} use BERT for dialogue act classification for a proprietary domain and achieves promising results, and \citet{ribeiro2019deep} surpass the previous state-of-the-art on generic dialog act recognition for Switchboard and MRDA corpora.
-In our work we are not attempting to beat the current state-of-the-art due to the different aims of the study.
-
-% TODO: \citep{chakravarty2019dialog,ribeiro2019deep,yu2019midas}
-% some motivation, maybe restate that we are not looking at the performance per say?
-
-\paragraph{Fine-tuning vs.~further in-domain pre-training}
-Transfer learning schemes for pre-trained language models such as BERT draw on one or more of the following three adaptation strategies \citep{sunHowFineTuneBERT2019}:
-\emph{further pre-training}, in which the model is trained in an un-supervised way, similar to its initial training scheme, but on data that is in-domain for the target task; 
-\emph{single-task fine-tuning}, in which the model's encoder layers are optimized during training for the target task;
-and \emph{multi-task fine-tuning}, in which models with shared encoder layers are jointly trained on several related tasks.
-In this paper, we investigate the first two methods and their combination, as applied to DAR.
-
-Regardless of whether an encoder model has undergone further in-domain pre-training, the choice of whether to fine-tune during task training remains.
-Freezing the encoder model during task training is more efficient, since the gradient of the loss function need only be computed for the task-specific layers.
-However, fine-tuning can lead to better performance since the encoding itself is adapted to the target task and domain.
-
-\citet{petersTuneNotTune2019} investigate when it is best to fine-tune BERT for sentence classification tasks.
-They find that when the target task is very similar to the pre-training task, fine-tuning provides less of a performance boost.
-We note that there is some conceptual relationship between DAR and next sentence prediction, since the dialogue act constrains (or at least is predictive of) the dialogue act that follows it.
-
-\citet{petersTuneNotTune2019} also consider whether the similarity of the pre-training and target domains may have similar consequences, but don't find an effect of domain similarly for the natural language inference tasks they tested on.
-As discussed in \S\ref{sec:data}, however, there are dramatic differences between written text and transcribed dialogue which may make fine-tuning necessary for DAR.
-
-\paragraph{} In the next section, we will present the datasets that we will use in our experiments along with their distinctive features.
-
-\section{Data}\label{sec:data}
+\subsection{Data}\label{sec:data}
 We perform experiments on the Switchboard Dialogue Act Corpus (SWDA), which is a subset of the larger Switchboard corpus, and the dialogue act-tagged portion of the AMI Meeting Corpus (AMI-DA). 
@@
 
-% - DA distribution              % Vlad
+% TODO add laughter numbers for AMI!
 
@@
 
-Utterances are tokenized using BERT's word piece tokenizer with a vocabulary of 30,000.
+Utterances are tokenized using with a word piece tokenizer \citep{Wu2016} with a vocabulary of 30,000.
 We add a special laughter token to the vocabulary and map all transcribed laughter to that token.
@@
 
-\paragraph{Laughs in the data}
-The distribution of laughs in different dialogue acts has a rather uniform shape with a few outliers (Figure~\ref{fig:box}). 
-Figure~\ref{fig:by-da} in Appendix~\ref{sec:suppl} provides a breakdown of dialogue act depending on whether current or adjacent utterances (the preceding utterance and the following one are counted as adjacent) contain laughter.\footnote{Note that SWDA has a ``Nonverbal'' dialogue act which is misleading with respect to laughter, because utterances only containing a single laughter token fall into this category, however they can serve, for example, to acknowledge a statement or to deflect a question  \citep{mazzocconi2019phd}.}
-
-\begin{figure}
-\centering
-\begin{subfigure}[b]{0.55\textwidth}
-  \includegraphics[width=0.9\linewidth]{img/box-swda.pdf}
-  \caption{SWDA}
-  \label{fig:box-swda}
-\end{subfigure}
-
-\begin{subfigure}[b]{0.55\textwidth}
-  \includegraphics[width=0.9\linewidth]{img/box-ami.pdf}
-  \caption{AMI}
-  \label{fig:box-ami}
-\end{subfigure}
-
-\caption{Box plots for dialogue acts associated with laughter. On the left: proportion of DAs having laughter in one of the adjacent utterances, on the right: proportion of DAs containing laughter. }
-\label{fig:box}
-\end{figure}
-
-\paragraph{Dialogue act grouping}
-For our corpora we also considered grouping the dialogue acts according to DAMSL coders manual \citep{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}: Forward-Communicative-Function (51.86\% of all DAs), Backwards-Communicative-Function (30.35\%), Other (9.04\%) and Communicative-Status (8.75\%).
-This allows the direct comparison between SWDA and AMI-DA.
-With respect to laughs, we observed an even distribution of them in the groups, except for the Communicative-Status group in the case of SWDA, because of the ``Nonverbal'' dialogue acts (see footnote~1).
-
 \subsection{Pre-training corpora}
-
 We also experiment with three unlabeled dialogue corpora (Table~\ref{tab:pretraining-corpora}), which we use to provide further pre-training for the BERT encoder.
@@
 
-\section{Model} % Bill
-
+\subsection{The model}
+\label{sec:model}
 To test the effectiveness of BERT for DAR, we employ a simple neural architecture with two components: an encoder that vectorizes utterances, and a sequence model that predicts dialogue act tags from the vectorized utterances (Figure~\ref{fig:model-architecture}).
@@
 
-\section{Experiments}
 \subsection{Experiment 1: Impact of laughter} \label{sec:experiment1}   % Vlad
@@
 
-In order to further investigate the differences between the models and datasets, we looked at the dialogue act groups.
-Mapping ground-truth labels and predictions into four groups allows direct comparison between model performances in SWDA and AMI-DA.
-Table~\ref{table:laughter-group-acc} compares accuracies between the two main groups: Forward-Communicative-Function and Backward-Communicative-Function (82.3\% of all DAs in SWDA and 76.7\% in AMI-DA).
-Our models tend to perform better for the Forward-Communicative-Function group for both corpora irrespective of the presence of laughs.
-Also, our models perform better on the SWDA corpus.
-Overall performance in these groups appears to be unaffected by presence of laughs.
+  % TODO: mapping groups?
 
-\begin{table}
-  \centering
-  \begin{tabular}{@{}llcc@{}}
-    \toprule
-    &                  & Forw.-CF  & Backw.-CF   \\ \midrule
-    \multirow{4}{*}{SWDA}    &\texttt{BERT-NL}  & 92.54 & 91.67       \\ 
-                             &\texttt{BERT-L}   & 95.42 & 90.91       \\ 
-                             &\texttt{CNN-NL}   & 93.30 & 90.85        \\
-                             &\texttt{CNN-L}    & 94.64 & 90.13        \\ \midrule
-    \multirow{4}{*}{AMI-DA}  &\texttt{BERT-NL}  & 87.77 & 80.83       \\ 
-                             &\texttt{BERT-L}   & 87.36 & 79.87       \\
-                             &\texttt{CNN-NL}   & 91.85 & 71.21        \\
-                             &\texttt{CNN-L}    & 91.25 & 71.28        \\    \bottomrule
-  \end{tabular}
-  \caption{Comparison of the accuracies among the two main dialogues act groups, depending on the utterance model and the presence of laughter.}
-  \label{table:laughter-group-acc}
-\end{table}
+\section{Laughter as a non-verbal dialogue act}
+\label{sec:laughter-as-non}
 
-\subsection{Experiment 2: Impact of pre-training vs. fine-tuning} \label{sec:experiment2} % Bill
-Next, we analyze how pre-training affects BERT's performance as an utterance encoder.
-To do so, we consider the performance of DAR models with three different utterance encoders:
-\begin{itemize}
-  \item \texttt{BERT-FT} -- pre-trained BERT with DAR fine-tuning 
-  \item \texttt{BERT-RI} -- randomly initialized BERT (with DAR fine-tuning)
-  \item \texttt{BERT-FZ} -- pre-trained BERT without fine-tuning (frozen during DAR training)
-\end{itemize}
-
-\begin{table}[]
-\centering
-\begin{tabular}{@{}lrrrr@{}}
-\toprule
-                           & \multicolumn{2}{c}{SWDA}                          & \multicolumn{2}{c}{AMI-DA}                        \\ \midrule
-                           & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
-\texttt{BERT-FT} & 36.75           & 76.60                    & 43.42                  & 64.93                    \\
-\texttt{BERT-RI} & 32.18           & 73.80                    & 34.88                  & 60.89                    \\
-\texttt{BERT-FZ} & 7.75            & 55.61                    & 14.86                  & 48.34 \\ \midrule
-    Majority class    & 0.78  & 33.56 &  1.88 & 28.27      \\ \bottomrule
-\end{tabular}
-  \caption{Macro-average F1 and accuracy of BERT with standard pre-training and DAR fine-tuning (\texttt{BERT-FT}) vs.~the same model without pre-training (\texttt{BERT-RI}) and without fine-tuning (\texttt{BERT-FZ}).}
-  \label{table:exp2}
-\end{table}
-
-The pre-trained model is more accurate than the randomly initialized model by several percentage points on both DA corpora,
-suggesting that BERT's extensive pre-training does provide some useful information for recognizing different dialogue acts (Table~\ref{table:exp2}).
-This performance boost is much more pronounced in the macro-averaged F1 score,
-which is explained by the fact that at the tag level, pre-training has a larger impact on less frequent tags.
-For a disaggregated view, see Figure \ref{fig:f1-by-da} in Appendix~\ref{sec:suppl}.
-
-A key aspiration of transfer learning is to expose the model to phenomena that are too infrequent to learn from labeled training data alone.
-One explanation for pre-trained BERT's superior performance on some infrequent dialogue acts is that it has learned to represent relevant features
-that the randomly initialized model was unable to learn due to their sparsity in the labeled training set.
-Indeed, a simple lexical probe supports this explanation: in utterances where the pre-trained model is correct and the randomly initialized model is not,
-the rarest word is 1.9 times rarer than is typical of corpus as a whole.
-
-Comparing the performance of the fine-tuned encoder to that of the frozen model, we note that pre-training alone is not enough.
-The frozen model is heavily biased towards the most frequent tags, which explains its especially poor macro-average score (Table~\ref{table:exp2}).
-In SWDA, for example, the model with a frozen encoder predicts one of the two most common tags (Statement-non-opinion or Acknowledge) 86\% of the time, whereas those two
-tags account for only 51\% of the ground truth tags.
-The fine-tuned model is much less biased; it predicts the two most common tags only 59\% of the time.
-
-%These observations raise two questions.
-%First, how does BERT's pre-training help with DAR? 
-%And second, in what way are the representations learned by pre-trained BERT lacking?
-%In other words, what is the contribution of fine-tuning?
-
-%To help answer these questions, we compare performance of the above three models by dialogue act tag.
-
-% TODO: add per dialogue act accuracy figures
-
-\paragraph{Fine-tuning and laughter}
-Since the laughter token doesn't appear in the original BERT vocabulary, only fine-tuned models can meaningfully make use of laughter in utterance representations. 
-This gives us another opportunity to assess whether laughter is useful in dialogue act recognition.
-We find that although 4.6\% of utterances in SWDA contain laughter, 
-7.3\% of utterances misclassified by the frozen model but correctly classified by the fine-tuned model contain laughter, 
-suggesting that the fine-tuned encoder makes use of laughter. 
-For AMI-DA, the effect is less pronounced, but still present: 
-overall, 8.5\% of utterances contain laughter, 
-compared to 9.6\% of utterances where fine-tuning makes a difference.
-
-\subsection{Experiment 3: Impact of dialogue pre-training} \label{sec:experiment3} % Bill
-
-Next, we assess the effect of additional dialogue pre-training on BERT's performance as an utterance encoder.\footnote{
-In-domain pre-training is sometimes referred to as \textit{fine-tuning}, but we reserve that term for task-specific training on labeled data.}
-\citet{sunHowFineTuneBERT2019} has reported that performing additional pre-training on unlabeled in-domain data improves performance on classification tasks. 
-We want to see if BERT can benefit from pre-training, on dialogue data, including from data outside the immediate target domain.
-
-For each of the target corpora (SWDA and AMI-DA), we compare four different pre-training conditions: 
-The in-domain corpus (\texttt{ID}), consisting of the AMI pre-training corpus for the AMI-DA model and the SWBD pre-traning corpus for the SWDA model; 
-the cross-domain corpus (\texttt{CC}), consisting of both the AMI and SWBD pre-training corpora; 
-the OpenSubtitles corpus (\texttt{OS});
-and finally the standard BERT\textsubscript{BASE} model with no additional pre-training.
-As before, we experiment with both frozen and fine-tuned models at the task training stage.
-
-We performed 10 epochs of pre-training on the in-domain models and 5 epochs of pre-training on the cross-domain models so that the total amount of training data was comparable.
-The OpenSubtitles models trained on much more data (see Table~\ref{tab:pretraining-corpora}) and were trained for only one epoch.
-
-In the fine-tuned condition, additional pre-training offers a modest boost in overall accuracy and a substantial boost to the macro-average scores.
-Any of the dialogue corpora appear helpful, but the cross-domain corpus generally provides the largest boost.
-In the frozen condition, only the very large OpenSubtitles corpus is helpful, suggesting that when adapting BERT to dialogue, the size of the corpus is more important than its quality or fidelity to the target domain.
-Still, pre-training provides nowhere near the performance improvement achieved by fine-tuning on the target task.
-
-\begin{table}[]
-\begin{tabular}{@{}lrrrr@{}}
-\toprule
-           & \multicolumn{2}{c}{SWDA}                          & \multicolumn{2}{c}{AMI-DA}                        \\ \midrule
-           & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
-\texttt{BERT-FT}    & 36.75                  & 76.60                    & 43.42                  & 64.93                    \\
-\texttt{BERT+ID-FT} & 43.63                  & 77.01                    & 46.70                  & \textbf{68.88}           \\
-\texttt{BERT+CC-FT} & \textbf{47.78}         & \textbf{77.35}           & \textbf{48.86}         & 68.79                    \\ 
-\texttt{BERT+OS-FT} & 41.42                  & 76.95                    & 48.65                  & 68.07                    \\ \midrule
-\texttt{BERT-FZ}    &  7.75                  & 55.61           & 14.86                  & 48.34                    \\
-\texttt{BERT+ID-FZ} &  6.46                  & 52.30                    & 14.48                  & 48.18                    \\
-\texttt{BERT+CC-FZ} &  5.76                  & 51.14                    & 11.34                  & 40.48                    \\ 
-\texttt{BERT+OS-FZ} &  \textbf{9.60}         & \textbf{57.67}           & \textbf{17.03}         & \textbf{51.03}           \\ \midrule
-    Majority class  & 0.78                   & 33.56                    &  1.88                  & 28.27      \\ \bottomrule
-\end{tabular}
-\caption{Comparison of macro-average F1 and accuracy with further in-domain (\texttt{ID}), combined corpus (\texttt{CC}), and OpenSubtitles (\texttt{OS}) dialogue pre-training,
-    for the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions.}
-  \label{table:exp3}
-\end{table}
-
-%\subsection{Experiment 4: Cross-domain pre-training (if time permits)} \label{sec:experiment4} % Bill
-%  - cross-domain pre-training
-\paragraph{}
-Having discussed the experimental results, the final section of the paper provides broader explanations of our findings.
-
-\section{Discussion} % add items to discuss
+\section{Discussion}
 On the question of laughter impact, this study found that laughter is more helpful in SWDA corpus than in AMI-DA.
@@
 
-Our experiments with further pre-training were inconclusive. 
-Although pre-training on data from the target domain proved useful, training on a much larger corpus of dialogue-like data (OpenSubtitles) yielded less substantial improvements in the fine-tuned condition.
-\citet{baoPLATOPretrainedDialogue2019} finds that further pre-training BERT on a large-scale Reddit and Twitter corpus is helpful for response selection, but given unimpressive results with subtitles, it remains an open question how well the text chat and social media domains transfer to transcribed dialogue.
+\section*{Acknowledgments}
 
-Another avenue for future research is what pre-training schemes are best for the dialogue domain.
-The training scheme for RoBERTa \citep{liuRoBERTaRobustlyOptimized2019}, for example, leaves out next sentence prediction as a pre-training task because they do not find that it improves performance on question answering and natural language inference tasks.
-The same may not be true of dialogue, however, where sequentiality is essential.
+The acknowledgments should go immediately before the references. Do not number the acknowledgments section.
+\textbf{Do not include this section when submitting your paper for review.}
 
-%\begin{itemize}
-  %\item RoBERTa training scheme finds that next sentence prediction is of little importance.
-Is this true for us too?
-(suspect not due to discourse importance).
-see: https://github.com/huggingface/transformers/issues/1622
-  %\item Issues related to working with transcribed speech: Different kinds of laughter are all represented by the same token.
-Does transcription orthography capture prosody?
-We know prosidy is useful for DAR (Jurafsky).
-  %\item future work: pre-training on very large un-labeled dialogue corpora. How does text chat transfer to the spoken/transcribed setting?
-  %\item Laughter is more helpful in SWDA than in AMI-DA. 
-  %\item The point above can also explain why our models better on SWDA: just a larger proportion of stuff that interlocutors rely on is in the transcription.
-%\end{itemize}
+\bibliographystyle{acl_natbib}
+\bibliography{semdial}
 
-\bibliography{acl2020}
-\bibliographystyle{acl_natbib}
-\appendix
-\onecolumn
-\section{Supplementary materials}\label{sec:suppl}
-
-\begin{figure*}[h!]
-  \centering
-  \includegraphics[width=\linewidth]{img/SWDA-bertLvsNL.pdf}
-  \includegraphics[width=\linewidth]{img/AMI-DA-bertLvsNL.pdf}
-  \caption{Change in accuracy for each dialogue act (\texttt{BERT-NL} vs \texttt{BERT-L}).
-Positive changes when adding laughter (\texttt{BERT-L}) are shown in blue.
-Vertical bars indicate how often dialogue act is associated with laughter.
-Top chart: SWDA, Bottom chart: AMI-DA.
-}
-    \label{fig:by-da}
-  \end{figure*}
-
-\begin{figure*}[h!]
-  \centering
-  \includegraphics[width=\linewidth]{img/swda-brf.pdf}
-  \includegraphics[width=\linewidth]{img/ami-brf.pdf}
-  \caption{F1 scores by dialogue act for BERT with standard pre-training and DAR fine-tuning (\texttt{BERT-FT}) vs.~the same model without pre-training (\texttt{BERT-RI}) and without fine-tuning (\texttt{BERT-FZ}).
-Dialogue acts are ordered with the most common on the left.}
-    \label{fig:f1-by-da}
-  \end{figure*}
+%\appendix
 

### 2021-05-31 reports/SemDial2021/semdial.tex
svg for box swda, few more words

@@
 \label{sec:corpus}
+
+% we analyse DAs according to their association with laughter and provide some qualitative insights
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{img/box-swda.pdf}
+  \caption{SWDA}
+  \label{fig:box-swda}
+\end{figure}
+
+% 1. overview: rather uniform distribution with few outliers
+% 2. let's look at outliers
+% 3. consider 5 dimensions of relations
+
+We take into consideration five laughter-related dimensions of an
+utterance, and create 5-dimensional representations of dialogue acts
+according to them. Each dimension's value equals to the proportion of
+utterances of a given type containing laughter.
+\begin{enumerate}
+\item current utterance;
+\item previous utterance by the same speaker;
+\item previous utterance by the other speaker;
+\item next utterance by the same speaker;
+\item next utterance by the other speaker.
+\end{enumerate}
+
+For instance,
 

### 2021-06-03 reports/SemDial2021/semdial.tex
svg image
examples, references

--- 2021-05-31 reports/SemDial2021/semdial.tex
@@
 \usepackage[hyperref]{acl2021}
+
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+
 \usepackage{times}
@@
 \newcolumntype{L}{>{\raggedright\arraybackslash}X}
-\usepackage{graphicx}
+\usepackage{svg}
 \usepackage{multirow}
@@
 \usepackage{natbib}
+\usepackage{tabulary}
+
+\usepackage{enumitem}
+\newlist{lingex}{enumerate}{3} % easy numbering of examples
+\setlist[lingex,1]{parsep=0pt,itemsep=1pt,label=(\arabic*),resume=lingexcount}
+\newcommand\onelingex[1]{\begin{lingex}\item #1 \end{lingex}}
+\usepackage{adjustbox}
+
+\usepackage{textcomp}
+\usepackage{amssymb}
 
@@
 \label{sec:corpus}
+
+In this section we analyse dialogue acts according to their co-location with
+laughter and provide some qualitative insights from the
+statistics. The distribution of laughs in different dialogue acts has
+a rather uniform shape with a few outliers (Figure~\ref{fig:box-swda}). The
+most distinct outlier is ``Nonverbal'' dialogue act which is
+misleading with respect to laughter, because utterances only
+containing a single laughter token fall into this category, however
+they can serve, for example, to acknowledge a statement or to deflect
+a question \citep{mazzocconi2019phd}.
+
+\begin{figure}
+  \includesvg[width=\linewidth]{img/box-swda}
+  \caption{Box plot for proportions of dialogue act which contain laughs.}
+  \label{fig:box-swda}
+\end{figure}
+
+Let us introduce our comparison schema for the other two outliers,
+Downplayer and Apology, comparing them with the most common dialogue
+act in SWDA---Statement-Non-Opinion.  We take into consideration five
+laughter-related dimensions of an utterance, and create 5-dimensional
+representations of dialogue acts according to them. Each dimension's
+value equals to the proportion of utterances of a given type which
+contain laughter.
+\begin{itemize}
+\item[$\uparrow$] current utterance;
+\item[$\nwarrow$] previous utterance by the same speaker;
+\item[$\swarrow$] previous utterance by the other speaker;
+\item[$\nearrow$] next utterance by the same speaker;
+\item[$\searrow$] next utterance by the other speaker.
+\end{itemize}
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{img/orbit-apology.pdf}
+  \caption{Comparison of the most common dialogue act in
+    SWDA---"Statement-Non-Opinion" (33.27\% of all utterances) with two
+    outliers "Apology" (0.04\%) and "Downplayer" (0.05\%). Proportion
+    of utterances which contain laughter are shown in association with
+    each dialogue act. }
+  \label{fig:orbit}
+\end{figure}
+
+% 1. overview: rather uniform distribution with few outliers
+% 2. let's look at outliers
+% 3. consider 5 dimensions of relations
+
+For instance, 
+\begin{lingex}
+\item
+  \adjustbox{valign=t}{
+    \begin{tabulary}{\linewidth}{>{\bf}lJ>{\em}l}
+    A: & I am so sorry to keep you on hold. & Apology \\
+    B: & <Laughter> No problem. & Downplayer \\
+    A: & Are you at work? & YN-Quest. \\
+  \end{tabulary}}
+\end{lingex}
 
@@
 \bibliography{semdial}
+\appendix
+\onecolumn
+\section{Supplementary materials}\label{sec:suppl}
 
-%\appendix
+\begin{figure*}[h!]
+  \centering
+  \includegraphics[width=\linewidth]{img/SWDA-bertLvsNL.pdf}
+  \includegraphics[width=\linewidth]{img/AMI-DA-bertLvsNL.pdf}
+  \caption{Change in accuracy for each dialogue act (\texttt{BERT-NL} vs \texttt{BERT-L}).
+Positive changes when adding laughter (\texttt{BERT-L}) are shown in blue.
+Vertical bars indicate how often dialogue act is associated with laughter.
+Top chart: SWDA, Bottom chart: AMI-DA.
+}
+    \label{fig:by-da}
+\end{figure*}
 

### 2021-06-04 reports/SemDial2021/semdial.tex
intro cut-n-paste, another example

@@
 
+One important dialogical feature missing from text data is laughter,
+which is ubiquitous in our everyday interactions.  We observe that in
+the Switchboard dialogue corpus laughter comes about every 200 tokens.
+Laughter also relates to the discourse structure of dialogue and can
+relate to a \emph{laughable}, which can be an event or an entity in
+the discourse (or external perceived event as well).  Laughter can
+precede, follow or overlap the laughable, with the time alignment
+between the laughter and laughable dependent on who produces the
+laughable and the form of the laughter \citep{tian2016we}.  Laughter
+can act as a contextual feature for determining the sincerity of an
+utterance, e.g. when detecting sarcasm \citep{tepperman2006yeah}.
+
 \section{Corpus study}
@@
 
-\begin{figure}
+\begin{figure}[htbp]
   \includesvg[width=\linewidth]{img/box-swda}
@@
 \item[$\uparrow$] current utterance;
-\item[$\nwarrow$] previous utterance by the same speaker;
-\item[$\swarrow$] previous utterance by the other speaker;
-\item[$\nearrow$] next utterance by the same speaker;
-\item[$\searrow$] next utterance by the other speaker.
+\item[$\nwarrow$] immediately preceding utterance by the same speaker;
+\item[$\swarrow$] immediately preceding utterance by the other speaker;
+\item[$\nearrow$] immediately following utterance by the same speaker;
+\item[$\searrow$] immediately following utterance by the other speaker.
 \end{itemize}
 
-\begin{figure}
+\begin{figure}[htbp]
   \includegraphics[width=\linewidth]{img/orbit-apology.pdf}
@@
 
-% 1. overview: rather uniform distribution with few outliers
-% 2. let's look at outliers
-% 3. consider 5 dimensions of relations
-
-For instance, 
+For instance, \ref{ex:apology-downplayer} is an illustrative example
+of the phenomenon shown on Figure \ref{fig:orbit}\footnote{Overlapping material is marked with hash signs.}. 
 \begin{lingex}
-\item
+\item\label{ex:apology-downplayer}
   \adjustbox{valign=t}{
-    \begin{tabulary}{\linewidth}{>{\bf}lJ>{\em}l}
-    A: & I am so sorry to keep you on hold. & Apology \\
-    B: & <Laughter> No problem. & Downplayer \\
-    A: & Are you at work? & YN-Quest. \\
+    \begin{tabulary}{\linewidth}{>{\bf}lJ>{\em}R}
+  A & I'm sorry to keep you waiting \#<laughter>.\# & Apology \\
+  B & \#Okay\# <laughter>. / & Downplayer \\
+  A & Uh, I was calling from work  & Statement (n/o) \\
     \end{tabulary}}

### 2021-06-06 ami.py
fix a datagen bug, add nolaughter option to opensubtitles; ignore 'x' tag in SWDA option on train

@@ -251,7 +251,7 @@ def get_corpus(ami_corpus_dir, da_only=True):
     words_files = [f for f in os.listdir(words_dir) if f.endswith('.xml')]
 
     da_dir = os.path.join(ami_corpus_dir, 'dialogueActs')
-    da_files = [f for f in os.listdir(da_dir) if f.endswith('dialogue-act.xml')] # ignore the adjacency-pairs files
+    da_files = [f for f in os.listdir(da_dir) if f.endswith('dialog-act.xml')] # ignore the adjacency-pairs files
 
     stream_da_acts = defaultdict(lambda: defaultdict(list))
     for file in tqdm(da_files, desc="Reading DA files"):
@@ -271,7 +271,6 @@ def get_corpus(ami_corpus_dir, da_only=True):
             token = AMIToken.from_xml(element)
             if token:
                 stream_tokens[token.meeting_id][token.speaker].append(token)
-
     meetings = [AMIMeeting(meeting_id, stream_tokens[meeting_id], stream_da_acts.get(meeting_id, None)) for meeting_id in stream_tokens ]
 
     return meetings

### 2021-06-06 data.py

@@ -80,13 +80,15 @@ def download_glove(data_dir):
         zip_ref.extractall('data/glove.6B')
 
 
-def load_data(corpus_file, tokenizer, tag2id, strip_laughter=False, tag_field='da_tags'):
+def load_data(corpus_file, tokenizer, tag2id, strip_laughter=False, tag_field='da_tags', ignore_tags=[]):
     with open(corpus_file) as f:
         dialogs = json.load(f)
     data = []
     for d in dialogs:
         utts, tags = [], []
         for speaker,utt,tag in zip(d['speakers'], d['utts'], d[tag_field]):
+            if tag in ignore_tags:
+                tag = TAG_PAD
             utt = [f'[SPKR_{speaker}]'] + tokenizer.tokenize(utt)
             if strip_laughter:
                 utt = [t for t in utt if t != LAUGHTER_TOKEN]
@@ -94,7 +96,7 @@ def load_data(corpus_file, tokenizer, tag2id, strip_laughter=False, tag_field='d
                     continue
             encoded_utt = tokenizer.encode(utt, add_special_tokens=True)
             utts.append(encoded_utt)
-            tags.append(tag2id[tag])
+            tags.append(tag2id.get(tag, 0))
         data.append((utts, tags))
     return data 
 
@@ -198,7 +200,7 @@ def parse_ami(corpus_dir, pause_threshold):
                 utts.append(normalize_ami(utt))
                 laughter_types.append(laughter_type(str(utt)))
             laughter_type_next = laughter_types[1:] + ['none'] # predict the laughter type of the next utterance. for the last utterance, use 'none' 
-            dialogs_da.append(Dialogue(m.meeting_id, speakers, utts, None, laughter_type_next))
+            dialogs_noda.append(Dialogue(m.meeting_id, speakers, utts, None, laughter_type_next))
     return dialogs_da, dialogs_noda
 
 
@@ -255,11 +257,14 @@ def write_tag_vocab(dialogs, data_dir, corpus_name):
     log.info(f"Wrote {len(tags)} to {tag_file}.")
 
 
-def load_tag_vocab(vocab_file):
+def load_tag_vocab(vocab_file, ignore_tags=[]):
     tag_vocab = []
     with open(vocab_file, 'r') as f:
         for tag in f.readlines():
-            tag_vocab.append(tag.strip())
+            tag = tag.strip()
+            if tag in ignore_tags:
+                continue
[…]

### 2021-06-06 eval_model.py

@@ -183,6 +183,7 @@ if __name__ == '__main__':
     encoder_model.eval()
     encoder_model.to(device)
 
+    log.info(f"Loading data from {test_file}.")
     test_data = data.load_data(test_file, tokenizer, tag2id, strip_laughter=args.no_laughter)
 
     criterion = nn.CrossEntropyLoss(ignore_index=0)  # pad targets don't contribute to the loss

### 2021-06-06 finetune_on_pregenerated.py

@@ -29,10 +29,15 @@ InputFeatures = namedtuple("InputFeatures", "input_ids input_mask segment_ids lm
 log_format = '%(asctime)-10s: %(message)s'
 logging.basicConfig(level=logging.INFO, format=log_format)
 
+LAUGHTER_TOKEN = '<laughter>'
 
-def convert_example_to_features(example, tokenizer, max_seq_length):
-    tokens = example["tokens"]
+def convert_example_to_features(example, tokenizer, max_seq_length, no_laughter=False):
+    laughter_idxs = [i for i,t in enumerate(example["tokens"]) if t == LAUGHTER_TOKEN]
+    tokens = example["tokens"].copy()
     segment_ids = example["segment_ids"]
+    if no_laughter and laughter_idxs:
+        tokens = [t for i,t in enumerate(tokens) if not i in laughter_idxs]
+        segment_ids = [s for i,s in enumerate(segment_ids) if not i in laughter_idxs]
     is_random_next = example["is_random_next"]
     masked_lm_positions = example["masked_lm_positions"]
     masked_lm_labels = example["masked_lm_labels"]
@@ -62,10 +67,11 @@ def convert_example_to_features(example, tokenizer, max_seq_length):
 
 
 class PregeneratedDataset(Dataset):
-    def __init__(self, training_path, epoch, tokenizer, num_data_epochs, reduce_memory=False):
+    def __init__(self, training_path, epoch, tokenizer, num_data_epochs, reduce_memory=False, no_laughter=False):
         self.vocab = tokenizer.vocab
         self.tokenizer = tokenizer
         self.epoch = epoch
+        self.no_laughter = no_laughter
         self.data_epoch = epoch % num_data_epochs
         data_file = training_path / f"epoch_{self.data_epoch}.json"
         metrics_file = training_path / f"epoch_{self.data_epoch}_metrics.json"
@@ -100,7 +106,7 @@ class PregeneratedDataset(Dataset):
             for i, line in enumerate(tqdm(f, total=num_samples, desc="Training examples")):
                 line = line.strip()
                 example = json.loads(line)
-                features = convert_example_to_features(example, tokenizer, seq_len)
+                features = convert_example_to_features(example, tokenizer, seq_len, self.no_laughter)
                 input_ids[i] = features.input_ids
                 segment_ids[i] = features.segment_ids
                 input_masks[i] = features.input_mask
@@ -136,7 +142,8 @@ def main():
[…]

### 2021-06-06 train.py

@@ -70,6 +70,8 @@ parser.add_argument("--training-limit", type=int, default=None,
         help="Limit the amount of training data to N dialogues.")
 parser.add_argument('--predict-laughter', dest='predict_laughter', action='store_true', default=False,
         help="Predict laughter type of the next utterance instead of dialogue act tag.")
+parser.add_argument('--no-nonverbal', dest='no_nonverbal', action='store_true', default=False,
+        help="SWDA ONLY: Nonverbal tag will be converted to pad (thus ignored by backprop).")
 
 def gen_batches(data, batch_size):
     data.sort(key=lambda x: len(x[0]))  # batch similarly lengthed dialogues together
@@ -172,8 +174,10 @@ if __name__ == '__main__':
     device = torch.device(f'cuda:{args.gpu_id}' if args.cuda and torch.cuda.is_available() else 'cpu')
     log.info(f"Training on {device}.")
 
-    tag_vocab, tag2id = data.load_tag_vocab(tag_vocab_file)
+    ignore_tags = ['x'] if args.no_nonverbal else []
+    tag_vocab, tag2id = data.load_tag_vocab(tag_vocab_file, ignore_tags=ignore_tags)
     n_tags = len(tag_vocab)
+    log.info(f"{n_tags} DA tags") 
     tokenizer = data.load_tokenizer('bert-base-uncased')
     vocab_size = len(tokenizer)
     min_utt_len = None  # CNNs require a min utt len (no utterance can be shorter than the biggest window size)
@@ -237,9 +241,12 @@ if __name__ == '__main__':
     dar_model.to(device)
     encoder_model.to(device)
 
+    print(train_file)
     tag_field = 'laughter_type_next' if args.predict_laughter else 'da_tags'
-    train_data = data.load_data(train_file, tokenizer, tag2id, strip_laughter=args.no_laughter, tag_field=tag_field)
-    val_data = data.load_data(val_file, tokenizer, tag2id, strip_laughter=args.no_laughter, tag_field=tag_field)
+    train_data = data.load_data(train_file, tokenizer, tag2id, strip_laughter=args.no_laughter, 
+            tag_field=tag_field, ignore_tags=ignore_tags)
+    val_data = data.load_data(val_file, tokenizer, tag2id, strip_laughter=args.no_laughter, 
+            tag_field=tag_field, ignore_tags=ignore_tags)
     if args.training_limit:
         train_data = train_data[:args.training_limit]
         val_data = val_data[:int(args.training_limit/2)]

### 2021-06-06 analysis/ACL/pca.py
forgotten PCAs

@@ -1,0 +1,16 @@
+import numpy as np
+import sys
+from sklearn.decomposition import PCA
+
+data = sys.stdin.readlines()[1:]
+
+das = [line.split(",")[0] for line in data]
+X = np.genfromtxt(data, delimiter=',')[:, [9,11,12,14,15]]
+print(das[1:])
+print(X)
+
+pca = PCA(n_components=2)
+X_ = pca.fit_transform(X)
+
+for da,x in zip(das,X_):
+    print("{},{},{}".format(da,x[0],x[1]))

### 2021-06-06 data.py
fix ignore_tags bug where it actually just didn't even load the tags instead of ignoring them during backprop

@@ -98,7 +98,7 @@ def load_data(corpus_file, tokenizer, tag2id, strip_laughter=False, tag_field='d
             utts.append(encoded_utt)
             tags.append(tag2id.get(tag, 0))
         data.append((utts, tags))
-    return data 
+    return data
 
 
 def prep_dialog_for_pretraining(dialog):
@@ -255,13 +255,11 @@ def write_tag_vocab(dialogs, data_dir, corpus_name):
     log.info(f"Wrote {len(tags)} to {tag_file}.")
 
 
-def load_tag_vocab(vocab_file, ignore_tags=[]):
+def load_tag_vocab(vocab_file):
     tag_vocab = []
     with open(vocab_file, 'r') as f:
         for tag in f.readlines():
             tag = tag.strip()
-            if tag in ignore_tags:
-                continue
             tag_vocab.append(tag)
     tag2id = {tag: i for i, tag in enumerate(tag_vocab)}
     tag2id = defaultdict(lambda: tag2id[TAG_PAD], tag2id)

### 2021-06-06 train.py

@@ -174,8 +174,7 @@ if __name__ == '__main__':
     device = torch.device(f'cuda:{args.gpu_id}' if args.cuda and torch.cuda.is_available() else 'cpu')
     log.info(f"Training on {device}.")
 
-    ignore_tags = ['x'] if args.no_nonverbal else []
-    tag_vocab, tag2id = data.load_tag_vocab(tag_vocab_file, ignore_tags=ignore_tags)
+    tag_vocab, tag2id = data.load_tag_vocab(tag_vocab_file)
     n_tags = len(tag_vocab)
     log.info(f"{n_tags} DA tags") 
     tokenizer = data.load_tokenizer('bert-base-uncased')
@@ -241,7 +240,8 @@ if __name__ == '__main__':
     dar_model.to(device)
     encoder_model.to(device)
 
-    print(train_file)
+    ignore_tags = ['x'] if args.no_nonverbal else []
+    log.info(f"Ignoring these tags during traininig {' ,'.join(ignore_tags)}")
     tag_field = 'laughter_type_next' if args.predict_laughter else 'da_tags'
     train_data = data.load_data(train_file, tokenizer, tag2id, strip_laughter=args.no_laughter, 
             tag_field=tag_field, ignore_tags=ignore_tags)

### 2021-06-08 analysis/ACL/util.py
fix no_laughter bug (don't skip utterances!

@@ -62,7 +62,11 @@ def gen_model_preds_df(corpus, models, model_dirs,group=False):
     preds = defaultdict(lambda x: dict)
     for model, model_dir in zip(models, model_dirs):
         best_epoch, _ = get_min_val_loss(model_dir)
+        print(best_epoch, model_dir)
         preds_file = os.path.join(model_dir, f'preds.E{best_epoch}.json')
+        if not os.path.exists(preds_file):
+            print(preds_file)
+            continue
         with open(os.path.join(model_dir, preds_file), 'r') as f:
             preds = json.load(f)
             if not group:

### 2021-06-08 eval_model.py

@@ -189,7 +189,7 @@ if __name__ == '__main__':
     encoder_model.to(device)
 
     tag_field = 'laughter_type_next' if args.predict_laughter else 'da_tags'
-    test_data = data.load_data(test_file, tokenizer, tag2id, strip_laughter=args.no_laughter, tag_field=tag_field)
+    test_data = data.load_data(test_file, tokenizer, tag2id, strip_laughter=False, tag_field=tag_field)
 
     criterion = nn.CrossEntropyLoss(ignore_index=0)  # pad targets don't contribute to the loss
     loss, preds, dialogue_states = eval_model(encoder_model, dar_model, test_data, n_tags, criterion, device)

### 2021-07-25 reports/ACL2020 Paper/acl2020-paper.tex
Updates from Overleaf

@@
 We observe that in the Switchboard dialogue corpus laughter comes about every 200 tokens.
-Laughter also relates to the discourse structure of dialogue and can relate to a laughable, which can be any an event or an entity in the discourse (and external perceived event as well).
+Laughter also relates to the discourse structure of dialogue and can relate to a laughable, which can be an event or an entity in the discourse (or an external perceived event as well).
 Laughter can precede, follow or overlap the laughable, with the time alignment between the laughter and laughable dependent on who produces the laughable and the form of the laughter \citep{tian2016we}.
-Laughter can act as a contextual feature for determining the sincerity of an utterance, e.g. to when detecting sarcasm \citep{tepperman2006yeah}.
+Laughter can act as a contextual feature for determining the sincerity of an utterance, e.g. when detecting sarcasm \citep{tepperman2006yeah}.
 
@@
 
-We use dialogue act recognition (DAR) as a proxy task, since both the internal content of contributions, and their sequential structure have bearing on this task.
-DAR is the task of assigning a dialogue act tag to each utterance in the dialogue, according to dialogue act it performs.
+We use dialogue act recognition (DAR) as a proxy task, since both the internal content of contributions, and their sequential structure have a bearing on this task.
+DAR is the task of assigning a dialogue act tag to each utterance in the dialogue, according to dialogue act it performs (see section \ref{sec:DAR}).
 Using this task we investigate whether transfer learning techniques based on pre-trained language models, such as BERT \citep{devlinBERTPretrainingDeep2018}, are useful for dialogue.
-By looking at laughter, which is certainly missing in pre-trained model, we can determine whether the domain-adapted model can make use of dialogue-specific features.
+By looking at laughter, which is certainly missing in the pre-trained model, we can determine whether the domain-adapted model can make use of dialogue-specific features.
 
@@
 
-\section{Background}
+\section{Background}\label{sec:background}
 
-\subsection{Dialogue Act Recognition}
+\subsection{Dialogue Act Recognition}\label{sec:DAR}
 The concept of a dialogue act is based on that of speech acts \citep{austinHowThingsWords2009}.
@@
                            & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
-\texttt{BERT-FT} & 45.99           & 76.93                    & 50.03                  & 66.94                    \\
-\texttt{BERT-RI} & 32.18           & 73.80                    & 33.45                  & 61.53                    \\
-\texttt{BERT-FZ} & 7.75            & 55.61                    & 14.44                  & 46.59 \\
+\texttt{BERT-FT}    & 36.75                  & 76.60                    & 43.42                  & 64.93                    \\
+\texttt{BERT-RI} & 32.18           & 73.80                    & 34.88                  & 60.89                    \\
+
+\texttt{BERT-FZ}    &  7.75                  & 55.61           & 14.86                  & 48.34                    \\
   \bottomrule
@@
            & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
-\texttt{BERT-FT}    & 45.99                  & 76.93                    & 50.03                  & 66.95                    \\
-\texttt{BERT+ID-FT} & 45.48                  & 77.02                    & 46.56                  & 68.66                    \\
-\texttt{BERT+CC-FT} & 47.78                  & 77.35                    & 48.72                  & 66.58                    \\ \midrule
-\texttt{BERT-FZ}    & 7.75                   & 55.61                    & 14.44                  & 46.60                    \\
-\texttt{BERT+ID-FZ} & 6.46                   & 52.30                    & 14.43                  & 48.07                    \\
-\texttt{BERT+CC-FZ} & 5.76                   & 51.14                    & 12.56                  & 42.42                    \\ \bottomrule
+\texttt{FT}    & 36.75                  & 76.60                    & 43.42                  & 64.93                    \\
+\texttt{ID-FT} & 43.63                  & 77.01                    & 46.70                  & \textbf{68.88}           \\
+\texttt{CC-FT} & \textbf{47.78}         & \textbf{77.35}           & \textbf{48.86}         & 68.79                    \\ 
+\texttt{OS-FT} & 41.42                  & 76.95                    & 48.65                  & 68.07                    \\ 
+\texttt{OS-NL-FT} & 43.71                  & 77.09                    & 43.68                  & 64.80                    \\ \midrule
+
+\texttt{FZ}    &  7.75                  & 55.61           & 14.86                  & 48.34                    \\
+\texttt{ID-FZ} &  6.46                  & 52.30                    & 14.48                  & 48.18                    \\
+\texttt{CC-FZ} &  5.76                  & 51.14                    & 11.34                  & 40.48                    \\ 
+\texttt{OS-FZ} &  \textbf{9.60}         & \textbf{57.67}           & \textbf{17.03}         & \textbf{51.03}           \\ 
+\texttt{OS-NL-FZ} & 7.69                  & 55.29                    & 16.99                  & 51.46                    \\ \midrule
+\midrule
+    Majority class  & 0.78                   & 33.56                    &  1.88                  & 28.27      \\ \bottomrule
 \end{tabular}
-  \caption{Comparison of macro-average F1 and accuracy  with further in-domain (\texttt{ID}) and combined corpus (\texttt{CC}) dialogue pre-training,
-    for both the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions.}
-  \label{table:exp3}
+\caption{Comparison of DAR macro-F1 and accuracy for BERT models with further in-domain (\texttt{ID}), cross-domain corpus (\texttt{CC}), and OpenSubtitles (\texttt{OS}) dialogue pre-training,
+for both the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions. OpenSubtitles pretraining was also tested with laughter removed (\texttt{NL}).}
+  \label{tab:results}
 \end{table}

### 2021-07-25 reports/SemDial2021/semdial.tex
blob for experiment 2
images
test Overleaf
Updates from Overleaf

--- 2021-06-03 reports/SemDial2021/semdial.tex
@@
-%
 % File acl2021.tex
@@
 \usepackage[T1]{fontenc}
+\usepackage{todonotes}
 
@@
 
-\usepackage{enumitem}
+\usepackage[inline,shortlabels]{enumitem}
 \newlist{lingex}{enumerate}{3} % easy numbering of examples
-\setlist[lingex,1]{parsep=0pt,itemsep=1pt,label=(\arabic*),resume=lingexcount}
+\setlist[lingex,1]{parsep=0pt,itemsep=1pt,label=(\arabic*),resume=lingexcount,font=\small}
 \newcommand\onelingex[1]{\begin{lingex}\item #1 \end{lingex}}
@@
 
-\title{Instructions for ACL-IJCNLP 2021 Proceedings}
+\title{Dialogue act classification is a laughing matter}
 
@@
 \begin{abstract}
-What we do: i) corpus study of laughter associated with dialogue acts and ii) testing the importance of laughter for DAR
+  In this paper we explore the role of laughter in attributing
+  communicative intents to utterances, i.e.\ detecting the dialogue act
+  performed by them. We conduct a corpus study in adult
+  phone conversations showing how different dialogue acts are
+  characterised by specific laughter patterns, both from the speaker
+  and from the partner. Furthermore, we show that laughs can
+  positively impact the performance of Transformer-based models in a
+  dialogue act recognition task.  Our results highlight the importance
+  of laughter for meaning construction and disambiguation in
+  interaction.
+  % In this paper we explore the role of laughter in interpreting the
+  % meaning of an utterance, more specifically, a dialogue act performed
+  % by it. We illustrate the role of laughter in pragmatic
+  % disambiguation in a corpus study, and highlight the interplay
+  % between non-verbal behaviours and dialogue acts performed by
+  % utterances. Furthermore, we show that laughs can positively impact the
+  % performance of Transformer-based models in a dialogue act recognition
+  % task.
 \end{abstract}
@@
 
-\section{Corpus study}
+Laughter is ubiquitous in our everyday interactions.  In the
+Switchboard Dialogue Act Corpus \citep[SWDA,][]{jurafsky1997switchboard} (US
+English, phone conversations where two participants that
+are not familiar with each other discuss a potentially controversial
+subject, such as gun control or the school system) non-verbally vocalised
+dialogue acts (whole utterances that are marked as non-verbal, 66\% of
+which contain laughter) constitute 1.7\% of all dialogue acts.
+Laughter tokens\footnote{Switchboard Dialogue Act Corpus does not include speech-laughs.} make up 0.5\% of all the tokens that occur in the
+corpus.
+
+Laughter relates to the discourse structure of dialogue
+and can refer to a \emph{laughable}, which can be a perceived event or an
+entity in the discourse.
+Laughter can precede, follow or overlap the laughable, with the time
+alignment between the laughter and laughable dependent on who produces
+the laughable, the form of the laughter, and the pragmatic function performed \citep{tian2016we}. 
+%Laughter can act as a contextual feature for determining the sincerity of an utterance, e.g. when detecting sarcasm
+% \citep{tepperman2006yeah}.% ??
+% VM (removed as too vague!): Some studies have already pointed out the role of laughter to disambiguate between literal or not literal interpretations of utterances.
+
+\citet{bryant2016laughter} shows how listeners are influenced towards a non-literal interpretation of sentences when accompanied by laughter.
+Similarly, \citet{tepperman2006yeah} shows that laughter can act as a contextual feature for determining the sincerity of an utterance, e.g.
+when detecting sarcasm.
+% \todo{I don't know if that's ok...
+and I don't know if you preferred this bit here or later in the laughter background...!
+% }
+% VM: it is good!
+
+Nevertheless there is a dearth of research exploring the use of
+laughter in relation to different dialogue acts in detail, and
+therefore little is known about the role that laughter may have in
+facilitating the detection of communicative intentions.
+% for Vlad! just to let you know! I noticed the "CAN" relate to a laughable ^^
+% VM: what do you mean?
+
+In this paper we investigate the disambiguation potential of laughter
+for interpreting the meaning of an utterance, with the central point
+being the dialogue act performed by it. To do so, we employ a
+Transformer-based model and look into laughter as a potentially useful
+feature for the task of \emph{dialogue act recognition} (DAR). Laughs are not
+present in a large-scale pre-trained models, such as BERT \citep{Devlin2019a}, but their
+representations can be learned while training for a dialogue-specific
+task (DAR in our case). We further explore whether such representations
+can be additionally learned, in an unsupervised fashion, from
+dialogue-like data, such as a movie subtitles corpus, and if it
+further improves the performance of our model. 
+% Vlad check if it is right what I have written!! XD XD
+% VM: perfect
+
+The paper is organised as follows. We start with some brief background
+in Section~\ref{sec:background}. In Section~\ref{sec:corpus} we
+observe how dialogue acts can be classified with respect to their
+collocations with laughs and discuss the patterns observed in relation
+to the pragmatic functions that laughter can perform in dialogue. In
+Section~\ref{sec:dar} we report our experimental results for the DAR
+task depending on whether the model includes laughter. We further
+investigate whether non-verbal dialogue acts can be classified as more
+specific dialogue acts by our model.  We conclude with a discussion and
+outlining the directions for further work in
+Section~\ref{sec:discussion}.
+
+\section{Background}
+\label{sec:background}
+
+\subsection{Laughter}
+\label{sec:laughter}
+%Laughter production in conversation is not exclusively related to humour.
+But, perhaps unsurprisingly, the study of laughter has often been linked to the study of humour and the two terms are frequently used interchangeably.
+However,
+% Laughter does not occur only in
+% response to humour or in order to frame it. Many studies,
+% particularly in conversation analysis, have shown the role of laughter in
+% managing conversations at several levels: dynamics (turn-taking and
+% topic-change), lexical (signalling problems of lexical retrieval or
+% imprecision in the lexical choice), pragmatic (marking irony,
+% disambiguating meaning, managing self-correction) and social
+% (smoothing and softening difficult situations or showing
+% (dis)affiliation)
+% \citep{glenn2003laughter,jefferson1984organization,mazzocconi2019phd,petitjean2015laughing}.
+Laughter does not occur only in
+response to humour or in order to frame it. It is crucial in managing conversations in terms of dynamics (turn-taking and
+topic-change), at the lexical level (signalling problems of lexical retrieval or
+imprecision in the lexical choice), but also at a pragmatic (marking irony,
+disambiguating meaning, managing self-correction) and social level (smoothing and softening difficult situations or showing
+(dis)affiliation)
+\citep{glenn2003laughter,jefferson1984organization,mazzocconi2019phd,petitjean2015laughing}.
+
+Moreover \citet{romaniuk2009clinton} and \citet{ginzburg2020laughter}
+discuss how laughter can answer or decline to answer a question, and
+\citet{mazzocconi2018laughter} discusses how even isolated laughter
+can be the object of clarification requests, signalling the need for
+interlocutors to clarify its meaning (e.g., in terms of what the
+``laughable'' is) in order to continue the conversation.
+
+% \textcolor{blue}{<-- this is really badly written!}
+%\todo{^^ I think I'll rephrase it later!! XD I've copied and pasted these sentences in way to many places already!!! XD XD XD }
+
+%\todo{Ah!
+I see now the comment!
+Yes!
+I was just about to ask you if you would agree if I say a bit about the role of laughter for expliciting/disambiguating intentions!
+I mean...
+there is not much specifically speaking explicitely about laughter and dialogue acts but quite a bit I can say about the role laughter can have to disambiguate communicative intentions!
+}
+
+% Chiara: is there something more related to DAs?..
+
+\subsection{Dialogue act recognition}
+\label{sec:dial-act-recogn}
+
+The concept of a dialogue act (DA) is based on that of the speech act
+\citep{austin1975things}. %CH 2009??? Not 1975? 
+Breaking with classical semantic
+theory, Speech Act Theory considers not only the propositional content
+of an utterance but also the actions, such as \emph{promising} or
+\emph{apologising}, it carries out.  Dialogue acts extend the concept
+of the speech act, with a focus on the interactional nature of most
+speech.  DAMSL \citep{coreCodingDialogsDAMSL1997}, for example, is an
+influential DA tagging scheme where DAs are
+defined in part by whether they have a \emph{forward-looking} function
+(expecting a response) or \emph{backward-looking} function (in
+response to a previous utterance).
+
+Dialogue act recognition (DAR) is the task of labelling utterances with
+the dialogue act they perform, given a set of dialogue act tags.  As
+with other sequence labelling tasks in NLP, some notion of context is
+helpful in DAR.  One of the first performant machine learning models
+for DAR was a Hidden Markov Model that used various lexical and
+prosodic features as input \citep{stolckeDialogueActModeling2000}.
+
+Recent state-of-the-art approaches to dialogue act recognition
+have used a hierarchical approach, using large pre-trained language models like BERT to represent utterances, and adding some representation of discourse context at the dialogue level \citep[e.g.,][]{Ribeiro2019,mehriPretrainingMethodsDialog2019}.
+However \citet{darbert} observe that without fine-tuning,
+standard BERT representations perform very poorly on dialogue,
+even when paired with a discourse model,
+suggesting that certain utterance-internal features missing
+from BERT's textual pre-training data (such as laughter) 
+may have an adverse effect on dialogue act recognition.
+
+% Bill: what’s the state-of-the-art? + refer to our IWCS paper
+
+\section{Laughs in the Switchboard Dialogue Act Corpus}
 \label{sec:corpus}
 
-In this section we analyse dialogue acts according to their co-location with
-laughter and provide some qualitative insights from the
-statistics. The distribution of laughs in different dialogue acts has
-a rather uniform shape with a few outliers (Figure~\ref{fig:box-swda}). The
-most distinct outlier is ``Nonverbal'' dialogue act which is
+In this section we analyse dialogue acts in the Switchboard Dialogue Act
+Corpus according to their collocation with laughter and provide some
+qualitative insights based on the statistics.
+
+SWDA is tagged with a set of 220 dialogue act tags which, following
+\citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}, we
+cluster into a smaller set of 42 tags.
+
+The distribution of laughs in different dialogue acts has a rather
+uniform shape with a few outliers (Figure~\ref{fig:box-swda}). The
+most distinct outlier is the \emph{Non-verbal} dialogue act which is
 misleading with respect to laughter, because utterances only
-containing a single laughter token fall into this category, however
-they can serve, for example, to acknowledge a statement or to deflect
-a question \citep{mazzocconi2019phd}.
+containing a single laughter token fall into this category. However
+isolated laughs can serve, for example, to acknowledge a statement, to
+deflect a question, or to show appreciation
+\citep{mazzocconi2019phd}. We will further conjecture on this class of
+DAs in Sec.~\ref{sec:laughter-as-non}.
+%is it to much if I put making a statement? too much commintment to the propositional content thingy right?! XD
+
+\subsection{Method}
+\label{sec:method}
 
 \begin{figure}
+    \fontsize{8}{10}\selectfont
   \includesvg[width=\linewidth]{img/box-swda}
-  \caption{Box plot for proportions of dialogue act which contain laughs.}
+  \caption{Box plots for proportions of dialogue acts which contain laughs in SWDA.
+On the left: proportion of DAs containing laughter, on the right: proportion of DAs having laughter in one of the adjacent utterances.}%CH: Is it justified to combine preceding and following laughters in the same plot given the differences highlighted later?
   \label{fig:box-swda}
@@
 
-Let us introduce our comparison schema for the other two outliers,
-Downplayer and Apology, comparing them with the most common dialogue
-act in SWDA---Statement-Non-Opinion.  We take into consideration five
+Let us illustrate our comparison schema using the other two outliers,
+\emph{Downplayer} (make up 0.05\% of all utterances) and \emph{Apology} (0.04\%), comparing them with the most common dialogue
+act in SWDA---\emph{Statement-Non-Opinion} (33.27\%).  We take into consideration five
 laughter-related dimensions of an utterance, and create 5-dimensional
-representations of dialogue acts according to them. Each dimension's
-value equals to the proportion of utterances of a given type which
-contain laughter.
+(pentagonal) representations of DAs according to them. Each
+dimension's value is equal to the proportion of utterances of a given
+type which contain laughter:
 \begin{itemize}
 \item[$\uparrow$] current utterance;
-\item[$\nwarrow$] previous utterance by the same speaker;
-\item[$\swarrow$] previous utterance by the other speaker;
-\item[$\nearrow$] next utterance by the same speaker;
-\item[$\searrow$] next utterance by the other speaker.
+\item[$\nwarrow$] immediately preceding utterance by the same speaker;
+\item[$\nearrow$] immediately following utterance by the same speaker;
+\item[$\swarrow$] immediately preceding utterance by the other speaker;
+\item[$\searrow$] immediately following utterance by the other speaker.
 \end{itemize}
@@
   \includegraphics[width=\linewidth]{img/orbit-apology.pdf}
-  \caption{Comparison of the most common dialogue act in
-    SWDA---"Statement-Non-Opinion" (33.27\% of all utterances) with two
-    outliers "Apology" (0.04\%) and "Downplayer" (0.05\%). Proportion
-    of utterances which contain laughter are shown in association with
-    each dialogue act. }
+  \caption{Comparison between the pentagonal representations of laughter collocations of dialogue acts.}
   \label{fig:orbit}
@@
 
-% 1. overview: rather uniform distribution with few outliers
-% 2. let's look at outliers
-% 3. consider 5 dimensions of relations
+For instance, \ref{ex:apology-downplayer} is an illustrative example
+of the phenomenon shown in Figure \ref{fig:orbit}.
 
-For instance, 
-\begin{lingex}
-\item
+\begin{lingex}%CH What are # ?
+\item\label{ex:apology-downplayer}\footnote{Overlapping material is marked wish hash signs.}
+  \small
   \adjustbox{valign=t}{
-    \begin{tabulary}{\linewidth}{>{\bf}lJ>{\em}l}
-    A: & I am so sorry to keep you on hold. & Apology \\
-    B: & <Laughter> No problem. & Downplayer \\
-    A: & Are you at work? & YN-Quest. \\
+    % \setlength\tabcolsep{1.5pt}
+    \begin{tabulary}{\linewidth}{@{}>{\bf}lJ>{\em}r@{}}
+      A: & I'm sorry to keep you waiting \#<laughter>.\# & Apology \\
+      B: & \#Okay\# <laughter>. / & Downplayer \\
+      A: & Uh, I was calling from work  & Statement (n/o) \\
 \end{tabulary}}
@@
 
-\section{Laughter’s role in dialogue act recognition}
+We show the representations of all dialogue acts on
+Figure~\ref{fig:da-orbits}. We believe that such a depiction helps
+the reader form impressions about similarities  between
+DAs based on their laughter collocations and notice the ones
+that stand out in some respects.
+
+\begin{figure*}[h!]
+  \centering
+  \includegraphics[width=\linewidth]{img/multiorbit.pdf}
+  \caption{Pentagonal representation of dialogue acts: proportions of utterances which include laughter. Dimensions:
+$\uparrow$ current utterance;
+$\nwarrow$ immediately preceding utterance by the same speaker;
+$\nearrow$ immediately following utterance by the same speaker;
+$\swarrow$ immediately preceding utterance by the other speaker;
+$\searrow$ immediately following utterance by the other speaker.
+DAs are ordered by their frequency in SWDA (left-to-right, then top-to-bottom).
+    \label{fig:da-orbits}}
+\vspace*{-0.5cm}
+\end{figure*}
+
+To further assess the similarity between dialogue acts based on their
+collocations with laughs we factorise their pentagonal representations
+into 2D space using singular value decomposition (SVD). We can see
+that dialogue acts form some distinct clusters.
+% TODO: CH's note
+The resulting plot is
+shown in Figure~\ref{fig:da-svd} in Appendix~\ref{sec:app:da-svd}. Let
+us now proceed with some qualitative observations.
+
+\subsection{Observations}
+\label{sec:observations}
+\paragraph{Laughter and modification or enrichment of the current DA}
+We observe a higher proportion of laughter accompanying the current
+dialogue act ($\uparrow$) when the laughter is aimed at modifying
+the current dialogue act with some degree of urgency in order to
+smooth or soften it (\emph{Action-directive}, \emph{Reject},
+\emph{Dispreferred answer}, \emph{Apology}), to contribute to its
+enrichment stressing the positive disposition towards the partner
+(\emph{Appreciation}, \emph{Downplayer}, \emph{Thanking}), or to cue
+for the need to consider a less probable meaning, therefore helping
+in non-literal meaning interpretation (\emph{Rhetorical question}).
+
+While \emph{Apology} and \emph{Downplayer} have rather distinct and peculiar
+patterns (Fig.~\ref{fig:da-svd}) discussed in more detail below, we
+observe \emph{Dispreferred answers}, \emph{Action directives},
+\emph{Offers/Options/Commits} and \emph{Thanking} to constitute a
+close cluster when considering the decomposed values of the pentagonal
+used for DA representation.%CH ??? I don't understand this sentence!
+
+\paragraph{Laughter for benevolence induction and laughter as a response}
+The patterns observed in relation to the preceding and following
+turns reflect the multitude of functions that
+laughter can perform in interaction, stressing the fact that it can be
+used both to induce or invite a determinate response (dialogue act) from
+the partner (\emph{Downplayer}, \emph{Agree/Accept}, \emph{Appreciation}, \emph{Acknowledge})
+as well as being a possible answer to specific dialogue acts
+(e.g. \emph{Apology}, \emph{Offers/Options/Commits}, \emph{Summarise/Reformulate},
+\emph{Tag-question}).
+
+A peculiar case is than the one of \emph{Self-talk}, often followed by
+laughter by the same speaker. In this case the laughter may be
+produced to signal the incongruity of the action (in dialogue we
+normally speak to others, not to ourselves), while at the same time
+function to smooth the situation, for instance, when having issues of
+lexical retrieval, as in \ref{ex:selftalk}, or some degree of
+embarrassment from the speaker, when questioning whether a
+contribution is appropriate or not, as in
+\ref{ex:appropriate}.
+
+% A[\%]: {F Oh, } what can, - /
+% A[t1]: what is his name <lipsmack>.  /
+% A[ba]: {F Oh, } durn <laughter>,  /
+
+\begin{lingex}
+\item\label{ex:selftalk}
+  \small
+  \adjustbox{valign=t}{
+    % \setlength\tabcolsep{1.5pt}
+    \begin{tabulary}{\linewidth}{@{}>{\bf}lJ>{\em}r@{}}
+      A: & Have, uh, really, - &  \\
+      A: & what's the word I'm looking for, & Self-talk \\
+      A: & I'm just totally drawing a blank <laughter>. & Statement (n/o) \\
+
+\end{tabulary}}
+
+\item\label{ex:appropriate}
+  \small
+  \adjustbox{valign=t}{
+    % \setlength\tabcolsep{1.5pt}
+    \begin{tabulary}{\linewidth}{@{}>{\bf}lJ>{\em}r@{}}
+      B: &  Well,  I don't have a Mexi-, - & Statement (n/o) \\
+      B: & I don't, shouldn't say that, & Self-talk \\
+      B: & I don't have an ethnic maid <laughter>. & Statement (n/o) \\
+
+\end{tabulary}}
+\end{lingex}
+
+% A[+]: Have, {F uh, } really, - /
+% A[t1]: what's the word I'm looking for,  /
+% A[sd]: I'm just totally drawing a blank <laughter>. /
+
+% A[\%]: {C And, } {F uh, } cold foo-, {F um, } - /
+% A[t1]: what's it called,  /
+% A[sd]: I forgot, <laughter>, what it's called, /
+% ----
+
+% A[sd]: {D Well, } I don't know T V shows,  /
+% A[t1]: what can I tell you, {F um, }  /
+% A[sv]: basically junk that's on television <laughter>. -/
+
+% B[sd]: {D Well, } I don't have a Mexi-, - /
+% B[t1]: I [ don't, + ] shouldn't say that,  /
+% B[sd]: I don't have an ethnic maid <laughter>. /
+
+% Ex. reject
+% B[sv]: {C So } I'm old <laughter>. /
+% A[ar]: No,  /
+% A[sv]: you're not old <laughter>. /
+
+\paragraph{Apology and Downplayer}\label{subs:ap-down}
+It is interesting to comment on the parallelisms of laughter usage
+in relation to \textit{Apology} and \textit{Downplayer}, represented
+in Fig. \ref{fig:orbit} in contrast to \emph{Statement-non-opinion}, in
+as much as their graphic representations are more or less mirror-images of each other
+ and show how the dialogue acts are 
+linked by the pragmatic functions laughter can perform in dialogue.
+
+In both \textit{Apology} and \textit{Downplayer} we observe a rather
+higher proportion of occurrences in which the dialogue act is
+accompanied by laughter ($\uparrow$) in comparison to other DAs
+(Fig. \ref{fig:da-orbits}). In the case of \textit{Apology}, laughter
+can be produced to induce benevolence from the partner
+\citep{mazzocconiTAC}, while in the case of \textit{Downplayer} the
+laughter can be produced to reassure the partner about some situation
+that had been appraised as discomforting (classified as \emph{social
+incongruity} by \citealp{mazzocconiTAC}) and somehow signal that the
+issue should be regarded %\todo{is declined a technical term here? If not I might swap with ``regarded''} 
+as not important
+\citep{romaniuk2009clinton,gazelaughter}, as in \ref{ex:socInc}.
+
+\begin{lingex}
+\item\label{ex:socInc}
+  \small
+  \adjustbox{valign=t}{
+    % \setlength\tabcolsep{1.5pt}
+    \begin{tabulary}{\linewidth}{@{}>{\bf}lJ>{\em}r@{}}
+      A: & I don't, I don't think I could do that <laughter>. \# & Statement (n/o) \\
+      B: & Oh, it's not bad at all. & Downplayer \\
+      A: &  It's, it's a beautiful drive.  & Statement (n/o)\\
+\end{tabulary}}
+\end{lingex}
+
+The interesting mirror-image %specular\todo{does it work in english?
+BN: I didn't know this word before but I think so?
+CH: I have no idea what it means.
+Can we rephrase so it's understandable to mere mortals??}
+patterns
+observable in the lower part of the graph can therefore be explained
+by considering the relation between the two dialogues acts.  We
+observe cases in which an \textit{Apology} is accompanied by a
+laughter, and then followed by a \textit{Downplayer}, showing 
+that the laughter’s positive effect was attained and successful. This
+allows us to explain both the bottom left spike ($\swarrow$) observed for
+\textit{Downplayer} (often preceded by an utterance by the
+partner containing laughter) and the bottom right spike ($\searrow$) observed
+for \emph{Apology} (often followed by an utterance by the
+partner containing laughter). In example \ref{ex:apology-downplayer}
+both the apology and the downplayer are accompanied by laughter, while
+in \ref{ex:sorry} a typical example of a laughter accompanying an \emph{Apology}
+is followed by a \emph{Downplayer}.
+
+\begin{lingex}
+\item\label{ex:sorry}
+  \small
+  \adjustbox{valign=t}{
+    % \setlength\tabcolsep{1.5pt}
+    \begin{tabulary}{\linewidth}{@{}>{\bf}lJ>{\em}r@{}}
+      B: & I'm sorry <laughter>. \# & Apology \\
+      A: & That's all right.  / & Downplayer \\
+      B: & You,  you were talking about, uh, uh,    & Summarise\\
+\end{tabulary}}
+\end{lingex}
+
+We now turn to the question of whether our qualitative observations of patters between laughs and dialogue acts can be used to improve a dialogue act recognition task.
+
+% E.g. social inc in general
+
+% B[sd]: [ I don't, + I don't ] think I could do that <laughter>. /
+% A[bd]: {F Oh, } it's not bad at all.  /
+% A[sd]: [  It's, + it's ] a beautiful drive. /
+
+% A[sd]: I hope you can understand what I s-, \# <laughter>. \# -/
+% B[bd]: \# That's okay <laughter>. \#  /
+% B[sd]: I got the dryer going --
+
+% E.g. pair apology downplayer
+% B[fa]: I'm sorry <laughter>. /
+% A[bd]: That's all right.  /
+% A[bf]: [ You, + you ] were talking about, {F uh, } {F uh, } --
+
+% A[fa]: I'm sorry to keep you waiting \# <laughter>. \# /
+% B[bd]: \# Okay \# <laughter>. /
+% A[sd]: {F Uh, } I was calling from work  /
+
+% A[fa]: I'm sorry <laughter>. /
+% B[bd]: That's okay.  /
+% B[sd]: I'm Bill from Raleigh. /
+
+% A[fa]: {D Well, } I'm sorry <laughter>. /
+% B[bd]: That's okay. /
+% A[qy]: {F Uh, } did you ever go to Texins at all  when you were working for T I?  /
+
+% A[fa]: {C And } I'm sorry <laughter>. /
+% B[bd]: {F Oh, } no. /
+% A[sd]: We're just not real big movie goers. /
+
+%of course these are too many examples, but we can choose! ; )
+
+%  by and bd "sYmpathy" and "Downplayers" of sympathy and compliments
+%These are subtypes of BACKWARDS-ATTITUDE which express not just acknoweldge or understanding, but also further emotional involvement.
+
+% by   A.44 utt1:  I'm real sorry. /
+% Actual apologies (for doing something), as opposed to markers of sympathies, are tagged as "fa", see above.
+
+% bd is any downplayer that speakers use to respond to apologize.
+
+% bd   B.45 utt1:  That's all right. /
+% Downplayers are also used to respond to compliments.
+
+%
+% \paragraph{action-directive}
+% \paragraph{summarise/reformulate }
+
+% \paragraph{agree/accept, appreciation}
+
+% \end{itemize}
+
+% \begin{table}[htbp]
+%       \small
+%   \centering
+%   \begin{tabularx}{\linewidth}{llL}
+%     \toprule
+%     Speaker & DA & Utterance \\ \midrule
+%     A	&Apology	& I'm sorry to keep you waiting \#\texttt{<laughter>}.\#  \\
+%     B &Downplayer & \#Okay\# \texttt{<laughter>}. \\
+%     A	&sd	& Uh, I was calling from work  \\
+%     \bottomrule
+%   \end{tabularx}
+%   \caption{Example from the SWDA corpus (TODO:SW???). Dialogue acts:
+%     \emph{sd}---Statement-non-opinion. Overlapping material is marked
+%     with hash signs. }
+%   \label{tab:ex:apology-downplayer}
+% \end{table}
+
+% \item Agree/accept + Appreciation
+
+\section{The importance of laughter in artificial dialogue act recognition}
 \label{sec:dar}
@@
 \subsection{Data}\label{sec:data}
-We perform experiments on the Switchboard Dialogue Act Corpus (SWDA), which is a subset of the larger Switchboard corpus, and the dialogue act-tagged portion of the AMI Meeting Corpus (AMI-DA). 
-SWDA is tagged with a set of 220 dialogue act tags which, following  \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a}, we cluster into a smaller set of 42 tags.
-AMI uses a smaller tagset of 16 dialogue acts \citep{GuidelinesDialogueAct2005}.
+We perform experiments on the Switchboard Dialogue Act Corpus (SWDA,
+42 dialogue act tags), which is a subset of the larger Switchboard
+corpus, and the dialogue act-tagged portion of the AMI Meeting Corpus
+(AMI-DA).  AMI uses a smaller tagset of 16 dialogue acts
+\citep{GuidelinesDialogueAct2005}.
 
@@
 
-\begin{table}[]
+\begin{table}[ht]
+\small
 \centering
 \begin{tabular}{@{}ll@{}}
-\toprule
-\textbf{Switchboard}       & \textbf{AMI Corpus}                     \\ \midrule
+\textbf{Switchboard}       & \textbf{AMI Corpus}                     \\\hline
 Dyadic                     & Multi-party                             \\
 Casual conversation        & Mock business meeting                   \\
-Telephone                  & In-person \& video                      \\ \midrule
+Telephone                  & In-person \& video                      \\
 English                    & English                                 \\ 
 Native speakers            & Native \& non-native speakers           \\ 
-early '90s                 & 2000s                                   \\ \midrule
+%  early '90s                 & 2000s                                   \\
 2200 conversations         & 171 meetings                            \\
@@
 400k utterances             & 118k utterances                         \\
-3M tokens                  & 1.2M tokens                             \\ \bottomrule
+  3M tokens                  & 1.2M tokens                             \\
 \end{tabular}  
-  \caption{Comparison between Switchboard and the AMI Meeting Corpus}
-  \label{table:corpora}
+\caption{Comparison between Switchboard and the AMI Meeting Corpus
+  \label{table:corpora}}
 \end{table}
@@
 \paragraph{Preprocessing}
-% - Preprocessing: remove disfluencies, acronyms and speaker tokens in AMI, removing laughter % Bill
 
-We make an effort to normalize transcription conventions across SWDA and AMI.
+We make an effort to normalise transcription conventions across SWDA and AMI.
 We remove disfluency annotations and slashes from the end of utterances in SWDA.
-In both corpora, acronyms are tokenized as individual letters. 
+In both corpora, acronyms are tokenised as individual letters. 
 All utterances are lower-cased.
 
-Utterances are tokenized using with a word piece tokenizer \citep{Wu2016} with a vocabulary of 30,000.
+Utterances are tokenised using a word piece tokeniser \citep{Wu2016} with a vocabulary of 30,000.
 We add a special laughter token to the vocabulary and map all transcribed laughter to that token.
-We also add five speaker tokens and prepend each utterance with a speaker token that uniquely identifies the corresponding speaker within that dialogue.
-
-\subsection{Pre-training corpora}
-We also experiment with three unlabeled dialogue corpora (Table~\ref{tab:pretraining-corpora}), which we use to provide further pre-training for the BERT encoder.
-
-The first two corpora are constructed from the same source as the dialogue act corpora.
-We use the SWDA portion of the un-labeled Switchboard corpus (SWBD) and the entire AMI corpus (including the 32 dialogues with no human-annotated DA tags that are not included in the DAR training set).
-In both cases, we exclude dialogues that are reserved for DAR testing.
-
-We also experiment with a much larger a corpus constructed from OpenSubtitles \citep{Lison2016}.
-We used a manually constructed list of words frequenty used to refer to laughter in subtitles and replaced every occurance of one of these words with the special laughter token. 
-Then, we collected every English-language subtitle file in which at least 1\% of the utterances contained laughter (about 11\% of the total).
-Because utterances are not labeled with speaker in the OpenSubtitles corpus, we randomly assigned a speaker token to each utterance to maintain the format of the other dialouge corpora.
-
-The pre-training corpora were prepared for the combined maksed language modeling and next sentence (utterance) prediction task, as described dy \citet{devlinBERTPretrainingDeep2018}.
-For the smaller SWBD and AMI corpora, we generate and train on multiple epochs of data.
-Since there is randomness in the data preparation (e.g., which distrcactor sentences are chosen and which tokens are masked), we generate each training epoch separately.\footnote{For details, see the \href{https://github.com/huggingface/transformers/tree/1.1.0/examples/lm_finetuning}{finetuning example} from Hugging Face.}
-
-\begin{table}[ht]
-\centering
-\begin{tabular}{@{}llll@{}}
-\toprule
-       & tokens & \% laughs & epochs\\ \midrule
-AMI           & 1M     & 1.3             & 10     \\
-SWBD          & 1.5M   & 0.5             & 10     \\
-OpenSubtitles & 350M   & 0.3             & 1      \\ \bottomrule
-\end{tabular}
-\caption{Pre-training corpora, showing laughter representation as a percentage of total tokens and number of pre-training epochs generated.}\label{tab:pretraining-corpora}
-\end{table}
-
-\paragraph{}
-Let us turn now to describing the neural network architectures that we used.
+We also  prepend each utterance with a speaker token that uniquely identifies the corresponding speaker within that dialogue.
 
@@
 \label{sec:model}
-To test the effectiveness of BERT for DAR, we employ a simple neural architecture with two components: an encoder that vectorizes utterances, and a sequence model that predicts dialogue act tags from the vectorized utterances (Figure~\ref{fig:model-architecture}).
+To test the effectiveness of BERT for DAR, we employ a simple neural architecture with two components: an encoder that vectorises utterances, and a sequence model that predicts dialogue act tags from the vectorised utterances (Figure~\ref{fig:model-architecture}).
 Since we are primarily interested in comparing different utterance encoders, we use a basic RNN as the sequence model in every configuration.\footnote{We have experimented with LSTM as the sequence model, but the accuracy was not significantly different compared to RNN.
@@
 As a baseline utterance encoder, we use a word-level CNN with window sizes of 3, 4, and 5, each with 100 feature maps \citep{kimConvolutionalNeuralNetworks2014}. 
-The model uses 100-dimensional word embeddings, which are initialized with pre-trained gloVe vectors \citep{penningtonGloveGlobalVectors2014}.
+The model uses 100-dimensional word embeddings, which are initialised with pre-trained gloVe vectors \citep{penningtonGloveGlobalVectors2014}.
 
@@
 In the first experiment we investigated whether laughter, as an example of a dialogue-specific signal, is a helpful feature for DAR.
-Therefore, we train another version of each model: one that containing laughs (\texttt{L}) and one with laughs left out (\texttt{NL}), and compare their performances in DAR task.
+Therefore, we train another version of each model: one containing laughs (\texttt{L}) and one with laughs left out (\texttt{NL}), and compare their performances in DAR task.
 Table~\ref{table:laughter-total-acc} compares the results from applying the models with two different utterance encoders (\texttt{BERT}, \texttt{CNN}).
 
-First of all, we can see that the \texttt{BERT} utterance encoder outperforms \texttt{CNN} in all the cases.
-From observing the effect of laughters, we can see differences in performance depending on the dialogue act, regardless how often laughter occurs in the current or adjacent utterances (see Figure~\ref{fig:by-da} in Appendix~\ref{sec:suppl}).
+First of all, we can see that  \texttt{BERT}  outperforms \texttt{CNN} in all cases.
+From observing the effect of laughters, we can see differences in performance depending on the dialogue act, regardless of how often laughter occurs in the current or adjacent utterances (see Figure~\ref{fig:by-da} in Appendix~\ref{sec:suppl}).
 The strongest evidence for laughter as a helpful feature was found in SWDA for the \texttt{BERT} utterance encoder, where macro-F1 score increases by 7.89 percentage points.
@@
 \begin{table}
+  \small
   \centering
-  \begin{tabular}{@{}lcccc@{}}
-    \toprule
-                      & \multicolumn{2}{c}{SWDA} & \multicolumn{2}{c}{AMI-DA} \\ \midrule
+  \begin{tabularx}{\linewidth}{@{}Lcccc@{}}
+                      & \multicolumn{2}{c}{\textbf{SWDA}} & \multicolumn{2}{c}{\textbf{AMI-DA}} \\ 
                       & F1    & acc.  & F1    & acc.       \\ 
-    \texttt{BERT-NL}  & 38.10 & 77.07 & 49.09 & 67.06       \\ 
-    \texttt{BERT-L}   & 45.99 & 76.93 & 50.17 & 67.12       \\ \midrule
-    \texttt{CNN-NL}   & 37.23 & 75.08 & 38.37 & 63.46        \\
-    \texttt{CNN-L}    & 27.59 & 75.40 & 37.94 & 64.30        \\ \midrule
-    Majority class    & 0.78  & 33.56 &  1.88 & 28.27      \\ \bottomrule
+    \texttt{BERT-NL}  & 36.48 & 76.00 & 44.75 & 68.04      \\ 
+    \texttt{BERT-L}   & 36.75 & 76.60 & 43.37 & 64.87       \\ \hline
+    \texttt{CNN-NL}   & 36.95 & 73.92 & 38.00 & 63.18        \\
+    \texttt{CNN-L}    & 37.59 & 75.40 & 37.89 & 64.27        \\ \hline
+    Majority class    & 0.78  & 33.56 &  1.88 & 28.27      \\
 
-  \end{tabular}
+  \end{tabularx}
   \caption{Comparison of macro-average F1 and accuracy depending on using laughter on the training phase. }
@@
 
-Confusion matrices (Figure~\ref{fig:swda-cm}) provide some food for thought.
-Most of the misclassifications fall into the majority classes, such as \emph{sd} (Statement-non-opinion), in the left edge of the matrix.
-However, there are some important exceptions, such as \emph{rhetorical questions}, that are misclassified as other forms of questions due to their surface question-like form.
-Importantly, laughter helps to classify rhetorical questions correctly, this is because in a conversation it can be used as a device to cancel seriousness or sincerity \citep{ginzburg2015understanding,tepperman2006yeah}, in this case, of a question.
-Therefore, questions, like the one we show in the example in Table~\ref{table:example-qh}, are easier to disambiguate with the help of laughter.
-\begin{table}
-      \small
-  \centering
-  \begin{tabularx}{\linewidth}{llL}
-    \toprule
-    Speaker & DA & Utterance \\ \midrule
-        \multicolumn{3}{c}{\emph{(Talking about hobbies)}}\\
-    B   & sd	&  Um, as far as spare time, they talked about, \\
-    B	& \% & I don't, + I think, \\
-    B	& qh & who has any spare time \texttt{<laughter>}? \\
-    A	& x & \texttt{<laughter>}.\\
-             \bottomrule
-  \end{tabularx}
-  \caption{Example from the SWDA corpus (sw3735). B's contribution \emph{qh} (Rhetorical question) is misinterpreted as \emph{qw} (Wh-question) by the BERT model without laughs in training data. }
-  \label{table:example-qh}
-\end{table}
+%                   SWDA        AMI-DA
+% NL_bert 	
+% macro precision 	0.437264 	0.513033
+% macro recall 	    0.350711 	0.447011
+% macro f1 	        0.364835 	0.447572
+% micro accuracy 	0.760045 	0.680351
+% L_bert 	
+% macro precision 	0.434728 	0.489694
+% macro recall 	    0.351546 	0.430792
+% macro f1 	        0.367521 	0.433668
+% micro accuracy 	0.766043 	0.648691
+% NL_cnn 	
+% macro precision 	0.526282 	0.492194
+% macro recall 	    0.335863 	0.356420
+% macro f1 	        0.369507 	0.379989
+% micro accuracy 	0.739256 	0.631760
+% L_cnn 	
+% macro precision 	0.488935 	0.499911
+% macro recall 	    0.346400 	0.371120
+% macro f1 	        0.375904 	0.378919
+% micro accuracy 	0.754047 	0.642738
 
@@
   \centering
-  \includegraphics[width=1.0\linewidth]{img/swda-cm.pdf}
-  \caption{Confusion matrices for \texttt{BERT-NL} (top) vs \texttt{BERT-L} (bottom); SWDA corpus. Solid line shows the improvement in classification of rhetorical questions.}
+    \fontsize{6}{10}\selectfont
+%      \includesvg[width=\linewidth]{img/da-svd-verbal}
+   \includegraphics[width=\linewidth]{img/swda-cm.pdf}
+  \caption{Confusion matrices for \texttt{BERT-NL} (top) vs \texttt{BERT-L} (bottom); SWDA corpus. Solid lines show classification improvement  of rhetorical questions.}
     \label{fig:swda-cm}
@@
 
+  % TODO: ^ insert SVG image!
+
+  Confusion matrices (Figure~\ref{fig:swda-cm}) provide some food for
+  thought. Most of the misclassifications fall into the majority
+  classes, such as \emph{sd} (Statement-non-opinion), on left edge
+  of the matrix. However, there are some important exceptions, such as
+  \emph{rhetorical questions}, that are misclassified as other forms
+  of questions due to their surface question-like form.  Importantly,
+  laughter helps to classify rhetorical questions correctly, this is
+  because in a conversation it can be used as a device to cancel
+  seriousness or reduce commitment to literal meaning % sincerity
+  \citep{ginzburg2015understanding,tepperman2006yeah} 
+  %\todo{I actually like much more to say that it signal a clash between the literal and the intended meanning....
+I think this is the basic think it does..
+and then one derive the inference that the person is "not being serious"...
+sincerity is a big issue...
+I wouldn't use that word....
+you know the non-bona fide stuff....
+but I don't know....
+I actually didn't reallu tepperman fully..
+XD}.
+  Therefore,
+  questions, like the one we show in example \ref{ex:rhet-qu}, are
+  easier to disambiguate with laughter.
+% \begin{table}
+%       \small
+%   \centering
+%   \begin{tabularx}{\linewidth}{llL}
+%     \toprule
+%     Speaker & DA & Utterance \\ \midrule
+%         \multicolumn{3}{c}{\emph{(Talking about hobbies)}}\\
+%     B   & sd	&  Um, as far as spare time, they talked about, \\
+%     B	& \% & I don't, + I think, \\
+%     B	& qh & who has any spare time \texttt{<laughter>}? \\
+%     A	& x & \texttt{<laughter>}.\\
+%              \bottomrule
+%   \end{tabularx}
+%   \caption{Example from the SWDA corpus (sw3735). B's contribution \emph{qh} (Rhetorical question) is misinterpreted as \emph{qw} (Wh-question) by the BERT model without laughs in training data. }
+%   \label{table:example-qh}
+% \end{table}
+
+\begin{lingex}
+\item\label{ex:rhet-qu}
+  \small
+  \adjustbox{valign=t}{
+    % \setlength\tabcolsep{1.5pt}
+    \begin{tabulary}{\linewidth}{@{}>{\bf}lJ>{\em}r@{}}
+      B: & Um, as far as spare time, they talked about, & Statement (n/o) \\
+      B: & I don't, + I think, &  Statement (n/o) \\
+       B: & who has any spare time \texttt{<laughter>}?  &  Rhetorical Quest. \\
+      A: & \texttt{<laughter>}. & Non-verbal
+\end{tabulary}}
+\end{lingex}
+
   % TODO: mapping groups?
 
-\section{Laughter as a non-verbal dialogue act}
+\subsection{Experiment 2: laughter and pre-training}
+\label{sec:exper-2:-laught}
+
+As previously noted, training data for BERT does not include
+features specific to dialogue (e.g.\ laughs). We therefore  experiment
+with a large and more dialogue-like corpus constructed from
+OpenSubtitles \citep{Lison2016} (350M tokens, where 0.3\% are laughter
+tokens).  We used a manually constructed list of words frequently used
+to refer to laughter in subtitles and replaced every occurance of one
+of these words with the special laughter token.  We then collected
+every English-language subtitle file in which at least 1\% of the
+utterances contained laughter (about 11\% of the total).  Because
+utterances are not labelled with speaker in the OpenSubtitles corpus,
+we randomly assigned a speaker token to each utterance to maintain the
+format of the other dialouge corpora.
+
+The pre-training corpus was prepared for the combined masked language
+modelling and next sentence (utterance) prediction task, as described
+by \citet{devlinBERTPretrainingDeep2018}.
+
+%Here, 
+We analyse how pre-training affects BERT's performance as an utterance encoder.
+To do so, we consider the performance of DAR models with three different utterance encoders:
+\begin{enumerate*}[i)]
+\item \texttt{FT} -- pre-trained BERT with DAR fine-tuning;
+\item \texttt{RI} -- randomly initialised BERT (with DAR fine-tuning);
+\item \texttt{FZ} -- pre-trained BERT without fine-tuning (frozen during DAR training).
+\end{enumerate*}
+For the pre-trained (\texttt{FT}, \texttt{FZ}) conditions we perform two types of
+pre-training:
+\begin{enumerate*}[i)]
+\item \texttt{OSL} -- pre-training on the portion of OpenSubtitles corpus
+\item \texttt{OSNL} -- same as \texttt{OSL}, but with all the laughs removed.
+\end{enumerate*}
+We fine-tune and test our models on the corpora containing laughs (\texttt{L}).
+
+%\textbf{TODO: describe the results}
+We observe that dialogue pre-training improves performance of the
+models. Fine-tuned models also perform better than the frozen ones
+because the latter provide less opportunities for the encoder to be
+trained for the specific task.
+
+Including laughter in pre-training data improves F1 scores in most
+cases, except for the SWDA in the fine-tuned condition. The difference
+is especially pronounced for AMI-DA corpus in the fine-tuned condition
+(4.97 p.p.\ difference in F1). The question of relevance of movies
+subtitle data for either SWDA or AMI-DA can be a subject for further
+study, including the types of laughs in the corpora. It might be the
+case that nature of AMI-DA is congruent with those of movie
+subtitles, since participants in AMI-DA basically are role-playing being in a 
+focus group rather than being involved in a natural
+dialogue. People might produce laughs in places only  where
+they intuitively expected by them to be produced (i.e.\ humour
+related), just as in scripted movie dialogues.
+
+\begin{table}[ht]
+  \small
+\begin{tabularx}{\linewidth}{@{}Lrrrr@{}}
+           & \multicolumn{2}{c}{\textbf{SWDA}}                          & \multicolumn{2}{c}{\textbf{AMI-DA}}                        \\ 
+           & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{acc.} \\
+\texttt{BERT-L-FT}         & 36.75 & 76.60 & 43.37 & 64.87 \\
+\bf\texttt{BERT-L+OSL-FT}  & 41.42 & 76.95 & 48.65 & 68.07 \\ 
+\bf\texttt{BERT-L+OSNL-FT} & 43.71 & 77.09 & 43.68 & 64.80 \\ \hline
+\bf\texttt{BERT-L+OSL-FZ}  &  9.60 & 57.67 & 17.03 & 51.03 \\ 
+\bf\texttt{BERT-L+OSNL-FZ} &  7.69 & 55.29 & 16.99 & 51.46  \\ \hline
+\texttt{BERT-L-RI}         & 32.18 & 73.80 & 34.88 & 60.89 \\ 
+ Majority class       & 0.78  & 33.56 &  1.88 & 28.27      \\ 
+    SotA              &    -  & 83.1\footnotemark & - & -  \\
+\end{tabularx}
+\caption{Comparison of macro-F1 and accuracy with further dialogue pre-training.  % ,
+  % for the frozen (\texttt{FZ}) and fine-tuned (\texttt{FT}) conditions.
+\texttt{L-RI} uses a randomly initialised utterance encoder with no pre-training but with fine-tuning.
+Pretraining is either performed on OpenSubtitles corpus with (\texttt{OSL}) or without including laughter (\texttt{OSNL}).
+\label{tab:results}}
+\end{table}
+
+\footnotetext{\citet{Kozareva2019}}
+
+\subsection{Experiment 3: Laughter as a non-verbal dialogue act}
 \label{sec:laughter-as-non}
 
+In this experiment, following the observations regarding the
+misleading character of \emph{Non-verbal} dialogue acts, we looked at
+the predictions that the model would give this class of dialogue acts
+if it wasn't aware of the \emph{Non-verbal} class. To do so, we mask
+the outputs of the model where the desired class was \emph{Non-verbal}
+and do not backpropagate these results. We used the \texttt{BERT-L-FT}
+for this experiment. After training we tested the resulting model on
+the test set containing 659 non-verbal dialogue acts, 413 of which
+contain laughter.
+
+For 314 (76\%) of such dialogue acts the model has predicted the
+\emph{Acknowledge (Backchannel)} class and for 46 (11\%) ---
+continuations of the previous DA by the same speaker. The rest were
+classified as either something uninformative (the \emph{Abandoned or
+  Turn-Exit or Uninterpretable} class) or, from manual observation,
+clearly unrelated.
+
+\emph{Acknowledge (Backchannel)} can cover some uses of laughter, for
+instance, to show to the interlocutor acknowledgement of their
+contribution, implying the appreciation of an incongruity, and
+inviting continuation (functioning simultaneously as a continuer and
+assessment feedback
+\citep{schegloff1982discourse}), as in example~\ref{ex:fish}.
+
+\begin{lingex}
+  \small
+\item\label{ex:fish}  \small
+  %From sw2290.
+  (We mark continuations of the previous DA by the same speaker with a plus, and indicate misclassified dialogue acts with a star. Laughs shown in bold constitute \emph{Non-verbal} dialogue acts)\\
+    % \adjustbox{valign=t}{
+    % \setlength\tabcolsep{2pt}
+    \begin{tabulary}{\linewidth}{@{}>{\bf}lJ>{\em}r@{}}
+B: & Everyone on the boat was catching snapper, snappers except guess who. & Statement (n/o)  \\ 
+A: & <laughter> It had to be you. & Summ./reform.  \\
+B: & <laughter> I ca-, I, - & Uninterpretable \\
+A: & Couldn't catch one to save your life. Huh. & %Summarize/reformulate $\to$
+Backchannel$^*$\\
+B: & That's right, & Agree/Accept \\
+B: & I would go from one side of the boat to the other, & Statement (n/o) \\
+B: & and, uh, & $+$ \\
+A: & \bf <laughter>. &Backchannel\\
+B: & the, uh, the party boat captain could not understand, you know, & $+$ \\
+B: & he even, even he started baiting my hook <laughter>, & Statement (n/o) \\
+A: & \bf <laughter>. &Backchannel\\
+B: & and holding, holding the, uh, the fishing rod. & $+$\\
+A: & How funny, & Appreciation \\
+% A & just hoping maybe, he could pull <laughter>. - & %Summarize/reformulate $\to$
+% Statement (n/o)$^*$ \\
+% B & Right, <laughter> & %aa $\to$
+% Backchannel$^*$ \\
+% B & and it was, it was really, really, really bad. & Statement (n/o)  
+\end{tabulary}
+% }
+\end{lingex}
+
+Nevertheless, these two cases clearly cannot account for all the
+examples discussed in the literature (e.g.\ standalone uses of
+laughter as signal of disbelief or negative response to a polar
+question \citealp{ginzburg2020laughter}) and above in
+Sec.~\ref{sec:observations}. Future models will therefore require a
+manual assignment of meaningful dialogue acts to standalone laughs.
+
+% \begin{table}
+%   \centering
+%   \begin{tabularx}{\linewidth}{@{}Ll@{}}
+%     \toprule
+%     Assigned class &  \\\midrule
+%     Backchannel   & 314 \\
+%     Other & 42 \\
+%     Continuer (preceding DA) & 46 \\
+%     Quotation & 8 \\
+%     Collaborative completion & 2 \\
+%     Conventional-closing & 1 \\\midrule
+%     TOTAL & 413 \\
+%     \bottomrule
+%   \end{tabularx}
+%   \caption{Distribution of model predictions for dialogue acts annotated as \emph{non-verbal}. }
+%   \label{tab:nv-results}
+% \end{table}
+
+% - inconclusive
+% not bad to consider as backchannels. But not the same as the examples above for standalone: glossa examples
+% - signalling understanding
+% - enriching this understanding with emotional appraisal
+% we need an annotation
+
 \section{Discussion}
-On the question of laughter impact, this study found that laughter is more helpful in SWDA corpus than in AMI-DA.
-Due to the nature of interactions over the phone, SWDA dialogue participants can not rely on visual signals, such as gestures and facial expressions.
-Our results support the hypothesis that in SWDA, vocalizations such as laughter are more pronounced and therefore more helpful in disambiguating dialogue acts.
+\label{sec:discussion}
+The implications of the results obtained are twofold: showing that
+laughter can help a computational model to attribute meaning to an
+utterance and help with pragmatic disambiguation, and consequently
+stressing once again the need for integrating laughter (and other
+non-verbal social signals) in any framework aimed to model meaning in
+interaction \citep{ginzburg2020laughter,Maraev.Mazzocconi.Howes.Ginzburg_ISCA_2018}. % TODO: and, in final version add LACATODA
 
-This may also explain why all our best models perform better on SWDA: more of the information that interlocutors and dialogue act annotators rely on is present SWDA transcripts, whereas AMI-DA annotators receive clear instructions to pay attention to the videos \citep{GuidelinesDialogueAct2005}.
-This finding is consistent with that of \citet{bavelas2008gesturing} who demonstrate that in face-to-face dialogue, visual components, such as gestures, can convey information that is independent from what is conveyed by speech.
+% \subsection{Laughter and pragmatic disambiguation}
+% \label{sec:laught-dial-acts}
 
-There is abundant room for further progress in determining how other speech-related information, such as prosody and disfluencies, can be incorporated into the DAR model.
-\citet{stolckeDialogueActModeling2000} showed that dialogue acts can have specific prosodic manifestations that can be used to improve dialogue act classification.
-Furthermore, in relation to laughter, its form (duration, arousal level) can be informative about its function and position w.r.t. to laughable \citep{tian2016we,mazzocconi2019phd}.
+Our results provide further evidence
+(e.g. \citet{torres1997modeling,gazelaughter}) for the fact that
+non-verbal behaviours are tightly related to the dialogue information
+structure, propositional content and  dialogue act performed by
+utterances.
+Laughter, along with other non-verbal social signals, can constitute a
+dialogue act in itself conveying meaning and affecting the unfolding
+ dialogue \citep{bavelas2000visible,ginzburg2020laughter}.
+
+% \subsection{Laughter and dialogue act recognition task}
+% \label{sec:dar-task}
+In this work we have shown that laughter is a valuable cue for DAR
+task. We believe that in our conversations laughter is informative
+about interlocutors' emotional and cognitive appraisals of events and
+communicative intents. %\citep{mazzocconi2019phd}. 
+Therefore, it should not come as a surprise
+%\todo{mmm... maybe I do not love it... I mean it super cool!!! maybe say it is not surprise makes it a bit less cool... should we rather say we think that's why it helps also the model? } 
+that laughter
+acts as a cue in a computational model.
+
+On the question of laughter impact on the dialogue act recognition
+(DAR) task, this study found that laughter is more helpful in SWDA
+corpus than in AMI-DA.  Due to the nature of interactions over the
+phone, SWDA dialogue participants can not rely on visual signals, such
+as gestures and facial expressions.  Our results support the
+hypothesis that in SWDA, vocalizations such as laughter are more
+pronounced and therefore more helpful in disambiguating dialogue acts.
+This may also explain why our best models perform better on SWDA:
+more of the information that interlocutors and dialogue act annotators
+rely on is present in SWDA transcripts, whereas AMI-DA annotators receive
+clear instructions to pay attention to the videos
+\citep{GuidelinesDialogueAct2005}.  This finding is consistent with
+that of \citet{bavelas2008gesturing} who demonstrate that in
+face-to-face dialogue, visual components, such as gestures, can convey
+information that is independent from what is conveyed by speech.
+
+Laughter can be used to mark the presence of an incongruity between
+what is said and what is intended, coined as \emph{pragmatic
+  incongruity} by \citet{mazzocconiTAC}. In those cases laughter is
+especially valuable for disambiguating between literal and non-literal
+meaning, as we have shown for rhetorical questions, a task which is
+still a struggle for most NLP models and dialogue systems.
+
+There is abundant room for further progress in determining how other speech-related information, such as prosody and disfluencies, can be incorporated into a DAR model.
+\citet{stolckeDialogueActModeling2000} showed that dialogue acts can have specific prosodic manifestations that can be used to improve DAR.
+Furthermore, in relation to laughter, its form (duration, arousal, overlap with speech) can be informative about its function and position w.r.t.\ the laughable \citep{tian2016we,mazzocconi2019phd}.
 Incorporating such information is crucial if models pre-trained on large-scale text corpora are to be adapted for use in dialogue applications.
 
-\section*{Acknowledgments}
+% - communicative intentions (not just turn and "sequencing") 
+% - non-literal meaning (also supported by the BERT model)
+% - not being "just" non-verbal! Bavelas!
 
-The acknowledgments should go immediately before the references. Do not number the acknowledgments section.
-\textbf{Do not include this section when submitting your paper for review.}
+% TODO: what about more appropriate dialogue act annotation schemes?
+
+% \section*{Acknowledgments}
+
+% The acknowledgments should go immediately before the references. Do not number the acknowledgments section.
+% \textbf{Do not include this section when submitting your paper for review.}
 
@@
 
+\subsection{Collocations of laughs and dialogue acts}
+\label{sec:app:da-svd}
+
 \begin{figure*}[h!]
+  \centering
+  \fontsize{6}{10}\selectfont
+  \sffamily
+  \includesvg[width=\linewidth]{img/da-svd-verbal}
+  \caption{Singular value decomposition of pentagonal representations of dialogue acts. For a selection of dialogue acts (in purple) we depict their pentagon representations.}
+    \label{fig:da-svd}
+\end{figure*}
+
+\pagebreak
+
+\begin{figure*}[h!]
+\subsection{Model performance in DAR task}
+\label{sec:app:bert}
+
   \centering

### 2021-09-19 reports/SemDial2021/semdial.tex
merge SemDial final version

@@
 
-%\aclfinalcopy % Uncomment this line for the final submission
+\aclfinalcopy % Uncomment this line for the final submission
 %\def\aclpaperid{***} %  Enter the acl Paper ID here
@@
 
-\author{First Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  \texttt{email@domain} \\\And
-  Second Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  \texttt{email@domain} \\}
+\author{Vladislav Maraev \\
+  University of Gothenburg \\
+  \texttt{vladislav.maraev@gu.se} \\\And
+  Bill Noble \\
+  University of Gothenburg \\
+  \texttt{bill.noble@gu.se} \\\AND
+  Chiara Mazzocconi  \\
+  Aix-Marseille University \\
+  \texttt{chiara.mazzocconi@live.it} \\\And
+  Christine Howes \\
+  University of Gothenburg \\
+  \texttt{christine.howes@gu.se} \\}
 
@@
 corpus.
-
+%
 Laughter relates to the discourse structure of dialogue
@@
 entity in the discourse.
-Laughter can precede, follow or overlap the laughable, with the time
-alignment between the laughter and laughable dependent on who produces
+Laughter can precede, follow or overlap the laughable, and the time alignment between them depends on who produces
 the laughable, the form of the laughter, and the pragmatic function performed \citep{tian2016we}. 
@@
 
-In this paper we investigate the disambiguation potential of laughter
-for interpreting the meaning of an utterance, with the central point
-being the dialogue act performed by it. To do so, we employ a
+Based on previous work and the corpus study presented in this paper, we argue that laughter is tightly related to the information structure of a dialogue.
+In this paper, we investigate the potential of laughter
+to disambiguate the meaning of an utterance, in terms of 
+the dialogue act it performs. To do so, we employ a
 Transformer-based model and look into laughter as a potentially useful
@@
 Laughter does not occur only in
-response to humour or in order to frame it. It is crucial in managing conversations in terms of dynamics (turn-taking and
+response to humour or in order to frame it.
+It is crucial in managing conversations in terms of dynamics (turn-taking and
 topic-change), at the lexical level (signalling problems of lexical retrieval or
@@
 discuss how laughter can answer or decline to answer a question, and
-\citet{mazzocconi2018laughter} discusses how even isolated laughter
-can be the object of clarification requests, signalling the need for
+\citet{mazzocconi2018laughter} explore  laughter
+as an object of clarification requests, signalling the need for
 interlocutors to clarify its meaning (e.g., in terms of what the
-``laughable'' is) in order to continue the conversation.
+``laughable'' is) to carry on with the conversation.
 
@@
 \emph{Downplayer} (make up 0.05\% of all utterances) and \emph{Apology} (0.04\%), comparing them with the most common dialogue
-act in SWDA---\emph{Statement-Non-Opinion} (33.27\%).  We take into consideration five
+act in SWDA -- \emph{Statement-Non-Opinion} (33.27\%).  We consider
 laughter-related dimensions of an utterance, and create 5-dimensional
@@
 \begin{itemize}
+\setlength\itemsep{0em}
 \item[$\uparrow$] current utterance;
@@
 \begin{lingex}%CH What are # ?
-\item\label{ex:apology-downplayer}\footnote{Overlapping material is marked wish hash signs.}
+\item\label{ex:apology-downplayer}\footnote{Overlapping material is marked with hash signs.}
   \small
@@
 dialogue act ($\uparrow$) when the laughter is aimed at modifying
-the current dialogue act with some degree of urgency in order to
+the current dialogue act with some degree of urgency to
 smooth or soften it (\emph{Action-directive}, \emph{Reject},
@@
 
-A peculiar case is than the one of \emph{Self-talk}, often followed by
+A peculiar case is the one of \emph{Self-talk}, often followed by
 laughter by the same speaker. In this case the laughter may be
@@
 observable in the lower part of the graph can therefore be explained
-by considering the relation between the two dialogues acts.  We
+by considering the relation between the two dialogue acts.  We
 observe cases in which an \textit{Apology} is accompanied by a
@@
 
-We now turn to the question of whether our qualitative observations of patters between laughs and dialogue acts can be used to improve a dialogue act recognition task.
+We now turn to the question of whether our qualitative observations of patterns between laughs and dialogue acts can be used to improve a dialogue act recognition task.
 
@@
 The model uses 100-dimensional word embeddings, which are initialised with pre-trained gloVe vectors \citep{penningtonGloveGlobalVectors2014}.
-
+%
 For the BERT utterance encoder, we use the BERT\textsubscript{BASE} model with hidden size of 768 and 12 transformer layers and self-attention heads \citep[][\S3.1]{devlinBERTPretrainingDeep2018}.
@@
 
-The next section will introduce the experiments that we have carried out and will discuss the results that we obtained from them.
+% The next section will introduce the experiments that we have carried out and will discuss the results that we obtained from them.
 
@@
 
-First of all, we can see that  \texttt{BERT}  outperforms \texttt{CNN} in all cases.
-From observing the effect of laughters, we can see differences in performance depending on the dialogue act, regardless of how often laughter occurs in the current or adjacent utterances (see Figure~\ref{fig:by-da} in Appendix~\ref{sec:suppl}).
-The strongest evidence for laughter as a helpful feature was found in SWDA for the \texttt{BERT} utterance encoder, where macro-F1 score increases by 7.89 percentage points.
+\texttt{BERT}  outperforms the \texttt{CNN} on AMI-DA.
+On SWDA, the two encoders are more comparable, though \texttt{BERT} has a slight edge in accuracy, suggesting that it relies more heavily on defaulting to common dialogue act tags.
+On SWDA, we see small improvements in accuracy and macro-F1 for models that included laughter. 
+For AMI-DA, the effect of laughter is small or even negative -- the impact of laughter on performance becomes more clear in the disaggregated performance over different dialogue acts. 
+Indeed, laughter improves the accuracy of the model even on some dialogue acts in which laughter occurs rarely in the current and adjacent utterances (see Figure~\ref{fig:by-da} in Appendix~\ref{sec:suppl}).
 
@@
 
-  \begin{figure}
+  \begin{figure}[h!]
   \centering
+  \vspace*{-0.3cm}
     \fontsize{6}{10}\selectfont
 %      \includesvg[width=\linewidth]{img/da-svd-verbal}
-   \includegraphics[width=\linewidth]{img/swda-cm.pdf}
+   \includegraphics[width=.9\linewidth]{img/swda-cm.pdf}
   \caption{Confusion matrices for \texttt{BERT-NL} (top) vs \texttt{BERT-L} (bottom); SWDA corpus. Solid lines show classification improvement  of rhetorical questions.}
+%  \vspace*{-0.7cm}
     \label{fig:swda-cm}
@@
 we randomly assigned a speaker token to each utterance to maintain the
-format of the other dialouge corpora.
+format of the other dialogue corpora.
 
@@
 For 314 (76\%) of such dialogue acts the model has predicted the
-\emph{Acknowledge (Backchannel)} class and for 46 (11\%) ---
+\emph{Acknowledge (Backchannel)} class and for 46 (11\%) --
 continuations of the previous DA by the same speaker. The rest were
@@
 instance, to show to the interlocutor acknowledgement of their
-contribution, implying the appreciation of an incongruity, and
-inviting continuation (functioning simultaneously as a continuer and
+contribution, implying the appreciation of an incongruity and
+inviting continuation, functioning simultaneously as a continuer and
 assessment feedback
-\citep{schegloff1982discourse}), as in example~\ref{ex:fish}.
+\citep{schegloff1982discourse}, as in example~\ref{ex:fish}.
 
@@
 non-verbal social signals) in any framework aimed to model meaning in
-interaction \citep{ginzburg2020laughter,Maraev.Mazzocconi.Howes.Ginzburg_ISCA_2018}. % TODO: and, in final version add LACATODA
+interaction \citep{ginzburg2020laughter,maraev2021lacatoda}. % TODO: and, in final version add LACATODA
 
@@
 Our results provide further evidence
-(e.g. \citet{torres1997modeling,gazelaughter}) for the fact that
+(e.g. \citet{torres1997modeling,mazzocconi2021looking}) for the fact that
 non-verbal behaviours are tightly related to the dialogue information
@@
 
-There is abundant room for further progress in determining how other speech-related information, such as prosody and disfluencies, can be incorporated into a DAR model.
-\citet{stolckeDialogueActModeling2000} showed that dialogue acts can have specific prosodic manifestations that can be used to improve DAR.
-Furthermore, in relation to laughter, its form (duration, arousal, overlap with speech) can be informative about its function and position w.r.t.\ the laughable \citep{tian2016we,mazzocconi2019phd}.
+% There is abundant room for further progress in determining how other speech-related information, such as prosody and disfluencies, can be incorporated into a DAR model.
+% \citet{stolckeDialogueActModeling2000} showed that dialogue acts can have specific prosodic manifestations that can be used to improve DAR.
+% Furthermore, in relation to laughter, its form (duration, arousal, overlap with speech) can be informative about its function and position w.r.t.\ the laughable \citep{mazzocconi2019phd}.
+% Incorporating such information is crucial if models pre-trained on large-scale text corpora are to be adapted for use in dialogue applications.
+
+There is abundant room for further study of how laughter can help to disambiguate communicative intent. 
+\citet{stolckeDialogueActModeling2000} showed that the specific prosodic manifestations of an utterance can be used to improve DAR.
+With respect to laughter, the form (duration, arousal, overlap with speech) can be informative about its function and position w.r.t.\ the laughable \citep{mazzocconi2019phd}.
 Incorporating such information is crucial if models pre-trained on large-scale text corpora are to be adapted for use in dialogue applications.
@@
 
-% \section*{Acknowledgments}
+\section*{Acknowledgments}
+Maraev, Noble and Howes were supported by  the Swedish Research Council (VR) grant  2014-39 for the establishment of the Centre for Linguistic Theory and Studies in Probability (CLASP).
+Mazzocconi was supported by the “Investissements d’Avenir” French government program managed by the French National Research Agency (reference: ANR-16-CONV-0002) and from the Excellence Initiative of Aix-Marseille University—“A*MIDEX” through the Institute of Language, Communication and the Brain.
 
